### 2018-03-01 logs/18-02-05.tex
added files

\documentclass{article}
%easy margins
\usepackage[top=.2in, bottom=.4in, left=.8in, right=.8in]{geometry}
%http links in text
\usepackage{hyperref}
%pictures
\usepackage{graphicx}
%quotes
\usepackage{csquotes}
%landscape single pages
\usepackage{lscape}
%inline enumeration
\usepackage[inline]{enumitem}
\usepackage{setspace}
%****************************************************************
% changing font family
\renewcommand{\familydefault}{\sfdefault} %change font

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Adding title and authors
%\title{Cell classification by applying graphlets on HiC data}
%\author{Behnam Rasoolian  \and Liangliang Xu \and Zheng Zhang}
%\date{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Chaning font to a local font
%\setmainfont[
%SmallCapsFont = Fontin-SmallCaps.otf,
%BoldFont = Fontin-Bold.otf,
%ItalicFont = Fontin-Italic.otf
%]
%{Fontin.otf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%page title
%\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\doublespacing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%micromanage font size, the first argument is
%%size of the font, the second line distance
\fontsize{11pt}{26pt}\selectfont

%No page numbers.
\pagenumbering{gobble}
%no indentaion for new paragraphs.
\setlength{\parindent}{0pt}
Good Afternoon Dr. ....,

I am a masters student at Auburn University. I am supervised by Dr. 
Bhattacharya. I am conducting research on HiC datasets. Specifically, 
I am looking at local differences between normal and leukemic cells.
In my research I am using your datasets from the link below:

\url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_ genome_data/}

I am emailing you since I have a question that I haven't been 
able to resolve. I have been trying different normalization methods on HiC
contact matrices that I have extracted from datasets in link  above
; however, I haven't be able to reproduces contact files that
are here:

\url{http://sysbio.rnet.missouri.edu/bdm_download/chromosome3d/unzipped/Input/HiC/}

I have tried sequential component normalization (SCN)
and pearson correlation but the results are not as smooth
and clean as the ones in the link above. For the sake of reproductibility,
could you let me know how such normalizations were made on the original
HiC contact maps? I would greatly appreciate your response since it will
be a great help in my research.

{\small
\setstretch{0.5}
Regards,\\
Behnam Rasoolian\\
M.Sc. student in Computer science and Software Engineering\\
Auburn University\\
}

\texttt{test.py} \\
I have been playing with HiC data some more. I have tried setting the 
values on and around the main diagonal to 0 and calculate pearson 
correlation matrix. The results where somehow smooth but not quitely.
The constact map corresponding to contact\_All dataset set shows
a smoothness close to what I am seeking.
I have also tried to perform linear transformation on one HiC data 
to 
\end{document}

### 2018-03-01 logs/18-02-06.tex
added files

--- 2018-03-01 logs/18-02-05.tex
@@
 \usepackage[inline]{enumitem}
+%for double spaces
 \usepackage{setspace}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\doublespacing
+\setstretch{2}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%size of the font, the second line distance
-\fontsize{11pt}{26pt}\selectfont
+\fontsize{13pt}{13pt}\selectfont
 
@@
 \setlength{\parindent}{0pt}
-Good Afternoon Dr. ....,
+I have downloaded some files from 
+\url{https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE63525}
+there are lots of intrachromosomal data in there, corresponding
+to (I think!) 11 cell lines. During the correspondense that I had
+with University of Missouri (Mr. Oluwadare), he told me that I have
+to used the  GM12878 data set it there, which is much larger than
+the original \cite{lieberman2009comprehensive} dataset.
+There are two inter- and intra-chromosomal data sets there:
 
-I am a masters student at Auburn University. I am supervised by Dr. 
-Bhattacharya. I am conducting research on HiC datasets. Specifically, 
-I am looking at local differences between normal and leukemic cells.
-In my research I am using your datasets from the link below:
+\begin{enumerate}
+\fontsize{13pt}{3pt}\selectfont
+    \item GSE63525\_GM12878\_primary\_interchromosomal\_contact\_matrices.tar.gz\\
+          GSE63525\_GM12878\_primary\_intrachromosomal\_contact\_matrices.tar.gz
+      \item GSE63525\_GM12878\_combined\_interchromosomal\_contact\_matrices.tar.gz\\
+          GSE63525\_GM12878\_combined\_intrachromosomal\_contact\_matrices.tar.gz
+\end{enumerate}
+I wonder which ones I should use at the moment.
 
-\url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_ genome_data/}
-
-I am emailing you since I have a question that I haven't been 
-able to resolve. I have been trying different normalization methods on HiC
-contact matrices that I have extracted from datasets in link  above
-; however, I haven't be able to reproduces contact files that
-are here:
-
-\url{http://sysbio.rnet.missouri.edu/bdm_download/chromosome3d/unzipped/Input/HiC/}
-
-I have tried sequential component normalization (SCN)
-and pearson correlation but the results are not as smooth
-and clean as the ones in the link above. For the sake of reproductibility,
-could you let me know how such normalizations were made on the original
-HiC contact maps? I would greatly appreciate your response since it will
-be a great help in my research.
-
-{\small
-\setstretch{0.5}
-Regards,\\
-Behnam Rasoolian\\
-M.Sc. student in Computer science and Software Engineering\\
-Auburn University\\
-}
-
-\texttt{test.py} \\
-I have been playing with HiC data some more. I have tried setting the 
-values on and around the main diagonal to 0 and calculate pearson 
-correlation matrix. The results where somehow smooth but not quitely.
-The constact map corresponding to contact\_All dataset set shows
-a smoothness close to what I am seeking.
-I have also tried to perform linear transformation on one HiC data 
-to 
+\section*{Things to consider}
+\begin{enumerate}
+    \item effect of multiple pearson normalizations
+    \item revised SCN algorithm
+\end{enumerate}
 \end{document}

### 2018-03-01 logs/18-02-22.tex
added files

--- 2018-03-01 logs/18-02-05.tex
@@
 \usepackage[inline]{enumitem}
+%to change spacing
 \usepackage{setspace}
+
+\usepackage{float}
 %****************************************************************
@@
 %\doublespacing
+% ****setstrech should always go before fontsize
+%\setstretch{2.0}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%size of the font, the second line distance
-\fontsize{11pt}{26pt}\selectfont
+\fontsize{13pt}{26pt}\selectfont
 
@@
 \setlength{\parindent}{0pt}
-Good Afternoon Dr. ....,
+I have extracted graphlets for all 23 chromosomes from
+the contact maps, using ice normalization and I
+have thresholed it (test.py). I then separated individual
+orbitals from each cell category and put them together.
+That is, I have put orbital 0 from MIT, ALL, RL and CALL4
+together and put them in a file. Then I did the same for orbital
+1 and put them in a separate file and so forth. I then ran MINE.jar
+for each file and captured pairwise MIC values for each orbital.
+By doing so, the result would have a dataset of the follwoing shape:
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+        \hline
+        Cell 1 & Cell 2 & Orbital & MIC value\\ \hline
+    \end{tabular}
+\end{table}
+My plan was to find a signinficance of pair-wice MIC values 
+fo example, using a
+null hypothesis of $H_0: MIC_{MIT-ALL} = 0$. This would mean
+That MIT-ALL are totally independent of each other. However,
+What we are trying to prove is that they are not the same,
+which is different. Actually I have to test this null hypothesis:\\
+$H_0: MIC_{MIT-ALL} = 1$\\
+which if cannot be rejected, means that the two sets of MIT and ALL
+are similar to each other.
 
-I am a masters student at Auburn University. I am supervised by Dr. 
-Bhattacharya. I am conducting research on HiC datasets. Specifically, 
-I am looking at local differences between normal and leukemic cells.
-In my research I am using your datasets from the link below:
+In order to validate my method, I have to be able to compare the two
+normal cell data that I have, namely, MIT and the one from Rao et. al.
+I have to be able to get a high value between the two.
 
-\url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_ genome_data/}
-
-I am emailing you since I have a question that I haven't been 
-able to resolve. I have been trying different normalization methods on HiC
-contact matrices that I have extracted from datasets in link  above
-; however, I haven't be able to reproduces contact files that
-are here:
-
-\url{http://sysbio.rnet.missouri.edu/bdm_download/chromosome3d/unzipped/Input/HiC/}
-
-I have tried sequential component normalization (SCN)
-and pearson correlation but the results are not as smooth
-and clean as the ones in the link above. For the sake of reproductibility,
-could you let me know how such normalizations were made on the original
-HiC contact maps? I would greatly appreciate your response since it will
-be a great help in my research.
-
-{\small
-\setstretch{0.5}
-Regards,\\
-Behnam Rasoolian\\
-M.Sc. student in Computer science and Software Engineering\\
-Auburn University\\
-}
-
-\texttt{test.py} \\
-I have been playing with HiC data some more. I have tried setting the 
-values on and around the main diagonal to 0 and calculate pearson 
-correlation matrix. The results where somehow smooth but not quitely.
-The constact map corresponding to contact\_All dataset set shows
-a smoothness close to what I am seeking.
-I have also tried to perform linear transformation on one HiC data 
-to 
 \end{document}

### 2018-03-01 data.old/graphlets/groupGraphlets.py

@@ -1,0 +1,36 @@
+import numpy as np
+
+chromosome = 14
+cells = {"mit":[], "all":[], "rl":[], "call4":[]}
+files = []
+
+for cell in cells.keys():
+    fileName = "chr%02d_chr%02d_%s.graphlet"%(chromosome, chromosome, cell)
+    print fileName
+    file = open(fileName, 'r')
+    file.readline()
+    for line in file:
+        numbers = [ int(x) for x in line.split(';')]
+        #print len(numbers)
+        cells[cell].append(numbers)
+
+for cell in cells.keys():
+    cells[cell] = np.array(cells[cell])
+    print cells[cell]
+
+for i in range(0, 73):
+    file = open("orbital%02d.csv"%i, 'w')
+    file.write("mit, all, rl, call4\n")
+    N = 100000
+    for cell in cells.keys():
+       N = np.min([cells[cell].shape[0], N]) 
+    for j in range(N):
+        toWrite = "%d, %d, %d, %d\n"% (cells['mit'][j, i],
+                cells['all'][j, i],
+                cells['rl'][j, i],
+                cells['call4'][j, i]
+                )
+        if j == 10:
+            print toWrite
+        file.write(toWrite)
+    file.close()

### 2018-03-01 data.old/graphlets/putPairsTogether.py

@@ -1,0 +1,9 @@
+fileToWrite = open("allTogether.csv", 'w')
+for i in range(0, 73):
+    fileName = "orbital%02d.csv,allpairs,cv=0.1,B=n^0.6,Results.csv"%i
+    fileToRead = open(fileName, 'r')
+    fileToRead.readline()
+    for line in fileToRead:
+        fileToWrite.write("%d, %s"%(i, line))
+    fileToRead.close()
+fileToWrite.close()

### 2018-03-01 data.old/graphlets/run.sh

@@ -1,0 +1,8 @@
+clear
+
+if [ "$1" = "extractAllData.py" ]
+then
+    python $1
+else
+    python $1
+fi

### 2018-03-01 utility.py

@@ -1,0 +1,290 @@
+import csv
+import numpy as np
+import os, errno
+import cv2
+import sys
+from scipy.stats.stats import pearsonr   
+import matplotlib.pyplot as plt
+#TODO: not used
+def eigendecompose(a):
+    w, v = np.linalg.eig(a)
+    max = np.abs(np.max(w))
+    min = np.abs(np.min(w))
+    t = np.max([min, max])
+    w = w / t
+    v = v * t * t
+    print "result of multiplying eigenvalues and eigenvectors:"
+    print v.dot(np.diag(w)).dot(np.linalg.inv(v))*t
+    return w, v/t/t
+
+def writeMatToFile(mat, fileName, delimiter=','):
+    """
+    Function:
+    ---------
+    Takes a matrix and writes it as a text matrix
+    where each row is separated by a new line
+    and each two cells in a row are separated
+    by the specified delimiter.
+
+    Parameters:
+    -----------
+    mat : ndarray(m, n) 
+        The input matrix
+
+    fileName: string
+        name of the file to write to
+
+    delimiter: string
+        the delimiter that separates the cells in
+        each row.
+    """
+    file = open(fileName, 'w')
+    n, m = mat.shape
+    for i in range(n):
+        for j in range(m):
+            file.write("%f"%mat[i, j])
+            if j < m-1:
+                file.write(delimiter)
+        file.write("\n")
+    file.close()
+
+def pyrProcess(original):
+    original = cv2.pyrDown(original)
+    original = cv2.pyrUp(original)
+    return scale(original)
+
+def scale(m):
+    min = np.min(m) + 1e-5
+    max = np.max(m)
+    n = (1. * m - min) / (max - min) 
+    return n
+
+#used to be simple read
+def readMat(fileName, delimiter="\t", ignoreHeader=False):
+    print "file directory:", fileName
+    if not os.path.isfile(fileName):
+        print "File %s does not exist"%fileName
+        sys.exit(2)
+    file = open(fileName, 'r')
+    if ignoreHeader:
+        file.readline()
+    x = []
+    for line in file:
+        strings = line.split(delimiter)
+        lineNums = []
+        for i in range(0, len(strings)-1):
+            num = strings[i]
+            lineNums.append(float(num))
+        x.append(lineNums)
+    observed = np.array(x).astype("float")
+    return observed
+
+def readYaml(filename, res, delimiter="\t"):
[…]

### 2018-03-01 rscript.r
Added Orca R file

@@ -1,0 +1,27 @@
+library("orca")
+chr <- 2
+
+mit_file_name <- sprintf("data/chr%02d_chr%02d_mit.edges", chr, chr)
+all_file_name <- sprintf("data/chr%02d_chr%02d_all.edges", chr, chr)
+rl_file_name <- sprintf("data/chr%02d_chr%02d_rl.edges", chr, chr)
+call4_file_name <- sprintf("data/chr%02d_chr%02d_call4.edges", chr, chr)
+
+mit_file <- read.csv(mit_file_name)
+all_file <- read.csv(all_file_name)
+rl_file <- read.csv(rl_file_name)
+call4_file <- read.csv(call4_file_name)
+
+mit_graphlets <- count4(mit_file)
+all_graphlets <- count4(all_file)
+rl_graphlets <- count4(rl_file)
+call4_graphlets <- count4(call4_file)
+
+mit_graphlet_file = sprintf("data/chr%02d_chr%02d_mit.graphlets", chr, chr)
+all_graphlet_file = sprintf("data/chr%02d_chr%02d_all.graphlets", chr, chr)
+rl_graphlet_file = sprintf("data/chr%02d_chr%02d_rl.graphlets", chr, chr)
+call4_graphlet_file = sprintf("data/chr%02d_chr%02d_call4.graphlets", chr, chr)
+
+write.csv2(mit_graphlets, file = mit_graphlet_file ,row.names=FALSE)
+write.csv2(all_graphlets, file = all_graphlet_file ,row.names=FALSE)
+write.csv2(rl_graphlets, file = rl_graphlet_file ,row.names=FALSE)
+write.csv2(call4_graphlets, file = call4_graphlet_file ,row.names=FALSE)

### 2018-03-01 utility.py

@@ -223,7 +223,7 @@ def convertBinaryMatToOrcaReadable(image, outputFileName=None):
     for index in range(len(positives[0])):
          i = positives[0][index]
          j = positives[1][index]
-         if i <= j:
+         if i < j:
              if outputFileName != None:
                  file.write("%d, %d\n"%(i+1, j+1))
              else:

### 2018-03-01 rscript.r
run R in python

@@ -21,7 +21,7 @@ all_graphlet_file = sprintf("data/chr%02d_chr%02d_all.graphlets", chr, chr)
 rl_graphlet_file = sprintf("data/chr%02d_chr%02d_rl.graphlets", chr, chr)
 call4_graphlet_file = sprintf("data/chr%02d_chr%02d_call4.graphlets", chr, chr)
 
-write.csv2(mit_graphlets, file = mit_graphlet_file ,row.names=FALSE)
-write.csv2(all_graphlets, file = all_graphlet_file ,row.names=FALSE)
-write.csv2(rl_graphlets, file = rl_graphlet_file ,row.names=FALSE)
-write.csv2(call4_graphlets, file = call4_graphlet_file ,row.names=FALSE)
+write.table(mit_graphlets, file = mit_graphlet_file ,row.names=FALSE, col.names=FALSE)
+write.table(all_graphlets, file = all_graphlet_file ,row.names=FALSE, col.names=FALSE)
+write.table(rl_graphlets, file = rl_graphlet_file ,row.names=FALSE, col.names=FALSE)
+write.table(call4_graphlets, file = call4_graphlet_file ,row.names=FALSE, col.names=FALSE)

### 2018-03-01 utility.py

@@ -72,7 +72,7 @@ def readMat(fileName, delimiter="\t", ignoreHeader=False):
     for line in file:
         strings = line.split(delimiter)
         lineNums = []
-        for i in range(0, len(strings)-1):
+        for i in range(0, len(strings)):
             num = strings[i]
             lineNums.append(float(num))
         x.append(lineNums)

### 2018-03-01 utility.py
Added graphlet distance functions

@@ -37,6 +37,9 @@ def writeMatToFile(mat, fileName, delimiter=','):
     delimiter: string
         the delimiter that separates the cells in
         each row.
+
+    Output:
+        Nothing
     """
     file = open(fileName, 'w')
     n, m = mat.shape
@@ -288,3 +291,100 @@ def approveToContinue(message):
         print("Exitting."),
         sys.exit(2)
     return answer
+
+def graphlet_distance(g1, g2):
+    """
+    ----------------------------------------------
+    Function:                                    #
+    ----------------------------------------------
+    Receives two matrices of graphlets of size 
+    N * O.  Each column correspons to the 
+    orbital with the corresponsing index.
+
+    ----------------------------------------------
+    Inputs:                                      #
+    ----------------------------------------------
+    - g1 and g2: two N * O matrix as explained above
+
+    ----------------------------------------------
+    Returns:                                     #
+    ----------------------------------------------
+    - out: an N * 1 matrix where each cell 
+    out[i, 0] is the graphlet signature
+    DISSIMILARITY between the ith rows of g1 and g2.
+    """
+    raw_weights = np.array([2, 4, 3, 9, 6, 10, 12, 4,
+                   24, 4, 10, 7, 6, 6, 28, 8,
+                   14, 8, 5, 12, 9, 11, 32, 15,
+                   12, 8, 22, 5, 9, 14, 11,
+                   16, 18, 15, 45, 7, 9, 20,
+                   13, 8, 20, 11, 15, 36, 15,
+                   7, 9, 13, 22, 36, 28, 22,
+                   10, 26, 36, 30, 8, 33, 15,
+                   22, 26, 15, 12, 28, 26, 12,
+                   26, 30, 56, 15, 28, 45, 50])
+    raw_numbers = np.array([2, 2, 1, 3, 2, 2, 3, 1,
+                   4, 1, 2, 1, 2, 2, 4, 2,
+                   2, 1, 1, 2, 1, 1, 4, 1,
+                   2, 1, 2, 1, 1, 2, 1,
+                   2, 2, 1, 5, 1, 1, 2, 
+                   1, 1, 2, 1, 1, 4, 1, 
+                   1, 1, 1, 2, 3, 2, 2,
+                   1, 2, 3, 2, 1, 3, 1,
+                   2, 2, 1, 1, 2, 2, 1,
+                   2, 2, 4, 1, 2, 3, 5])
+    #print(raw_weights.shape)
[…]

### 2018-03-02 Thresholding.py
Calculated all MIC values. chr19 and 22didn't work since the number of rows and columns were not the same

@@ -1,0 +1,262 @@
+
+# coding: utf-8
+
+# Importing some stuff
+
+# In[1]:
+
+
+import numpy as np
+import cv2
+from utility import *
+import matplotlib.pyplot as plt
+from iced import normalization
+from iced import filter
+import os
+
+
+# In[2]:
+
+
+def log(image):
+    out = image * 1.
+    out[np.where(out <= 0)] = 1
+    return np.log(out)
+
+def pearsonII(image):
+    out = pearson(image)
+    out[np.where(out <= 0)] = 0
+    return out
+
+def rel_error(m1 ,m2):
+    diff = np.abs(m1 - m2)
+    return diff / (np.abs(np.minimum(m1+100, m2+100)))
+
+def print_statistics(m1, text = "", print_results=True):
+    max = np.max(m1)
+    min = np.min(m1)
+    mean = m1.mean()
+    median = np.percentile(m1, 50)
+    std = m1.std()
+    if (print_results):
+        print("#-----------------------------------------------------------------------#")
+        print("Stats for %s: "% text)
+        print("max: %f | min: %f | median: %f | mean: %f | std: %f"%(max, min, median, mean, std))
+        print("#-----------------------------------------------------------------------#")
+    return max, min, mean, std
+
+def t_test(m1, m2):
+    diff = m1 - m2
+    n = diff.shape[0] * diff.shape[1]
+    std = np.sqrt(np.sum(diff * diff) / (n - 1))
+    t0 = diff.mean() * np.sqrt(n) / std
+    return t0
+
+def threshold_within_std(m1, k):
+    min, max, mean, std = print_statistics(m1, print_results=False)
+    return (m1 > mean - k * std) * (m1 < mean + k * std)
+
+
+# Initiating matrices
+
+# In[129]:
+
+chr1 = 22
+chr2 = chr1
+print "chromosome 1: %s, chromosome 2: %s"%(chr1, chr2)
+#print observed_mit_original.shape
+
+mit = readMat("../data/extracted_all_contact_MIT/chr_%02d_%02d_500kb.mat"%              (chr1, chr2), "\t")
[…]

### 2018-03-02 rscript.r

@@ -1,20 +1,26 @@
 library("orca")
-chr <- 2
+args <- commandArgs(trailingOnly = TRUE)
+chr <- as.integer(args[1])
 
 mit_file_name <- sprintf("data/chr%02d_chr%02d_mit.edges", chr, chr)
 all_file_name <- sprintf("data/chr%02d_chr%02d_all.edges", chr, chr)
 rl_file_name <- sprintf("data/chr%02d_chr%02d_rl.edges", chr, chr)
 call4_file_name <- sprintf("data/chr%02d_chr%02d_call4.edges", chr, chr)
 
+print(mit_file_name)
+print(all_file_name)
+print(rl_file_name)
+print(call4_file_name)
+
 mit_file <- read.csv(mit_file_name)
 all_file <- read.csv(all_file_name)
 rl_file <- read.csv(rl_file_name)
 call4_file <- read.csv(call4_file_name)
 
-mit_graphlets <- count4(mit_file)
-all_graphlets <- count4(all_file)
-rl_graphlets <- count4(rl_file)
-call4_graphlets <- count4(call4_file)
+mit_graphlets <- count5(mit_file)
+all_graphlets <- count5(all_file)
+rl_graphlets <- count5(rl_file)
+call4_graphlets <- count5(call4_file)
 
 mit_graphlet_file = sprintf("data/chr%02d_chr%02d_mit.graphlets", chr, chr)
 all_graphlet_file = sprintf("data/chr%02d_chr%02d_all.graphlets", chr, chr)

### 2018-03-02 utility.py

@@ -388,3 +388,42 @@ def graphlet_correlational_distance(g1, g2):
         for j in range(n2):
             out[i, j] = graphlet_distance(g1[i, :], g2[j, :])
     return out
+
+def pair_orbits(graphlets, chromosome, delimiter=','):
+    count = 0
+    for key in graphlets:
+        n, o = graphlets[key].shape
+        print("shape of graphlet for chromosome %d of cell %s: \
+                %d by %d"%(chromosome, key, n, o))
+        count += 1
+    print("number of matrices:", count)
+    for orbit in range(0, 73):
+        file_name = "data/chr%02d_orbit%02d.paired.csv"\
+                %(chromosome, orbit)
+        print(file_name)
+        file = open(file_name, 'w')
+        for key in graphlets:
+            file.write(key)
+            file.write(delimiter)
+        file.write("\n")
+        for i in range(n):
+            for key in graphlets:
+                file.write("%d"%graphlets[key][i, orbit])
+                file.write(delimiter)
+            file.write("\n")
+        file.close()
+
+def get_mic_from_file(file_name, delimiter=','):
+    print(file_name)
+    file = open(file_name)
+    line = [x for x in file.readline().split(delimiter)]
+    #print(line)
+    f1 = []
+    f2 = []
+    mic = []
+    for line in file:
+        content = [x for x in line.split(delimiter)]
+        f1.append(content[0])
+        f2.append(content[1])
+        mic.append(content[2])
+    return f1, f2, mic

### 2018-03-02 utility.py
added comments to the notebook

@@ -185,12 +185,14 @@ def scn(a, minDiff=1e-3, numIterations=1000):
         a[i, :] = a[:, i]
     return a
 
-def normalize(heatmap):
+def gaussian_normalize(heatmap):
     return (heatmap - np.mean(heatmap) ) / np.std(heatmap)
+
 def showImages(imageList, rows):
     cols = (len(imageList) + rows - 1) / rows
     print "Number of columnts:", cols
     count = 1
+    plt.subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=0.2, hspace=None)
     for image in imageList:
         ax = plt.subplot(rows, cols, count)
         count += 1
@@ -414,7 +416,7 @@ def pair_orbits(graphlets, chromosome, delimiter=','):
         file.close()
 
 def get_mic_from_file(file_name, delimiter=','):
-    print(file_name)
+    #print(file_name)
     file = open(file_name)
     line = [x for x in file.readline().split(delimiter)]
     #print(line)
@@ -425,5 +427,5 @@ def get_mic_from_file(file_name, delimiter=','):
         content = [x for x in line.split(delimiter)]
         f1.append(content[0])
         f2.append(content[1])
-        mic.append(content[2])
+        mic.append(float(content[2]))
     return f1, f2, mic

### 2018-03-06 utility.py
modified the notebooks

@@ -5,6 +5,11 @@ import cv2
 import sys
 from scipy.stats.stats import pearsonr   
 import matplotlib.pyplot as plt
+
+def rel_error(x, y):
+    """ returns relative error """
+    return np.max(np.abs(x - y) / (np.maximum(1e-8, np.abs(x) + np.abs(y))))
+
 #TODO: not used
 def eigendecompose(a):
     w, v = np.linalg.eig(a)
@@ -435,18 +440,12 @@ def get_mic_from_file(file_name, delimiter=','):
         mic.append(float(content[2]))
     return f1, f2, mic
 def log(image):
-    out = image * 1.
-    out[np.where(out <= 0)] = 1
-    return np.log(out)
+    return np.where(out > 0, np.log(out), 0)
 
 def pearsonII(image):
     out = pearson(image)
     out[np.where(out <= 0)] = 0
     return out
-
-def rel_error(m1 ,m2):
-    diff = np.abs(m1 - m2)
-    return diff / (np.abs(np.minimum(m1, m2))+1e-5)
 
 def print_statistics(m1, text = "", print_results=True):
     max = np.max(m1)
@@ -474,3 +473,49 @@ def t_test(m1, m2=None):
 def threshold_within_std(m1, k):
     min, max, mean, std = print_statistics(m1, print_results=False)
     return (m1 > mean - k * std) * (m1 < mean + k * std)
+
+def kl_div(m1, m2, num_bins=10, same_range = False, normalization=False):
+    ''''
+    performs KL-divergence between two matrices m1 and m2.
+    m1 and m2 should be vectors of size 1 * N.
+    -----------------------------------------------------
+    inputs:
+    ----------------------------------------------------
+    m1 , m2: matrices of size(1 * N)  
+    '''
+    n1 = m1.shape
+    n2 = m2.shape
+    N = np.min([n1, n2])
+    m1 = m1[:N]
+    m2 = m2[:N]
+    if (normalization):
+        print("normalizatoin is on")
+        m1 = gaussian_normalize(m1)
+        m2 = gaussian_normalize(m2)
+    if same_range:
+        max_val1 = np.max(m1)
+        max_val2 = np.max(m2)
+        max_val = np.max([max_val1, max_val2])
+        min_val1 = np.min(m1)
+        min_val2 = np.min(m2)
+        min_val = np.min([min_val1, min_val2])
[…]

### 2018-03-07 utility.py
modified the read and write functions. extracted overal contact maps.

@@ -68,7 +68,7 @@ def scale(m):
     return n
 
 #used to be simple read
-def readMat(fileName, delimiter="\t", ignoreHeader=False):
+def readMat(fileName, delimiter="\t", ignoreHeader=False, remove_blanks=False):
     #print "file directory:", fileName
     if not os.path.isfile(fileName):
         print "File %s does not exist"%fileName
@@ -85,9 +85,11 @@ def readMat(fileName, delimiter="\t", ignoreHeader=False):
             lineNums.append(float(num))
         x.append(lineNums)
     observed = np.array(x).astype("float")
+    if remove_blanks:
+        observed, a, b = removeBlankRowsAndColumns(observed)
     return observed
 
-def readYaml(filename, res, delimiter="\t"):
+def readYamlIntensities(filename, res, delimiter="\t", remove_blanks=False):
     file = open(filename, 'r')
     n = 0
     lines = []
@@ -106,10 +108,11 @@ def readYaml(filename, res, delimiter="\t"):
         #print line
         img[line[0], line[1]] = line[2]
         img[line[1], line[0]] = line[2]
-    img  = removeBlankRowsAndColumns(img)
+    if remove_blanks:
+        img, a, b  = removeBlankRowsAndColumns(img)
     return img
 
-def removeBlankRowsAndColumns(mat, thresh=5):
+def removeBlankRowsAndColumns(mat, thresh=1):
     n, m = mat.shape
     symmetric = True
     if n != m:
@@ -117,6 +120,7 @@ def removeBlankRowsAndColumns(mat, thresh=5):
         symmetric = False
     matrixWithRowAndColumnsRemoved = mat
     blankRows = []
+    blankCols = []
     for i in range(0, n):
         if np.sum(mat[i, :] > 0) <= thresh:
             blankRows.append(i)
@@ -127,7 +131,6 @@ def removeBlankRowsAndColumns(mat, thresh=5):
             matrixWithRowAndColumnsRemoved = np.delete(matrixWithRowAndColumnsRemoved, i, 0)
             matrixWithRowAndColumnsRemoved = np.delete(matrixWithRowAndColumnsRemoved, i, 1)
     else:
-        blankCols = []
         for i in range(0, m):
             if np.sum(mat[:, i] > 0) <= thresh:
                 blankCols.append(i)
@@ -138,7 +141,7 @@ def removeBlankRowsAndColumns(mat, thresh=5):
         for i in blankCols:
[…]

### 2018-03-07 utility.py
added new notebook overal analysis to check the whole network

@@ -3,8 +3,10 @@ import numpy as np
 import os, errno
 import cv2
 import sys
+import scipy.misc
 from scipy.stats.stats import pearsonr   
 import matplotlib.pyplot as plt
+from matplotlib import colors
 
 def rel_error(x, y):
     """ returns relative error """
@@ -21,6 +23,9 @@ def eigendecompose(a):
     print "result of multiplying eigenvalues and eigenvectors:"
     print v.dot(np.diag(w)).dot(np.linalg.inv(v))*t
     return w, v/t/t
+
+def writeMatToImage(mat, fileName):
+    scipy.misc.imsave(fileName, mat)
 
 def writeMatToFile(mat, fileName, delimiter=','):
     """
@@ -47,6 +52,7 @@ def writeMatToFile(mat, fileName, delimiter=','):
         Nothing
     """
     file = open(fileName, 'w')
+    print("writing to %s"%fileName)
     n, m = mat.shape
     for i in range(n):
         for j in range(m):
@@ -69,7 +75,7 @@ def scale(m):
 
 #used to be simple read
 def readMat(fileName, delimiter="\t", ignoreHeader=False, remove_blanks=False):
-    #print "file directory:", fileName
+    print "file directory:", fileName
     if not os.path.isfile(fileName):
         print "File %s does not exist"%fileName
         sys.exit(2)
@@ -196,15 +202,22 @@ def scn(a, minDiff=1e-3, numIterations=1000):
 def gaussian_normalize(heatmap):
     return (heatmap - np.mean(heatmap) ) / np.std(heatmap)
 
-def showImages(imageList, rows):
+def showImages(imageList, rows, color_bar=False):
     cols = (len(imageList) + rows - 1) / rows
     print "Number of columnts:", cols
-    count = 1
     plt.subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=0.2, hspace=None)
+    fig, axes = plt.subplots(nrows=rows, ncols=cols)
+    count = 0
     for image in imageList:
-        ax = plt.subplot(rows, cols, count)
+        if rows * cols == 1:
+            m = axes.imshow(image, cmap="RdBu_r", norm=colors.SymLogNorm(1))
+        elif rows == 1 or cols == 1:
+            m = axes[count].imshow(image, cmap="RdBu_r", norm=colors.SymLogNorm(1))
+        else:
[…]

### 2018-03-08 notebook.tex
add correlation as well as hic data

% Default to the notebook output style

% Inherit from the specified cell style.

\documentclass[11pt]{article}

    \usepackage[T1]{fontenc}
    % Nicer default font (+ math font) than Computer Modern for most use cases
    \usepackage{mathpazo}

    % Basic figure setup, for now with no caption control since it's done
    % automatically by Pandoc (which extracts ![](path) syntax from Markdown).
    \usepackage{graphicx}
    % We will generate all images so they have a width \maxwidth. This means
    % that they will get their normal width if they fit onto the page, but
    % are scaled down if they would overflow the margins.
    \makeatletter
    \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
    \else\Gin@nat@width\fi}
    \makeatother
    \let\Oldincludegraphics\includegraphics
    % Set max figure width to be 80% of text width, for now hardcoded.
    \renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=.8\maxwidth]{#1}}
    % Ensure that by default, figures have no caption (until we provide a
    % proper Figure object with a Caption API and a way to capture that
    % in the conversion process - todo).
    \usepackage{caption}
    \DeclareCaptionLabelFormat{nolabel}{}
    \captionsetup{labelformat=nolabel}

    \usepackage{adjustbox} % Used to constrain images to a maximum size 
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage[utf8x]{inputenc} % Allow utf-8 characters in the tex document
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range 
    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines

    % Colors for the hyperref package
    \definecolor{urlcolor}{rgb}{0,.145,.698}
    \definecolor{linkcolor}{rgb}{.71,0.21,0.01}
    \definecolor{citecolor}{rgb}{.12,.54,.11}

    % ANSI colors
    \definecolor{ansi-black}{HTML}{3E424D}
    \definecolor{ansi-black-intense}{HTML}{282C36}
    \definecolor{ansi-red}{HTML}{E75C58}
    \definecolor{ansi-red-intense}{HTML}{B22B31}
    \definecolor{ansi-green}{HTML}{00A250}
    \definecolor{ansi-green-intense}{HTML}{007427}
    \definecolor{ansi-yellow}{HTML}{DDB62B}
    \definecolor{ansi-yellow-intense}{HTML}{B27D12}
    \definecolor{ansi-blue}{HTML}{208FFB}
    \definecolor{ansi-blue-intense}{HTML}{0065CA}
    \definecolor{ansi-magenta}{HTML}{D160C4}
    \definecolor{ansi-magenta-intense}{HTML}{A03196}
    \definecolor{ansi-cyan}{HTML}{60C6C8}
    \definecolor{ansi-cyan-intense}{HTML}{258F8F}
    \definecolor{ansi-white}{HTML}{C5C1B4}
    \definecolor{ansi-white-intense}{HTML}{A1A6B2}

    % commands and environments needed by pandoc snippets
    % extracted from the output of `pandoc -s`
    \providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
    % Add ',fontsize=\small' for more characters per line
    \newenvironment{Shaded}{}{}
    \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
    \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
    \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
    \newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
    \newcommand{\RegionMarkerTok}[1]{{#1}}
    \newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\NormalTok}[1]{{#1}}

    % Additional commands for more recent versions of Pandoc
    \newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{{#1}}}
    \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{{#1}}}
    \newcommand{\ImportTok}[1]{{#1}}
    \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{{#1}}}}
    \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{{#1}}}
    \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{{#1}}}
    \newcommand{\BuiltInTok}[1]{{#1}}
    \newcommand{\ExtensionTok}[1]{{#1}}
    \newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{{#1}}}
    \newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{{#1}}}
    \newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{Thresholding\_local}

    % Pygments definitions

\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@dl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@ch\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@fm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@cpf\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sa\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

    % Exact colors from NB
    \definecolor{incolor}{rgb}{0.0, 0.0, 0.5}
    \definecolor{outcolor}{rgb}{0.545, 0.0, 0.0}

    % Prevent overflowing lines due to hard-to-break entities
    \sloppy 
    % Setup hyperref package
    \hypersetup{
      breaklinks=true,  % so long urls are correctly broken across lines
      colorlinks=true,
      urlcolor=urlcolor,
      linkcolor=linkcolor,
      citecolor=citecolor,
      }
    % Slightly bigger margins than the latex defaults

    \geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

    \begin{document}

    \maketitle

    \section{Local Thresholding}\label{local-thresholding}

In this notebook, I extract orbits for a signle chromosome in all 4 cell
lines, using a different method of thresholding. In order to do this, I
slide a kernel of size k through each pixel and check if it has a
particular property. If the property is satisified, then the pixel is
set to 1, otherwise it is set to 0. The two properties that I experiment
with are \emph{maximum thresholding} and \emph{normal thresholding}. 1.
\textbf{Maximum Thresholding}: in max thresholding, if the pixel is the
maximum of its neighbors with respect to the kernel, then it is set. 2.
\textbf{Normal Thresholding}: in normal thresholding, if the pixel is
larger that the average of the neighbors then it is set.

first I perform the most lates normalization method that I have found to
be most useful: a combination of gaussian normalization, SCN and pearson
correlation, in the same order mentioned. The normalized results are of
type \texttt{pearson(scn(gaussian(graph)))}.

Then I threshold the results by setting pearson values larger than 0 to
1 and the rest to 0. In order to extract graphlets, I used the
\emph{orca} package in R. the script \texttt{./rscript.r} read a binary
thresholded matrix representing an unweighted graph and outputs orbtis 0
through 72 for each node in the network. After thredholding the
matrices, I save them so that orca in R can read it and extract orbits.

By repeating the procedure explained above for all 23 chromosomes, we
will have graphlets for all contact maps.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}5}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
        \PY{k+kn}{import} \PY{n+nn}{cv2}
        \PY{k+kn}{from} \PY{n+nn}{utility} \PY{k+kn}{import} \PY{o}{*}
        \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n}{normalization}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n+nb}{filter}
        \PY{k+kn}{import} \PY{n+nn}{os}
        \PY{o}{\PYZpc{}}\PY{k}{load\PYZus{}ext} autoreload
        \PY{o}{\PYZpc{}}\PY{k}{autoreload} 2
        \PY{o}{\PYZpc{}}\PY{k}{pylab} inline
        \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
The autoreload extension is already loaded. To reload it, use:
  \%reload\_ext autoreload
Populating the interactive namespace from numpy and matplotlib

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/watson/scripts/virt/local/lib/python2.7/site-packages/IPython/core/magics/pylab.py:161: UserWarning: pylab import has clobbered these variables: ['all', 'colors', 'log']
`\%matplotlib` prevents importing * from pylab and numpy
  "\textbackslash{}n`\%matplotlib` prevents importing * from pylab and numpy"

    \end{Verbatim}

    \subsection{Initiating matrices}\label{initiating-matrices}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}18}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{2}
         \PY{n}{chr2} \PY{o}{=} \PY{n}{chr1}
         \PY{k}{print} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{chromosome 1: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{, chromosome 2: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
         \PY{c+c1}{\PYZsh{}print observed\PYZus{}mit\PYZus{}original.shape}

         \PY{n}{mit} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}MIT/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PYZbs{}
                       \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
         \PY{n}{call4} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}call4/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PYZbs{}
                         \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
         \PY{n}{rl} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}RL/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

         \PY{n+nb}{all} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}ALL/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

         \PY{c+c1}{\PYZsh{}There are some blank rows and columns in the matrix. let\PYZsq{}s remove them.}
         \PY{n}{blankRows0}\PY{p}{,} \PY{n}{blankCols0} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
         \PY{n}{blankRows1}\PY{p}{,} \PY{n}{blankCols1} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}
         \PY{n}{blankRows2}\PY{p}{,} \PY{n}{blankCols2} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
         \PY{n}{blankRows3}\PY{p}{,} \PY{n}{blankCols3} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
         \PY{n}{blankRows} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
         \PY{n}{blankCols} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows0}\PY{p}{)}
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows1}\PY{p}{)}
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows2}\PY{p}{)}
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows3}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols0}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols1}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols2}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols3}\PY{p}{)}
         \PY{n}{mit} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
         \PY{n+nb}{all} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
         \PY{n}{rl} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
         \PY{n}{call4} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
chromosome 1: 2, chromosome 2: 2
file directory: ../data/extracted\_all\_contact\_MIT/chr\_02\_02\_500kb.mat
file directory: ../data/extracted\_all\_contact\_call4/chr\_02\_02\_500kb.mat
file directory: ../data/extracted\_all\_contact\_RL/chr\_02\_02\_500kb.mat
file directory: ../data/extracted\_all\_contact\_ALL/chr\_02\_02\_500kb.mat
size of old matrix: (486, 486)
size of new matrix: (480, 480)
size of old matrix: (486, 486)
size of new matrix: (480, 480)
size of old matrix: (486, 486)
size of new matrix: (480, 480)
size of old matrix: (486, 486)
size of new matrix: (480, 480)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}19}]:} \PY{n}{n0}\PY{p}{,} \PY{n}{m0} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
         \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
         \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
         \PY{n}{n3}\PY{p}{,} \PY{n}{m3} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}

         \PY{n}{n} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{n0}\PY{p}{,} \PY{n}{m0}\PY{p}{,} \PY{n}{n1}\PY{p}{,} \PY{n}{m1}\PY{p}{,} \PY{n}{n2}\PY{p}{,} \PY{n}{m2}\PY{p}{,} \PY{n}{n3}\PY{p}{,} \PY{n}{m3}\PY{p}{]}\PY{p}{)}

         \PY{n}{images} \PY{o}{=} \PY{p}{[}\PY{n}{mit}\PY{p}{,} \PY{n+nb}{all}\PY{p}{,} \PY{n}{rl}\PY{p}{,} \PY{n}{call4}\PY{p}{]}
         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Number of columnts: 2

    \end{Verbatim}

    \begin{verbatim}
<matplotlib.figure.Figure at 0x7f65c3721610>
    \end{verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_4_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}20}]:} \PY{n}{mit} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{mit}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)} 
         \PY{n+nb}{all} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{n}{rl} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{rl}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)} 
         \PY{n}{call4} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{call4}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)} 
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}21}]:} \PY{n}{images} \PY{o}{=} \PY{p}{[} 
                 \PY{n}{mit}\PY{p}{,} \PY{n+nb}{all}\PY{p}{,} \PY{n}{rl}\PY{p}{,} \PY{n}{call4}
                 \PY{p}{,} \PY{p}{(}\PY{n}{mit} \PY{o}{==} \PY{n+nb}{all}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{mit} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n+nb}{all} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{p}{,} \PY{n+nb}{all} \PY{o}{!=} \PY{n}{mit}
                 \PY{p}{,} \PY{p}{(}\PY{n}{mit} \PY{o}{==} \PY{n}{rl}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{mit} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{rl} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{p}{,} \PY{n}{rl} \PY{o}{!=} \PY{n}{mit}
                 \PY{p}{,} \PY{p}{(}\PY{n}{mit} \PY{o}{==} \PY{n}{call4}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{mit} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{call4} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{p}{,} \PY{n}{call4} \PY{o}{!=} \PY{n}{mit}
                  \PY{p}{]} 
         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{5}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Number of columnts: 2

    \end{Verbatim}

    \begin{verbatim}
<matplotlib.figure.Figure at 0x7f65c3718390>
    \end{verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_6_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}22}]:} \PY{n+nb}{min}\PY{p}{,} \PY{n+nb}{max}\PY{p}{,} \PY{n}{mean\PYZus{}mit}\PY{p}{,} \PY{n}{std\PYZus{}mit} \PY{o}{=} \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{mit}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
         \PY{n+nb}{min}\PY{p}{,} \PY{n+nb}{max}\PY{p}{,} \PY{n}{mean\PYZus{}rl}\PY{p}{,} \PY{n}{std\PYZus{}rl} \PY{o}{=} \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{rl}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{rl}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
         \PY{n+nb}{min}\PY{p}{,} \PY{n+nb}{max}\PY{p}{,} \PY{n}{mean\PYZus{}call4}\PY{p}{,} \PY{n}{std\PYZus{}call4} \PY{o}{=} \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{call4}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{call4}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
         \PY{n+nb}{min}\PY{p}{,} \PY{n+nb}{max}\PY{p}{,} \PY{n}{mean\PYZus{}all}\PY{p}{,} \PY{n}{std\PYZus{}all} \PY{o}{=} \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n+nb}{all}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{all}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
\#-----------------------------------------------------------------------\#
Stats for mit: 
max: 1.000000 | min: 0.000000 | median: 0.000000 | mean: 0.188247 | std: 0.390909
\#-----------------------------------------------------------------------\#
\#-----------------------------------------------------------------------\#
Stats for rl: 
max: 1.000000 | min: 0.000000 | median: 0.000000 | mean: 0.153229 | std: 0.360208
\#-----------------------------------------------------------------------\#
\#-----------------------------------------------------------------------\#
Stats for call4: 
max: 1.000000 | min: 0.000000 | median: 0.000000 | mean: 0.158854 | std: 0.365540
\#-----------------------------------------------------------------------\#
\#-----------------------------------------------------------------------\#
Stats for all: 
max: 1.000000 | min: 0.000000 | median: 0.000000 | mean: 0.159688 | std: 0.366316
\#-----------------------------------------------------------------------\#

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}23}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
         \PY{n}{images} \PY{o}{=} \PY{p}{[}
                 \PY{p}{(}\PY{n}{mit}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1e\PYZhy{}2}
                 \PY{p}{,} \PY{p}{(}\PY{n+nb}{all}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1e\PYZhy{}2}
                 \PY{p}{,} \PY{p}{(}\PY{n}{rl}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1e\PYZhy{}2}
                 \PY{p}{,} \PY{p}{(}\PY{n}{call4}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1e\PYZhy{}2}
                 \PY{p}{]}
         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Number of columnts: 4

    \end{Verbatim}

    \begin{verbatim}
<matplotlib.figure.Figure at 0x7f65c3752790>
    \end{verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_8_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}24}]:} \PY{n}{images} \PY{o}{=} \PY{p}{[}
                 \PY{n}{log}\PY{p}{(}\PY{n}{call4}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}
                 \PY{p}{,} \PY{n}{log}\PY{p}{(}\PY{n}{mit}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}
                 \PY{p}{,} \PY{n}{log}\PY{p}{(}\PY{n}{rl}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}
                 \PY{p}{,} \PY{n}{log}\PY{p}{(}\PY{n+nb}{all}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}
                 \PY{p}{]}
         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Number of columnts: 4

    \end{Verbatim}

    \begin{verbatim}
<matplotlib.figure.Figure at 0x7f65c37400d0>
    \end{verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_9_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}10}]:} \PY{n}{convertBinaryMatToOrcaReadable}\PY{p}{(}\PY{n}{call4} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}call4.edges}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{)}
         \PY{n}{convertBinaryMatToOrcaReadable}\PY{p}{(}\PY{n}{mit} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}mit.edges}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{)}
         \PY{n}{convertBinaryMatToOrcaReadable}\PY{p}{(}\PY{n}{rl} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}rl.edges}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{)}
         \PY{n}{convertBinaryMatToOrcaReadable}\PY{p}{(}\PY{n+nb}{all} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}all.edges}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{)}
\end{Verbatim}

    % Add a bibliography block to the postdoc

    \end{document}

### 2018-03-08 thresholding_local.py

@@ -1,0 +1,110 @@
+
+# coding: utf-8
+
+# # Local Thresholding
+# In this notebook, I extract orbits for a signle chromosome in all 4 cell lines, using a
+# different method of thresholding.
+# In order to do this, I slide a kernel of size k 
+# through each pixel and check if it has a 
+# particular property. If the property is satisified, then the pixel is set to 1,
+# otherwise it is set to 0. 
+# The two properties that I experiment with are *maximum thresholding* and *normal 
+# thresholding*.
+# 1. **Maximum Thresholding**: in max thresholding, if the pixel is the maximum of its 
+# neighbors with respect to the kernel, then it is set.
+# 2. **Normal Thresholding**: in normal thresholding, if the pixel is larger that the 
+# average of the neighbors then it is set.
+# 
+# first I perform the most lates normalization method that I have found to be most useful: a combination of gaussian normalization, SCN and pearson correlation, in the same order mentioned. The normalized results are of type ```pearson(scn(gaussian(graph)))```.
+# 
+# Then I threshold the results by setting pearson values larger than 0 to 1 and the rest to 0.
+# In order to extract graphlets, I used the *orca* package in R. the script `./rscript.r`
+# read a binary thresholded matrix representing an unweighted graph and outputs orbtis 0 
+# through 72 for each node in the network.
+# After thredholding the matrices, I save them so that orca in R can read it and extract orbits.
+# 
+# By repeating the procedure explained above for all 23 chromosomes, we will have graphlets
+# for all contact maps.
+
+# In[5]:
+
+
+import numpy as np
+import cv2
+from utility import *
+import matplotlib.pyplot as plt
+from iced import normalization
+from iced import filter
+import os
+
+
+# ## Initiating matrices
+
+# In[18]:
+
+def main():
+    chr1 = 2
+    for chr1 in range(1, 23):
+        chr2 = chr1
+        print "chromosome 1: %s, chromosome 2: %s"%(chr1, chr2)
+        #print observed_mit_original.shape
+
+        mit = readMat("../data/extracted_all_contact_MIT/chr_%02d_%02d_500kb.mat"%              (chr1, chr2), "\t")
[…]

### 2018-03-08 utility.py

@@ -7,6 +7,7 @@ import scipy.misc
 from scipy.stats.stats import pearsonr   
 import matplotlib.pyplot as plt
 from matplotlib import colors
+from sets import Set
 
 def rel_error(x, y):
     """ returns relative error """
@@ -117,39 +118,61 @@ def readYamlIntensities(filename, res, delimiter="\t", remove_blanks=False):
     if remove_blanks:
         img, a, b  = removeBlankRowsAndColumns(img)
     return img
+def getBlankRowsAndColumns(mat, thresh=1):
+    n, m = mat.shape
+    blankRows = Set([])
+    blankCols = Set([])
+    for i in range(0, n):
+        if np.sum(mat[i, :] > 0) <= thresh:
+            blankRows.add(i)
+    for i in range(0, m):
+        if np.sum(mat[:, i] > 0) <= thresh:
+            blankCols.add(i)
+    return blankRows, blankCols
+
+def removeRowsAndColumns(mat, blankRows, blankCols):
+    print "size of old matrix:", mat.shape
+    blankRows = sorted(blankRows, reverse=True)
+    blankCols = sorted(blankCols, reverse=True)
+    matrixWithRowAndColumnsRemoved = mat
+    for i in blankRows:
+        matrixWithRowAndColumnsRemoved = np.delete(matrixWithRowAndColumnsRemoved, i, 0)
+    for i in blankCols:
+        matrixWithRowAndColumnsRemoved = np.delete(matrixWithRowAndColumnsRemoved, i, 1)
+    print "size of new matrix:", matrixWithRowAndColumnsRemoved.shape
+    return matrixWithRowAndColumnsRemoved
 
 def removeBlankRowsAndColumns(mat, thresh=1):
+    print "size of old matrix:", mat.shape
     n, m = mat.shape
+    blankRows, blankCols = getBlankRowsAndColumns(mat, thresh=thresh)
     symmetric = True
     if n != m:
         print("Matrix is not symmetric!")
         symmetric = False
-    matrixWithRowAndColumnsRemoved = mat
-    blankRows = []
-    blankCols = []
-    for i in range(0, n):
-        if np.sum(mat[i, :] > 0) <= thresh:
-            blankRows.append(i)
-    blankRows = sorted(blankRows, reverse=True)
-    print "blonk rows:", blankRows
     if symmetric:
-        for i in blankRows:
[…]

### 2018-03-08 notebook.tex
added papers

@@
     % Document parameters
-    \title{Thresholding\_local}
+    \title{02\_graphlet\_correlation\_Analysis}
 
@@
 
-    \section{Local Thresholding}\label{local-thresholding}
+    \section{Graphlet Correlation
+Analysis}\label{graphlet-correlation-analysis}
 
-In this notebook, I extract orbits for a signle chromosome in all 4 cell
-lines, using a different method of thresholding. In order to do this, I
-slide a kernel of size k through each pixel and check if it has a
-particular property. If the property is satisified, then the pixel is
-set to 1, otherwise it is set to 0. The two properties that I experiment
-with are \emph{maximum thresholding} and \emph{normal thresholding}. 1.
-\textbf{Maximum Thresholding}: in max thresholding, if the pixel is the
-maximum of its neighbors with respect to the kernel, then it is set. 2.
-\textbf{Normal Thresholding}: in normal thresholding, if the pixel is
-larger that the average of the neighbors then it is set.
+Remember, in notebook \emph{Thresholding}, I thresholded contact maps
+and saved so that orca can read them.
 
-first I perform the most lates normalization method that I have found to
-be most useful: a combination of gaussian normalization, SCN and pearson
-correlation, in the same order mentioned. The normalized results are of
-type \texttt{pearson(scn(gaussian(graph)))}.
+In this notebook, I perform two actions: 1. I apply \texttt{count5}
+procedure in orca to extract 73 orbits for each loci in each chromosome.
+After this stage, graphlets will be save with \texttt{.graphlets}
+extension in the \texttt{./data} folder.
 
-Then I threshold the results by setting pearson values larger than 0 to
-1 and the rest to 0. In order to extract graphlets, I used the
-\emph{orca} package in R. the script \texttt{./rscript.r} read a binary
-thresholded matrix representing an unweighted graph and outputs orbtis 0
-through 72 for each node in the network. After thredholding the
-matrices, I save them so that orca in R can read it and extract orbits.
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  I then read the graphlets and find both loci-wise distance and
+  graphlet-wise correlations between the four cell lines.
+\end{enumerate}
 
-By repeating the procedure explained above for all 23 chromosomes, we
-will have graphlets for all contact maps.
+By repeating steps 1 and 2 for all 23 chromosomes, I will have pairwise
+MIC values for all orbits of all cell lines. I would eventually be able
+to have a data array of shape \texttt{A(23\ *\ 73)}, for each pair of
+cell lines where \texttt{A{[}i,\ j{]}} denotes the correlation between
+the jth orbit in the ith chromosome.
 
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}5}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
+{\color{incolor}In [{\color{incolor}102}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
           \PY{k+kn}{import} \PY{n+nn}{cv2}
@@
           \PY{o}{\PYZpc{}}\PY{k}{pylab} inline
-        \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
 \end{Verbatim}
@@
 
+    \section{1. Orbit Extraction:}\label{orbit-extraction}
+
+The following R-script reads edge files (\texttt{.edges}) corresponding
+to a chromosome under \texttt{data/} directory. It then writes the
+resulting orbits into \texttt{data/*.graphlets}.
+
     \begin{Verbatim}[commandchars=\\\{\}]
-/home/bzr0014/watson/scripts/virt/local/lib/python2.7/site-packages/IPython/core/magics/pylab.py:161: UserWarning: pylab import has clobbered these variables: ['all', 'colors', 'log']
-`\%matplotlib` prevents importing * from pylab and numpy
-  "\textbackslash{}n`\%matplotlib` prevents importing * from pylab and numpy"
+{\color{incolor}In [{\color{incolor}2}]:} \PY{c+c1}{\PYZsh{}for chr1 in range(1, 24):}
+        \PY{c+c1}{\PYZsh{}    os.system(\PYZsq{}Rscript rscript.r \PYZpc{}s\PYZsq{}\PYZpc{}chr1)}
+\end{Verbatim}
+
+    \section{2. Loci-wise Distance:}\label{loci-wise-distance}
+
+I can now read the orbitfiles and put them into a \(N \times O\) matrix
+where \(N\) denotes number of loci in the chromosome and \(O\) denotes
+the number or obitals extracted, which can be either 14 or 73 (depending
+on whether \texttt{count4()} or \texttt{count5()} are called in the
+R-script above.
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}152}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{2}
+          \PY{n}{graphlets\PYZus{}mit} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}mit.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+          \PY{n}{graphlets\PYZus{}all} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}all.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+          \PY{n}{graphlets\PYZus{}rl} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}rl.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+          \PY{n}{graphlets\PYZus{}call4} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}call4.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+          \PY{k}{print}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
+          \PY{k}{print}\PY{p}{(}\PY{n}{graphlets\PYZus{}all}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
+          \PY{k}{print}\PY{p}{(}\PY{n}{graphlets\PYZus{}rl}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
+          \PY{k}{print}\PY{p}{(}\PY{n}{graphlets\PYZus{}call4}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr02\_chr02\_mit.graphlets
+file directory: data/chr02\_chr02\_all.graphlets
+file directory: data/chr02\_chr02\_rl.graphlets
+file directory: data/chr02\_chr02\_call4.graphlets
+(478, 73)
+(478, 73)
+(478, 73)
+(478, 73)
 
@@
 
-    \subsection{Initiating matrices}\label{initiating-matrices}
+    Calculating Loci-wise correlations:
 
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}18}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{2}
-         \PY{n}{chr2} \PY{o}{=} \PY{n}{chr1}
-         \PY{k}{print} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{chromosome 1: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{, chromosome 2: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
-         \PY{c+c1}{\PYZsh{}print observed\PYZus{}mit\PYZus{}original.shape}
-
-         \PY{n}{mit} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}MIT/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PYZbs{}
-                       \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-         \PY{n}{call4} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}call4/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PYZbs{}
-                         \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-         \PY{n}{rl} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}RL/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-
-         \PY{n+nb}{all} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}ALL/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-
-         \PY{c+c1}{\PYZsh{}There are some blank rows and columns in the matrix. let\PYZsq{}s remove them.}
-         \PY{n}{blankRows0}\PY{p}{,} \PY{n}{blankCols0} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
-         \PY{n}{blankRows1}\PY{p}{,} \PY{n}{blankCols1} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}
-         \PY{n}{blankRows2}\PY{p}{,} \PY{n}{blankCols2} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
-         \PY{n}{blankRows3}\PY{p}{,} \PY{n}{blankCols3} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
-         \PY{n}{blankRows} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
-         \PY{n}{blankCols} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
-         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows0}\PY{p}{)}
-         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows1}\PY{p}{)}
-         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows2}\PY{p}{)}
-         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows3}\PY{p}{)}
-         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols0}\PY{p}{)}
-         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols1}\PY{p}{)}
-         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols2}\PY{p}{)}
-         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols3}\PY{p}{)}
-         \PY{n}{mit} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
-         \PY{n+nb}{all} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
-         \PY{n}{rl} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
-         \PY{n}{call4} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
+{\color{incolor}In [{\color{incolor}153}]:} \PY{n}{mit\PYZus{}all\PYZus{}corr} \PY{o}{=} \PYZbs{}
+              \PY{n}{graphlet\PYZus{}correlational\PYZus{}distance}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{p}{,} \PY{n}{graphlets\PYZus{}all}\PY{p}{)}
 \end{Verbatim}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-chromosome 1: 2, chromosome 2: 2
-file directory: ../data/extracted\_all\_contact\_MIT/chr\_02\_02\_500kb.mat
-file directory: ../data/extracted\_all\_contact\_call4/chr\_02\_02\_500kb.mat
-file directory: ../data/extracted\_all\_contact\_RL/chr\_02\_02\_500kb.mat
-file directory: ../data/extracted\_all\_contact\_ALL/chr\_02\_02\_500kb.mat
-size of old matrix: (486, 486)
-size of new matrix: (480, 480)
-size of old matrix: (486, 486)
-size of new matrix: (480, 480)
-size of old matrix: (486, 486)
-size of new matrix: (480, 480)
-size of old matrix: (486, 486)
-size of new matrix: (480, 480)
-
+{\color{incolor}In [{\color{incolor}154}]:} \PY{n}{mit\PYZus{}mit\PYZus{}corr} \PY{o}{=} \PYZbs{}
+              \PY{n}{graphlet\PYZus{}correlational\PYZus{}distance}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{p}{,} \PY{n}{graphlets\PYZus{}mit}\PY{p}{)}
 \end{Verbatim}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}19}]:} \PY{n}{n0}\PY{p}{,} \PY{n}{m0} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
-         \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
-         \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
-         \PY{n}{n3}\PY{p}{,} \PY{n}{m3} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}
+{\color{incolor}In [{\color{incolor}155}]:} \PY{n}{mit\PYZus{}call4\PYZus{}corr} \PY{o}{=} \PYZbs{}
+              \PY{n}{graphlet\PYZus{}correlational\PYZus{}distance}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{p}{,} \PY{n}{graphlets\PYZus{}call4}\PY{p}{)}
+\end{Verbatim}
 
-         \PY{n}{n} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{n0}\PY{p}{,} \PY{n}{m0}\PY{p}{,} \PY{n}{n1}\PY{p}{,} \PY{n}{m1}\PY{p}{,} \PY{n}{n2}\PY{p}{,} \PY{n}{m2}\PY{p}{,} \PY{n}{n3}\PY{p}{,} \PY{n}{m3}\PY{p}{]}\PY{p}{)}
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}156}]:} \PY{n}{mit\PYZus{}rl\PYZus{}corr} \PY{o}{=} \PYZbs{}
+              \PY{n}{graphlet\PYZus{}correlational\PYZus{}distance}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{p}{,} \PY{n}{graphlets\PYZus{}rl}\PY{p}{)}
+\end{Verbatim}
 
-         \PY{n}{images} \PY{o}{=} \PY{p}{[}\PY{n}{mit}\PY{p}{,} \PY{n+nb}{all}\PY{p}{,} \PY{n}{rl}\PY{p}{,} \PY{n}{call4}\PY{p}{]}
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}157}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
+          \PY{n}{images} \PY{o}{=} \PY{p}{[} \PY{n}{mit\PYZus{}mit\PYZus{}corr}
+                    \PY{p}{,} \PY{n}{mit\PYZus{}all\PYZus{}corr}
+                   \PY{p}{,} \PY{n}{mit\PYZus{}rl\PYZus{}corr}
+                   \PY{p}{,} \PY{n}{mit\PYZus{}call4\PYZus{}corr}\PY{p}{]}
           \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}
@@
 
-    \begin{verbatim}
-<matplotlib.figure.Figure at 0x7f65c3721610>
-    \end{verbatim}
-
     \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_4_2.png}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_11_1.png}
     \end{center}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}20}]:} \PY{n}{mit} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{mit}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
-         \PY{n+nb}{all} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
-         \PY{n}{rl} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{rl}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
-         \PY{n}{call4} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{call4}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
+{\color{incolor}In [{\color{incolor}161}]:} \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Total correlation statistics}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{mit\PYZus{}mit\PYZus{}corr}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs mit}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{mit\PYZus{}all\PYZus{}corr}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs all}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{mit\PYZus{}rl\PYZus{}corr}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs rl}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{mit\PYZus{}call4\PYZus{}corr}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs call4}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+
+          \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+s2}{Total correlation statistics}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}mit\PYZus{}corr}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs mit}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}all\PYZus{}corr}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs all}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}rl\PYZus{}corr}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs rl}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+          \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}call4\PYZus{}corr}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs call4}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
 \end{Verbatim}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}21}]:} \PY{n}{images} \PY{o}{=} \PY{p}{[} 
-                 \PY{n}{mit}\PY{p}{,} \PY{n+nb}{all}\PY{p}{,} \PY{n}{rl}\PY{p}{,} \PY{n}{call4}
-                 \PY{p}{,} \PY{p}{(}\PY{n}{mit} \PY{o}{==} \PY{n+nb}{all}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{mit} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n+nb}{all} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{p}{,} \PY{n+nb}{all} \PY{o}{!=} \PY{n}{mit}
-                 \PY{p}{,} \PY{p}{(}\PY{n}{mit} \PY{o}{==} \PY{n}{rl}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{mit} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{rl} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{p}{,} \PY{n}{rl} \PY{o}{!=} \PY{n}{mit}
-                 \PY{p}{,} \PY{p}{(}\PY{n}{mit} \PY{o}{==} \PY{n}{call4}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{mit} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{call4} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{p}{,} \PY{n}{call4} \PY{o}{!=} \PY{n}{mit}
-                  \PY{p}{]} 
-         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{5}\PY{p}{)}
-\end{Verbatim}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-Number of columnts: 2
-
-    \end{Verbatim}
-
-    \begin{verbatim}
-<matplotlib.figure.Figure at 0x7f65c3718390>
-    \end{verbatim}
-
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_6_2.png}
-    \end{center}
-    { \hspace*{\fill} \\}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}22}]:} \PY{n+nb}{min}\PY{p}{,} \PY{n+nb}{max}\PY{p}{,} \PY{n}{mean\PYZus{}mit}\PY{p}{,} \PY{n}{std\PYZus{}mit} \PY{o}{=} \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{mit}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-         \PY{n+nb}{min}\PY{p}{,} \PY{n+nb}{max}\PY{p}{,} \PY{n}{mean\PYZus{}rl}\PY{p}{,} \PY{n}{std\PYZus{}rl} \PY{o}{=} \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{rl}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{rl}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-         \PY{n+nb}{min}\PY{p}{,} \PY{n+nb}{max}\PY{p}{,} \PY{n}{mean\PYZus{}call4}\PY{p}{,} \PY{n}{std\PYZus{}call4} \PY{o}{=} \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{call4}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{call4}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-         \PY{n+nb}{min}\PY{p}{,} \PY{n+nb}{max}\PY{p}{,} \PY{n}{mean\PYZus{}all}\PY{p}{,} \PY{n}{std\PYZus{}all} \PY{o}{=} \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n+nb}{all}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{all}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\end{Verbatim}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
+Total correlation statistics
 \#-----------------------------------------------------------------------\#
-Stats for mit: 
-max: 1.000000 | min: 0.000000 | median: 0.000000 | mean: 0.188247 | std: 0.390909
+Stats for mit vs mit: 
+max: 4.469689 | min: 0.000000 | median: 0.118804 | mean: 0.177694 | std: 0.406987
 \#-----------------------------------------------------------------------\#
 \#-----------------------------------------------------------------------\#
-Stats for rl: 
-max: 1.000000 | min: 0.000000 | median: 0.000000 | mean: 0.153229 | std: 0.360208
+Stats for mit vs all: 
+max: 4.469821 | min: 0.000000 | median: 0.254837 | mean: 0.331607 | std: 0.424543
 \#-----------------------------------------------------------------------\#
 \#-----------------------------------------------------------------------\#
-Stats for call4: 
-max: 1.000000 | min: 0.000000 | median: 0.000000 | mean: 0.158854 | std: 0.365540
+Stats for mit vs rl: 
+max: 4.469689 | min: 0.000000 | median: 0.368116 | mean: 0.429916 | std: 0.418677
 \#-----------------------------------------------------------------------\#
 \#-----------------------------------------------------------------------\#
-Stats for all: 
-max: 1.000000 | min: 0.000000 | median: 0.000000 | mean: 0.159688 | std: 0.366316
+Stats for mit vs call4: 
+max: 4.469790 | min: 0.000000 | median: 0.296439 | mean: 0.359209 | std: 0.420711
+\#-----------------------------------------------------------------------\#
+
+Total correlation statistics
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 0.000000 | min: 0.000000 | median: 0.000000 | mean: 0.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 1.805932 | min: 0.000000 | median: 0.243699 | mean: 0.287908 | std: 0.178464
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 1.235199 | min: 0.000000 | median: 0.368138 | mean: 0.391644 | std: 0.196214
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 1.392509 | min: 0.000000 | median: 0.298928 | mean: 0.317962 | std: 0.175240
 \#-----------------------------------------------------------------------\#
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}23}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
-         \PY{n}{images} \PY{o}{=} \PY{p}{[}
-                 \PY{p}{(}\PY{n}{mit}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1e\PYZhy{}2}
-                 \PY{p}{,} \PY{p}{(}\PY{n+nb}{all}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1e\PYZhy{}2}
-                 \PY{p}{,} \PY{p}{(}\PY{n}{rl}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1e\PYZhy{}2}
-                 \PY{p}{,} \PY{p}{(}\PY{n}{call4}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1e\PYZhy{}2}
+{\color{outcolor}Out[{\color{outcolor}161}]:} (1.3925089365419872, 0.0, 0.3179615758460628, 0.17523973020518074)
+\end{Verbatim}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}182}]:} \PY{n}{n} \PY{o}{=} \PY{n}{mit\PYZus{}mit\PYZus{}corr}\PY{o}{.}\PY{n}{shape}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}
+          \PY{c+c1}{\PYZsh{}t1 = (t\PYZus{}test(np.diagonal(mit\PYZus{}mit\PYZus{}corr)))}
+          \PY{n}{t2} \PY{o}{=} \PY{p}{(}\PY{n}{t\PYZus{}test}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}all\PYZus{}corr}\PY{p}{)}\PY{p}{)}\PY{p}{)}
+          \PY{n}{t3} \PY{o}{=} \PY{p}{(}\PY{n}{t\PYZus{}test}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}rl\PYZus{}corr}\PY{p}{)}\PY{p}{)}\PY{p}{)}
+          \PY{n}{t4} \PY{o}{=} \PY{p}{(}\PY{n}{t\PYZus{}test}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}call4\PYZus{}corr}\PY{p}{)}\PY{p}{)}\PY{p}{)}
+          \PY{k}{print}\PY{p}{(}\PY{n}{n}\PY{p}{)}
+          \PY{c+c1}{\PYZsh{}print(t1)}
+          \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{t statistic for mit vs all: }\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}} \PY{n}{t2}\PY{p}{)}
+          \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{t statistic for mit vs rl: }\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}} \PY{n}{t3}\PY{p}{)}
+          \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{t statistic for mit vs call4: }\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}} \PY{n}{t4}\PY{p}{)}
+          \PY{k+kn}{from} \PY{n+nn}{scipy.stats} \PY{k+kn}{import} \PY{n}{t}
+          \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{p\PYZhy{}value for mit\PYZhy{}all: }\PY{l+s+si}{\PYZpc{}10.3e}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{l+m+mi}{1} \PY{o}{\PYZhy{}} \PY{n}{t}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{t2}\PY{p}{,} \PY{n}{n}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}\PY{p}{)}
+          \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{p\PYZhy{}value for mit\PYZhy{}rl: }\PY{l+s+si}{\PYZpc{}10.3e}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{l+m+mi}{1} \PY{o}{\PYZhy{}} \PY{n}{t}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{t3}\PY{p}{,} \PY{n}{n}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}\PY{p}{)}
+          \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{p\PYZhy{}value for mit\PYZhy{}call4: }\PY{l+s+si}{\PYZpc{}10.3e}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{l+m+mi}{1} \PY{o}{\PYZhy{}} \PY{n}{t}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{t4}\PY{p}{,} \PY{n}{n}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+478
+t statistic for mit vs all: 18
+t statistic for mit vs rl: 19
+t statistic for mit vs call4: 19
+p-value for mit-all:  0.000e+00
+p-value for mit-rl:  0.000e+00
+p-value for mit-call4:  0.000e+00
+
+    \end{Verbatim}
+
+    \section{3. Orbit-wise Correlation}\label{orbit-wise-correlation}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}192}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
+          \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
+              \PY{n}{graphlets\PYZus{}mit} \PY{o}{=} \PY{n}{readMat}\PYZbs{}
+              \PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}mit.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+              \PY{n}{graphlets\PYZus{}all} \PY{o}{=} \PY{n}{readMat}\PYZbs{}
+              \PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}all.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+              \PY{n}{graphlets\PYZus{}rl} \PY{o}{=} \PY{n}{readMat}\PYZbs{}
+              \PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}rl.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+              \PY{n}{graphlets\PYZus{}call4} \PY{o}{=} \PY{n}{readMat}\PYZbs{}
+              \PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}call4.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+              \PY{n}{mit\PYZus{}all\PYZus{}corr\PYZus{}orbit\PYZus{}wise} \PY{o}{=} \PYZbs{}
+                  \PY{n}{pearson}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{o}{.}\PY{n}{T}\PY{p}{,} \PY{n}{graphlets\PYZus{}all}\PY{o}{.}\PY{n}{T}\PY{p}{)}
+              \PY{n}{mit\PYZus{}mit\PYZus{}corr\PYZus{}orbit\PYZus{}wise}\PY{o}{=} \PYZbs{}
+                  \PY{n}{pearson}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{o}{.}\PY{n}{T}\PY{p}{,} \PY{n}{graphlets\PYZus{}mit}\PY{o}{.}\PY{n}{T}\PY{p}{)}
+              \PY{n}{mit\PYZus{}call4\PYZus{}corr\PYZus{}orbit\PYZus{}wise}\PY{o}{=} \PYZbs{}
+                  \PY{n}{pearson}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{o}{.}\PY{n}{T}\PY{p}{,} \PY{n}{graphlets\PYZus{}call4}\PY{o}{.}\PY{n}{T}\PY{p}{)}
+              \PY{n}{mit\PYZus{}rl\PYZus{}corr\PYZus{}orbit\PYZus{}wise}\PY{o}{=} \PYZbs{}
+                  \PY{n}{pearson}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{o}{.}\PY{n}{T}\PY{p}{,} \PY{n}{graphlets\PYZus{}rl}\PY{o}{.}\PY{n}{T}\PY{p}{)}
+              \PY{n}{images} \PY{o}{=} \PY{p}{[} \PY{n}{mit\PYZus{}mit\PYZus{}corr\PYZus{}orbit\PYZus{}wise}
+                    \PY{p}{,} \PY{n}{mit\PYZus{}all\PYZus{}corr\PYZus{}orbit\PYZus{}wise}
+                   \PY{p}{,} \PY{n}{mit\PYZus{}rl\PYZus{}corr\PYZus{}orbit\PYZus{}wise}
+                   \PY{p}{,} \PY{n}{mit\PYZus{}call4\PYZus{}corr\PYZus{}orbit\PYZus{}wise}
                    \PY{p}{]}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr01\_chr01\_mit.graphlets
+file directory: data/chr01\_chr01\_all.graphlets
+file directory: data/chr01\_chr01\_rl.graphlets
+file directory: data/chr01\_chr01\_call4.graphlets
 Number of columnts: 4
@@
 
-    \begin{verbatim}
-<matplotlib.figure.Figure at 0x7f65c3752790>
-    \end{verbatim}
-
     \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_8_2.png}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_1.png}
     \end{center}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}24}]:} \PY{n}{images} \PY{o}{=} \PY{p}{[}
-                 \PY{n}{log}\PY{p}{(}\PY{n}{call4}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}
-                 \PY{p}{,} \PY{n}{log}\PY{p}{(}\PY{n}{mit}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}
-                 \PY{p}{,} \PY{n}{log}\PY{p}{(}\PY{n}{rl}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}
-                 \PY{p}{,} \PY{n}{log}\PY{p}{(}\PY{n+nb}{all}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}
-                 \PY{p}{]}
-         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
-\end{Verbatim}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr02\_chr02\_mit.graphlets
+file directory: data/chr02\_chr02\_all.graphlets
+file directory: data/chr02\_chr02\_rl.graphlets
+file directory: data/chr02\_chr02\_call4.graphlets
 Number of columnts: 4
@@
 
-    \begin{verbatim}
-<matplotlib.figure.Figure at 0x7f65c37400d0>
-    \end{verbatim}
-
     \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_9_2.png}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_3.png}
     \end{center}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}10}]:} \PY{n}{convertBinaryMatToOrcaReadable}\PY{p}{(}\PY{n}{call4} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}call4.edges}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{)}
-         \PY{n}{convertBinaryMatToOrcaReadable}\PY{p}{(}\PY{n}{mit} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}mit.edges}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{)}
-         \PY{n}{convertBinaryMatToOrcaReadable}\PY{p}{(}\PY{n}{rl} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}rl.edges}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{)}
-         \PY{n}{convertBinaryMatToOrcaReadable}\PY{p}{(}\PY{n+nb}{all} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}all.edges}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{)}
+file directory: data/chr03\_chr03\_mit.graphlets
+file directory: data/chr03\_chr03\_all.graphlets
+file directory: data/chr03\_chr03\_rl.graphlets
+file directory: data/chr03\_chr03\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_5.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr04\_chr04\_mit.graphlets
+file directory: data/chr04\_chr04\_all.graphlets
+file directory: data/chr04\_chr04\_rl.graphlets
+file directory: data/chr04\_chr04\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_7.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr05\_chr05\_mit.graphlets
+file directory: data/chr05\_chr05\_all.graphlets
+file directory: data/chr05\_chr05\_rl.graphlets
+file directory: data/chr05\_chr05\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_9.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr06\_chr06\_mit.graphlets
+file directory: data/chr06\_chr06\_all.graphlets
+file directory: data/chr06\_chr06\_rl.graphlets
+file directory: data/chr06\_chr06\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_11.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr07\_chr07\_mit.graphlets
+file directory: data/chr07\_chr07\_all.graphlets
+file directory: data/chr07\_chr07\_rl.graphlets
+file directory: data/chr07\_chr07\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_13.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr08\_chr08\_mit.graphlets
+file directory: data/chr08\_chr08\_all.graphlets
+file directory: data/chr08\_chr08\_rl.graphlets
+file directory: data/chr08\_chr08\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_15.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr09\_chr09\_mit.graphlets
+file directory: data/chr09\_chr09\_all.graphlets
+file directory: data/chr09\_chr09\_rl.graphlets
+file directory: data/chr09\_chr09\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_17.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr10\_chr10\_mit.graphlets
+file directory: data/chr10\_chr10\_all.graphlets
+file directory: data/chr10\_chr10\_rl.graphlets
+file directory: data/chr10\_chr10\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_19.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr11\_chr11\_mit.graphlets
+file directory: data/chr11\_chr11\_all.graphlets
+file directory: data/chr11\_chr11\_rl.graphlets
+file directory: data/chr11\_chr11\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_21.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr12\_chr12\_mit.graphlets
+file directory: data/chr12\_chr12\_all.graphlets
+file directory: data/chr12\_chr12\_rl.graphlets
+file directory: data/chr12\_chr12\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_23.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr13\_chr13\_mit.graphlets
+file directory: data/chr13\_chr13\_all.graphlets
+file directory: data/chr13\_chr13\_rl.graphlets
+file directory: data/chr13\_chr13\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_25.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr14\_chr14\_mit.graphlets
+file directory: data/chr14\_chr14\_all.graphlets
+file directory: data/chr14\_chr14\_rl.graphlets
+file directory: data/chr14\_chr14\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_27.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr15\_chr15\_mit.graphlets
+file directory: data/chr15\_chr15\_all.graphlets
+file directory: data/chr15\_chr15\_rl.graphlets
+file directory: data/chr15\_chr15\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_29.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr16\_chr16\_mit.graphlets
+file directory: data/chr16\_chr16\_all.graphlets
+file directory: data/chr16\_chr16\_rl.graphlets
+file directory: data/chr16\_chr16\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_31.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr17\_chr17\_mit.graphlets
+file directory: data/chr17\_chr17\_all.graphlets
+file directory: data/chr17\_chr17\_rl.graphlets
+file directory: data/chr17\_chr17\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_33.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr18\_chr18\_mit.graphlets
+file directory: data/chr18\_chr18\_all.graphlets
+file directory: data/chr18\_chr18\_rl.graphlets
+file directory: data/chr18\_chr18\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_35.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr19\_chr19\_mit.graphlets
+file directory: data/chr19\_chr19\_all.graphlets
+file directory: data/chr19\_chr19\_rl.graphlets
+file directory: data/chr19\_chr19\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_37.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr20\_chr20\_mit.graphlets
+file directory: data/chr20\_chr20\_all.graphlets
+file directory: data/chr20\_chr20\_rl.graphlets
+file directory: data/chr20\_chr20\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_39.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr21\_chr21\_mit.graphlets
+file directory: data/chr21\_chr21\_all.graphlets
+file directory: data/chr21\_chr21\_rl.graphlets
+file directory: data/chr21\_chr21\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_41.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr22\_chr22\_mit.graphlets
+file directory: data/chr22\_chr22\_all.graphlets
+file directory: data/chr22\_chr22\_rl.graphlets
+file directory: data/chr22\_chr22\_call4.graphlets
+Number of columns (68 and 67) not the same.
+            picking the minimum value{\ldots}
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_43.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr23\_chr23\_mit.graphlets
+file directory: data/chr23\_chr23\_all.graphlets
+file directory: data/chr23\_chr23\_rl.graphlets
+file directory: data/chr23\_chr23\_call4.graphlets
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_45.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}198}]:} \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
+              \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Chromosome }\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{)}\PY{p}{)}
+              \PY{n}{graphlets\PYZus{}mit} \PY{o}{=} \PY{n}{readMat}\PYZbs{}
+              \PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}mit.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+              \PY{n}{graphlets\PYZus{}all} \PY{o}{=} \PY{n}{readMat}\PYZbs{}
+              \PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}all.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+              \PY{n}{graphlets\PYZus{}rl} \PY{o}{=} \PY{n}{readMat}\PYZbs{}
+              \PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}rl.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+              \PY{n}{graphlets\PYZus{}call4} \PY{o}{=} \PY{n}{readMat}\PYZbs{}
+              \PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}call4.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+              \PY{n}{mit\PYZus{}all\PYZus{}corr\PYZus{}orbit\PYZus{}wise} \PY{o}{=} \PYZbs{}
+                  \PY{n}{pearson}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{o}{.}\PY{n}{T}\PY{p}{,} \PY{n}{graphlets\PYZus{}all}\PY{o}{.}\PY{n}{T}\PY{p}{)}
+              \PY{n}{mit\PYZus{}mit\PYZus{}corr\PYZus{}orbit\PYZus{}wise}\PY{o}{=} \PYZbs{}
+                  \PY{n}{pearson}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{o}{.}\PY{n}{T}\PY{p}{,} \PY{n}{graphlets\PYZus{}mit}\PY{o}{.}\PY{n}{T}\PY{p}{)}
+              \PY{n}{mit\PYZus{}call4\PYZus{}corr\PYZus{}orbit\PYZus{}wise}\PY{o}{=} \PYZbs{}
+                  \PY{n}{pearson}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{o}{.}\PY{n}{T}\PY{p}{,} \PY{n}{graphlets\PYZus{}call4}\PY{o}{.}\PY{n}{T}\PY{p}{)}
+              \PY{n}{mit\PYZus{}rl\PYZus{}corr\PYZus{}orbit\PYZus{}wise}\PY{o}{=} \PYZbs{}
+                  \PY{n}{pearson}\PY{p}{(}\PY{n}{graphlets\PYZus{}mit}\PY{o}{.}\PY{n}{T}\PY{p}{,} \PY{n}{graphlets\PYZus{}rl}\PY{o}{.}\PY{n}{T}\PY{p}{)} 
+              \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}mit\PYZus{}corr\PYZus{}orbit\PYZus{}wise}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit vs mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+              \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}all\PYZus{}corr\PYZus{}orbit\PYZus{}wise}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit vs all}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+              \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}rl\PYZus{}corr\PYZus{}orbit\PYZus{}wise}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit vs rl}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+              \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{mit\PYZus{}call4\PYZus{}corr\PYZus{}orbit\PYZus{}wise}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit vs call4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+Chromosome 1
+file directory: data/chr01\_chr01\_mit.graphlets
+file directory: data/chr01\_chr01\_all.graphlets
+file directory: data/chr01\_chr01\_rl.graphlets
+file directory: data/chr01\_chr01\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.691546 | min: 0.264693 | median: 0.447225 | mean: 0.458319 | std: 0.107821
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.488262 | min: 0.005228 | median: 0.064152 | mean: 0.115254 | std: 0.145756
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.735380 | min: 0.067395 | median: 0.209633 | mean: 0.266105 | std: 0.183532
+\#-----------------------------------------------------------------------\#
+Chromosome 2
+file directory: data/chr02\_chr02\_mit.graphlets
+file directory: data/chr02\_chr02\_all.graphlets
+file directory: data/chr02\_chr02\_rl.graphlets
+file directory: data/chr02\_chr02\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.612056 | min: 0.154044 | median: 0.397228 | mean: 0.394162 | std: 0.112857
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.544215 | min: 0.111064 | median: 0.186193 | mean: 0.239152 | std: 0.127777
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.654175 | min: 0.179010 | median: 0.387024 | mean: 0.398918 | std: 0.120441
+\#-----------------------------------------------------------------------\#
+Chromosome 3
+file directory: data/chr03\_chr03\_mit.graphlets
+file directory: data/chr03\_chr03\_all.graphlets
+file directory: data/chr03\_chr03\_rl.graphlets
+file directory: data/chr03\_chr03\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.662087 | min: 0.104050 | median: 0.202309 | mean: 0.256182 | std: 0.150717
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.547617 | min: -0.099389 | median: -0.048790 | mean: 0.040852 | std: 0.186404
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.612281 | min: 0.211936 | median: 0.284129 | mean: 0.317399 | std: 0.101562
+\#-----------------------------------------------------------------------\#
+Chromosome 4
+file directory: data/chr04\_chr04\_mit.graphlets
+file directory: data/chr04\_chr04\_all.graphlets
+file directory: data/chr04\_chr04\_rl.graphlets
+file directory: data/chr04\_chr04\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.671499 | min: 0.122204 | median: 0.288221 | mean: 0.322727 | std: 0.126746
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.594044 | min: 0.010192 | median: 0.105796 | mean: 0.158603 | std: 0.167435
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.619095 | min: 0.180210 | median: 0.219814 | mean: 0.274621 | std: 0.124545
+\#-----------------------------------------------------------------------\#
+Chromosome 5
+file directory: data/chr05\_chr05\_mit.graphlets
+file directory: data/chr05\_chr05\_all.graphlets
+file directory: data/chr05\_chr05\_rl.graphlets
+file directory: data/chr05\_chr05\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.690312 | min: 0.150168 | median: 0.270318 | mean: 0.325072 | std: 0.139688
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.656837 | min: 0.092786 | median: 0.184570 | mean: 0.243654 | std: 0.165851
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.695475 | min: 0.050792 | median: 0.212408 | mean: 0.271915 | std: 0.163642
+\#-----------------------------------------------------------------------\#
+Chromosome 6
+file directory: data/chr06\_chr06\_mit.graphlets
+file directory: data/chr06\_chr06\_all.graphlets
+file directory: data/chr06\_chr06\_rl.graphlets
+file directory: data/chr06\_chr06\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.632833 | min: 0.057611 | median: 0.200461 | mean: 0.261235 | std: 0.151247
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.603632 | min: 0.085527 | median: 0.163064 | mean: 0.221928 | std: 0.146656
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.641864 | min: 0.146304 | median: 0.345319 | mean: 0.373079 | std: 0.107218
+\#-----------------------------------------------------------------------\#
+Chromosome 7
+file directory: data/chr07\_chr07\_mit.graphlets
+file directory: data/chr07\_chr07\_all.graphlets
+file directory: data/chr07\_chr07\_rl.graphlets
+file directory: data/chr07\_chr07\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.610315 | min: 0.112599 | median: 0.257948 | mean: 0.299058 | std: 0.110721
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.557602 | min: 0.093335 | median: 0.173999 | mean: 0.218020 | std: 0.131495
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.624037 | min: 0.194459 | median: 0.260055 | mean: 0.310916 | std: 0.116809
+\#-----------------------------------------------------------------------\#
+Chromosome 8
+file directory: data/chr08\_chr08\_mit.graphlets
+file directory: data/chr08\_chr08\_all.graphlets
+file directory: data/chr08\_chr08\_rl.graphlets
+file directory: data/chr08\_chr08\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.622792 | min: 0.064770 | median: 0.218786 | mean: 0.241913 | std: 0.149463
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.548060 | min: -0.072579 | median: 0.022616 | mean: 0.081929 | std: 0.183618
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.565263 | min: 0.029225 | median: 0.136874 | mean: 0.176655 | std: 0.141294
+\#-----------------------------------------------------------------------\#
+Chromosome 9
+file directory: data/chr09\_chr09\_mit.graphlets
+file directory: data/chr09\_chr09\_all.graphlets
+file directory: data/chr09\_chr09\_rl.graphlets
+file directory: data/chr09\_chr09\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.673587 | min: 0.215801 | median: 0.486040 | mean: 0.475922 | std: 0.089530
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.584072 | min: 0.085406 | median: 0.163250 | mean: 0.193730 | std: 0.114805
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.564110 | min: 0.239796 | median: 0.353665 | mean: 0.358896 | std: 0.070965
+\#-----------------------------------------------------------------------\#
+Chromosome 10
+file directory: data/chr10\_chr10\_mit.graphlets
+file directory: data/chr10\_chr10\_all.graphlets
+file directory: data/chr10\_chr10\_rl.graphlets
+file directory: data/chr10\_chr10\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.580837 | min: 0.039492 | median: 0.149594 | mean: 0.209214 | std: 0.152388
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.610226 | min: 0.028290 | median: 0.136378 | mean: 0.188366 | std: 0.170261
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.557048 | min: 0.128177 | median: 0.192862 | mean: 0.248928 | std: 0.121032
+\#-----------------------------------------------------------------------\#
+Chromosome 11
+file directory: data/chr11\_chr11\_mit.graphlets
+file directory: data/chr11\_chr11\_all.graphlets
+file directory: data/chr11\_chr11\_rl.graphlets
+file directory: data/chr11\_chr11\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.653530 | min: 0.071174 | median: 0.234628 | mean: 0.264804 | std: 0.146381
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.617074 | min: 0.053525 | median: 0.245710 | mean: 0.267019 | std: 0.119514
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.655354 | min: 0.185627 | median: 0.264436 | mean: 0.307051 | std: 0.116659
+\#-----------------------------------------------------------------------\#
+Chromosome 12
+file directory: data/chr12\_chr12\_mit.graphlets
+file directory: data/chr12\_chr12\_all.graphlets
+file directory: data/chr12\_chr12\_rl.graphlets
+file directory: data/chr12\_chr12\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.614255 | min: 0.095773 | median: 0.199803 | mean: 0.247623 | std: 0.146455
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.582140 | min: 0.086246 | median: 0.208719 | mean: 0.257760 | std: 0.132487
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.697678 | min: 0.002999 | median: 0.176178 | mean: 0.236578 | std: 0.164529
+\#-----------------------------------------------------------------------\#
+Chromosome 13
+file directory: data/chr13\_chr13\_mit.graphlets
+file directory: data/chr13\_chr13\_all.graphlets
+file directory: data/chr13\_chr13\_rl.graphlets
+file directory: data/chr13\_chr13\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.656408 | min: -0.096631 | median: 0.156068 | mean: 0.209380 | std: 0.172578
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.595335 | min: -0.013590 | median: 0.111875 | mean: 0.164435 | std: 0.150826
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.619183 | min: -0.053744 | median: 0.118303 | mean: 0.185206 | std: 0.183478
+\#-----------------------------------------------------------------------\#
+Chromosome 14
+file directory: data/chr14\_chr14\_mit.graphlets
+file directory: data/chr14\_chr14\_all.graphlets
+file directory: data/chr14\_chr14\_rl.graphlets
+file directory: data/chr14\_chr14\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.543247 | min: -0.018916 | median: 0.161567 | mean: 0.193250 | std: 0.150059
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.632834 | min: 0.044777 | median: 0.318658 | mean: 0.345974 | std: 0.107771
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.589953 | min: -0.015215 | median: 0.146438 | mean: 0.199090 | std: 0.139573
+\#-----------------------------------------------------------------------\#
+Chromosome 15
+file directory: data/chr15\_chr15\_mit.graphlets
+file directory: data/chr15\_chr15\_all.graphlets
+file directory: data/chr15\_chr15\_rl.graphlets
+file directory: data/chr15\_chr15\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.627744 | min: -0.082786 | median: 0.270007 | mean: 0.295242 | std: 0.137112
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.563995 | min: -0.032939 | median: 0.066092 | mean: 0.130166 | std: 0.169149
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.555546 | min: -0.105676 | median: 0.049453 | mean: 0.122544 | std: 0.172953
+\#-----------------------------------------------------------------------\#
+Chromosome 16
+file directory: data/chr16\_chr16\_mit.graphlets
+file directory: data/chr16\_chr16\_all.graphlets
+file directory: data/chr16\_chr16\_rl.graphlets
+file directory: data/chr16\_chr16\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.663765 | min: 0.069383 | median: 0.262083 | mean: 0.282577 | std: 0.131222
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.571480 | min: 0.110550 | median: 0.250025 | mean: 0.273534 | std: 0.103604
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.512031 | min: -0.025588 | median: 0.119995 | mean: 0.155271 | std: 0.129841
+\#-----------------------------------------------------------------------\#
+Chromosome 17
+file directory: data/chr17\_chr17\_mit.graphlets
+file directory: data/chr17\_chr17\_all.graphlets
+file directory: data/chr17\_chr17\_rl.graphlets
+file directory: data/chr17\_chr17\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.630219 | min: 0.002755 | median: 0.203456 | mean: 0.247660 | std: 0.158113
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.594223 | min: -0.041055 | median: 0.090041 | mean: 0.145245 | std: 0.165721
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.613410 | min: 0.025560 | median: 0.129442 | mean: 0.185947 | std: 0.150671
+\#-----------------------------------------------------------------------\#
+Chromosome 18
+file directory: data/chr18\_chr18\_mit.graphlets
+file directory: data/chr18\_chr18\_all.graphlets
+file directory: data/chr18\_chr18\_rl.graphlets
+file directory: data/chr18\_chr18\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.523809 | min: -0.090717 | median: 0.084290 | mean: 0.116331 | std: 0.151788
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.610116 | min: -0.160623 | median: 0.020117 | mean: 0.101178 | std: 0.192265
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.474894 | min: -0.019191 | median: 0.119772 | mean: 0.158747 | std: 0.116521
+\#-----------------------------------------------------------------------\#
+Chromosome 19
+file directory: data/chr19\_chr19\_mit.graphlets
+file directory: data/chr19\_chr19\_all.graphlets
+file directory: data/chr19\_chr19\_rl.graphlets
+file directory: data/chr19\_chr19\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.635402 | min: 0.028820 | median: 0.258356 | mean: 0.271281 | std: 0.128827
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.529379 | min: -0.104304 | median: 0.157916 | mean: 0.191153 | std: 0.144419
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: nan | min: nan | median: nan | mean: nan | std: nan
+\#-----------------------------------------------------------------------\#
+Chromosome 20
+file directory: data/chr20\_chr20\_mit.graphlets
+file directory: data/chr20\_chr20\_all.graphlets
+file directory: data/chr20\_chr20\_rl.graphlets
+file directory: data/chr20\_chr20\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.575553 | min: -0.031425 | median: 0.167951 | mean: 0.175358 | std: 0.143634
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.570305 | min: -0.011435 | median: 0.236590 | mean: 0.256076 | std: 0.105848
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.553739 | min: 0.094144 | median: 0.240062 | mean: 0.262793 | std: 0.089579
+\#-----------------------------------------------------------------------\#
+Chromosome 21
+file directory: data/chr21\_chr21\_mit.graphlets
+file directory: data/chr21\_chr21\_all.graphlets
+file directory: data/chr21\_chr21\_rl.graphlets
+file directory: data/chr21\_chr21\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: nan | min: nan | median: nan | mean: nan | std: nan
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: nan | min: nan | median: nan | mean: nan | std: nan
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: nan | min: nan | median: nan | mean: nan | std: nan
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: nan | min: nan | median: nan | mean: nan | std: nan
+\#-----------------------------------------------------------------------\#
+Chromosome 22
+file directory: data/chr22\_chr22\_mit.graphlets
+file directory: data/chr22\_chr22\_all.graphlets
+file directory: data/chr22\_chr22\_rl.graphlets
+file directory: data/chr22\_chr22\_call4.graphlets
+Number of columns (68 and 67) not the same.
+            picking the minimum value{\ldots}
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: nan | min: nan | median: nan | mean: nan | std: nan
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: nan | min: nan | median: nan | mean: nan | std: nan
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: nan | min: nan | median: nan | mean: nan | std: nan
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: nan | min: nan | median: nan | mean: nan | std: nan
+\#-----------------------------------------------------------------------\#
+Chromosome 23
+file directory: data/chr23\_chr23\_mit.graphlets
+file directory: data/chr23\_chr23\_all.graphlets
+file directory: data/chr23\_chr23\_rl.graphlets
+file directory: data/chr23\_chr23\_call4.graphlets
+\#-----------------------------------------------------------------------\#
+Stats for mit vs mit: 
+max: 1.000000 | min: 1.000000 | median: 1.000000 | mean: 1.000000 | std: 0.000000
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs all: 
+max: 0.661035 | min: 0.007166 | median: 0.193827 | mean: 0.258310 | std: 0.167515
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs rl: 
+max: 0.520688 | min: 0.009042 | median: 0.106761 | mean: 0.168885 | std: 0.144671
+\#-----------------------------------------------------------------------\#
+\#-----------------------------------------------------------------------\#
+Stats for mit vs call4: 
+max: 0.594355 | min: 0.094710 | median: 0.184106 | mean: 0.239780 | std: 0.128988
+\#-----------------------------------------------------------------------\#
+
+    \end{Verbatim}
+
+    Now Let's repeat the above procedure for all 23 chromosomes and store
+them in a dictionary:
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}115}]:} \PY{n}{cells} \PY{o}{=} \PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{all}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{rl}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{call4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}
+          \PY{n}{graphlets} \PY{o}{=} \PY{p}{[} \PY{n+nb+bp}{None} \PY{p}{]} \PY{o}{*} \PY{l+m+mi}{24}
+          \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
+              \PY{n}{graphlets}\PY{p}{[}\PY{n}{chr1}\PY{p}{]} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
+              \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
+                 \PY{n}{graphlets}\PY{p}{[}\PY{n}{chr1}\PY{p}{]}\PY{p}{[}\PY{n}{cell}\PY{p}{]} \PY{o}{=} \PY{n}{readMat}\PYZbs{}
+              \PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{cell}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+
+          \PY{n}{correlations} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
+          \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
+              \PY{n}{correlations}\PY{p}{[}\PY{n}{cell1}\PY{p}{]} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
+              \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
+                  \PY{k}{if} \PY{n}{cell1} \PY{o}{==} \PY{n}{cell2}\PY{p}{:}
+                      \PY{k}{continue}
+                  \PY{n}{correlations}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{zeros}\PY{p}{(}\PY{p}{(}\PY{l+m+mi}{24}\PY{p}{,} \PY{l+m+mi}{73}\PY{p}{)}\PY{p}{)}
+                  \PY{c+c1}{\PYZsh{}cell (i, j) will store correlation between orbital j in }
+                  \PY{c+c1}{\PYZsh{}ith chromosome}
+
+          \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
+              \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{correlations}\PY{p}{:}
+                  \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{correlations}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{:}
+                      \PY{n}{correlations}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{,} \PY{p}{:}\PY{p}{]} \PY{o}{=} \PYZbs{}
+                          \PY{n}{np}\PY{o}{.}\PY{n}{diagonal}\PY{p}{(}\PY{n}{pearson}\PY{p}{(}\PY{n}{graphlets}\PY{p}{[}\PY{n}{chr1}\PY{p}{]}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{o}{.}\PY{n}{T}\PY{p}{,} \PY{n}{graphlets}\PY{p}{[}\PY{n}{chr1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{o}{.}\PY{n}{T}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+file directory: data/chr01\_chr01\_mit.graphlets
+file directory: data/chr01\_chr01\_all.graphlets
+file directory: data/chr01\_chr01\_rl.graphlets
+file directory: data/chr01\_chr01\_call4.graphlets
+file directory: data/chr02\_chr02\_mit.graphlets
+file directory: data/chr02\_chr02\_all.graphlets
+file directory: data/chr02\_chr02\_rl.graphlets
+file directory: data/chr02\_chr02\_call4.graphlets
+file directory: data/chr03\_chr03\_mit.graphlets
+file directory: data/chr03\_chr03\_all.graphlets
+file directory: data/chr03\_chr03\_rl.graphlets
+file directory: data/chr03\_chr03\_call4.graphlets
+file directory: data/chr04\_chr04\_mit.graphlets
+file directory: data/chr04\_chr04\_all.graphlets
+file directory: data/chr04\_chr04\_rl.graphlets
+file directory: data/chr04\_chr04\_call4.graphlets
+file directory: data/chr05\_chr05\_mit.graphlets
+file directory: data/chr05\_chr05\_all.graphlets
+file directory: data/chr05\_chr05\_rl.graphlets
+file directory: data/chr05\_chr05\_call4.graphlets
+file directory: data/chr06\_chr06\_mit.graphlets
+file directory: data/chr06\_chr06\_all.graphlets
+file directory: data/chr06\_chr06\_rl.graphlets
+file directory: data/chr06\_chr06\_call4.graphlets
+file directory: data/chr07\_chr07\_mit.graphlets
+file directory: data/chr07\_chr07\_all.graphlets
+file directory: data/chr07\_chr07\_rl.graphlets
+file directory: data/chr07\_chr07\_call4.graphlets
+file directory: data/chr08\_chr08\_mit.graphlets
+file directory: data/chr08\_chr08\_all.graphlets
+file directory: data/chr08\_chr08\_rl.graphlets
+file directory: data/chr08\_chr08\_call4.graphlets
+file directory: data/chr09\_chr09\_mit.graphlets
+file directory: data/chr09\_chr09\_all.graphlets
+file directory: data/chr09\_chr09\_rl.graphlets
+file directory: data/chr09\_chr09\_call4.graphlets
+file directory: data/chr10\_chr10\_mit.graphlets
+file directory: data/chr10\_chr10\_all.graphlets
+file directory: data/chr10\_chr10\_rl.graphlets
+file directory: data/chr10\_chr10\_call4.graphlets
+file directory: data/chr11\_chr11\_mit.graphlets
+file directory: data/chr11\_chr11\_all.graphlets
+file directory: data/chr11\_chr11\_rl.graphlets
+file directory: data/chr11\_chr11\_call4.graphlets
+file directory: data/chr12\_chr12\_mit.graphlets
+file directory: data/chr12\_chr12\_all.graphlets
+file directory: data/chr12\_chr12\_rl.graphlets
+file directory: data/chr12\_chr12\_call4.graphlets
+file directory: data/chr13\_chr13\_mit.graphlets
+file directory: data/chr13\_chr13\_all.graphlets
+file directory: data/chr13\_chr13\_rl.graphlets
+file directory: data/chr13\_chr13\_call4.graphlets
+file directory: data/chr14\_chr14\_mit.graphlets
+file directory: data/chr14\_chr14\_all.graphlets
+file directory: data/chr14\_chr14\_rl.graphlets
+file directory: data/chr14\_chr14\_call4.graphlets
+file directory: data/chr15\_chr15\_mit.graphlets
+file directory: data/chr15\_chr15\_all.graphlets
+file directory: data/chr15\_chr15\_rl.graphlets
+file directory: data/chr15\_chr15\_call4.graphlets
+file directory: data/chr16\_chr16\_mit.graphlets
+file directory: data/chr16\_chr16\_all.graphlets
+file directory: data/chr16\_chr16\_rl.graphlets
+file directory: data/chr16\_chr16\_call4.graphlets
+file directory: data/chr17\_chr17\_mit.graphlets
+file directory: data/chr17\_chr17\_all.graphlets
+file directory: data/chr17\_chr17\_rl.graphlets
+file directory: data/chr17\_chr17\_call4.graphlets
+file directory: data/chr18\_chr18\_mit.graphlets
+file directory: data/chr18\_chr18\_all.graphlets
+file directory: data/chr18\_chr18\_rl.graphlets
+file directory: data/chr18\_chr18\_call4.graphlets
+file directory: data/chr19\_chr19\_mit.graphlets
+file directory: data/chr19\_chr19\_all.graphlets
+file directory: data/chr19\_chr19\_rl.graphlets
+file directory: data/chr19\_chr19\_call4.graphlets
+file directory: data/chr20\_chr20\_mit.graphlets
+file directory: data/chr20\_chr20\_all.graphlets
+file directory: data/chr20\_chr20\_rl.graphlets
+file directory: data/chr20\_chr20\_call4.graphlets
+file directory: data/chr21\_chr21\_mit.graphlets
+file directory: data/chr21\_chr21\_all.graphlets
+file directory: data/chr21\_chr21\_rl.graphlets
+file directory: data/chr21\_chr21\_call4.graphlets
+file directory: data/chr22\_chr22\_mit.graphlets
+file directory: data/chr22\_chr22\_all.graphlets
+file directory: data/chr22\_chr22\_rl.graphlets
+file directory: data/chr22\_chr22\_call4.graphlets
+file directory: data/chr23\_chr23\_mit.graphlets
+file directory: data/chr23\_chr23\_all.graphlets
+file directory: data/chr23\_chr23\_rl.graphlets
+file directory: data/chr23\_chr23\_call4.graphlets
+Number of columns not the same.                picking the minimum value{\ldots}
+Number of columns not the same.                picking the minimum value{\ldots}
+Number of columns not the same.                picking the minimum value{\ldots}
+Number of columns not the same.                picking the minimum value{\ldots}
+Number of columns not the same.                picking the minimum value{\ldots}
+Number of columns not the same.                picking the minimum value{\ldots}
+
+    \end{Verbatim}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}199}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
+          \PY{n}{x} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}
+          \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
+          \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{correlations}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{:}
+              \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{correlations}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
+              \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{o}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{k}{cell})
+          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
+          \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_19_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}146}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
+          \PY{n}{x} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}
+          \PY{n}{count} \PY{o}{=} \PY{l+m+mi}{1}
+          \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{correlations}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{:}
+              \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{3}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{n}{count}\PY{p}{)}
+              \PY{n}{count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
+              \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{correlations}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
+              \PY{n}{y\PYZus{}error} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{n}{correlations}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
+              \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{o}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{k}{cell})
+              \PY{n}{ax}\PY{o}{.}\PY{n}{errorbar}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{yerr}\PY{o}{=}\PY{n}{y\PYZus{}error}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{dashed}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{None}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{green}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+              \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{k}{cell})
+          \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_20_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}137}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
+          \PY{n}{x} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{73}\PY{p}{)}
+          \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
+          \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{correlations}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{:}
+              \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{correlations}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}
+              \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{o}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{k}{cell})
+          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
+          \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_21_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}147}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
+          \PY{n}{x} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{73}\PY{p}{)}
+          \PY{n}{count} \PY{o}{=} \PY{l+m+mi}{1}
+          \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{correlations}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{:}
+              \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{3}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{n}{count}\PY{p}{)}
+              \PY{n}{count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
+              \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{correlations}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}
+              \PY{n}{y\PYZus{}error} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{n}{correlations}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}
+              \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{o}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{k}{cell})
+              \PY{n}{ax}\PY{o}{.}\PY{n}{errorbar}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{yerr}\PY{o}{=}\PY{n}{y\PYZus{}error}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{dashed}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{None}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{green}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+              \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{k}{cell})
+          \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_22_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    Compare The cancer cells only:
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}151}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
+          \PY{n}{x} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}
+          \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
+          \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{correlations}\PY{p}{:}
+              \PY{k}{if} \PY{n}{cell1} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}
+                  \PY{k}{continue}
+              \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{correlations}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{:}
+                  \PY{k}{if} \PY{n}{cell2} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}} \PY{o+ow}{or} \PY{n}{cell1} \PY{o}{\PYZgt{}} \PY{n}{cell2}\PY{p}{:}
+                      \PY{k}{continue}
+                  \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{correlations}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
+                  \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{o}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{ vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{cell1}\PY{p}{,} \PY{n}{cell2}\PY{p}{)}\PY{p}{)}
+          \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
+          \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_24_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}206}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
+          \PY{n}{x} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}
+          \PY{n}{count} \PY{o}{=} \PY{l+m+mi}{1}
+          \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{correlations}\PY{p}{:}
+              \PY{k}{if} \PY{n}{cell1} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}
+                  \PY{k}{continue}
+              \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{correlations}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{:}
+                  \PY{k}{if} \PY{n}{cell2} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}} \PY{o+ow}{or} \PY{n}{cell1} \PY{o}{\PYZgt{}} \PY{n}{cell2}\PY{p}{:}
+                      \PY{k}{continue}
+                  \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{3}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{n}{count}\PY{p}{)}
+                  \PY{n}{count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
+                  \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{correlations}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
+                  \PY{n}{y\PYZus{}error} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{n}{correlations}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
+                  \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{o}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{ vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{cell1}\PY{p}{,} \PY{n}{cell2}\PY{p}{)}\PY{p}{)}
+                  \PY{n}{ax}\PY{o}{.}\PY{n}{errorbar}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{yerr}\PY{o}{=}\PY{n}{y\PYZus{}error}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{dashed}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{None}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{green}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+                  \PY{n}{ax}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
+          \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_25_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor} }]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
+        \PY{n}{x} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}
+        \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
+        \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{correlations}\PY{p}{:}
+            \PY{k}{if} \PY{n}{cell1} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}
+                \PY{k}{continue}
+            \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{correlations}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{:}
+                \PY{k}{if} \PY{n}{cell2} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}} \PY{o+ow}{or} \PY{n}{cell1} \PY{o}{\PYZgt{}} \PY{n}{cell2}\PY{p}{:}
+                    \PY{k}{continue}
+                \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{correlations}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
+                \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{o}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{ vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{cell1}\PY{p}{,} \PY{n}{cell2}\PY{p}{)}\PY{p}{)}
+        \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
+        \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
 \end{Verbatim}

### 2018-03-08 papers/basics.tex
added papers

\documentclass{article}
\usepackage[top=1in, bottom=1.25in, left=1in, right=1in]{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{float}
\usepackage{caption}
\usepackage[font=small, labelfont=bf]{subcaption}
\usepackage{lscape} %landscape
\renewcommand{\familydefault}{\sfdefault} %change font

\begin{document}
\doublespacing
\setlength{\parindent}{0pt}
\section{Resources}
\textbf{Publications related to Hi-C:}
\begin{enumerate}
    \item \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2858594/}
    \item \url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0058793 }
    \item \url{http://nar.oxfordjournals.org/content/42/7/e52.full}
    \item \url{http://bioinformatics.oxfordjournals.org/content/early/2015/12/31/bioinformatics.btv754.abstract?keytype=ref&ijkey=A97WhKqBiEIcuzd}
    \item \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4417147/}
    \item \url{http://www.pnas.org/content/112/47/E6456.full}
    \item \url{http://www.pnas.org/content/113/12/E1663.full}
\end{enumerate}
\textbf{Hi-C Datasets:}
\begin{enumerate}
    \item Original Datasets: \url{https://bcm.app.box.com/v/aidenlab/folder/11234760671}
    \item Including cancerous cells: \url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}
    \item Chromosome3D project: \url{http://sysbio.rnet.missouri.edu/bdm_download/chromosome3d/}
\end{enumerate}
\textbf{Contact Matrix Analysis:}
\begin{enumerate}
    \item \url{https://omictools.com/contact-matrix-normalization-category}
    \item \url{http://hifive.docs.taylorlab.org/en/latest/}
\end{enumerate}

\textbf{Labs working on 3D Human Genome:}

\begin{enumerate}
    \item \url{http://mirnylab.mit.edu}
    \item \url{http://dostielab.biochem.mcgill.ca}
    \item \url{http://www.aidenlab.org/}
    \item \url{http://web.cmb.usc.edu/people/alber/index.htm}
    \item \url{http://calla.rnet.missouri.edu/cheng/nsf_career.html}
\end{enumerate}
\textbf{Resources related to Graphlet:}

\begin{enumerate}
    \item \url{https://en.wikipedia.org/wiki/Graphlets}
    \item \url{https://academic.oup.com/bioinformatics/article/23/2/e177/202080/Biological-network-comparison-using-graphlet}
    \item \url{http://www0.cs.ucl.ac.uk/staff/N.Przulj/index.html}
\end{enumerate}
\section{Purpose of this research}

In this study, we plan to find dissimilarities between normal cells and cancerous cells,
through investigating HiC contact maps. 
We suspect that there are systematic differences between how chromosomes are structured
between normal cells and cancerous cells.
we 
Ideally, it is desirable to compare 3D structures of 
cell in order to make such comparisons.
However, the main challenge that we face is that 
3D structure of a cell is not readily available. Based on
\cite{adhikari2016chromosome3d}, fluorescence in situ hybridizaiton
(FISH) is used for investigating 3D configuration of chromosomes.
However, this method can only be used locally and cannot map
the whole structure of the chromosomes.
In orther to find dissimilarities in the 3D structure of 
chromosomes, we used HiC dataset.
The HiC method, which was developed by \cite{lieberman2009comprehensive}, captures interactions between 
chromosomal fragments in kilobase resolution. Based on HiC data, an
\textit{interaction frequency (IF) } matrix can be developed between \textit{loci} at a desired resolution.
A cell $IF_{ij}$ in an interaction frequency matrix captures the number of interaction detected
in HiC dataset between locus $i$ and locus $j$ in the genome.
An interaction matrix can be used to develop both inter- and intra-chromosomal interaction matrices.
We believe differences in interaction matrices can be found between normal cells and cancerous ones.

\section{Genetics and Genomics}
\textbf{What is genetics?}
studies heredity. Offspring resembles its parents becasue they
inherit their \textit{genes}.\\
\textbf{Gene}: Sets of instructions that determine the traits of an organism.
A sequence of DNA. A DNA thread builds chromosomes.
Each organism has a unique number of chromosomes:
Humans: 46 chromosomes. You get 23 from your mother and 23 from your
father.\\
\textbf{Homologous chromosomes}: A set of two chromosomes consisting of genes
that correspond to the same traits, one coming from mother and the 
other coming from father. These corresponding genes are called
\textit{alleles}. Alleles are either \textit{dominant} or \textit{
    recessive}.\\
\textbf{Phenotype vs. Genotype}: Phenotype is a visible physical trait that
is caused partially by genes and partially environmental.
These traits include eye of hair color, height etc.
\textit{genotype} is the gense that correspond to a particular
phenotype. 
Their presence is necessary but not enough for the 
existence of phenotype.

\textbf{Homozygous vs. Heterozygous alleles}:
There are 3 combinations of genotypes:
tt, tT (or Tt) and TT. 
If the two alleles are the same
then the person is Homozygous (dominant or recessive)
in the corresponding
trait. Otherwise, the person is Heterozygous in that trait.

\textbf{Nucleotide}:  The monomer units that comprise DNAs. There
 are 4 types of nucleotides: (C, G, A, and T)

\textbf{DNA}: Macro-molecules that provide recipes for creating 
proteins.

\textbf{Gene Expression}:
\url{https://en.wikipedia.org/wiki/Gene_expression} \\
Authors of \cite{wang2013properties} provide good insight into structure a nucleus
of a eukaryotic cell: \\
\begin{displayquote}
``The cell of a eukaryotic species forms a multi-granularity genome structure
(e.g., nucleosome, chromatin fiber, chromatin cluster, chromosome,
and genome) in order to compactly store a very long genomic 
DNA sequence in its small nucleus. A nucleosome is a basic unit 
consisting of 145-147 base pairs of DNA wrapped around a
protein complex (histone octamer). Tens of nucleosomes are
further collapsed into a larger dense structural unit
– chromatin fiber - of several kilobase (Kb) pairs.
Multiple chromatin fibers form a large module of megabase pairs 
(Mb) DNA, which may be referred to as domains, globules, gene
loci, or chromatin clusters in different contexts.
A number of chromatin clusters then fold into a large
independent physical structure - chromosome,
which occupies a physical space in nucleus often
being referred to as chromosome territory.
One or more chromosomes interact to constitute the dynamic
three-dimensional (3D) conformation of the entire genome of a cell.''
\end{displayquote}

The following is from this 
\href{https://www.youtube.com/watch?v=dES-ozV65u4}{Youtube video}:
\\\textbf{Base}: Each pair of nucleotides in the DNA are called
a base.
A kilo-base resolution is a resolution in which each cell in
the matrix corresponds to 1000 pairs of nucleotides in DNA.
If you unfold the DNA inside one of your cells, it would measure
2 meters end to end. How is it folded up withing a nucleus which
is only 6 micorns wide?
\\[.1in]\textbf{Procedure:}
\begin{enumerate}
    \item Freeze the DNA in place.
    \item Cut the genome in tiny pieces.
        Mark the ends using Biotin, and glue them together into
        diffused pieces of DNA. These diffused pieces is made
        up of two bits of the genome that are spatial neighbors.
    \item Using DNA sequencing, the two parts of the 
        diffused DNA are identified and a dataset is created
        where each cell corresponds to a pair.
\end{enumerate}
\textbf{Frequent types of folds:}
\begin{enumerate}
    \item \textbf{ Loop:}
        \\When two parts of the genome that 
        are far from each other sequentially are
        attached.
        \\The length is $~200Kb$.
        \\Often seen that the gene that occures at
        one of the ends of the loop is turned on.
        \\A protein called CTCF is always present
        at the loops. Of the four possible directions
        that the two CTCF can take, in a loop, the
        two CTCF alwas point to one another (towards
        the loop).
    \item \textbf{ Contact domains:}
        \\Can happen in or out of a loop.
        \\Typical length: $~200Kb$
        \\Domains with same \textit{marks}
        tend to be located in the same place 
        inside the nucleus.
    \item \textbf{ Nuclear sub-compartments:}
        \\Spatial neighborhoods where domains
        with the same \textit{flavor} are
        present.
\end{enumerate}
Many of the folding principles that were present in 
human cells were also present in mouse cells at 
corresponding genomic positions.

Speculation: Like genes, folds are preserved across species.

each cell in the body has the same gene but different
cell types have different 3D structure (folding types).

\section{Graph-theoretic concepts}
\subsection*{Definitions: (from \cite{Automorphisms})}
\begin{figure}
    \centering
    \includegraphics[scale=.5]{graphlets.png}
    \caption{Graphlets and Orbits}
    \label{fig:graphletsAndOrbits}
\end{figure}
\begin{itemize}
    \item \textbf{Fragment:} A connected subgraph.
    \item \textbf{Motifs:} Fragments that occur with a frequency much higher than
        that occuring in a randomly generated graph.
    \item \textbf{Graphlets:} An arbitrary, induced fragment.
An edge is the only two-node graphlet.
    \item \textbf{Induced graphs:} Given a graph $G(V, E)$ and $S \subseteq V$, then $G'(S, E')$
        is a graphlet iff $E' = \{(u, v) | u, v \in V \text{ and } 
        (u, v) \in E \rightarrow (u, v) \in E'\}$
    \item \textbf{Orbits:} Set of all nodes in a graphlet that can be
        swapped with each other while not changing the graph.
\end{itemize}
\subsection*{Concepts}
\begin{itemize}
    \item \textbf{Global vs. local network comparison}:\\
        Global is inappropriate for incomplete networks.

    \item \textbf{Problem of Motifs:}
        They don't take into account infrequent and average subnetworks.

    \item \textbf{GDD: graphlet degree distribution}
\end{itemize}
\section{Literature Review}
\subsection{Hi-C}

Authors of \cite{trieu2015mogen} developed MOGEN.

\subsection{Graphlets}
Graphlet comparison is a novel method used to compare large networks in order to
find local similarities in them.
Authors of \cite{prvzulj2007biological} provide a new measure of PPI
network comparison
based on 73 constraints. This is used in order to compare two large
networks in order to detect similarities.

\cite{milenkoviae2008uncovering} 
 provide heuristics to compare two nodes based on some feature
(or signature) vectors, which is a 73-dimensional vector
$\mathbf{s}^T
= [s_0, s_2, ..., s_{72}]$ where $s_i$ denotes the number of nodes in
the network that are part of an orbit $i$. \\
\textit{Important Result}: Proteins with similar surroundings perform
similar functions.

In \cite{milenkovic2010cancer}, the same author investigates 
cancer-causing genes to find similarities in their signatures. After
clustering the genes based on \textit{signature similarity} criteria,
some clusters contain a lot of cancerous genes.
They use 4 different clustering methods with varying parameters to cluster
the proteins. They then predict the cancer-relatedness of a protein 
$i$ using
an enrichment criteria $\frac{k}{|C_i|}$ where $C_i$ is the cluster
where protein $i$ belongs and $k$ is the number of cancer-causing
proteins in $C_i$ and $|C_i|$ is the size of $C_i$.

Implementations of algorithms of extracting graphlets: \\
\begin{itemize}
    \item GraphCrunch: 
        \url{http://www0.cs.ucl.ac.uk/staff/natasa/graphcrunch2/usage.html}
    \item PGD: \url{http://nesreenahmed.com/graphlets/}
    \item ORCA: Graphlet and orbit counting algorithm \\
        \url{ https://CRAN.R-project.org/package=orca} \\
        This package is in R. In order to install it, type
        \texttt{install.packages("orca")}.

\end{itemize}

The authors of \cite{di2010fast} generalized the idea of graphlets to 
ordered graphs were the nodes are labeled in ascending order.
These graphlets are illustrated in Figure \ref{fig:ordered_graphlets}.
As can be viewed, there are a total of 14 orbits for graphlets of size
2 and 3 since the label of graphlets is also included in toplogy.
In the new definition, $d_v^i$ denotes the number of orbit $i$ touches 
node $v$. Each node, is then assigned a vector of length 14 
\footnote{number of orbits in graphlets of size 2 and 3}
$(d_v^1, d_v^2, ..., d_v^{14})$ 
and similarity of two nodes in two contact maps can be compared by
how geometrically close their corresponding vectors are.
\begin{figure}[H]
    \centering
    \includegraphics[width=.5\textwidth]{figures/ordered_graphlets.png}
    \caption{The five 2-and 3-node ordered graphlets and the corresponding 14
    automorphism orbits. The ordering of the graphlet nodes within each
    graphlet $G_i,\quad i \in \{1, ... , 5\}$ is represented by their colors: white nodes
    $<$ gray nodes $<$ black nodes}
    \label{fig:ordered_graphlets}
\end{figure}

\subsection{Balanced Network Deconvolution and Residual Networks}
Proposed by \cite{feizi2013network}. They developed a method that
eliminated indirect effect from a weighted graph. Their method
assumes that the observed graph $G_{obs}$ is a summation of its 
direct graph $G_{dir}$ and some indirect terms as follows:
\begin{equation}
    \label{indirect_effects}
    G_{obs} = G_{dir} + G_{dir}^2 + G_{dir} + ...
\end{equation}
They assume also that both $G_{obs}$ and $G_{dir}$ can be 
eigen-decomposed and they have the same eigen-vectors, that is
\begin{equation}
    G_{obs} = X \Sigma_{obs} X^T
\end{equation}
where 
\begin{equation}
    \Sigma_{obs} = 
    \begin{pmatrix}  
        \lambda^{obs}_1 &   0            & \cdots    &    0 \\
        0               &\lambda^{obs}_2 &           &      \\
        \vdots          &                & \ddots    &      \\
        0               &                &           & \lambda^{obs}_n
    \end{pmatrix}
\end{equation}
and
\begin{equation}
    G_{dir} = X \Sigma_{dir} X^T
\end{equation}
where
\begin{equation}
    \Sigma_{dir} = 
    \begin{pmatrix}  
        \lambda^{dir}_1 &   0            & \cdots    &    0 \\
        0               &\lambda^{dir}_2 &           &      \\
        \vdots          &                & \ddots    &      \\
        0               &                &           & \lambda^{dir}_n
    \end{pmatrix}
\end{equation}
so
\begin{equation}
    G_{obs} = X \Sigma_{obs} X^T = X ( \Sigma_{dir} + \Sigma_{dir}^2 + ...) X^T
\end{equation}
They also assume that eigen-values of the direct network are all
between -1 and 1, i.e. 
\begin{equation}
    -1 < \lambda^{dir}_i < 1 \quad \forall 1 \le i \le n
\end{equation}
Thus 
\begin{equation}
    \Sigma_{obs} = \Sigma_{dir} + \Sigma_{dir}^2 + ...
\end{equation}
\begin{equation}
    \lambda_i^{obs} = \sum_{j=1}^{\infty} \lambda^{dir}_{ij} \quad\quad \forall i = 1 ... n
\end{equation}
\begin{equation}
    \lambda_i^{obs} = \frac{\lambda_i^{dir}}{1 - \lambda_i^{dir}}
\end{equation}
\begin{equation}
   \lambda_i^{dir} = \frac{\lambda_i^{obs}}{1 + \lambda_i^{obs}} 
\end{equation}

\textbf{Source codes:} 
\begin{itemize}
    \item Python: \url{https://github.com/gidonro/Network-Deconvolution} 
    \item Matlab: \url{http://compbio.mit.edu/nd/}
\end{itemize}

Authors of \cite{sun2015improving} proposed ...
\subsection{Weighted graph comparison}
\url{https://www.cs.cmu.edu/~jingx/docs/DBreport.pdf}

\url{https://en.wikipedia.org/wiki/Gromov%E2%80%93Hausdorff_convergence}

Authors of \cite{soufiani2012graphlet} propose a graphlet
decomposition method
which considers situations where we observe an undirected
weighted network, encoded by a symmetric adjacency matrix with integer entries and diagonal
elements equal to zero. The term graphlet here is UNRELATED to the
Przulj graphlet.

Authors of \cite{ginestet2011statistical} developed Statistical Network (SPN) analysis
where the choice of thresholding value is made by statistical inference.
This method works within the framework of design of experiments where the same
network can be extracted for different individuals under different treatments. The
effect of those treatments can then be infered using this method.
In \cite{ginestet2011statistical} for example, they studied neuron connectivity
networks among 43 subjects for 4 different memory tasks (0-back, 1-back, 2-back and
3-back), and obtained the following thresholded networks. The results of which can 
be viewed in Figure \ref{fig:thresholded_adjacency}.

Their method can be very usefull if a large population of information from the same
chromosomes exist.
\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figures/thresholded_adjacency.png}
    \caption{}
    \label{fig:thresholded_adjacency}
\end{figure}

Distance between two weighted graphs can be measured based on \cite{daneshpajouh2009metric}:\\
$d(G_1, G_2) = |\displaystyle\sum_{w\in V_1} w -
\displaystyle\sum_{v \in V_2} v|$

Exhaustive enumeration of all graphlets being
prohibitively expensive, \cite{shervashidze2009efficient} introduce two
theoretically grounded speedup schemes, one
based on sampling and the second one specifically
designed for bounded degree graphs

\section{Problems and Questions}
\begin{enumerate}
    \item Can we convert larger Hi-C data sets by combining data from 
        several loci? This way we can create a DOE of different 
        individuals.
    \item How can we verify our results? Do we have any information on 
        similarities that we already know exist?
    \item how do we get inter-chromosomal graphs?
        I was not able to find them.
    \item Is there indirect depencecies in the Hi-graphs? How are they caused?
    \item How to run the algorithms on such huge matrices?
    \item What are random graph models?
    \item As far as I get, graphlet distribution is a means of finding similarities
        in graphs. What we are trying to do is to find dissimilarities. is it 
        the right track to go?
\end{enumerate}

\section{Experiments and Observations}
I have changed the network deconvolution code where it deals
with scaling factor. The rationale behind it was not clear to me
so I replaced it with my own understanding of it which might not 
be correct.

The intensity values in each data set follows an exponential
distribution, that is the majority of the intensities lie
close to the minimum value while some intensities are absurdly
large.
Because of this, thresholding intensity values based on quantiles (percentiles)
cannot be helpful since first and third quartiles are very close to each other
but very far from the maximum value.
\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{.45\textwidth} 
        \includegraphics[width=\textwidth]{figures/hist01.png}
        \caption{}
        \label{fig:hist01}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}
        \includegraphics[width=\textwidth]{figures/hist02.png}
        \caption{}
        \label{fig:hist02}
    \end{subfigure}
    \caption{\ref{fig:hist01} is a histogram of intensities form 
    ``\texttt{chr1\_1mb\_matrix}'',
    in the interval of $[0, 0.1]$ and bin size of $0.005$.
    \ref{fig:hist02} is a histogram of the same data
    but for interval of $[0.1, 1]$ and bin size of $0.01$.
    As can be seen, the two histograms are orders of magnitude
    different in terms of frequency.}
    \label{fig:hists}
\end{figure}
Each row and column in the graphs represents a loci on the chromosome,
the next row (column) represents the adjacent loci on the same chromosome,
thus the graph cannot be scrambled, that is, it is constructed as a stack
of interaction intensities of a locus with all other loci on the chromosome.
You cannot just swap two rows in the graph and have the same information since
the order is important. The only valid case is when last rows are removed 
and stacked on top of the graph.

Taking a logarithm can be very useful in this case. As can be viewed in Figures
\ref{fig:all_hists01} and \ref{fig:all_hists_deconvoluted01}, you can see that the data for 
all chromosomes look normal.
\begin{landscape}
\begin{figure}[H]
    \centering
    \includegraphics[width=1.5\textwidth]{figures/all_hists01.png}
    \caption{The histogram of the logarithm of the data for all 23
            chromosomes. The data looks normal now.}
    \label{fig:all_hists01}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1.5\textwidth]{figures/all_hists_deconvoluted01.png}
    \caption{The histogram of the deconvoluted  data in Figure 
            \ref{fig:all_hists01}. }
    \label{fig:all_hists_deconvoluted01}
\end{figure}
\end{landscape}

We decided to lock our data set on \href{http://sysbio.rnet.missouri.edu/bdm_download}{this}
dataset, since it includes Hi-C data for both normal test cells and 3 various cancerous
cells. This allows for the sort of comparison we are looking for in this study.

Cleaning the data requires some step that I'm not familiar yet. For example a normalized
Hi-C heatmap for chromosome 1 should look like something like \ref{fig:normalized_heatmap},
which can be found 
\href{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}{here},
but what I have managed to get from raw data is \ref{fig:my_result}, which clearly is
not normalized.
\begin{figure}[H]
    \centering
        \begin{subfigure}[b]{.4\textwidth}
            \includegraphics[width=\textwidth]{figures/normalized_heatmap.png}
            \caption{}
            \label{fig:normalized_heatmap}
        \end{subfigure}
        \begin{subfigure}[b]{.4\textwidth}
            \includegraphics[width=\textwidth]{figures/my_result.png}
            \caption{}
            \label{fig:my_result}
        \end{subfigure}
    \caption{As can be seen, \ref{fig:my_result} is not
                as smooth as \ref{fig:normalized_heatmap}.
                The black area in \ref{fig:my_result} account for 
                19 rows and columns, which is
                exactly the difference between the number of columns 
                in \ref{fig:my_result} and \ref{fig:normalized_heatmap}.
                }
    \label{fig:heatmap_comparison}
\end{figure}

Based on \cite{wang2013properties}, two normalization methods can be 
implemented on a contact matrix. The first of is Sequential Component 
Normalization (SCN \cite{cournac2012normalization})
and the other is simple Pearson's correlation.

In SCN, each column of the contact matrix is divied by its norm, then
its rows are divided by theirs norms. This process continues until the 
contact matrix is symmetric again.

In Pearson's correlation, a matrix $C$ is produced where $C_{ij}$
is the pearson correlation of rows i and j.

I have come up with what I call the \textit{pyramid algorithm}
where I simply apply a pyramid down and then pyramic up
on contact matrices to fill the empty spaces between. 
This algorithm is readily available
in OpenCV \footnote{www.opencv.org}.

The results of the normalizations on chrmosome 1 of a normal
cell is presented in Figure \ref{fig:normalizations}.

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{.3\textwidth}
        \includegraphics[width=\textwidth]{figures/original_cleaned.png}
        \caption{}
        \label{fig:original_cleaned}
    \end{subfigure}
    \begin{subfigure}[b]{.3\textwidth}
        \includegraphics[width=\textwidth]{figures/pearson.png}
        \caption{}
        \label{fig:pearson}
    \end{subfigure}
    \begin{subfigure}[b]{.3\textwidth}
        \includegraphics[width=\textwidth]{figures/scn.png}
        \caption{}
        \label{fig:scn}
    \end{subfigure}
    \begin{subfigure}[b]{.3\textwidth}
        \includegraphics[width=\textwidth]{figures/scn+pearson.png}
        \caption{}
        \label{fig:scn+pearson}
    \end{subfigure}
    \begin{subfigure}[b]{.3\textwidth}
        \includegraphics[width=\textwidth]{figures/pearson+scn.png}
        \caption{}
        \label{fig:pearson+scn}
    \end{subfigure}
    \begin{subfigure}[b]{.3\textwidth}
        \includegraphics[width=\textwidth]{figures/pyr.png}
        \caption{}
        \label{fig:pyr}
    \end{subfigure}
\caption{Results of different normalizing methods: 
    \ref{fig:original_cleaned} is the original matrix of \ref{fig:my_result}
    with the 19 empty rows and columns removed.
    \ref{fig:pearson} demonstrates the result of applying pearson normalization
    to the \ref{fig:original_cleaned}.
    In the same manner \ref{fig:scn} demonstrates the 
    result of applying scn to \ref{fig:original_cleaned}.
    \ref{fig:scn+pearson} shows the result of applying pearson to 
    \ref{fig:scn} and \ref{fig:pearson+scn} illustrates
    result of applying scn to \ref{fig:pearson}.
    \ref{fig:pyr} is the result of applying my pyramid method to the image
    which makes it somehow smooth and as I will describe later, will
    significantly improve histogram of logarithm matrix.
    }
    \label{fig:normalizations}
\end{figure}

Figure \ref{fig:pearson_hist} illustrates the result of histograms of
logarithms of figures that result from pearson normalization or chromosomes
1 through 22 and chromosome X (the last one).

Figure \ref{fig:pyr_hist_1mb} illustrates the result of histograms of
logarithms of figures that result from applying pyramid normalization
on the contact matrices of chromosomes
1 through 22 and chromosome X (the last one).
\begin{landscape}
    \begin{figure}[H]
        \centering
        \includegraphics[width=1.5\textwidth]{figures/pearson_hist.png}
        \caption{}
        \label{fig:pearson_hist}
    \end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1.5\textwidth]{figures/pyr_hist_1mb.png}
    \caption{}
    \label{fig:pyr_hist_1mb}
\end{figure}
\end{landscape}

\subsection*{ALL and MIT cell comparison}
One idea is the vary the threshold limits on the two indices to 
find the optimal set of thresholds $(t_{ALL}, t_{MIT})$, where 
the difference between the two pixels are minimum. The remaining
pixels that are still different are the ones that are definitely
correct. In this case, the objective function should be properly
penalized in order to prevent the thresholds from getting too
high or too low.
\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{.45\textwidth} 
        \includegraphics[width=\textwidth]{figures/ALL_60per_thresh.png}
        \caption{}
        \label{fig:all_thresh}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}
        \includegraphics[width=\textwidth]{figures/MIT_60per_thresh.png}
        \caption{}
        \label{fig:mit_thresh}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}
        \includegraphics[width=\textwidth]{figures/ALL_MIT_common.png}
        \caption{}
        \label{fig:all_mit_common}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}
        \includegraphics[width=\textwidth]{figures/ALL_MIT_diff.png}
        \caption{}
        \label{fig:all_mit_diff}
    \end{subfigure}
    \caption{\ref{fig:all_thresh} is HiC contact matrix of 
             chromosome 14 of ALL cell and
             \ref{fig:mit_thresh} is the contact matrix of
             the same chromosome in MIT cells. 
             Both matrices are thresholded based on their 60th
             percentile. \ref{fig:all_mit_common} is the common pixels
             and \ref{fig:all_mit_diff} is the pixels where they 
             are different.}
\end{figure}
\input{../scripts/logs/2018-01-31.log}
\bibliography{lit}
\bibliographystyle{unsrt}
\end{document}

### 2018-03-08 papers/temp/transcript.tex
added papers

--- 2018-03-08 papers/basics.tex
@@
 \usepackage{lscape} %landscape
-\renewcommand{\familydefault}{\sfdefault} %change font
-
 \begin{document}
@@
 \setlength{\parindent}{0pt}
-\section{Resources}
-\textbf{Publications related to Hi-C:}
-\begin{enumerate}
-    \item \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2858594/}
-    \item \url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0058793 }
-    \item \url{http://nar.oxfordjournals.org/content/42/7/e52.full}
-    \item \url{http://bioinformatics.oxfordjournals.org/content/early/2015/12/31/bioinformatics.btv754.abstract?keytype=ref&ijkey=A97WhKqBiEIcuzd}
-    \item \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4417147/}
-    \item \url{http://www.pnas.org/content/112/47/E6456.full}
-    \item \url{http://www.pnas.org/content/113/12/E1663.full}
-\end{enumerate}
-\textbf{Hi-C Datasets:}
-\begin{enumerate}
-    \item Original Datasets: \url{https://bcm.app.box.com/v/aidenlab/folder/11234760671}
-    \item Including cancerous cells: \url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}
-    \item Chromosome3D project: \url{http://sysbio.rnet.missouri.edu/bdm_download/chromosome3d/}
-\end{enumerate}
-\textbf{Contact Matrix Analysis:}
-\begin{enumerate}
-    \item \url{https://omictools.com/contact-matrix-normalization-category}
-    \item \url{http://hifive.docs.taylorlab.org/en/latest/}
-\end{enumerate}
+This work is about finding dissimilarities in genome configuration between normal and cancerous cells.
 
-\textbf{Labs working on 3D Human Genome:}
+Ideally, we would need to have the 3D structure to make such comparisons, however, such data does not yet exist.
 
-\begin{enumerate}
-    \item \url{http://mirnylab.mit.edu}
-    \item \url{http://dostielab.biochem.mcgill.ca}
-    \item \url{http://www.aidenlab.org/}
-    \item \url{http://web.cmb.usc.edu/people/alber/index.htm}
-    \item \url{http://calla.rnet.missouri.edu/cheng/nsf_career.html}
-\end{enumerate}
-\textbf{Resources related to Graphlet:}
+All we have is sets of data that is called HiC data.
+Which can be used to come up with matrices of this type that we call contact matrices.
 
-\begin{enumerate}
-    \item \url{https://en.wikipedia.org/wiki/Graphlets}
-    \item \url{https://academic.oup.com/bioinformatics/article/23/2/e177/202080/Biological-network-comparison-using-graphlet}
-    \item \url{http://www0.cs.ucl.ac.uk/staff/N.Przulj/index.html}
-\end{enumerate}
-\section{Purpose of this research}
+Contact matrices are ...
 
-In this study, we plan to find dissimilarities between normal cells and cancerous cells,
-through investigating HiC contact maps. 
-We suspect that there are systematic differences between how chromosomes are structured
-between normal cells and cancerous cells.
-we 
-Ideally, it is desirable to compare 3D structures of 
-cell in order to make such comparisons.
-However, the main challenge that we face is that 
-3D structure of a cell is not readily available. Based on
-\cite{adhikari2016chromosome3d}, fluorescence in situ hybridizaiton
-(FISH) is used for investigating 3D configuration of chromosomes.
-However, this method can only be used locally and cannot map
-the whole structure of the chromosomes.
-In orther to find dissimilarities in the 3D structure of 
-chromosomes, we used HiC dataset.
-The HiC method, which was developed by \cite{lieberman2009comprehensive}, captures interactions between 
-chromosomal fragments in kilobase resolution. Based on HiC data, an
-\textit{interaction frequency (IF) } matrix can be developed between \textit{loci} at a desired resolution.
-A cell $IF_{ij}$ in an interaction frequency matrix captures the number of interaction detected
-in HiC dataset between locus $i$ and locus $j$ in the genome.
-An interaction matrix can be used to develop both inter- and intra-chromosomal interaction matrices.
-We believe differences in interaction matrices can be found between normal cells and cancerous ones.
+Let's go into a more detailed discussion...
 
-\section{Genetics and Genomics}
-\textbf{What is genetics?}
-studies heredity. Offspring resembles its parents becasue they
-inherit their \textit{genes}.\\
-\textbf{Gene}: Sets of instructions that determine the traits of an organism.
-A sequence of DNA. A DNA thread builds chromosomes.
-Each organism has a unique number of chromosomes:
-Humans: 46 chromosomes. You get 23 from your mother and 23 from your
-father.\\
-\textbf{Homologous chromosomes}: A set of two chromosomes consisting of genes
-that correspond to the same traits, one coming from mother and the 
-other coming from father. These corresponding genes are called
-\textit{alleles}. Alleles are either \textit{dominant} or \textit{
-    recessive}.\\
-\textbf{Phenotype vs. Genotype}: Phenotype is a visible physical trait that
-is caused partially by genes and partially environmental.
-These traits include eye of hair color, height etc.
-\textit{genotype} is the gense that correspond to a particular
-phenotype. 
-Their presence is necessary but not enough for the 
-existence of phenotype.
+If you unfold DNA ...
 
-\textbf{Homozygous vs. Heterozygous alleles}:
-There are 3 combinations of genotypes:
-tt, tT (or Tt) and TT. 
-If the two alleles are the same
-then the person is Homozygous (dominant or recessive)
-in the corresponding
-trait. Otherwise, the person is Heterozygous in that trait.
-
-\textbf{Nucleotide}:  The monomer units that comprise DNAs. There
- are 4 types of nucleotides: (C, G, A, and T)
-
-\textbf{DNA}: Macro-molecules that provide recipes for creating 
-proteins.
-
-\textbf{Gene Expression}:
-\url{https://en.wikipedia.org/wiki/Gene_expression} \\
-Authors of \cite{wang2013properties} provide good insight into structure a nucleus
-of a eukaryotic cell: \\
-\begin{displayquote}
-``The cell of a eukaryotic species forms a multi-granularity genome structure
-(e.g., nucleosome, chromatin fiber, chromatin cluster, chromosome,
-and genome) in order to compactly store a very long genomic 
-DNA sequence in its small nucleus. A nucleosome is a basic unit 
-consisting of 145-147 base pairs of DNA wrapped around a
-protein complex (histone octamer). Tens of nucleosomes are
-further collapsed into a larger dense structural unit
-– chromatin fiber - of several kilobase (Kb) pairs.
-Multiple chromatin fibers form a large module of megabase pairs 
-(Mb) DNA, which may be referred to as domains, globules, gene
-loci, or chromatin clusters in different contexts.
-A number of chromatin clusters then fold into a large
-independent physical structure - chromosome,
-which occupies a physical space in nucleus often
-being referred to as chromosome territory.
-One or more chromosomes interact to constitute the dynamic
-three-dimensional (3D) conformation of the entire genome of a cell.''
-\end{displayquote}
-
-The following is from this 
-\href{https://www.youtube.com/watch?v=dES-ozV65u4}{Youtube video}:
-\\\textbf{Base}: Each pair of nucleotides in the DNA are called
-a base.
-A kilo-base resolution is a resolution in which each cell in
-the matrix corresponds to 1000 pairs of nucleotides in DNA.
-If you unfold the DNA inside one of your cells, it would measure
-2 meters end to end. How is it folded up withing a nucleus which
-is only 6 micorns wide?
-\\[.1in]\textbf{Procedure:}
-\begin{enumerate}
-    \item Freeze the DNA in place.
-    \item Cut the genome in tiny pieces.
-        Mark the ends using Biotin, and glue them together into
-        diffused pieces of DNA. These diffused pieces is made
-        up of two bits of the genome that are spatial neighbors.
-    \item Using DNA sequencing, the two parts of the 
-        diffused DNA are identified and a dataset is created
-        where each cell corresponds to a pair.
-\end{enumerate}
-\textbf{Frequent types of folds:}
-\begin{enumerate}
-    \item \textbf{ Loop:}
-        \\When two parts of the genome that 
-        are far from each other sequentially are
-        attached.
-        \\The length is $~200Kb$.
-        \\Often seen that the gene that occures at
-        one of the ends of the loop is turned on.
-        \\A protein called CTCF is always present
-        at the loops. Of the four possible directions
-        that the two CTCF can take, in a loop, the
-        two CTCF alwas point to one another (towards
-        the loop).
-    \item \textbf{ Contact domains:}
-        \\Can happen in or out of a loop.
-        \\Typical length: $~200Kb$
-        \\Domains with same \textit{marks}
-        tend to be located in the same place 
-        inside the nucleus.
-    \item \textbf{ Nuclear sub-compartments:}
-        \\Spatial neighborhoods where domains
-        with the same \textit{flavor} are
-        present.
-\end{enumerate}
-Many of the folding principles that were present in 
-human cells were also present in mouse cells at 
-corresponding genomic positions.
-
-Speculation: Like genes, folds are preserved across species.
-
-each cell in the body has the same gene but different
-cell types have different 3D structure (folding types).
-
-\section{Graph-theoretic concepts}
-\subsection*{Definitions: (from \cite{Automorphisms})}
-\begin{figure}
-    \centering
-    \includegraphics[scale=.5]{graphlets.png}
-    \caption{Graphlets and Orbits}
-    \label{fig:graphletsAndOrbits}
-\end{figure}
-\begin{itemize}
-    \item \textbf{Fragment:} A connected subgraph.
-    \item \textbf{Motifs:} Fragments that occur with a frequency much higher than
-        that occuring in a randomly generated graph.
-    \item \textbf{Graphlets:} An arbitrary, induced fragment.
-An edge is the only two-node graphlet.
-    \item \textbf{Induced graphs:} Given a graph $G(V, E)$ and $S \subseteq V$, then $G'(S, E')$
-        is a graphlet iff $E' = \{(u, v) | u, v \in V \text{ and } 
-        (u, v) \in E \rightarrow (u, v) \in E'\}$
-    \item \textbf{Orbits:} Set of all nodes in a graphlet that can be
-        swapped with each other while not changing the graph.
-\end{itemize}
-\subsection*{Concepts}
-\begin{itemize}
-    \item \textbf{Global vs. local network comparison}:\\
-        Global is inappropriate for incomplete networks.
-
-    \item \textbf{Problem of Motifs:}
-        They don't take into account infrequent and average subnetworks.
-
-    \item \textbf{GDD: graphlet degree distribution}
-\end{itemize}
-\section{Literature Review}
-\subsection{Hi-C}
-
-Authors of \cite{trieu2015mogen} developed MOGEN.
-
-\subsection{Graphlets}
-Graphlet comparison is a novel method used to compare large networks in order to
-find local similarities in them.
-Authors of \cite{prvzulj2007biological} provide a new measure of PPI
-network comparison
-based on 73 constraints. This is used in order to compare two large
-networks in order to detect similarities.
-
-\cite{milenkoviae2008uncovering} 
- provide heuristics to compare two nodes based on some feature
-(or signature) vectors, which is a 73-dimensional vector
-$\mathbf{s}^T
-= [s_0, s_2, ..., s_{72}]$ where $s_i$ denotes the number of nodes in
-the network that are part of an orbit $i$. \\
-\textit{Important Result}: Proteins with similar surroundings perform
-similar functions.
-
-In \cite{milenkovic2010cancer}, the same author investigates 
-cancer-causing genes to find similarities in their signatures. After
-clustering the genes based on \textit{signature similarity} criteria,
-some clusters contain a lot of cancerous genes.
-They use 4 different clustering methods with varying parameters to cluster
-the proteins. They then predict the cancer-relatedness of a protein 
-$i$ using
-an enrichment criteria $\frac{k}{|C_i|}$ where $C_i$ is the cluster
-where protein $i$ belongs and $k$ is the number of cancer-causing
-proteins in $C_i$ and $|C_i|$ is the size of $C_i$.
-
-Implementations of algorithms of extracting graphlets: \\
-\begin{itemize}
-    \item GraphCrunch: 
-        \url{http://www0.cs.ucl.ac.uk/staff/natasa/graphcrunch2/usage.html}
-    \item PGD: \url{http://nesreenahmed.com/graphlets/}
-    \item ORCA: Graphlet and orbit counting algorithm \\
-        \url{ https://CRAN.R-project.org/package=orca} \\
-        This package is in R. In order to install it, type
-        \texttt{install.packages("orca")}.
-
-\end{itemize}
-
-The authors of \cite{di2010fast} generalized the idea of graphlets to 
-ordered graphs were the nodes are labeled in ascending order.
-These graphlets are illustrated in Figure \ref{fig:ordered_graphlets}.
-As can be viewed, there are a total of 14 orbits for graphlets of size
-2 and 3 since the label of graphlets is also included in toplogy.
-In the new definition, $d_v^i$ denotes the number of orbit $i$ touches 
-node $v$. Each node, is then assigned a vector of length 14 
-\footnote{number of orbits in graphlets of size 2 and 3}
-$(d_v^1, d_v^2, ..., d_v^{14})$ 
-and similarity of two nodes in two contact maps can be compared by
-how geometrically close their corresponding vectors are.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.5\textwidth]{figures/ordered_graphlets.png}
-    \caption{The five 2-and 3-node ordered graphlets and the corresponding 14
-    automorphism orbits. The ordering of the graphlet nodes within each
-    graphlet $G_i,\quad i \in \{1, ... , 5\}$ is represented by their colors: white nodes
-    $<$ gray nodes $<$ black nodes}
-    \label{fig:ordered_graphlets}
-\end{figure}
-
-\subsection{Balanced Network Deconvolution and Residual Networks}
-Proposed by \cite{feizi2013network}. They developed a method that
-eliminated indirect effect from a weighted graph. Their method
-assumes that the observed graph $G_{obs}$ is a summation of its 
-direct graph $G_{dir}$ and some indirect terms as follows:
-\begin{equation}
-    \label{indirect_effects}
-    G_{obs} = G_{dir} + G_{dir}^2 + G_{dir} + ...
-\end{equation}
-They assume also that both $G_{obs}$ and $G_{dir}$ can be 
-eigen-decomposed and they have the same eigen-vectors, that is
-\begin{equation}
-    G_{obs} = X \Sigma_{obs} X^T
-\end{equation}
-where 
-\begin{equation}
-    \Sigma_{obs} = 
-    \begin{pmatrix}  
-        \lambda^{obs}_1 &   0            & \cdots    &    0 \\
-        0               &\lambda^{obs}_2 &           &      \\
-        \vdots          &                & \ddots    &      \\
-        0               &                &           & \lambda^{obs}_n
-    \end{pmatrix}
-\end{equation}
-and
-\begin{equation}
-    G_{dir} = X \Sigma_{dir} X^T
-\end{equation}
-where
-\begin{equation}
-    \Sigma_{dir} = 
-    \begin{pmatrix}  
-        \lambda^{dir}_1 &   0            & \cdots    &    0 \\
-        0               &\lambda^{dir}_2 &           &      \\
-        \vdots          &                & \ddots    &      \\
-        0               &                &           & \lambda^{dir}_n
-    \end{pmatrix}
-\end{equation}
-so
-\begin{equation}
-    G_{obs} = X \Sigma_{obs} X^T = X ( \Sigma_{dir} + \Sigma_{dir}^2 + ...) X^T
-\end{equation}
-They also assume that eigen-values of the direct network are all
-between -1 and 1, i.e. 
-\begin{equation}
-    -1 < \lambda^{dir}_i < 1 \quad \forall 1 \le i \le n
-\end{equation}
-Thus 
-\begin{equation}
-    \Sigma_{obs} = \Sigma_{dir} + \Sigma_{dir}^2 + ...
-\end{equation}
-\begin{equation}
-    \lambda_i^{obs} = \sum_{j=1}^{\infty} \lambda^{dir}_{ij} \quad\quad \forall i = 1 ... n
-\end{equation}
-\begin{equation}
-    \lambda_i^{obs} = \frac{\lambda_i^{dir}}{1 - \lambda_i^{dir}}
-\end{equation}
-\begin{equation}
-   \lambda_i^{dir} = \frac{\lambda_i^{obs}}{1 + \lambda_i^{obs}} 
-\end{equation}
-
-\textbf{Source codes:} 
-\begin{itemize}
-    \item Python: \url{https://github.com/gidonro/Network-Deconvolution} 
-    \item Matlab: \url{http://compbio.mit.edu/nd/}
-\end{itemize}
-
-Authors of \cite{sun2015improving} proposed ...
-\subsection{Weighted graph comparison}
-\url{https://www.cs.cmu.edu/~jingx/docs/DBreport.pdf}
-
-\url{https://en.wikipedia.org/wiki/Gromov%E2%80%93Hausdorff_convergence}
-
-Authors of \cite{soufiani2012graphlet} propose a graphlet
-decomposition method
-which considers situations where we observe an undirected
-weighted network, encoded by a symmetric adjacency matrix with integer entries and diagonal
-elements equal to zero. The term graphlet here is UNRELATED to the
-Przulj graphlet.
-
-Authors of \cite{ginestet2011statistical} developed Statistical Network (SPN) analysis
-where the choice of thresholding value is made by statistical inference.
-This method works within the framework of design of experiments where the same
-network can be extracted for different individuals under different treatments. The
-effect of those treatments can then be infered using this method.
-In \cite{ginestet2011statistical} for example, they studied neuron connectivity
-networks among 43 subjects for 4 different memory tasks (0-back, 1-back, 2-back and
-3-back), and obtained the following thresholded networks. The results of which can 
-be viewed in Figure \ref{fig:thresholded_adjacency}.
-
-Their method can be very usefull if a large population of information from the same
-chromosomes exist.
-\begin{figure}
-    \centering
-    \includegraphics[width=.5\textwidth]{figures/thresholded_adjacency.png}
-    \caption{}
-    \label{fig:thresholded_adjacency}
-\end{figure}
-
-Distance between two weighted graphs can be measured based on \cite{daneshpajouh2009metric}:\\
-$d(G_1, G_2) = |\displaystyle\sum_{w\in V_1} w -
-\displaystyle\sum_{v \in V_2} v|$
-
-Exhaustive enumeration of all graphlets being
-prohibitively expensive, \cite{shervashidze2009efficient} introduce two
-theoretically grounded speedup schemes, one
-based on sampling and the second one specifically
-designed for bounded degree graphs
-
-\section{Problems and Questions}
-\begin{enumerate}
-    \item Can we convert larger Hi-C data sets by combining data from 
-        several loci? This way we can create a DOE of different 
-        individuals.
-    \item How can we verify our results? Do we have any information on 
-        similarities that we already know exist?
-    \item how do we get inter-chromosomal graphs?
-        I was not able to find them.
-    \item Is there indirect depencecies in the Hi-graphs? How are they caused?
-    \item How to run the algorithms on such huge matrices?
-    \item What are random graph models?
-    \item As far as I get, graphlet distribution is a means of finding similarities
-        in graphs. What we are trying to do is to find dissimilarities. is it 
-        the right track to go?
-\end{enumerate}
-
-\section{Experiments and Observations}
-I have changed the network deconvolution code where it deals
-with scaling factor. The rationale behind it was not clear to me
-so I replaced it with my own understanding of it which might not 
-be correct.
-
-The intensity values in each data set follows an exponential
-distribution, that is the majority of the intensities lie
-close to the minimum value while some intensities are absurdly
-large.
-Because of this, thresholding intensity values based on quantiles (percentiles)
-cannot be helpful since first and third quartiles are very close to each other
-but very far from the maximum value.
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}[b]{.45\textwidth} 
-        \includegraphics[width=\textwidth]{figures/hist01.png}
-        \caption{}
-        \label{fig:hist01}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/hist02.png}
-        \caption{}
-        \label{fig:hist02}
-    \end{subfigure}
-    \caption{\ref{fig:hist01} is a histogram of intensities form 
-    ``\texttt{chr1\_1mb\_matrix}'',
-    in the interval of $[0, 0.1]$ and bin size of $0.005$.
-    \ref{fig:hist02} is a histogram of the same data
-    but for interval of $[0.1, 1]$ and bin size of $0.01$.
-    As can be seen, the two histograms are orders of magnitude
-    different in terms of frequency.}
-    \label{fig:hists}
-\end{figure}
-Each row and column in the graphs represents a loci on the chromosome,
-the next row (column) represents the adjacent loci on the same chromosome,
-thus the graph cannot be scrambled, that is, it is constructed as a stack
-of interaction intensities of a locus with all other loci on the chromosome.
-You cannot just swap two rows in the graph and have the same information since
-the order is important. The only valid case is when last rows are removed 
-and stacked on top of the graph.
-
-Taking a logarithm can be very useful in this case. As can be viewed in Figures
-\ref{fig:all_hists01} and \ref{fig:all_hists_deconvoluted01}, you can see that the data for 
-all chromosomes look normal.
-\begin{landscape}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1.5\textwidth]{figures/all_hists01.png}
-    \caption{The histogram of the logarithm of the data for all 23
-            chromosomes. The data looks normal now.}
-    \label{fig:all_hists01}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1.5\textwidth]{figures/all_hists_deconvoluted01.png}
-    \caption{The histogram of the deconvoluted  data in Figure 
-            \ref{fig:all_hists01}. }
-    \label{fig:all_hists_deconvoluted01}
-\end{figure}
-\end{landscape}
-
-We decided to lock our data set on \href{http://sysbio.rnet.missouri.edu/bdm_download}{this}
-dataset, since it includes Hi-C data for both normal test cells and 3 various cancerous
-cells. This allows for the sort of comparison we are looking for in this study.
-
-Cleaning the data requires some step that I'm not familiar yet. For example a normalized
-Hi-C heatmap for chromosome 1 should look like something like \ref{fig:normalized_heatmap},
-which can be found 
-\href{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}{here},
-but what I have managed to get from raw data is \ref{fig:my_result}, which clearly is
-not normalized.
-\begin{figure}[H]
-    \centering
-        \begin{subfigure}[b]{.4\textwidth}
-            \includegraphics[width=\textwidth]{figures/normalized_heatmap.png}
-            \caption{}
-            \label{fig:normalized_heatmap}
-        \end{subfigure}
-        \begin{subfigure}[b]{.4\textwidth}
-            \includegraphics[width=\textwidth]{figures/my_result.png}
-            \caption{}
-            \label{fig:my_result}
-        \end{subfigure}
-    \caption{As can be seen, \ref{fig:my_result} is not
-                as smooth as \ref{fig:normalized_heatmap}.
-                The black area in \ref{fig:my_result} account for 
-                19 rows and columns, which is
-                exactly the difference between the number of columns 
-                in \ref{fig:my_result} and \ref{fig:normalized_heatmap}.
-                }
-    \label{fig:heatmap_comparison}
-\end{figure}
-
-Based on \cite{wang2013properties}, two normalization methods can be 
-implemented on a contact matrix. The first of is Sequential Component 
-Normalization (SCN \cite{cournac2012normalization})
-and the other is simple Pearson's correlation.
-
-In SCN, each column of the contact matrix is divied by its norm, then
-its rows are divided by theirs norms. This process continues until the 
-contact matrix is symmetric again.
-
-In Pearson's correlation, a matrix $C$ is produced where $C_{ij}$
-is the pearson correlation of rows i and j.
-
-I have come up with what I call the \textit{pyramid algorithm}
-where I simply apply a pyramid down and then pyramic up
-on contact matrices to fill the empty spaces between. 
-This algorithm is readily available
-in OpenCV \footnote{www.opencv.org}.
-
-The results of the normalizations on chrmosome 1 of a normal
-cell is presented in Figure \ref{fig:normalizations}.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}[b]{.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/original_cleaned.png}
-        \caption{}
-        \label{fig:original_cleaned}
-    \end{subfigure}
-    \begin{subfigure}[b]{.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/pearson.png}
-        \caption{}
-        \label{fig:pearson}
-    \end{subfigure}
-    \begin{subfigure}[b]{.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/scn.png}
-        \caption{}
-        \label{fig:scn}
-    \end{subfigure}
-    \begin{subfigure}[b]{.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/scn+pearson.png}
-        \caption{}
-        \label{fig:scn+pearson}
-    \end{subfigure}
-    \begin{subfigure}[b]{.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/pearson+scn.png}
-        \caption{}
-        \label{fig:pearson+scn}
-    \end{subfigure}
-    \begin{subfigure}[b]{.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/pyr.png}
-        \caption{}
-        \label{fig:pyr}
-    \end{subfigure}
-\caption{Results of different normalizing methods: 
-    \ref{fig:original_cleaned} is the original matrix of \ref{fig:my_result}
-    with the 19 empty rows and columns removed.
-    \ref{fig:pearson} demonstrates the result of applying pearson normalization
-    to the \ref{fig:original_cleaned}.
-    In the same manner \ref{fig:scn} demonstrates the 
-    result of applying scn to \ref{fig:original_cleaned}.
-    \ref{fig:scn+pearson} shows the result of applying pearson to 
-    \ref{fig:scn} and \ref{fig:pearson+scn} illustrates
-    result of applying scn to \ref{fig:pearson}.
-    \ref{fig:pyr} is the result of applying my pyramid method to the image
-    which makes it somehow smooth and as I will describe later, will
-    significantly improve histogram of logarithm matrix.
-    }
-    \label{fig:normalizations}
-\end{figure}
-
-Figure \ref{fig:pearson_hist} illustrates the result of histograms of
-logarithms of figures that result from pearson normalization or chromosomes
-1 through 22 and chromosome X (the last one).
-
-Figure \ref{fig:pyr_hist_1mb} illustrates the result of histograms of
-logarithms of figures that result from applying pyramid normalization
-on the contact matrices of chromosomes
-1 through 22 and chromosome X (the last one).
-\begin{landscape}
-    \begin{figure}[H]
-        \centering
-        \includegraphics[width=1.5\textwidth]{figures/pearson_hist.png}
-        \caption{}
-        \label{fig:pearson_hist}
-    \end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1.5\textwidth]{figures/pyr_hist_1mb.png}
-    \caption{}
-    \label{fig:pyr_hist_1mb}
-\end{figure}
-\end{landscape}
-
-\subsection*{ALL and MIT cell comparison}
-One idea is the vary the threshold limits on the two indices to 
-find the optimal set of thresholds $(t_{ALL}, t_{MIT})$, where 
-the difference between the two pixels are minimum. The remaining
-pixels that are still different are the ones that are definitely
-correct. In this case, the objective function should be properly
-penalized in order to prevent the thresholds from getting too
-high or too low.
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}[b]{.45\textwidth} 
-        \includegraphics[width=\textwidth]{figures/ALL_60per_thresh.png}
-        \caption{}
-        \label{fig:all_thresh}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/MIT_60per_thresh.png}
-        \caption{}
-        \label{fig:mit_thresh}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/ALL_MIT_common.png}
-        \caption{}
-        \label{fig:all_mit_common}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/ALL_MIT_diff.png}
-        \caption{}
-        \label{fig:all_mit_diff}
-    \end{subfigure}
-    \caption{\ref{fig:all_thresh} is HiC contact matrix of 
-             chromosome 14 of ALL cell and
-             \ref{fig:mit_thresh} is the contact matrix of
-             the same chromosome in MIT cells. 
-             Both matrices are thresholded based on their 60th
-             percentile. \ref{fig:all_mit_common} is the common pixels
-             and \ref{fig:all_mit_diff} is the pixels where they 
-             are different.}
-\end{figure}
-\input{../scripts/logs/2018-01-31.log}
-\bibliography{lit}
-\bibliographystyle{unsrt}
 \end{document}

### 2018-03-08 papers/temp/run.sh

@@ -1,0 +1,4 @@
+pdflatex $1
+#bibtex basics.aux
+#pdflatex basics.tex
+#pdfllatex basics.tex

### 2018-03-08 utility.py

@@ -235,7 +235,7 @@ def showImages(imageList, rows, color_bar=False, titles=None):
     cols = (len(imageList) + rows - 1) / rows
     print "Number of columnts:", cols
     fig, axes = plt.subplots(nrows=rows, ncols=cols)
-    plt.subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=0.01, hspace=.3)
+    plt.subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=0.03, hspace=.3)
     count = 0
     for image in imageList:
         if rows * cols == 1:
@@ -251,6 +251,7 @@ def showImages(imageList, rows, color_bar=False, titles=None):
             ax.title.set_text(titles[count])
         count += 1
     plt.show()
+
 def cvShowImages(imageList):
     count = 1
     for image in imageList:

### 2018-03-09 papers/presentation.tex
improved

\documentclass{beamer}
\usepackage{apacite}
\usepackage{caption}
\usepackage[font=small, labelfont=bf]{subcaption}
\usepackage{textpos}
\usetheme{Darmstadt}
\usepackage{graphicx}
\usepackage{float}
%packages for definitions%%%%%%%%%%%%%%
\usepackage{blindtext}
\usepackage{scrextend}
\addtokomafont{labelinglabel}{\sffamily}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\AtBeginSection[]{
    \begin{frame}
    \vfill
    \centering
    \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
        \usebeamerfont{title}\insertsectionhead\par%
    \end{beamercolorbox}
    \vfill
    \end{frame}
}
\title{Garaphlet Analysis for HiC data}
\author{Behnam Rasoolian}
\institute{Auburn University}
\definecolor{auburn_orange}{RGB}{221, 85, 12}
\definecolor{auburn_blue}{RGB}{3, 36, 77}
\date{}
\begin{document}
\frame{\titlepage}
%\addtobeamertemplate{frametitle}{}{%
%    \begin{textblock*}{100mm}(.8\textwidth,-1.65cm)
%        \includegraphics[height=1.65cm,width=3cm]{figures/auburn_logo.jpeg}
%    \end{textblock*}}
\section{Biological Background}
\begin{frame}[t]
    \frametitle{Purpose of this research}
    \framesubtitle{Introduction}
    \begin{columns}
        \begin{column}{.5\textwidth}
            \begin{itemize}
                \item In this research we plan to find dissimilarities 
                    between normal cells and cancerous cells.
                \item Ideally, it is desirable to compare \textbf{3D confomation}
                    of genomes in order to make such comparisons.
            \end{itemize}
        \end{column}
        \begin{column}[c]{.5\textwidth}
            \begin{figure}
                \includegraphics[width=.6\textwidth]{figures/chromosome_3d_structure.png}
                \caption*{ \cite{lieberman2009comprehensive}}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Purpose of this research}
    \framesubtitle{Challenges}
        \begin{columns}
            \begin{column}[c]{.6\textwidth}
                \begin{itemize}
                        \item We still don't have enough information  
                            regarding the exact configuration
                        of a genome inside nucleus.
                        \item However, we can map interactions  in an
                        \textit{HiC contact map} ($C$).
                    \item Rows and columns signify genome fragments.
                    \item $C_{ij} = $ Number/strength of interactions detected between
                        fragment $i$ and $j$.
                \end{itemize}                                                                                 
            \end{column}
            \begin{column}{.4\textwidth}
                \begin{figure}
                    \centering
                    \includegraphics[width=\textwidth]{figures/original_contact_map_chr14.png}
                    \caption*{ \cite{lieberman2009comprehensive}}
                \end{figure}
            \end{column}
        \end{columns}
\end{frame}  
\begin{frame}
    \frametitle{Preliminaries}
    \framesubtitle{What is 3D conformation?}
    If you unfold the DNA inside one of your cells, it would measure
    2 meters end to end. How is it folded up withing a nucleus which
    is only 6 micorns wide?
    \begin{figure}
        \includegraphics[width=.7\textwidth]{figures/loops.png}
        \caption*{ \cite{rao20143d}}
    \end{figure}
\end{frame}
\begin{frame}
    \frametitle{Preliminaries}
    \framesubtitle{Terminology \cite{wang2013properties}}
    \begin{columns}
        \begin{column}{1.15\textwidth}
     \fontsize{10}{10}\selectfont{
         \begin{itemize}
             \item \textbf{Nucleotide}:  The monomer units that comprise DNAs. There
        are 4 types of nucleotides: (C, G, A, and T)

        \item \textbf{Base}: Each pair of nucleotides in the DNA are called
        a base.
        \\A kilo-base resolution is a resolution that
        corresponds to 1000 pairs of nucleotides in DNA.

        \item \textbf{Nucleosome}: A basic unit 
        consisting of 145-147 bases wrapped around a
        protein complex.

        \item \textbf{Chromatin Fiber}: Tens of nucleosomes are
        further collapsed into a larger dense structural unit
        of several kilobase (Kb) pairs.

        \item \textbf{Locus}: Multiple chromatin fibers form a large module of megabase pairs 
            (Mb) DNA, which may be referred to as \textit{domains, globules, gene
                 loci, or chromatin clusters} in different contexts.

        \item \textbf{Chromosome}: A number of loci then fold into a large
        independent physical structure, chromosome. 
         \end{itemize} }
        \end{column}
    \end{columns}
\end{frame}
\begin{frame}
    \frametitle{HiC Method}
    \framesubtitle{Procedure}
    \begin{columns}
        \begin{column}{1.1\textwidth}
            \begin{enumerate}
                \item Freeze the DNA in place.
                \item Cut the genome in tiny pieces.
                    Mark the ends using Biotin, and glue them together into
                    diffused pieces of DNA. These diffused pieces is made
                    up of two bits of the genome that are spatial neighbors.
                \item Using DNA sequencing, the two parts of the 
                    diffused DNA are identified and a dataset is created
                    where each cell corresponds to a pair.
            \end{enumerate}
        \end{column}
    \end{columns}
\end{frame}
\begin{frame}
    \frametitle{HiC Method}
    \framesubtitle{Illustration}
    \begin{figure}
        \centering
        \includegraphics[width=1.1\textwidth]{figures/hic_process.png}
        \caption*{ \cite{lieberman2009comprehensive}}
    \end{figure}
\end{frame}

\begin{frame}
    \frametitle{HiC Method}
    \framesubtitle{Contact Maps}
    \begin{columns}
        \begin{column}{.5\textwidth}
            \begin{itemize}
                \item The whole genome is then divided into sections of certain length (i.e. 500kB or 1MB)
                    and interactions are aggregated over them.
                \item Contact maps can be used to develop both inter- and 
                    intra-chromosomal interaction matrices.

            \end{itemize}
        \end{column}
        \begin{column}{.5\textwidth}
             \begin{figure}[H]
                \centering
                \includegraphics[width=\textwidth]{figures/grand_scheme_of_things.png}
                \caption*{}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

\frame{
    \frametitle{HiC Data: An Overal Picture}
     \begin{figure}[H]
        \centering
        \includegraphics[width=.8\textwidth]{figures/grand_scheme_of_things.png}
        \caption*{}
    \end{figure}

}

\frame {
    \begin{figure}
        \centering
        \includegraphics[width=.8\textwidth, height=.82\textheight]{figures/normal-b-cell-all-heatmaps.jpeg}
        \caption*{\cite{wang2013properties}}
    \end{figure}

}

\section{Strategies}
\begin{frame}
    \frametitle{Graphlets}
    \framesubtitle{Definitions}
    Graphlet comparison, introduced by \citeA{prvzulj2007biological},
    is a novel method used to compare large networks in order to
    find local similarities in them.
    \begin{itemize}
        \item \textbf{Fragment:} A connected subgraph.
        \item \textbf{Motifs:} Fragments that occur with a frequency much higher than
            that occuring in a randomly generated graph.
        \item \textbf{Graphlets:} An arbitrary, induced fragment.
        An edge is the only two-node graphlet.
        \item \textbf{Induced graphs:} Given a graph $G(V, E)$ and $S \subseteq V$,
            then $G'(S, E')$
            is a graphlet iff $E' = \{(u, v) | u, v \in V \text{ and } 
            (u, v) \in E \rightarrow (u, v) \in E'\}$
        \item \textbf{Orbits:} Set of all nodes in a graphlet that can be
            swapped with each other while not changing the graph.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Graphlets}
    \begin{figure}
        \centering
        \includegraphics[scale=.4]{graphlets.png}
        \caption*{All 30 undirected two- to five-node
        graphlets with 73 orbits \cite{prvzulj2007biological}}
    \end{figure}
\end{frame}
\begin{frame}
    \frametitle{Graphlets}
    \framesubtitle{Applications}
    \textbf{\citeA{milenkoviae2008uncovering}:}

    \textit{Signature vector:} A 73-dimensional vector
    $\mathbf{s}^T
    = [s_0, s_2, ..., s_{72}]$ where $s_i$ denotes the number of nodes in
    the network that are part of an orbit $i$.

    \textit{Important Result}: Proteins with similar surroundings perform
    similar functions.
    \begin{figure}[H]
        \centering
        \includegraphics[width=\textwidth]{figures/signature-comparison.png}
        \caption*{\cite{milenkoviae2008uncovering}}
    \end{figure}
\end{frame}

\begin{frame}
    \frametitle{Introduction}
    \textbf{\citeA{milenkovic2010cancer}}:

    Investigate cancer-causing genes to find similarities in their signatures. 
    \begin{enumerate}
        \item Cluster the genes based on \textit{signature similarity} criteria.
            Some clusters contain a lot of cancerous genes.

        \item Predict the cancer-relatedness of a protein $i$ using
            an enrichment criteria $\frac{k}{|C_i|}$ \\
            \begin{itemize}
                \item $C_i$ : the cluster where protein $i$ belongs\\
                \item $k$ : the number of cancer-causing proteins in $C_i$ \\
                \item $|C_i|$ : the size of $C_i$
            \end{itemize}
    \end{enumerate}
\end{frame}

\frame {
    \frametitle{Stage I: Thresholding}
    For thresholding, I use \textit{local thresholding} methods.
    \begin{enumerate}
        \item Create a zero matrix with the same size as the contact 
            map (M)
        \item Slide a kernel through each pixel
        \item If the pixel $(i, j)$  satisfies a particular condition
            the set $A[i, j]$.
    \end{enumerate}
    \bigskip
    Conditions that I considered:
    \begin{enumerate}
        \item If the pixel is local maximum with respect to the pixels
            that fall in the kernel \\
            $A_{ij} > A_{i',j'} 
            \hspace{2cm}  (i', j') \in \{i-k, i+k\}\times \{j-k, j+k\}$
        \item If the pixel value is larger that some standard deviation
            from the mean of the values that fall inside the kernel.
            $A_{ij} > mean(A_{i',j'}) + std(A_{i',j'})$ \\
    \end{enumerate}
}

\frame {
    \frametitle{Kernels}
    \begin{figure}[H]
        \centering
        \includegraphics[width=.9\textwidth]{figures/kernels.png}
        \caption*{}
    \end{figure}
}

\frame {
    \frametitle { Extracting graphlets }
    \begin{enumerate}
        \item I used the \texttt{orca} library in \texttt{R} programming 
        language.
        \item For each loci, a \textit{signature vector} of length 73 is 
        created.
        \item For each chromosome, an $N_c \times 73$, matrix is returned.
        where $N_c$ is the number of loci in chromosome $c$.
    \end{enumerate}
}

\frame {
    \frametitle { Finding distance between loci }
    In order to see how different two loci are in 
    terms of local neighborhood, we need to compare
    their corresponding \textit{signature values}.
    The distance measure proposed by \citeA{prvzulj2007biological}:

    \begin{equation}
        d_i = w_i \times \frac{log(S_i+1) - log(S'_i+1)}{log(max(S_i, S'_i) + 2)}
    \end{equation}
    The distance between $S$ and $S'$ can be calculated as follows:
    \begin{equation}
        D = \sum_{0}^{72}{d_i^2}
    \end{equation}
}

\frame {
    \frametitle{loci-loci distances between cell lines}
    I calculated loci-loci distance between cell lines using the formula
    above:
    \begin{figure}[H]
        \centering
        \includegraphics[width=.6\textwidth]{figures/loci_wise_distance.png}
        \caption*{\small {$A_{ij}$ in matrices above denotes distance between loci
        $i$ in row cell line and loci $j$ in the column cell line.} }
    \end{figure}
}

\frame {
    \frametitle{Loci-loci distances}
    \begin{figure}[H]
        \centering
        \includegraphics[width=\textwidth]{figures/cross_chromosomal_signature_distance.png}
        \caption*{}
    \end{figure}
}

\frame {
    \frametitle{Loci-loci distances}
    \begin{figure}[H]
        \centering
        \includegraphics[width=\textwidth]{figures/cross_chromosomal_signature_distance_separated.png}
        \caption*{cross-chromosomal signature distance with 1 standard deviation error bars}
    \end{figure}
}

\frame {
    \frametitle{Orbit correlations}
    \begin{figure}[H]
        \centering
        \includegraphics[width=\textwidth]{figures/orbit_wise_correlation_chr1.png}
        \caption*{\small {$A_{ij}$ in matrices above denotes correlation between 
        orbit $i$ in row cell line and orbit $j$ in the column cell line.} }
    \end{figure}
}

\begin{frame}[allowframebreaks]
    \frametitle{References}
    \bibliographystyle{apacite}
    \bibliography{lit}
\end{frame}

\end{document}

### 2018-03-09 papers/presentation_2018_03_08.tex
improved

--- 2018-03-09 papers/presentation.tex
@@
         \begin{column}{.5\textwidth}
-             \begin{figure}[H]
+            \begin{figure}
                 \centering
-                \includegraphics[width=\textwidth]{figures/grand_scheme_of_things.png}
-                \caption*{}
+                \includegraphics[width=.9\textwidth]{figures/normal-b-cell-all-heatmaps.jpeg}
+                \caption*{\cite{wang2013properties}}
             \end{figure}
@@
 \end{frame}
-
-\frame{
-    \frametitle{HiC Data: An Overal Picture}
-     \begin{figure}[H]
-        \centering
-        \includegraphics[width=.8\textwidth]{figures/grand_scheme_of_things.png}
-        \caption*{}
-    \end{figure}
-
-}
-
-\frame {
-    \begin{figure}
-        \centering
-        \includegraphics[width=.8\textwidth, height=.82\textheight]{figures/normal-b-cell-all-heatmaps.jpeg}
-        \caption*{\cite{wang2013properties}}
-    \end{figure}
-
-}
-
 \section{Strategies}
@@
 \end{frame}
-
 \begin{frame}
@@
 \end{frame}
+\begin{frame}
+    \frametitle{Graphlets}
+    \framesubtitle{Challenges}
+    \begin{enumerate}
+        \item HiC contact maps are noisy. How do we de-noise them?
+        \item Current applications of graphlets were on unweighted
+            graphs, while HiC contact maps are weighted.
+    \end{enumerate}
+\end{frame}
 
-\frame {
-    \frametitle{Stage I: Thresholding}
-    For thresholding, I use \textit{local thresholding} methods.
-    \begin{enumerate}
-        \item Create a zero matrix with the same size as the contact 
-            map (M)
-        \item Slide a kernel through each pixel
-        \item If the pixel $(i, j)$  satisfies a particular condition
-            the set $A[i, j]$.
-    \end{enumerate}
-    \bigskip
-    Conditions that I considered:
-    \begin{enumerate}
-        \item If the pixel is local maximum with respect to the pixels
-            that fall in the kernel \\
-            $A_{ij} > A_{i',j'} 
-            \hspace{2cm}  (i', j') \in \{i-k, i+k\}\times \{j-k, j+k\}$
-        \item If the pixel value is larger that some standard deviation
-            from the mean of the values that fall inside the kernel.
-            $A_{ij} > mean(A_{i',j'}) + std(A_{i',j'})$ \\
-    \end{enumerate}
-}
-
-\frame {
-    \frametitle{Kernels}
+\begin{frame}
+    \frametitle{Balanced Network Deconvolution}
+    \framesubtitle{Introduction}
+    Proposed by \citeA{feizi2013network}, Balanced Network Deconvolution, is 
+    a method that can be used to remove \textit{indirect effects} from a graph.
+    \begin{figure}
+        \centering
+        \includegraphics[width=\textwidth]{figures/nd.png}
+        \caption*{ \cite{feizi2013network}}
+    \end{figure}
+\end{frame}
+\begin{frame}
+    \frametitle{Balanced Network Deconvolution}
+    \framesubtitle{Details}
+    They assume that:
+    \begin{equation}
+        \label{indirect_effects}
+        G_{obs} = G_{dir} + G_{dir}^2 + G_{dir} + ...
+    \end{equation}
+    They assume also that both $G_{obs}$ and $G_{dir}$ can be 
+    eigen-decomposed and they have the same eigen-vectors:
+    \begin{equation}
+        G_{dir} = X \Sigma_{dir} X^T
+    \end{equation}
+    \begin{equation}
+        G_{obs} = X \Sigma_{obs} X^T
+    \end{equation}
+    \begin{equation}
+        G_{obs} = X \Sigma_{obs} X^T = X ( \Sigma_{dir} + \Sigma_{dir}^2 + ...) X^T
+    \end{equation}
+\end{frame}
+\begin{frame}
+    \frametitle{Balanced Network Deconvolution}
+    \framesubtitle{Details}
+    They also assume that eigen-values of the direct network are all
+    between -1 and 1, i.e. 
+    \begin{equation}
+        -1 < \lambda^{dir}_i < 1 \quad \forall 1 \le i \le n
+    \end{equation}
+    \begin{equation}
+        \Sigma_{obs} = \Sigma_{dir} + \Sigma_{dir}^2 + ...
+    \end{equation}
+    \begin{equation}
+        \lambda_i^{obs} = \sum_{j=1}^{\infty} \lambda^{dir}_{ij} \quad\quad \forall i = 1 ... n
+    \end{equation}
+    \begin{equation}
+        \lambda_i^{obs} = \frac{\lambda_i^{dir}}{1 - \lambda_i^{dir}}
+    \end{equation}
+    \begin{equation}
+       \lambda_i^{dir} = \frac{\lambda_i^{obs}}{1 + \lambda_i^{obs}} 
+    \end{equation}
+\end{frame}
+\begin{frame}
+    \frametitle{Statistical Parametric Network (SPN)}
+    Developed by \citeA{ginestet2011statistical}.
+    \begin{figure}
+        \centering
+        \includegraphics[width=.5\textwidth]{figures/thresholded_adjacency.png}
+        \caption*{An study of neuron connectivity
+            networks among 43 subjects for 4 different memory tasks 
+            (0-back, 1-back, 2-back and 3-back), and the
+            resulting thresholded networks \cite{ginestet2011statistical}}
+        \label{fig:thresholded_adjacency}
+    \end{figure}
+\end{frame}
+\section{Results Thus Far}
+\begin{frame}
+    \frametitle{Histogram of frequencies in HiC}
     \begin{figure}[H]
         \centering
-        \includegraphics[width=.9\textwidth]{figures/kernels.png}
-        \caption*{}
+        \begin{subfigure}[b]{.45\textwidth} 
+            \includegraphics[width=\textwidth]{figures/hist01.png}
+            \caption{Interval $[0, 0.1]$}
+            \label{fig:hist01}
+        \end{subfigure}
+        \begin{subfigure}[b]{.45\textwidth}
+            \includegraphics[width=\textwidth]{figures/hist02.png}
+            \caption{Interval $[0.1, 1]$}
+            \label{fig:hist02}
+        \end{subfigure}
+        \caption{\ref{fig:hist01} is a histogram of intensities from
+        chromosome 1 
+        As can be seen, the two histograms are orders of magnitude
+        different in terms of frequency.}
+        \label{fig:hists}
     \end{figure}
-}
-
-\frame {
-    \frametitle { Extracting graphlets }
-    \begin{enumerate}
-        \item I used the \texttt{orca} library in \texttt{R} programming 
-        language.
-        \item For each loci, a \textit{signature vector} of length 73 is 
-        created.
-        \item For each chromosome, an $N_c \times 73$, matrix is returned.
-        where $N_c$ is the number of loci in chromosome $c$.
-    \end{enumerate}
-}
-
-\frame {
-    \frametitle { Finding distance between loci }
-    In order to see how different two loci are in 
-    terms of local neighborhood, we need to compare
-    their corresponding \textit{signature values}.
-    The distance measure proposed by \citeA{prvzulj2007biological}:
-
-    \begin{equation}
-        d_i = w_i \times \frac{log(S_i+1) - log(S'_i+1)}{log(max(S_i, S'_i) + 2)}
-    \end{equation}
-    The distance between $S$ and $S'$ can be calculated as follows:
-    \begin{equation}
-        D = \sum_{0}^{72}{d_i^2}
-    \end{equation}
-}
-
-\frame {
-    \frametitle{loci-loci distances between cell lines}
-    I calculated loci-loci distance between cell lines using the formula
-    above:
+\end{frame}
+\begin{frame}
+    \frametitle{Histogram of logarithm}
     \begin{figure}[H]
         \centering
-        \includegraphics[width=.6\textwidth]{figures/loci_wise_distance.png}
-        \caption*{\small {$A_{ij}$ in matrices above denotes distance between loci
-        $i$ in row cell line and loci $j$ in the column cell line.} }
+        \includegraphics[width=1.05\textwidth]{figures/pyr_hist_1mb.png}
+        \caption*{}
+        \label{fig:pyr_hist_1mb}
     \end{figure}
-}
-
-\frame {
-    \frametitle{Loci-loci distances}
+\end{frame}
+\begin{frame}
+    \frametitle{Different Normalization methods}
     \begin{figure}[H]
         \centering
-        \includegraphics[width=\textwidth]{figures/cross_chromosomal_signature_distance.png}
+        \begin{subfigure}[b]{.25\textwidth}
+            \includegraphics[width=\textwidth]{figures/original_cleaned.png}
+            \caption{}
+            \label{fig:original_cleaned}
+        \end{subfigure}
+        \begin{subfigure}[b]{.25\textwidth}
+            \includegraphics[width=\textwidth]{figures/pearson.png}
+            \caption{}
+            \label{fig:pearson}
+        \end{subfigure}
+        \begin{subfigure}[b]{.25\textwidth}
+            \includegraphics[width=\textwidth]{figures/scn.png}
+            \caption{}
+            \label{fig:scn}
+        \end{subfigure}
+        \begin{subfigure}[b]{.25\textwidth}
+            \includegraphics[width=\textwidth]{figures/scn+pearson.png}
+            \caption{}
+            \label{fig:scn+pearson}
+        \end{subfigure}
+        \begin{subfigure}[b]{.25\textwidth}
+            \includegraphics[width=\textwidth]{figures/pearson+scn.png}
+            \caption{}
+            \label{fig:pearson+scn}
+        \end{subfigure}
+        \begin{subfigure}[b]{.25\textwidth}
+            \includegraphics[width=\textwidth]{figures/pyr.png}
+            \caption{}
+            \label{fig:pyr}
+        \end{subfigure}
         \caption*{}
+        \label{fig:normalizations}
     \end{figure}
-}
-
-\frame {
-    \frametitle{Loci-loci distances}
-    \begin{figure}[H]
-        \centering
-        \includegraphics[width=\textwidth]{figures/cross_chromosomal_signature_distance_separated.png}
-        \caption*{cross-chromosomal signature distance with 1 standard deviation error bars}
-    \end{figure}
-}
-
-\frame {
-    \frametitle{Orbit correlations}
-    \begin{figure}[H]
-        \centering
-        \includegraphics[width=\textwidth]{figures/orbit_wise_correlation_chr1.png}
-        \caption*{\small {$A_{ij}$ in matrices above denotes correlation between 
-        orbit $i$ in row cell line and orbit $j$ in the column cell line.} }
-    \end{figure}
-}
-
+\end{frame}
 \begin{frame}[allowframebreaks]

### 2018-03-09 utility.py

@@ -187,6 +187,18 @@ def pearson(a, b=None):
     else:
         return pearson_sym(a)
 
+def row_wise_pearson(a, b):
+    n1, m1 = a.shape
+    n2, m2 = b.shape
+    n = np.min([n1, n2])
+    m = np.min([m1, m2])
+    a = a[:n, :m]
+    b = b[:n, :m]
+    counter2 = np.zeros(n)
+    for i in range(n):
+        counter2[i] = pearsonr(a[i, :], b[i, :])[0]
+    return counter2
+
 def setDiagonals(mat, depth, value):
     n, m  = mat.shape
     if n != m:
@@ -420,7 +432,7 @@ def graphlet_distance(g1, g2):
     out = np.linalg.norm(pairwise_distance, axis=1) 
     return out
 
-def graphlet_correlational_distance(g1, g2):
+def full_graphlet_distance(g1, g2):
     """
     -------------------------------------------------------
     Function
@@ -445,6 +457,33 @@ def graphlet_correlational_distance(g1, g2):
     for i in range(n1):
         for j in range(n2):
             out[i, j] = graphlet_distance(g1[i, :], g2[j, :])
+    return out
+
+def row_wise_graphlet_distance(g1, g2):
+    """
+    -------------------------------------------------------
+    Function
+    ------------------------------------------------------
+    Calculate correlation between two matrices of graphlets
+    -------------------------------------------------------
+    Inputs:
+    -------------------------------------------------------
+    - g1, g2 : N * O matrices
+    -------------------------------------------------------
+    Returns:
+    -------------------------------------------------------
+
+    - out: an N * N matrix where each cell 
+    out[i, j] is the graphlet DISSIMILARITY between
+    orbit i in g1 and orbit j in g2.
+    """
+    n1, o1 = g1.shape
+    n2, o2 = g2.shape
+    n = np.min([n1, n2])
+    o = np.min([o1, o2])
+    out = np.zeros(n)
+    for i in range(n):
+        out[i] = graphlet_distance(g1[i, :], g2[i, :])
     return out
 
 def pair_orbits(graphlets, chromosome, delimiter=','):
@@ -488,20 +527,16 @@ def get_mic_from_file(file_name, delimiter=','):
         f2.append(content[1])
         mic.append(float(content[2]))
     return f1, f2, mic
+
 def log(image):
     return np.where(out > 0, np.log(out), 0)
 
[…]

### 2018-03-09 utility.py
presentable versions

@@ -243,7 +243,7 @@ def scn(a, minDiff=1e-3, numIterations=1000):
 def gaussian_normalize(heatmap):
     return (heatmap - np.mean(heatmap) ) / np.std(heatmap)
 
-def showImages(imageList, rows, color_bar=False, titles=None):
+def showImages(imageList, rows, color_bar=False, titles=None, ax_labels=None):
     cols = (len(imageList) + rows - 1) / rows
     print "Number of columnts:", cols
     fig, axes = plt.subplots(nrows=rows, ncols=cols)
@@ -257,11 +257,16 @@ def showImages(imageList, rows, color_bar=False, titles=None):
         else:
             ax = axes[count // cols, count % cols]
         m = ax.imshow(image, cmap="RdBu_r", norm=colors.SymLogNorm(1))
-        if color_bar:
-            cb = fig.colorbar(m)
         if titles != None:
             ax.title.set_text(titles[count])
+        if ax_labels != None:
+            ax.set(xlabel=ax_labels[1][count], ylabel=ax_labels[0][count])
         count += 1
+    if color_bar:
+        from mpl_toolkits.axes_grid1 import make_axes_locatable
+        divider = make_axes_locatable(ax)
+        cax = divider.append_axes("right", size="2%", pad=0.05)
+        cb = fig.colorbar(m, cax=cax)
     plt.show()
 
 def cvShowImages(imageList):
@@ -609,7 +614,7 @@ def svd_reconstruct(mat, k, u='empty', sig='empty', v='empty'):
         b += sig[i] * np.outer(u[:, i], v[i, :])
     return b, u, sig, v
 
-def local_threshold(mat, k=1, method='max', t=1, params=None):
+def local_threshold(mat, k=1, method='max', t=1, params=None, ignore_zeros=True, symmetric=False):
     mat2 = np.zeros_like(mat)
     n, m = mat.shape
     if isinstance(k, tuple):
@@ -624,17 +629,24 @@ def local_threshold(mat, k=1, method='max', t=1, params=None):
     for i in range(0, n):
         i_low = np.max([i - k11, 0])
         i_high = np.min([i + k12+1, n])
-        for j in range(0, m):
-            j_low = np.max([j - k21, 0])
+        j_beg = 0
+        if symmetric:
+            j_beg = i
+        for j in range(j_beg, m-1):
+            j_low = np.max([j - k21, j_beg])
             j_high = np.min([j + k22+1, m])
[…]

### 2018-03-14 papers/manuscripts/manuscript.tex
added manuscripts

--- 2018-03-08 papers/basics.tex
@@
-\documentclass{article}
-\usepackage[top=1in, bottom=1.25in, left=1in, right=1in]{geometry}
+\documentclass[a4,center,fleqn]{NAR}
 \usepackage{hyperref}
@@
 \usepackage{caption}
-\usepackage[font=small, labelfont=bf]{subcaption}
-\usepackage{lscape} %landscape
-\renewcommand{\familydefault}{\sfdefault} %change font
 
 \begin{document}
-\doublespacing
-\setlength{\parindent}{0pt}
-\section{Resources}
-\textbf{Publications related to Hi-C:}
-\begin{enumerate}
-    \item \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2858594/}
-    \item \url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0058793 }
-    \item \url{http://nar.oxfordjournals.org/content/42/7/e52.full}
-    \item \url{http://bioinformatics.oxfordjournals.org/content/early/2015/12/31/bioinformatics.btv754.abstract?keytype=ref&ijkey=A97WhKqBiEIcuzd}
-    \item \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4417147/}
-    \item \url{http://www.pnas.org/content/112/47/E6456.full}
-    \item \url{http://www.pnas.org/content/113/12/E1663.full}
-\end{enumerate}
-\textbf{Hi-C Datasets:}
-\begin{enumerate}
-    \item Original Datasets: \url{https://bcm.app.box.com/v/aidenlab/folder/11234760671}
-    \item Including cancerous cells: \url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}
-    \item Chromosome3D project: \url{http://sysbio.rnet.missouri.edu/bdm_download/chromosome3d/}
-\end{enumerate}
-\textbf{Contact Matrix Analysis:}
-\begin{enumerate}
-    \item \url{https://omictools.com/contact-matrix-normalization-category}
-    \item \url{http://hifive.docs.taylorlab.org/en/latest/}
-\end{enumerate}
-
-\textbf{Labs working on 3D Human Genome:}
-
-\begin{enumerate}
-    \item \url{http://mirnylab.mit.edu}
-    \item \url{http://dostielab.biochem.mcgill.ca}
-    \item \url{http://www.aidenlab.org/}
-    \item \url{http://web.cmb.usc.edu/people/alber/index.htm}
-    \item \url{http://calla.rnet.missouri.edu/cheng/nsf_career.html}
-\end{enumerate}
-\textbf{Resources related to Graphlet:}
-
-\begin{enumerate}
-    \item \url{https://en.wikipedia.org/wiki/Graphlets}
-    \item \url{https://academic.oup.com/bioinformatics/article/23/2/e177/202080/Biological-network-comparison-using-graphlet}
-    \item \url{http://www0.cs.ucl.ac.uk/staff/N.Przulj/index.html}
-\end{enumerate}
-\section{Purpose of this research}
+\section{Abstract}
 
@@
 
-\section{Genetics and Genomics}
-\textbf{What is genetics?}
-studies heredity. Offspring resembles its parents becasue they
-inherit their \textit{genes}.\\
-\textbf{Gene}: Sets of instructions that determine the traits of an organism.
-A sequence of DNA. A DNA thread builds chromosomes.
-Each organism has a unique number of chromosomes:
-Humans: 46 chromosomes. You get 23 from your mother and 23 from your
-father.\\
-\textbf{Homologous chromosomes}: A set of two chromosomes consisting of genes
-that correspond to the same traits, one coming from mother and the 
-other coming from father. These corresponding genes are called
-\textit{alleles}. Alleles are either \textit{dominant} or \textit{
-    recessive}.\\
-\textbf{Phenotype vs. Genotype}: Phenotype is a visible physical trait that
-is caused partially by genes and partially environmental.
-These traits include eye of hair color, height etc.
-\textit{genotype} is the gense that correspond to a particular
-phenotype. 
-Their presence is necessary but not enough for the 
-existence of phenotype.
+\section{Introduction}
 
-\textbf{Homozygous vs. Heterozygous alleles}:
-There are 3 combinations of genotypes:
-tt, tT (or Tt) and TT. 
-If the two alleles are the same
-then the person is Homozygous (dominant or recessive)
-in the corresponding
-trait. Otherwise, the person is Heterozygous in that trait.
-
-\textbf{Nucleotide}:  The monomer units that comprise DNAs. There
- are 4 types of nucleotides: (C, G, A, and T)
-
-\textbf{DNA}: Macro-molecules that provide recipes for creating 
-proteins.
-
-\textbf{Gene Expression}:
-\url{https://en.wikipedia.org/wiki/Gene_expression} \\
-Authors of \cite{wang2013properties} provide good insight into structure a nucleus
-of a eukaryotic cell: \\
-\begin{displayquote}
-``The cell of a eukaryotic species forms a multi-granularity genome structure
-(e.g., nucleosome, chromatin fiber, chromatin cluster, chromosome,
-and genome) in order to compactly store a very long genomic 
-DNA sequence in its small nucleus. A nucleosome is a basic unit 
-consisting of 145-147 base pairs of DNA wrapped around a
-protein complex (histone octamer). Tens of nucleosomes are
-further collapsed into a larger dense structural unit
-– chromatin fiber - of several kilobase (Kb) pairs.
-Multiple chromatin fibers form a large module of megabase pairs 
-(Mb) DNA, which may be referred to as domains, globules, gene
-loci, or chromatin clusters in different contexts.
-A number of chromatin clusters then fold into a large
-independent physical structure - chromosome,
-which occupies a physical space in nucleus often
-being referred to as chromosome territory.
-One or more chromosomes interact to constitute the dynamic
-three-dimensional (3D) conformation of the entire genome of a cell.''
-\end{displayquote}
-
-The following is from this 
-\href{https://www.youtube.com/watch?v=dES-ozV65u4}{Youtube video}:
-\\\textbf{Base}: Each pair of nucleotides in the DNA are called
-a base.
-A kilo-base resolution is a resolution in which each cell in
-the matrix corresponds to 1000 pairs of nucleotides in DNA.
-If you unfold the DNA inside one of your cells, it would measure
-2 meters end to end. How is it folded up withing a nucleus which
-is only 6 micorns wide?
-\\[.1in]\textbf{Procedure:}
-\begin{enumerate}
-    \item Freeze the DNA in place.
-    \item Cut the genome in tiny pieces.
-        Mark the ends using Biotin, and glue them together into
-        diffused pieces of DNA. These diffused pieces is made
-        up of two bits of the genome that are spatial neighbors.
-    \item Using DNA sequencing, the two parts of the 
-        diffused DNA are identified and a dataset is created
-        where each cell corresponds to a pair.
-\end{enumerate}
-\textbf{Frequent types of folds:}
-\begin{enumerate}
-    \item \textbf{ Loop:}
-        \\When two parts of the genome that 
-        are far from each other sequentially are
-        attached.
-        \\The length is $~200Kb$.
-        \\Often seen that the gene that occures at
-        one of the ends of the loop is turned on.
-        \\A protein called CTCF is always present
-        at the loops. Of the four possible directions
-        that the two CTCF can take, in a loop, the
-        two CTCF alwas point to one another (towards
-        the loop).
-    \item \textbf{ Contact domains:}
-        \\Can happen in or out of a loop.
-        \\Typical length: $~200Kb$
-        \\Domains with same \textit{marks}
-        tend to be located in the same place 
-        inside the nucleus.
-    \item \textbf{ Nuclear sub-compartments:}
-        \\Spatial neighborhoods where domains
-        with the same \textit{flavor} are
-        present.
-\end{enumerate}
-Many of the folding principles that were present in 
-human cells were also present in mouse cells at 
-corresponding genomic positions.
-
-Speculation: Like genes, folds are preserved across species.
-
-each cell in the body has the same gene but different
-cell types have different 3D structure (folding types).
-
-\section{Graph-theoretic concepts}
-\subsection*{Definitions: (from \cite{Automorphisms})}
-\begin{figure}
-    \centering
-    \includegraphics[scale=.5]{graphlets.png}
-    \caption{Graphlets and Orbits}
-    \label{fig:graphletsAndOrbits}
-\end{figure}
-\begin{itemize}
-    \item \textbf{Fragment:} A connected subgraph.
-    \item \textbf{Motifs:} Fragments that occur with a frequency much higher than
-        that occuring in a randomly generated graph.
-    \item \textbf{Graphlets:} An arbitrary, induced fragment.
-An edge is the only two-node graphlet.
-    \item \textbf{Induced graphs:} Given a graph $G(V, E)$ and $S \subseteq V$, then $G'(S, E')$
-        is a graphlet iff $E' = \{(u, v) | u, v \in V \text{ and } 
-        (u, v) \in E \rightarrow (u, v) \in E'\}$
-    \item \textbf{Orbits:} Set of all nodes in a graphlet that can be
-        swapped with each other while not changing the graph.
-\end{itemize}
-\subsection*{Concepts}
-\begin{itemize}
-    \item \textbf{Global vs. local network comparison}:\\
-        Global is inappropriate for incomplete networks.
-
-    \item \textbf{Problem of Motifs:}
-        They don't take into account infrequent and average subnetworks.
-
-    \item \textbf{GDD: graphlet degree distribution}
-\end{itemize}
-\section{Literature Review}
-\subsection{Hi-C}
-
-Authors of \cite{trieu2015mogen} developed MOGEN.
-
-\subsection{Graphlets}
 Graphlet comparison is a novel method used to compare large networks in order to
@@
 how geometrically close their corresponding vectors are.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.5\textwidth]{figures/ordered_graphlets.png}
-    \caption{The five 2-and 3-node ordered graphlets and the corresponding 14
-    automorphism orbits. The ordering of the graphlet nodes within each
-    graphlet $G_i,\quad i \in \{1, ... , 5\}$ is represented by their colors: white nodes
-    $<$ gray nodes $<$ black nodes}
-    \label{fig:ordered_graphlets}
-\end{figure}
+\section{Materials and Methods}
+\subsection{Thresholding contact maps}
+In order to be able to extract graphlets, HiC contact maps should be modeled as
+unweighted graphs where the nodes represent the loci and an edge between two 
+nodes represent a \textit{significant} interaction between the loci the nodes
+represent.
 
-\subsection{Balanced Network Deconvolution and Residual Networks}
-Proposed by \cite{feizi2013network}. They developed a method that
-eliminated indirect effect from a weighted graph. Their method
-assumes that the observed graph $G_{obs}$ is a summation of its 
-direct graph $G_{dir}$ and some indirect terms as follows:
-\begin{equation}
-    \label{indirect_effects}
-    G_{obs} = G_{dir} + G_{dir}^2 + G_{dir} + ...
-\end{equation}
-They assume also that both $G_{obs}$ and $G_{dir}$ can be 
-eigen-decomposed and they have the same eigen-vectors, that is
-\begin{equation}
-    G_{obs} = X \Sigma_{obs} X^T
-\end{equation}
-where 
-\begin{equation}
-    \Sigma_{obs} = 
-    \begin{pmatrix}  
-        \lambda^{obs}_1 &   0            & \cdots    &    0 \\
-        0               &\lambda^{obs}_2 &           &      \\
-        \vdots          &                & \ddots    &      \\
-        0               &                &           & \lambda^{obs}_n
-    \end{pmatrix}
-\end{equation}
-and
-\begin{equation}
-    G_{dir} = X \Sigma_{dir} X^T
-\end{equation}
-where
-\begin{equation}
-    \Sigma_{dir} = 
-    \begin{pmatrix}  
-        \lambda^{dir}_1 &   0            & \cdots    &    0 \\
-        0               &\lambda^{dir}_2 &           &      \\
-        \vdots          &                & \ddots    &      \\
-        0               &                &           & \lambda^{dir}_n
-    \end{pmatrix}
-\end{equation}
-so
-\begin{equation}
-    G_{obs} = X \Sigma_{obs} X^T = X ( \Sigma_{dir} + \Sigma_{dir}^2 + ...) X^T
-\end{equation}
-They also assume that eigen-values of the direct network are all
-between -1 and 1, i.e. 
-\begin{equation}
-    -1 < \lambda^{dir}_i < 1 \quad \forall 1 \le i \le n
-\end{equation}
-Thus 
-\begin{equation}
-    \Sigma_{obs} = \Sigma_{dir} + \Sigma_{dir}^2 + ...
-\end{equation}
-\begin{equation}
-    \lambda_i^{obs} = \sum_{j=1}^{\infty} \lambda^{dir}_{ij} \quad\quad \forall i = 1 ... n
-\end{equation}
-\begin{equation}
-    \lambda_i^{obs} = \frac{\lambda_i^{dir}}{1 - \lambda_i^{dir}}
-\end{equation}
-\begin{equation}
-   \lambda_i^{dir} = \frac{\lambda_i^{obs}}{1 + \lambda_i^{obs}} 
-\end{equation}
+Thresholding is achieved by thresholding the contact maps. The result
+of the thresholding procedure would be a binary matrix which also can serve as
+an adjacency matrix for an unweighted, undirected graph. The graph can then be
+used for orbit extraction.
 
-\textbf{Source codes:} 
-\begin{itemize}
-    \item Python: \url{https://github.com/gidonro/Network-Deconvolution} 
-    \item Matlab: \url{http://compbio.mit.edu/nd/}
-\end{itemize}
+In order to go about the process of thresholding, it is necessary to make sure
+that both global and local features are maintained. We could consider 
+thresholding the contact maps by simply setting values above a fixed value to
+one and the rest to zero. However, in practice, this proved result in graphs
+that capture the local structure of the contact maps poorly. This is because
+intensities follow an exponential distribution with a mean close to zero and
+some very larges values that correspond t interactions along and close to 
+the main diagonal of the contact maps.
+Thus, picking relatively large numbers would result in ignoring interactions
+that are far from the main diagonal and picking small numbers will lead to
+capturing too many \textit{insignificant} interactions.
 
-Authors of \cite{sun2015improving} proposed ...
-\subsection{Weighted graph comparison}
-\url{https://www.cs.cmu.edu/~jingx/docs/DBreport.pdf}
+In order to threshold the matrix so that both global and local patterns are
+kept, we borrowed the concept of \textit{adaptive thresholding} from image 
+processing context. In this method, in order to be set, a pixel should have
+an intensity that is larger than the average of non-zero intensities in its
+\textit{neighborhood}. The neighborhood is defined by an sliding kernel 
+that passes through the contact map with a pixel at its middle at 
+each step.
 
-\url{https://en.wikipedia.org/wiki/Gromov%E2%80%93Hausdorff_convergence}
-
-Authors of \cite{soufiani2012graphlet} propose a graphlet
-decomposition method
-which considers situations where we observe an undirected
-weighted network, encoded by a symmetric adjacency matrix with integer entries and diagonal
-elements equal to zero. The term graphlet here is UNRELATED to the
-Przulj graphlet.
-
-Authors of \cite{ginestet2011statistical} developed Statistical Network (SPN) analysis
-where the choice of thresholding value is made by statistical inference.
-This method works within the framework of design of experiments where the same
-network can be extracted for different individuals under different treatments. The
-effect of those treatments can then be infered using this method.
-In \cite{ginestet2011statistical} for example, they studied neuron connectivity
-networks among 43 subjects for 4 different memory tasks (0-back, 1-back, 2-back and
-3-back), and obtained the following thresholded networks. The results of which can 
-be viewed in Figure \ref{fig:thresholded_adjacency}.
-
-Their method can be very usefull if a large population of information from the same
-chromosomes exist.
-\begin{figure}
-    \centering
-    \includegraphics[width=.5\textwidth]{figures/thresholded_adjacency.png}
-    \caption{}
-    \label{fig:thresholded_adjacency}
-\end{figure}
-
-Distance between two weighted graphs can be measured based on \cite{daneshpajouh2009metric}:\\
-$d(G_1, G_2) = |\displaystyle\sum_{w\in V_1} w -
-\displaystyle\sum_{v \in V_2} v|$
-
-Exhaustive enumeration of all graphlets being
-prohibitively expensive, \cite{shervashidze2009efficient} introduce two
-theoretically grounded speedup schemes, one
-based on sampling and the second one specifically
-designed for bounded degree graphs
-
-\section{Problems and Questions}
+\section{Resources}
+\textbf{Publications related to Hi-C:}
 \begin{enumerate}
-    \item Can we convert larger Hi-C data sets by combining data from 
-        several loci? This way we can create a DOE of different 
-        individuals.
-    \item How can we verify our results? Do we have any information on 
-        similarities that we already know exist?
-    \item how do we get inter-chromosomal graphs?
-        I was not able to find them.
-    \item Is there indirect depencecies in the Hi-graphs? How are they caused?
-    \item How to run the algorithms on such huge matrices?
-    \item What are random graph models?
-    \item As far as I get, graphlet distribution is a means of finding similarities
-        in graphs. What we are trying to do is to find dissimilarities. is it 
-        the right track to go?
+    \item \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2858594/}
+    \item \url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0058793 }
+    \item \url{http://nar.oxfordjournals.org/content/42/7/e52.full}
+    \item \url{http://bioinformatics.oxfordjournals.org/content/early/2015/12/31/bioinformatics.btv754.abstract?keytype=ref&ijkey=A97WhKqBiEIcuzd}
+    \item \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4417147/}
+    \item \url{http://www.pnas.org/content/112/47/E6456.full}
+    \item \url{http://www.pnas.org/content/113/12/E1663.full}
+\end{enumerate}
+\textbf{Hi-C Datasets:}
+\begin{enumerate}
+    \item Original Datasets: \url{https://bcm.app.box.com/v/aidenlab/folder/11234760671}
+    \item Including cancerous cells: \url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}
+    \item Chromosome3D project: \url{http://sysbio.rnet.missouri.edu/bdm_download/chromosome3d/}
+\end{enumerate}
+\textbf{Contact Matrix Analysis:}
+\begin{enumerate}
+    \item \url{https://omictools.com/contact-matrix-normalization-category}
+    \item \url{http://hifive.docs.taylorlab.org/en/latest/}
 \end{enumerate}
 
-\section{Experiments and Observations}
-I have changed the network deconvolution code where it deals
-with scaling factor. The rationale behind it was not clear to me
-so I replaced it with my own understanding of it which might not 
-be correct.
+\textbf{Labs working on 3D Human Genome:}
 
-The intensity values in each data set follows an exponential
-distribution, that is the majority of the intensities lie
-close to the minimum value while some intensities are absurdly
-large.
-Because of this, thresholding intensity values based on quantiles (percentiles)
-cannot be helpful since first and third quartiles are very close to each other
-but very far from the maximum value.
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}[b]{.45\textwidth} 
-        \includegraphics[width=\textwidth]{figures/hist01.png}
-        \caption{}
-        \label{fig:hist01}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/hist02.png}
-        \caption{}
-        \label{fig:hist02}
-    \end{subfigure}
-    \caption{\ref{fig:hist01} is a histogram of intensities form 
-    ``\texttt{chr1\_1mb\_matrix}'',
-    in the interval of $[0, 0.1]$ and bin size of $0.005$.
-    \ref{fig:hist02} is a histogram of the same data
-    but for interval of $[0.1, 1]$ and bin size of $0.01$.
-    As can be seen, the two histograms are orders of magnitude
-    different in terms of frequency.}
-    \label{fig:hists}
-\end{figure}
-Each row and column in the graphs represents a loci on the chromosome,
-the next row (column) represents the adjacent loci on the same chromosome,
-thus the graph cannot be scrambled, that is, it is constructed as a stack
-of interaction intensities of a locus with all other loci on the chromosome.
-You cannot just swap two rows in the graph and have the same information since
-the order is important. The only valid case is when last rows are removed 
-and stacked on top of the graph.
+\begin{enumerate}
+    \item \url{http://mirnylab.mit.edu}
+    \item \url{http://dostielab.biochem.mcgill.ca}
+    \item \url{http://www.aidenlab.org/}
+    \item \url{http://web.cmb.usc.edu/people/alber/index.htm}
+    \item \url{http://calla.rnet.missouri.edu/cheng/nsf_career.html}
+\end{enumerate}
+\textbf{Resources related to Graphlet:}
 
-Taking a logarithm can be very useful in this case. As can be viewed in Figures
-\ref{fig:all_hists01} and \ref{fig:all_hists_deconvoluted01}, you can see that the data for 
-all chromosomes look normal.
-\begin{landscape}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1.5\textwidth]{figures/all_hists01.png}
-    \caption{The histogram of the logarithm of the data for all 23
-            chromosomes. The data looks normal now.}
-    \label{fig:all_hists01}
-\end{figure}
+\begin{enumerate}
+    \item \url{https://en.wikipedia.org/wiki/Graphlets}
+    \item \url{https://academic.oup.com/bioinformatics/article/23/2/e177/202080/Biological-network-comparison-using-graphlet}
+    \item \url{http://www0.cs.ucl.ac.uk/staff/N.Przulj/index.html}
+\end{enumerate}
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1.5\textwidth]{figures/all_hists_deconvoluted01.png}
-    \caption{The histogram of the deconvoluted  data in Figure 
-            \ref{fig:all_hists01}. }
-    \label{fig:all_hists_deconvoluted01}
-\end{figure}
-\end{landscape}
-
-We decided to lock our data set on \href{http://sysbio.rnet.missouri.edu/bdm_download}{this}
-dataset, since it includes Hi-C data for both normal test cells and 3 various cancerous
-cells. This allows for the sort of comparison we are looking for in this study.
-
-Cleaning the data requires some step that I'm not familiar yet. For example a normalized
-Hi-C heatmap for chromosome 1 should look like something like \ref{fig:normalized_heatmap},
-which can be found 
-\href{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}{here},
-but what I have managed to get from raw data is \ref{fig:my_result}, which clearly is
-not normalized.
-\begin{figure}[H]
-    \centering
-        \begin{subfigure}[b]{.4\textwidth}
-            \includegraphics[width=\textwidth]{figures/normalized_heatmap.png}
-            \caption{}
-            \label{fig:normalized_heatmap}
-        \end{subfigure}
-        \begin{subfigure}[b]{.4\textwidth}
-            \includegraphics[width=\textwidth]{figures/my_result.png}
-            \caption{}
-            \label{fig:my_result}
-        \end{subfigure}
-    \caption{As can be seen, \ref{fig:my_result} is not
-                as smooth as \ref{fig:normalized_heatmap}.
-                The black area in \ref{fig:my_result} account for 
-                19 rows and columns, which is
-                exactly the difference between the number of columns 
-                in \ref{fig:my_result} and \ref{fig:normalized_heatmap}.
-                }
-    \label{fig:heatmap_comparison}
-\end{figure}
-
-Based on \cite{wang2013properties}, two normalization methods can be 
-implemented on a contact matrix. The first of is Sequential Component 
-Normalization (SCN \cite{cournac2012normalization})
-and the other is simple Pearson's correlation.
-
-In SCN, each column of the contact matrix is divied by its norm, then
-its rows are divided by theirs norms. This process continues until the 
-contact matrix is symmetric again.
-
-In Pearson's correlation, a matrix $C$ is produced where $C_{ij}$
-is the pearson correlation of rows i and j.
-
-I have come up with what I call the \textit{pyramid algorithm}
-where I simply apply a pyramid down and then pyramic up
-on contact matrices to fill the empty spaces between. 
-This algorithm is readily available
-in OpenCV \footnote{www.opencv.org}.
-
-The results of the normalizations on chrmosome 1 of a normal
-cell is presented in Figure \ref{fig:normalizations}.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}[b]{.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/original_cleaned.png}
-        \caption{}
-        \label{fig:original_cleaned}
-    \end{subfigure}
-    \begin{subfigure}[b]{.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/pearson.png}
-        \caption{}
-        \label{fig:pearson}
-    \end{subfigure}
-    \begin{subfigure}[b]{.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/scn.png}
-        \caption{}
-        \label{fig:scn}
-    \end{subfigure}
-    \begin{subfigure}[b]{.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/scn+pearson.png}
-        \caption{}
-        \label{fig:scn+pearson}
-    \end{subfigure}
-    \begin{subfigure}[b]{.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/pearson+scn.png}
-        \caption{}
-        \label{fig:pearson+scn}
-    \end{subfigure}
-    \begin{subfigure}[b]{.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/pyr.png}
-        \caption{}
-        \label{fig:pyr}
-    \end{subfigure}
-\caption{Results of different normalizing methods: 
-    \ref{fig:original_cleaned} is the original matrix of \ref{fig:my_result}
-    with the 19 empty rows and columns removed.
-    \ref{fig:pearson} demonstrates the result of applying pearson normalization
-    to the \ref{fig:original_cleaned}.
-    In the same manner \ref{fig:scn} demonstrates the 
-    result of applying scn to \ref{fig:original_cleaned}.
-    \ref{fig:scn+pearson} shows the result of applying pearson to 
-    \ref{fig:scn} and \ref{fig:pearson+scn} illustrates
-    result of applying scn to \ref{fig:pearson}.
-    \ref{fig:pyr} is the result of applying my pyramid method to the image
-    which makes it somehow smooth and as I will describe later, will
-    significantly improve histogram of logarithm matrix.
-    }
-    \label{fig:normalizations}
-\end{figure}
-
-Figure \ref{fig:pearson_hist} illustrates the result of histograms of
-logarithms of figures that result from pearson normalization or chromosomes
-1 through 22 and chromosome X (the last one).
-
-Figure \ref{fig:pyr_hist_1mb} illustrates the result of histograms of
-logarithms of figures that result from applying pyramid normalization
-on the contact matrices of chromosomes
-1 through 22 and chromosome X (the last one).
-\begin{landscape}
-    \begin{figure}[H]
-        \centering
-        \includegraphics[width=1.5\textwidth]{figures/pearson_hist.png}
-        \caption{}
-        \label{fig:pearson_hist}
-    \end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1.5\textwidth]{figures/pyr_hist_1mb.png}
-    \caption{}
-    \label{fig:pyr_hist_1mb}
-\end{figure}
-\end{landscape}
-
-\subsection*{ALL and MIT cell comparison}
-One idea is the vary the threshold limits on the two indices to 
-find the optimal set of thresholds $(t_{ALL}, t_{MIT})$, where 
-the difference between the two pixels are minimum. The remaining
-pixels that are still different are the ones that are definitely
-correct. In this case, the objective function should be properly
-penalized in order to prevent the thresholds from getting too
-high or too low.
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}[b]{.45\textwidth} 
-        \includegraphics[width=\textwidth]{figures/ALL_60per_thresh.png}
-        \caption{}
-        \label{fig:all_thresh}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/MIT_60per_thresh.png}
-        \caption{}
-        \label{fig:mit_thresh}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/ALL_MIT_common.png}
-        \caption{}
-        \label{fig:all_mit_common}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/ALL_MIT_diff.png}
-        \caption{}
-        \label{fig:all_mit_diff}
-    \end{subfigure}
-    \caption{\ref{fig:all_thresh} is HiC contact matrix of 
-             chromosome 14 of ALL cell and
-             \ref{fig:mit_thresh} is the contact matrix of
-             the same chromosome in MIT cells. 
-             Both matrices are thresholded based on their 60th
-             percentile. \ref{fig:all_mit_common} is the common pixels
-             and \ref{fig:all_mit_diff} is the pixels where they 
-             are different.}
-\end{figure}
-\input{../scripts/logs/2018-01-31.log}
 \bibliography{lit}

### 2018-03-14 papers/manuscripts/manuscript2.tex
added manuscripts

\documentclass[a4,center,fleqn]{NAR}

% Enter dates of publication
\copyrightyear{2008}
\pubdate{31 July 2009}
\pubyear{2009}
\jvolume{37}
\jissue{12}

%\articlesubtype{This is the article type (optional)}

\begin{document}

\title{A comparison between leukemic and non-leukemic cells using HiC
contacts map and graphlet approach.}

\author{%
Behnam Rasoolian\,$^{1,*}$,
Debswapna Bhattacharya\,$^{1}$
\footnote{Tel: +1 334 5212814; Email: bzr0014@auburn.edu}
}

\address{%
$^{1}$Department of Computer Science and Software
Engineering, Auburn University,
345 W Magnolia Ave, Auburn, AL 36849
}
% Affiliation must include:
% Department name, institution name, full road and district address,
% state, Zip or postal code, country

\history{%
Received ;
Revised ;
Accepted }

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}

\section{MATERIALS AND METHODS}

\subsection{Materials subsection one}

\subsubsection{Materials subsubsection one.}

\subsection{Materials subsection two}

\section{RESULTS}

\subsection{Results subsection one}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text.
% **************************************************************
% Keep this command to avoid text of first page running into the
% first page footnotes
\enlargethispage{-65.1pt}
% **************************************************************

\begin{table}[b]
\tableparts{%
\caption{This is a table caption}
\label{table:01}%
}{%
\begin{tabular*}{\columnwidth}{@{}lllll@{}}
\toprule
Col. head 1 & Col. head 2 & Col. head 3 & Col. head 4 & Col. head 5
\\
& (\%) & (s$^{-1}$) & (\%) & (s$^{-1}$)
\\
\colrule
Row 1 & Row 1 & Row 1 & -- & --
\\
Row 2 & Row 2 & Row 2 & Row 2 & Row 2
\\
\botrule
\end{tabular*}%
}
{This is a table footnote}
\end{table}

\subsection{Results subsection two}

Text.  Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text (see Table \ref{table:01}).

Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text (see Figure \ref{NAR-fig2}a).

Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

\begin{figure*}[t]
\begin{center}
\includegraphics{NAR-fig2.eps}
\end{center}
\caption{Caption for wide figure over two columns.
\textbf{(a)} Left figure.
\textbf{(b)} Right figure (see (a)).
}
\label{NAR-fig2}
\end{figure*}

\subsection{Results subsection three}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text.

\section{DISCUSSION}

\subsection{Discussion subsection one}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text.

\subsection{Discussion subsection two}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

\subsection{Discussion subsection three}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text.

\section{CONCLUSION}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text.

\section{ACKNOWLEDGEMENTS}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text.

\subsubsection{Conflict of interest statement.} None declared.
\newpage

\begin{thebibliography}{4}

% Format for article
\bibitem{1}
Author,A.B. and Author,C. (1992)
Article title.
\textit{Abbreviated Journal Name}, \textbf{5}, 300--330.

% Format for book
\bibitem{2}
Author,D., Author,E.F. and Author,G. (1995)
\textit{Book Title}.
Publisher Name, Publisher Address.

% Format for chapter in book
\bibitem{3}
Author,H. and Author,I. (2005)
Chapter title.
In
Editor,A. and Editor,B. (eds),
\textit{Book Title},
Publisher Name, Publisher Address,
pp.\ 60--80.

% Another article
\bibitem{4}
Author,Y. and Author,Z. (2002)
Article title.
\textit{Abbreviated Journal Name}, \textbf{53}, 500--520.

\end{thebibliography}

\end{document}

### 2018-03-14 papers/manuscripts/presentation.tex
added manuscripts

--- 2018-03-09 papers/presentation.tex
@@
 \frame {
+    \frametitle{Thresholding example}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[height=.8\textheight]{figures/thresholding_example.png}
+        \caption*{}
+    \end{figure}
+}
+
+\frame {
     \frametitle { Extracting graphlets }
@@
 
+\frame {
+    \frametitle { Extracting graphlets }
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=.9\textwidth]{figures/graphlet_extraction.png}
+        \caption*{}
+    \end{figure}
+}
 \frame {
@@
 
+\section{Loci Signature Comparison Among Cells}
+
 \frame {
-    \frametitle{loci-loci distances between cell lines}
+    \frametitle{Loci-loci distances between cell lines}
     I calculated loci-loci distance between cell lines using the formula
     above:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=.85\textwidth]{figures/graphlet_distance_extraction.png}
+        \caption*{}
+    \end{figure}
+}
+\frame{
+    \frametitle{Loci-loci distance between cell lines}
     \begin{figure}[H]
@@
 }
-
 \frame {
@@
 
+\section{Orbit Distribution correlation Comparison Among Cells}
+
 \frame {
     \frametitle{Orbit correlations}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/orbit_distribution_comparison.png}
+        \caption*{}
+    \end{figure}
+}
+
+\begin{frame}
+    \frametitle{Orbit distribution comparison among cells}
     \begin{figure}[H]
@@
         orbit $i$ in row cell line and orbit $j$ in the column cell line.} }
+    \end{figure}
+\end{frame}
+
+\frame {
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/graphlet_correlation_aggregation.png}
+        \caption*{}
+    \end{figure}
+}
+\frame {
+    \frametitle{Comparison of mean correlation among all orbits across the 23 chromosomes.}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/graphlet_correlation_comparison_chromosomes.png}
+    \end{figure}
+}
+
+\frame {
+    \frametitle{Comparison of mean correlation among all orbits across the 23 chromosomes.}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/graphlet_correlation_comparison_chromosomes_separated.png}
+    \end{figure}
+}
+
+\frame {
+    \frametitle{Comparison of mean correlation among all chromosomes across the 73 orbits.}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/graphlet_correlation_comparison_orbits.png}
+    \end{figure}
+}
+
+\frame {
+    \frametitle{Comparison of mean correlation among all chromosomes across the 73 orbits.}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/graphlet_correlation_comparison_orbits_separate.png}
+    \end{figure}
+}
+
+\section{Orbit Distribution MIC Comparison Among Cells}
+\frame {
+    \frametitle{About MIC}
+    A powerfull method that captures both functional and 
+    non-functional relationships.
+
+    \begin{equation}
+        MIC(X, Y) = \mathbb{KL}(p(X, Y), p(X)p(Y)
+    \end{equation}
+}
+\frame {
+    \frametitle{Comparison of mean MIC among all chromosomes across the 23 chromosomes.}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/graphlet_mic_comparison_chromosomes.png}
+    \end{figure}
+}
+
+\frame {
+    \frametitle{Comparison of mean MIC among all chromosomes across the 23 chromosomes.}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/graphlet_mic_comparison_chromosomes_separate.png}
+    \end{figure}
+}
+
+\frame {
+    \frametitle{Comparison of mean MIC among all chromosomes across the 73 orbits.}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/graphlet_mic_comparison_orbits.png}
+    \end{figure}
+}
+
+\frame {
+    \frametitle{Comparison of mean MIC among all chromosomes across the 73 orbits.}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/graphlet_mic_comparison_orbits_separate.png}
+    \end{figure}
+}
+
+\section{Correlation and MIC comparison}
+
+\frame {
+    \frametitle{Comparison of mean MIC among all chromosomes across the 73 orbits.}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/graphlet_correlation_mic_comparison_chromosomes.png}
+    \end{figure}
+}
+
+\frame {
+    \frametitle{Comparison of mean MIC among all chromosomes across the 73 orbits.}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/graphlet_correlation_mic_comparison_orbits.png}
+    \end{figure}
+}
+\section{Cancer Cell Comparison}
+\frame {
+    \frametitle{Cancer cell MIC comparison}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=\textwidth]{figures/graphlet_mic_comparison_orbits_cancer.png}
+        \caption*{}
+    \end{figure}
+}
+
+\frame {
+    \frametitle{Cancer cell correlation comparison}
+    \begin{figure}[H]
+        \centering
+        \begin{subfigure}[b]{\textwidth}
+            \centering
+            \includegraphics[width=.8\textwidth, height=.35\paperheight]{figures/graphlet_mic_comparison_orbits_cancer.png}
+        \end{subfigure}
+        \begin{subfigure}[b]{\textwidth}
+            \centering
+            \includegraphics[width=.8\textwidth, height=.35\paperheight]{figures/graphlet_correlation_comparison_orbits_cancer.png}
+        \end{subfigure}
+        \caption*{}
+    \end{figure}
+}
+
+\frame {
+    \frametitle{Cancer cell correlation comparison}
+    \begin{figure}[H]
+        \centering
+        \begin{subfigure}[b]{\textwidth}
+            \centering
+            \includegraphics[width=.8\textwidth, height=.35\paperheight]{figures/graphlet_mic_comparison_chromosomes_cancer.png}
+        \end{subfigure}
+        \begin{subfigure}[b]{\textwidth}
+            \centering
+            \includegraphics[width=.8\textwidth, height=.35\paperheight]{figures/graphlet_correlation_comparison_chromosomes_cancer.png}
+        \end{subfigure}
+        \caption*{}
     \end{figure}

### 2018-03-14 papers/run.sh

@@ -1,4 +1,0 @@
-pdflatex $1
-#bibtex basics.aux
-#pdflatex basics.tex
-#pdfllatex basics.tex

### 2018-03-14 utility.py

@@ -68,14 +68,63 @@ def pyrProcess(original):
     original = cv2.pyrUp(original)
     return scale(original)
 
-def scale(m):
-    min = np.min(m) + 1e-5
+def scale(m, epsilon=1e-5):
+    """
+    Function:
+    ---------
+    Takes a matrix and scales int so that all values
+    fall between epsilon and 1.
+
+    Parameters:
+    -----------
+    mat : ndarray(m, n) 
+        The input ndarray
+
+    epsilon: 
+        The lower bound for values. In some applicatons,
+        values of 0 will result in numerical problems so
+        epsilon is defaulted to zero to prevent such
+        problems.
+
+    delimiter: string
+        the delimiter that separates the cells in
+        each row.
+
+    Output:
+        n: The thresholded numpy ndarray
+    """
+    min = np.min(m) + epsilon
     max = np.max(m)
     n = (1. * m - min) / (max - min) 
     return n
 
 #used to be simple read
 def readMat(fileName, delimiter="\t", ignoreHeader=False, remove_blanks=False):
+    """
+    Function:
+    --------- 
+    Reads a file and parses it into a numpy ndarray
+
+    Parameters:
+    -----------
+    fileName
+
+    delimiter
+
+    ignoreHeader:
+        ignore the first line of the file. Used when the
+        columns have titles.
+
+    remove_blanks:
+        if True, calls 'removeBlankRowsAndColumns' to the
+        matrix so as to remove rows and column that 
+        cosist of all zero values.
+
+    Output:
+    ---------
+    observed
+
+    """
     print "file directory:", fileName
     if not os.path.isfile(fileName):
         print "File %s does not exist"%fileName
@@ -97,6 +146,17 @@ def readMat(fileName, delimiter="\t", ignoreHeader=False, remove_blanks=False):
     return observed
 
 def readYamlIntensities(filename, res, delimiter="\t", remove_blanks=False):
+    """
+    Function:
+    --------- 
+
+    Parameters:
+    -----------
+
+    Output:
+    -----------
+
+    """
     file = open(filename, 'r')
     n = 0
     lines = []
@@ -247,7 +307,7 @@ def showImages(imageList, rows, color_bar=False, titles=None, ax_labels=None):
     cols = (len(imageList) + rows - 1) / rows
     print "Number of columnts:", cols
     fig, axes = plt.subplots(nrows=rows, ncols=cols)
[…]

### 2018-03-15 notebook.tex
wrote manuscript

--- 2018-03-08 notebook.tex
@@
     % Document parameters
-    \title{Thresholding\_local}
+    \title{01\_Thresholding\_local}
 
@@
 \textbf{Maximum Thresholding}: in max thresholding, if the pixel is the
-maximum of its neighbors with respect to the kernel, then it is set. 2.
+maximum of its neighbors with respect to the kernel, then it is set.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{def}\NormalTok{ local_threshold(mat, k}\OperatorTok{=}\DecValTok{1}\NormalTok{, method}\OperatorTok{=}\StringTok{'max'}\NormalTok{, t}\OperatorTok{=}\DecValTok{1}\NormalTok{):}
+\NormalTok{    mat2 }\OperatorTok{=}\NormalTok{ np.zeros_like(mat)}
+\NormalTok{    n, m }\OperatorTok{=}\NormalTok{ mat.shape}
+    \ControlFlowTok{if} \BuiltInTok{isinstance}\NormalTok{(k, }\BuiltInTok{tuple}\NormalTok{):}
+\NormalTok{        k1, k2 }\OperatorTok{=}\NormalTok{ k}
+    \ControlFlowTok{else}\NormalTok{:}
+\NormalTok{        k1 }\OperatorTok{=}\NormalTok{ k2 }\OperatorTok{=}\NormalTok{ k}
+    \ControlFlowTok{for}\NormalTok{ i }\KeywordTok{in} \BuiltInTok{range}\NormalTok{(k1, n}\OperatorTok{-}\NormalTok{k1):}
+        \ControlFlowTok{for}\NormalTok{ j }\KeywordTok{in} \BuiltInTok{range}\NormalTok{(k, m}\OperatorTok{-}\NormalTok{k2):}
+            \ControlFlowTok{if}\NormalTok{ method }\OperatorTok{==} \StringTok{'max'}\NormalTok{:}
+\NormalTok{                condition }\OperatorTok{=}\NormalTok{ mat[i, j] }\OperatorTok{==}\NormalTok{ np.}\BuiltInTok{max}\NormalTok{(mat[i}\OperatorTok{-}\NormalTok{k1:i}\OperatorTok{+}\NormalTok{k1, j}\OperatorTok{-}\NormalTok{k2:j}\OperatorTok{+}\NormalTok{k2])}
+            \ControlFlowTok{elif}\NormalTok{ method}\OperatorTok{==}\StringTok{'normal'}\NormalTok{:}
+\NormalTok{                temp }\OperatorTok{=}\NormalTok{ mat[i}\OperatorTok{-}\NormalTok{k1:i}\OperatorTok{+}\NormalTok{k1, j}\OperatorTok{-}\NormalTok{k2:j}\OperatorTok{+}\NormalTok{k2]}
+\NormalTok{                condition }\OperatorTok{=}\NormalTok{ mat[i, j] }\OperatorTok{>=}\NormalTok{ np.mean(temp) }\OperatorTok{+}\NormalTok{ t }\OperatorTok{*}\NormalTok{ np.std(temp)}
+            \ControlFlowTok{elif}\NormalTok{ method }\OperatorTok{=} \StringTok{'max_linear'}\NormalTok{:}
+\NormalTok{                condition }\OperatorTok{=}\NormalTok{ mat[i, j] }\OperatorTok{==}\NormalTok{ np.}\BuiltInTok{max}\NormalTok{(mat[i, j}\OperatorTok{-}\NormalTok{k1:j}\OperatorTok{+}\NormalTok{k2])}
+            \ControlFlowTok{if}\NormalTok{ condition:}
+\NormalTok{                mat2[i, j] }\OperatorTok{=} \DecValTok{1}
+    \ControlFlowTok{return}\NormalTok{ mat2}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
   \textbf{Normal Thresholding}: in normal thresholding, if the pixel is
   larger that the average of the neighbors then it is set.
-
-first I perform the most lates normalization method that I have found to
-be most useful: a combination of gaussian normalization, SCN and pearson
-correlation, in the same order mentioned. The normalized results are of
-type \texttt{pearson(scn(gaussian(graph)))}.
-
-Then I threshold the results by setting pearson values larger than 0 to
-1 and the rest to 0. In order to extract graphlets, I used the
-\emph{orca} package in R. the script \texttt{./rscript.r} read a binary
-thresholded matrix representing an unweighted graph and outputs orbtis 0
-through 72 for each node in the network. After thredholding the
-matrices, I save them so that orca in R can read it and extract orbits.
-
-By repeating the procedure explained above for all 23 chromosomes, we
-will have graphlets for all contact maps.
+\end{enumerate}
 
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}5}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
+{\color{incolor}In [{\color{incolor}1}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
         \PY{k+kn}{import} \PY{n+nn}{cv2}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-The autoreload extension is already loaded. To reload it, use:
-  \%reload\_ext autoreload
 Populating the interactive namespace from numpy and matplotlib
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-/home/bzr0014/watson/scripts/virt/local/lib/python2.7/site-packages/IPython/core/magics/pylab.py:161: UserWarning: pylab import has clobbered these variables: ['all', 'colors', 'log']
+/home/bzr0014/watson/scripts/virt/local/lib/python2.7/site-packages/IPython/core/magics/pylab.py:161: UserWarning: pylab import has clobbered these variables: ['colors', 'log']
 `\%matplotlib` prevents importing * from pylab and numpy
@@
 
-    \subsection{Initiating matrices}\label{initiating-matrices}
+    \subsubsection{Initiating matrices}\label{initiating-matrices}
 
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}18}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{2}
+{\color{incolor}In [{\color{incolor}2}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{1}
         \PY{n}{chr2} \PY{o}{=} \PY{n}{chr1}
@@
         \PY{c+c1}{\PYZsh{}print observed\PYZus{}mit\PYZus{}original.shape}
+        \PY{n}{mit\PYZus{}original} \PY{o}{=} \PY{n}{readYamlIntensities}\PYZbs{}
+        \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../data/GM12878\PYZus{}primary/500kb\PYZus{}resolution\PYZus{}intrachromosomal/chr}\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s1}{/MAPQG0/chr}\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s1}{\PYZus{}500kb.RAWobserved}\PY{l+s+s1}{\PYZsq{}}\PYZbs{}
+         \PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{l+m+mi}{500000}\PY{p}{)}
 
@@
         \PY{c+c1}{\PYZsh{}There are some blank rows and columns in the matrix. let\PYZsq{}s remove them.}
+        \PY{n}{blankRows4}\PY{p}{,} \PY{n}{blankCols4} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{mit\PYZus{}original}\PY{p}{)}
         \PY{n}{blankRows0}\PY{p}{,} \PY{n}{blankCols0} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
@@
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows3}\PY{p}{)}
+        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows4}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols0}\PY{p}{)}
@@
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols3}\PY{p}{)}
+        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols4}\PY{p}{)}
+        \PY{n}{mit\PYZus{}original} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{mit\PYZus{}original}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
         \PY{n}{mit} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-chromosome 1: 2, chromosome 2: 2
-file directory: ../data/extracted\_all\_contact\_MIT/chr\_02\_02\_500kb.mat
-file directory: ../data/extracted\_all\_contact\_call4/chr\_02\_02\_500kb.mat
-file directory: ../data/extracted\_all\_contact\_RL/chr\_02\_02\_500kb.mat
-file directory: ../data/extracted\_all\_contact\_ALL/chr\_02\_02\_500kb.mat
-size of old matrix: (486, 486)
-size of new matrix: (480, 480)
-size of old matrix: (486, 486)
-size of new matrix: (480, 480)
-size of old matrix: (486, 486)
-size of new matrix: (480, 480)
-size of old matrix: (486, 486)
-size of new matrix: (480, 480)
+chromosome 1: 1, chromosome 2: 1
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_01\_01\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_01\_01\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_01\_01\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_01\_01\_500kb.mat
+size of old matrix: (499, 499)
+size of new matrix: (456, 456)
+size of old matrix: (495, 495)
+size of new matrix: (452, 452)
+size of old matrix: (495, 495)
+size of new matrix: (452, 452)
+size of old matrix: (495, 495)
+size of new matrix: (452, 452)
+size of old matrix: (495, 495)
+size of new matrix: (452, 452)
+
+    \end{Verbatim}
+
+    \subsubsection{Comparing MIT with the Rao et al high-resolution
+data:}\label{comparing-mit-with-the-rao-et-al-high-resolution-data}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}12}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{20}\PY{p}{)}
+         \PY{n}{k} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}
+         \PY{n}{method} \PY{o}{=} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{max}\PY{l+s+s1}{\PYZsq{}}
+         \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{0}
+         \PY{n}{params} \PY{o}{=} \PY{n+nb+bp}{None}
+         \PY{n}{symmetric}\PY{o}{=}\PY{n+nb+bp}{True}
+         \PY{n}{call4\PYZus{}os} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{call4}\PY{o}{+}\PY{l+m+mi}{1}\PY{o}{+}\PY{l+m+mf}{1e\PYZhy{}5}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{n}{method}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{n}{t}\PY{p}{,} \PY{n}{params}\PY{o}{=}\PY{n}{params}\PY{p}{,} \PY{n}{symmetric}\PY{o}{=}\PY{n}{symmetric}\PY{p}{)}
+         \PY{n}{rl\PYZus{}os} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{rl}\PY{o}{+}\PY{l+m+mi}{1}\PY{o}{+}\PY{l+m+mf}{1e\PYZhy{}5}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{n}{method}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{n}{t}\PY{p}{,} \PY{n}{params}\PY{o}{=}\PY{n}{params}\PY{p}{,} \PY{n}{symmetric}\PY{o}{=}\PY{n}{symmetric}\PY{p}{)}
+         \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{call4\PYZus{}os}\PY{o}{.}\PY{n}{shape}
+         \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{rl\PYZus{}os}\PY{o}{.}\PY{n}{shape}
+         \PY{n}{n} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{n1}\PY{p}{,} \PY{n}{n2}\PY{p}{]}\PY{p}{)}
+         \PY{n}{m} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{m1}\PY{p}{,} \PY{n}{m2}\PY{p}{]}\PY{p}{)}
+         \PY{n}{call4\PYZus{}os} \PY{o}{=} \PY{n}{call4\PYZus{}os}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
+         \PY{n}{call4} \PY{o}{=} \PY{n}{call4}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
+         \PY{n}{rl\PYZus{}os} \PY{o}{=} \PY{n}{rl\PYZus{}os}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
+         \PY{n}{rl} \PY{o}{=} \PY{n}{rl}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
+         \PY{n}{a} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{n}{call4\PYZus{}os} \PY{o}{*} \PY{n}{call4}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{l+m+mi}{1}
+         \PY{n}{b} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{n}{rl\PYZus{}os} \PY{o}{*} \PY{n}{rl}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{l+m+mi}{1}
+\end{Verbatim}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+(2, 2, 2, 2)
+(2, 2, 2, 2)
 
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}19}]:} \PY{n}{n0}\PY{p}{,} \PY{n}{m0} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
+{\color{incolor}In [{\color{incolor}17}]:} \PY{n}{images} \PY{o}{=} \PY{p}{[} \PY{n}{rl}\PY{p}{,} \PY{n}{a}\PY{p}{,} \PY{p}{(}\PY{n}{a}\PY{o}{\PYZhy{}}\PY{n}{b}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{n}{call4}\PY{p}{,}  \PY{n}{b}\PY{p}{,} \PY{n}{a} \PY{o}{*} \PY{n}{b} \PY{p}{]}
+         \PY{n}{titles} \PY{o}{=} \PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Thresholded RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Difference}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Thresholded CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Simmilarity}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}
+         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{titles}\PY{o}{=}\PY{n}{titles}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+Number of columnts: 3
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_6_1.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}22}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
+
+         \PY{n}{n0}\PY{p}{,} \PY{n}{m0} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
          \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
@@
 
-    \begin{verbatim}
-<matplotlib.figure.Figure at 0x7f65c3721610>
-    \end{verbatim}
-
     \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_4_2.png}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_7_1.png}
     \end{center}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}20}]:} \PY{n}{mit} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{mit}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
-         \PY{n+nb}{all} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
-         \PY{n}{rl} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{rl}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
-         \PY{n}{call4} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{call4}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
+{\color{incolor}In [{\color{incolor}28}]:} \PY{n}{k} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{3}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}
+         \PY{n}{mit} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{n}{mit}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
+         \PY{n+nb}{all} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
+         \PY{n}{rl} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{n}{rl}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
+         \PY{n}{call4} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{n}{call4}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
 \end{Verbatim}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}21}]:} \PY{n}{images} \PY{o}{=} \PY{p}{[} 
+(0, 0, 3, 0)
+(0, 0, 3, 0)
+(0, 0, 3, 0)
+(0, 0, 3, 0)
+
+    \end{Verbatim}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}29}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{10}\PY{p}{,} \PY{l+m+mi}{18}\PY{p}{)}
+         \PY{n}{images} \PY{o}{=} \PY{p}{[} 
                  \PY{n}{mit}\PY{p}{,} \PY{n+nb}{all}\PY{p}{,} \PY{n}{rl}\PY{p}{,} \PY{n}{call4}
@@
 
-    \begin{verbatim}
-<matplotlib.figure.Figure at 0x7f65c3718390>
-    \end{verbatim}
-
     \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_6_2.png}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_9_1.png}
     \end{center}
@@
     \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_8_2.png}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_11_2.png}
     \end{center}
@@
     \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_9_2.png}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_12_2.png}
     \end{center}
@@
 
+    The following is the implementation of the above procedure for all 24
+chromosomes:
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}51}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
+         \PY{k+kn}{from} \PY{n+nn}{thresholding\PYZus{}local} \PY{k+kn}{import} \PY{n}{main}
+         \PY{n}{main}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 1, chromosome 2: 1
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_01\_01\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_01\_01\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_01\_01\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_01\_01\_500kb.mat
+size of old matrix: (495, 495)
+size of new matrix: (455, 455)
+size of old matrix: (495, 495)
+size of new matrix: (455, 455)
+size of old matrix: (495, 495)
+size of new matrix: (455, 455)
+size of old matrix: (495, 495)
+size of new matrix: (455, 455)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_1.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 2, chromosome 2: 2
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_02\_02\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_02\_02\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_02\_02\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_02\_02\_500kb.mat
+size of old matrix: (486, 486)
+size of new matrix: (480, 480)
+size of old matrix: (486, 486)
+size of new matrix: (480, 480)
+size of old matrix: (486, 486)
+size of new matrix: (480, 480)
+size of old matrix: (486, 486)
+size of new matrix: (480, 480)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_3.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 3, chromosome 2: 3
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_03\_03\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_03\_03\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_03\_03\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_03\_03\_500kb.mat
+size of old matrix: (399, 399)
+size of new matrix: (392, 392)
+size of old matrix: (399, 399)
+size of new matrix: (392, 392)
+size of old matrix: (399, 399)
+size of new matrix: (392, 392)
+size of old matrix: (399, 399)
+size of new matrix: (392, 392)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_5.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 4, chromosome 2: 4
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_04\_04\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_04\_04\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_04\_04\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_04\_04\_500kb.mat
+size of old matrix: (383, 383)
+size of new matrix: (378, 378)
+size of old matrix: (383, 383)
+size of new matrix: (378, 378)
+size of old matrix: (383, 383)
+size of new matrix: (378, 378)
+size of old matrix: (383, 383)
+size of new matrix: (378, 378)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_7.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 5, chromosome 2: 5
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_05\_05\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_05\_05\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_05\_05\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_05\_05\_500kb.mat
+size of old matrix: (362, 362)
+size of new matrix: (357, 357)
+size of old matrix: (362, 362)
+size of new matrix: (357, 357)
+size of old matrix: (362, 362)
+size of new matrix: (357, 357)
+size of old matrix: (362, 362)
+size of new matrix: (357, 357)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_9.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 6, chromosome 2: 6
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_06\_06\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_06\_06\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_06\_06\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_06\_06\_500kb.mat
+size of old matrix: (342, 342)
+size of new matrix: (337, 337)
+size of old matrix: (342, 342)
+size of new matrix: (337, 337)
+size of old matrix: (342, 342)
+size of new matrix: (337, 337)
+size of old matrix: (342, 342)
+size of new matrix: (337, 337)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_11.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 7, chromosome 2: 7
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_07\_07\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_07\_07\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_07\_07\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_07\_07\_500kb.mat
+size of old matrix: (318, 318)
+size of new matrix: (313, 313)
+size of old matrix: (318, 318)
+size of new matrix: (313, 313)
+size of old matrix: (318, 318)
+size of new matrix: (313, 313)
+size of old matrix: (318, 318)
+size of new matrix: (313, 313)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_13.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 8, chromosome 2: 8
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_08\_08\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_08\_08\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_08\_08\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_08\_08\_500kb.mat
+size of old matrix: (293, 293)
+size of new matrix: (288, 288)
+size of old matrix: (293, 293)
+size of new matrix: (288, 288)
+size of old matrix: (293, 293)
+size of new matrix: (288, 288)
+size of old matrix: (293, 293)
+size of new matrix: (288, 288)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_15.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 9, chromosome 2: 9
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_09\_09\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_09\_09\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_09\_09\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_09\_09\_500kb.mat
+size of old matrix: (281, 281)
+size of new matrix: (246, 246)
+size of old matrix: (281, 281)
+size of new matrix: (246, 246)
+size of old matrix: (281, 281)
+size of new matrix: (246, 246)
+size of old matrix: (281, 281)
+size of new matrix: (246, 246)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_17.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 10, chromosome 2: 10
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_10\_10\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_10\_10\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_10\_10\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_10\_10\_500kb.mat
+size of old matrix: (271, 271)
+size of new matrix: (267, 267)
+size of old matrix: (271, 271)
+size of new matrix: (267, 267)
+size of old matrix: (271, 271)
+size of new matrix: (267, 267)
+size of old matrix: (271, 271)
+size of new matrix: (267, 267)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_19.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 11, chromosome 2: 11
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_11\_11\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_11\_11\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_11\_11\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_11\_11\_500kb.mat
+size of old matrix: (269, 269)
+size of new matrix: (264, 264)
+size of old matrix: (269, 269)
+size of new matrix: (264, 264)
+size of old matrix: (269, 269)
+size of new matrix: (264, 264)
+size of old matrix: (269, 269)
+size of new matrix: (264, 264)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_21.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 12, chromosome 2: 12
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_12\_12\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_12\_12\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_12\_12\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_12\_12\_500kb.mat
+size of old matrix: (265, 265)
+size of new matrix: (263, 263)
+size of old matrix: (265, 265)
+size of new matrix: (263, 263)
+size of old matrix: (265, 265)
+size of new matrix: (263, 263)
+size of old matrix: (265, 265)
+size of new matrix: (263, 263)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_23.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 13, chromosome 2: 13
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_13\_13\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_13\_13\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_13\_13\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_13\_13\_500kb.mat
+size of old matrix: (229, 229)
+size of new matrix: (194, 194)
+size of old matrix: (229, 229)
+size of new matrix: (194, 194)
+size of old matrix: (229, 229)
+size of new matrix: (194, 194)
+size of old matrix: (229, 229)
+size of new matrix: (194, 194)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_25.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 14, chromosome 2: 14
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_14\_14\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_14\_14\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_14\_14\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_14\_14\_500kb.mat
+size of old matrix: (213, 213)
+size of new matrix: (177, 177)
+size of old matrix: (213, 213)
+size of new matrix: (177, 177)
+size of old matrix: (213, 213)
+size of new matrix: (177, 177)
+size of old matrix: (213, 213)
+size of new matrix: (177, 177)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_27.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 15, chromosome 2: 15
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_15\_15\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_15\_15\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_15\_15\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_15\_15\_500kb.mat
+size of old matrix: (201, 201)
+size of new matrix: (165, 165)
+size of old matrix: (201, 201)
+size of new matrix: (165, 165)
+size of old matrix: (201, 201)
+size of new matrix: (165, 165)
+size of old matrix: (201, 201)
+size of new matrix: (165, 165)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_29.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 16, chromosome 2: 16
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_16\_16\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_16\_16\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_16\_16\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_16\_16\_500kb.mat
+size of old matrix: (178, 178)
+size of new matrix: (160, 160)
+size of old matrix: (178, 178)
+size of new matrix: (160, 160)
+size of old matrix: (178, 178)
+size of new matrix: (160, 160)
+size of old matrix: (178, 178)
+size of new matrix: (160, 160)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_31.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 17, chromosome 2: 17
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_17\_17\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_17\_17\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_17\_17\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_17\_17\_500kb.mat
+size of old matrix: (158, 158)
+size of new matrix: (158, 158)
+size of old matrix: (158, 158)
+size of new matrix: (158, 158)
+size of old matrix: (158, 158)
+size of new matrix: (158, 158)
+size of old matrix: (158, 158)
+size of new matrix: (158, 158)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_33.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 18, chromosome 2: 18
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_18\_18\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_18\_18\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_18\_18\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_18\_18\_500kb.mat
+size of old matrix: (153, 153)
+size of new matrix: (151, 151)
+size of old matrix: (153, 153)
+size of new matrix: (151, 151)
+size of old matrix: (153, 153)
+size of new matrix: (151, 151)
+size of old matrix: (153, 153)
+size of new matrix: (151, 151)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_35.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 19, chromosome 2: 19
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_19\_19\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_19\_19\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_19\_19\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_19\_19\_500kb.mat
+size of old matrix: (128, 128)
+size of new matrix: (113, 113)
+size of old matrix: (128, 128)
+size of new matrix: (113, 113)
+size of old matrix: (128, 128)
+size of new matrix: (113, 113)
+size of old matrix: (128, 128)
+size of new matrix: (113, 113)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_37.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 20, chromosome 2: 20
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_20\_20\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_20\_20\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_20\_20\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_20\_20\_500kb.mat
+size of old matrix: (125, 125)
+size of new matrix: (121, 121)
+size of old matrix: (125, 125)
+size of new matrix: (121, 121)
+size of old matrix: (125, 125)
+size of new matrix: (121, 121)
+size of old matrix: (125, 125)
+size of new matrix: (121, 121)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_39.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 21, chromosome 2: 21
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_21\_21\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_21\_21\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_21\_21\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_21\_21\_500kb.mat
+size of old matrix: (94, 94)
+size of new matrix: (70, 70)
+size of old matrix: (94, 94)
+size of new matrix: (70, 70)
+size of old matrix: (94, 94)
+size of new matrix: (70, 70)
+size of old matrix: (94, 94)
+size of new matrix: (70, 70)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_41.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+chromosome 1: 22, chromosome 2: 22
+file directory: ../data/extracted\_all\_contact\_MIT/chr\_22\_22\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_call4/chr\_22\_22\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_RL/chr\_22\_22\_500kb.mat
+file directory: ../data/extracted\_all\_contact\_ALL/chr\_22\_22\_500kb.mat
+size of old matrix: (100, 100)
+size of new matrix: (70, 70)
+size of old matrix: (100, 100)
+size of new matrix: (70, 70)
+size of old matrix: (100, 100)
+size of new matrix: (70, 70)
+size of old matrix: (100, 100)
+size of new matrix: (70, 70)
+Number of columnts: 4
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_43.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor} }]:} \PY{c+c1}{\PYZsh{}for chr1 in range(1, 24):}
+        \PY{c+c1}{\PYZsh{}    os.system(\PYZsq{}Rscript rscript.r \PYZpc{}s\PYZsq{}\PYZpc{}chr1)}
+\end{Verbatim}
+
     % Add a bibliography block to the postdoc

### 2018-03-15 papers/manuscripts/manuscript.tex
wrote manuscript

@@
 
-Implementations of algorithms of extracting graphlets: \\
-\begin{itemize}
-    \item GraphCrunch: 
-        \url{http://www0.cs.ucl.ac.uk/staff/natasa/graphcrunch2/usage.html}
-    \item PGD: \url{http://nesreenahmed.com/graphlets/}
-    \item ORCA: Graphlet and orbit counting algorithm \\
-        \url{ https://CRAN.R-project.org/package=orca} \\
-        This package is in R. In order to install it, type
-        \texttt{install.packages("orca")}.
-
-\end{itemize}
-
 The authors of \cite{di2010fast} generalized the idea of graphlets to 
 ordered graphs were the nodes are labeled in ascending order.
-These graphlets are illustrated in Figure \ref{fig:ordered_graphlets}.
 As can be viewed, there are a total of 14 orbits for graphlets of size
@@
 that passes through the contact map with a pixel at its middle at 
-each step.
+each step. Figure \ref{local_thresholded_chr1_chr1} demonstrates result of 
+this thresholding approach for interchromosomal contact map of chromosome 1.
+Refer to supplementary material for all 23 interchromosomal thresholding
+results.
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/local_thresholded_chr1_chr1.png}
+    \caption{Result of thresholding interchromosomal contact map of chromosome 1
+    using a kernels of size $5 \times 5$. The first row shows the thresholded
+    maps. Second and third rows demonstrate pair-wisesimilarities and 
+    differences between contact maps respectively.}
+    \label{local_thresholded_chr1_chr1}
+\end{figure*}
 
+\subsection{Orbit Extraction}
+Once the thresholded contact maps are obtained, graphlets and orbits can be 
+extracted. We used the \texttt{orca} package in \texttt{R} programming 
+language to extract the graphlets. As a result of graphlet extraction, 
+For each loci in each contact map, a \textit{signature vector} of size
+73 is created.
+
+We divied the task of graphlet comparison into two parts: first we compare
+graphlets from each contact map in normal cell lines (MIT) with the 
+same contact maps in the other three Leukemic cells. Second we compare 
+contact maps in a similar way but this time only between leukemic cells.
+In the former case, the null hypothesis is that there is no difference
+between contact maps of normal cells and leukemic celss and in the later
+case, the null hypotheis is that there is no difference between 
+different leukemic cells.
+
+We consider two measures of \textit{difference} when comparing contact
+map graphlets. The first measure is the distance between signature vectors
+of a loci in two cell lines. If $S^A_{k}$  and $S^B_{k}$ are 
+signature vectors corresponding to loci $k$ in contact maps A and B 
+respectively, then we can caclulate the distance between the two loci 
+using the following formula from \cite{prvzulj2007biological}:
+
+\begin{equation}
+    d_{ki} = w_i \times \frac{log(S^A_{ki}+1) - log(S^B_{ki}+1)}{log(max(S^A_{ki}, S^B_{ki}) + 2)}
+\end{equation}
+The distance between $S$ and $S'$ can be calculated as follows:
+\begin{equation}
+    D(S^A_k, S^B_k) = \sqrt{\sum_{0}^{72}{d_{ki}^2}}
+\end{equation}
+
+Using this distance measure, we can quantify how two loci are close to
+each other in terms of local neighborhood between the two contact maps.
+
+The second measure of comparison that we use captures how 
+similar two orbits are in terms of their frequencies across loci
+between the two contact maps. For each contact map, we can calculate
+similarity between orbit distributions by calculating pearso's r 
+correlation. However, pearson's r might not be able to capture
+non-functional relationships between distributions. As a result, we
+also used Maximal Information Coefficient (MIC) 
+\cite{reshef2011detecting} in order to compare
+correlations. MIC calculates mutual information (MI) between two
+distributions, but utilizes dynamic programming in order adjust
+bin sizes and numbers in order to achieve highest MI.
+MIC values between two variables fall between 0 and 1,
+with 0 meaning that the two variables are completely independent
+and 1 meaning they are totally correlated.
+We used both Pearson's r and MI in order to compare orbit
+frequencies. Although results from both approaches were more
+or less consistent, MIC showed higher robustness than Pearson's 
+r method.
+
+\subsection{Hypotheses}
+\subsubsection{terminology}
+We denote the set of all contact maps of normal (MIT) cell line with
+$CM$. In the same manner we denote $CA$, $CR$ and $CC$ as the set of all
+contact maps corresponding to ALL, RL and CALL4 cell lines.
+We denote a member of any of the aforementioned sets using small
+letters of the set name. For example, we denote any member of $CA$ with
+$ca$.
+
+We denote a contact map by $C^{\{cell_{\{chr1\}\{chr2\}}\}}$, where the
+superscript denotes the cell type and the subscripts in the superscripts
+determines the pair of chromosomes the contact map is about. For 
+example $C^{MIT_{1,14}}$ denotes the contact map between chromosomes
+1 and 14 in MIT (Normal) dataset. In such a manner $C^{MIT_{1,14}}_{ij}$
+denotes the interaction between loci $i$ and $j$ in the aforementioned
+contact map.
+
+We denote $S^C_i$ as the extracted 
+signature vector of locus $i$ in contact map $C$. 
+Also $P^C_k$ denotes
+the frequency distribution of orbital $k$ in contact map $C$.
+
+With regard to the two aforementioned comparison methods, we define
+our two null hypotheses as the following:
+
+\begin{enumerate}
+    \item For a locus in a contact map in MIT cell type, its distance
+        from the same locus in the same contact map of the other three
+        cell types are equal to $0$.
+            \begin{align}
+                \begin{split}
+                    H_0: D(sm, sa) = 0  \\
+                \hspace{.5cm} \forall cm \in CM \quad\&\quad ca \in CA
+                \end{split} \\
+                \begin{split}
+                    H_0: D(sm, sr) = 0   \\
+                \hspace{.5cm} \forall cm \in CM\quad \&\quad cr \in CR
+                \end{split} \\
+                \begin{split}
+                    H_0: D(sm, sc) = 0   \\
+                \hspace{.5cm} \forall cm \in CM\quad \&\quad cc \in CC
+                \end{split}
+            \end{align}
+    \item For an orbit extracted from a contact map of MIT cell, the 
+        Pearson's r correlation between its frequency and the frequency
+        of the same orbit extracted from the same contact map in 
+        the other three cell types in equal to 1.
+        \begin{align}
+            H_0: Corr(P^CM_k, P^CA_k) = 1 \\
+            H_0: Corr(P^CM_k, P^CR_k) = 1 \\
+            H_0: Corr(P^CM_k, P^CC_k) = 1
+        \end{align}
+
+        or
+
+        For an orbit extracted from a contact map of MIT cell, the 
+        MIC between its frequency and the frequency
+        of the same orbit extracted from the same contact map in 
+        the other three cell types in equal to 1.
+\end{enumerate}
+
+\newpage
 \section{Resources}
-\textbf{Publications related to Hi-C:}
-\begin{enumerate}
-    \item \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2858594/}
-    \item \url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0058793 }
-    \item \url{http://nar.oxfordjournals.org/content/42/7/e52.full}
-    \item \url{http://bioinformatics.oxfordjournals.org/content/early/2015/12/31/bioinformatics.btv754.abstract?keytype=ref&ijkey=A97WhKqBiEIcuzd}
-    \item \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4417147/}
-    \item \url{http://www.pnas.org/content/112/47/E6456.full}
-    \item \url{http://www.pnas.org/content/113/12/E1663.full}
-\end{enumerate}
 \textbf{Hi-C Datasets:}
 \begin{enumerate}
-    \item Original Datasets: \url{https://bcm.app.box.com/v/aidenlab/folder/11234760671}
-    \item Including cancerous cells: \url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}
-    \item Chromosome3D project: \url{http://sysbio.rnet.missouri.edu/bdm_download/chromosome3d/}
-\end{enumerate}
-\textbf{Contact Matrix Analysis:}
-\begin{enumerate}
-    \item \url{https://omictools.com/contact-matrix-normalization-category}
-    \item \url{http://hifive.docs.taylorlab.org/en/latest/}
-\end{enumerate}
-
-\textbf{Labs working on 3D Human Genome:}
-
-\begin{enumerate}
-    \item \url{http://mirnylab.mit.edu}
-    \item \url{http://dostielab.biochem.mcgill.ca}
-    \item \url{http://www.aidenlab.org/}
-    \item \url{http://web.cmb.usc.edu/people/alber/index.htm}
-    \item \url{http://calla.rnet.missouri.edu/cheng/nsf_career.html}
-\end{enumerate}
-\textbf{Resources related to Graphlet:}
-
-\begin{enumerate}
-    \item \url{https://en.wikipedia.org/wiki/Graphlets}
-    \item \url{https://academic.oup.com/bioinformatics/article/23/2/e177/202080/Biological-network-comparison-using-graphlet}
-    \item \url{http://www0.cs.ucl.ac.uk/staff/N.Przulj/index.html}
+    \item \href{https://github.com/rasoolianbehnam/watson}{Code base for this article}
+    \item \href{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}
+        {Datasets including cancerous cells}
+    \item \href{https://bcm.app.box.com/v/aidenlab/folder/11234760671}{Original Datasets}
 \end{enumerate}

### 2018-03-15 utility.py

@@ -27,7 +27,6 @@ def eigendecompose(a):
 
 def writeMatToImage(mat, fileName):
     scipy.misc.imsave(fileName, mat)
-
 def writeMatToFile(mat, fileName, delimiter=','):
     """
     Function:
@@ -303,11 +302,17 @@ def scn(a, minDiff=1e-3, numIterations=1000):
 def gaussian_normalize(heatmap):
     return (heatmap - np.mean(heatmap) ) / np.std(heatmap)
 
-def showImages(imageList, rows, color_bar=False, titles=None, ax_labels=None):
-    cols = (len(imageList) + rows - 1) / rows
-    print "Number of columnts:", cols
+def _showImages(imageList, rows=None, cols=None, color_bar=False, titles=None, ax_labels=None):
+    if rows == None and cols == None:
+        rows = 1
+        cols = (len(imageList) + rows - 1) / rows
+    elif cols == None:
+        cols = (len(imageList) + rows - 1) / rows
+    elif rows == None:
+        rows = (len(imageList) + cols - 1) / cols
+    print "Number of rows and columns: %d, %d"%(rows, cols)
     fig, axes = plt.subplots(nrows=rows, ncols=cols)
-    plt.subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=0.03, hspace=.01)
+    plt.subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=0.1, hspace=.1)
     count = 0
     for image in imageList:
         if rows * cols == 1:
@@ -328,6 +333,20 @@ def showImages(imageList, rows, color_bar=False, titles=None, ax_labels=None):
         cax = divider.append_axes("right", size="2%", pad=0.05)
         cb = fig.colorbar(m, cax=cax)
     plt.show()
+
+def showImages(imageList, rows=None, cols=None, color_bar=False, titles=None, ax_labels=None):
+    if isinstance(imageList, dict):
+        images = []
+        titles = []
+        for key in imageList:
+            images.append(imageList[key])
+            titles.append(key)
+        _showImages(images, rows=rows, cols=cols, \
+                color_bar=color_bar, titles=titles, ax_labels=ax_labels)
+    else:
+        _showImages(imageList, rows=rows, cols=cols, \
+                color_bar=color_bar, titles=titles, ax_labels=ax_labels)
+
 
 def cvShowImages(imageList):
     count = 1
@@ -674,7 +693,9 @@ def svd_reconstruct(mat, k, u='empty', sig='empty', v='empty'):
[…]

### 2018-03-19 papers/manuscripts/manuscript.tex
editted manuscript

--- 2018-03-14 papers/manuscripts/manuscript.tex
@@
 \usepackage{caption}
+\usepackage{subcaption}
+\usepackage[super]{nth}
+% Enter dates of publication
+\copyrightyear{2017}
+\pubdate{18 March 2017}
+\pubyear{2017}
+\jvolume{37}
+\jissue{12}
+
+%\articlesubtype{This is the article type (optional)}
 
 \begin{document}
-\section{Abstract}
+\title{HiC Contact Map Comaprison Using Graphlet Approach}
+
+\author{%
+    Behnam Rasoolian\,$^{1,*}$,
+    Debswapna Bhattacharya\,$^{1}$
+    \footnote{
+    Tel: +1 334 5212814; Email: bzr0014@auburn.edu}}
+
+    \address{%
+        $^{1}$ Auburn University
+        }
+        % Affiliation must include:
+        % Department name, institution name, full road and district address,
+        % state, Zip or postal code, country
+
+%        \history{%
+%            Received January 1, 2009;
+%            Revised February 1, 2009;
+%            Accepted March 1, 2009}
+
+            \maketitle
+
+\begin{abstract}
 
@@
 We believe differences in interaction matrices can be found between normal cells and cancerous ones.
-
+\end{abstract}
 \section{Introduction}
@@
 \section{Materials and Methods}
+\subsubsection{Notations}
+In this paper, matrices and vectors are represented as bold
+capital and bold small letters respectively.
+matrix rows and columns are represented by a \textit{dot}
+notation. For example, the $i$th row of matrix $M$ is
+denoted by $M_{i.}$ and its $j$th column is represented
+by $M_{.j}$.
+
+We denote the set of all contact maps in cell line $T$ with 
+$\mathbb{C}^T$. If no particular cell line is addressed, the
+subscripts are dropped.
+Any arbitrary member of $\mathbb{C}$ is denoted by 
+$C_{ij}$, where $i$ and $j$ ($j \ge i$) represent the two chromosomes involved. 
+In human cells this set contains a total of 276 contact maps,
+23 of which are intra-chromosomal and the rest are inter-chromosomal.
+For ease of representations, intra-chromosomal contact maps are
+distinguished by a single superscript, so we have $C_{i,i} =
+C_i$.
+
+We denote the number of loci in a chromosome $i$ by $N_i$.
+The set of all loci involved in contact map $C_{ij}$ is denoted 
+by $V_{ij}$.
+In intra-chromosomal contact maps, $V_{i,i}$ containts only the 
+loci of that particular chromosome ($|V_i| = N_i$), while in 
+inter-chromosomal contact maps $V_{ij}$ contains the loci in
+the both of chromosomes involved ($|V_{ij}| = N_i + N_j$).
+
+% **************************************************************
+% Keep this command to avoid text of first page running into the
+% first page footnotes
+\enlargethispage{-65.1pt}
+% **************************************************************
+
 \subsection{Thresholding contact maps}
@@
 unweighted graphs where the nodes represent the loci and an edge between two 
-nodes represent a \textit{significant} interaction between the loci the nodes
-represent.
-
-Thresholding is achieved by thresholding the contact maps. The result
-of the thresholding procedure would be a binary matrix which also can serve as
+nodes represent a \textit{significant} interaction between the loci.
+This can be achieved by thresholding the contact maps. The result
+of the thresholding procedure is a binary matrix which also can serve as
 an adjacency matrix for an unweighted, undirected graph. The graph can then be
@@
 
-In order to go about the process of thresholding, it is necessary to make sure
+When thresholding contact maps, it is necessary to make sure
 that both global and local features are maintained. We could consider 
 thresholding the contact maps by simply setting values above a fixed value to
-one and the rest to zero. However, in practice, this proved result in graphs
+one and the rest to zero; However, in practice, this method resulted in graphs
 that capture the local structure of the contact maps poorly. This is because
-intensities follow an exponential distribution with a mean close to zero and
-some very larges values that correspond t interactions along and close to 
-the main diagonal of the contact maps.
+intensities follow an exponential distribution with a mean close to zero
+with a few very larges values that correspond to interactions along 
+or close to the main diagonal of the contact maps.
 Thus, picking relatively large numbers would result in ignoring interactions
-that are far from the main diagonal and picking small numbers will lead to
-capturing too many \textit{insignificant} interactions.
+that are far from the main diagonal while picking small values will lead to
+capturing too many (insignificant) interactions.
 
 In order to threshold the matrix so that both global and local patterns are
-kept, we borrowed the concept of \textit{adaptive thresholding} from image 
+captured, we borrowed the concept of \textit{adaptive thresholding} from image 
 processing context. In this method, in order to be set, a pixel should have
-an intensity that is larger than the average of non-zero intensities in its
-\textit{neighborhood}. The neighborhood is defined by an sliding kernel 
-that passes through the contact map with a pixel at its middle at 
-each step.
+an intensity larger than the average of non-zero intensities in its
+\textit{neighborhood}. The neighborhood is defined by a sliding kernel 
+that passes through the contact map with the pixel at its middle at 
+each step. Figure \ref{local_thresholded_chr1_chr1} demonstrates result of 
+this thresholding approach for intra-chromosomal contact maps of chromosome 1.
+Refer to supplementary material for all 23 interchromosomal thresholding
+results.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=.5\textwidth]{figures/local_thresholded_chr1_chr1.png}
+    \caption{Result of thresholding interchromosomal contact map of chromosome 1
+    using a kernels of size $5 \times 5$ for all cell lines. 
+    The first row shows the thresholded
+    maps. Second and third rows demonstrate pair-wise similarities and 
+    differences between contact maps respectively.}
+    \label{local_thresholded_chr1_chr1}
+\end{figure}
 
+\subsection{Orbit Extraction}
+Once the thresholded contact maps are obtained, graphlets and orbits can be 
+extracted. We used the \texttt{orca} package in \texttt{R} programming 
+language to extract the graphlets. As a result of graphlet extraction, 
+For each loci in each contact map, a \textit{signature vector} of size
+73 is created. Thus for each cell line, we would have 276 
+\textit{signature matrices} of
+size $|V^{ij}|\times 73$, where $V^{ij}$ is the number of loci
+involved in contact map between chromosomes $i$ and $j$. Figure
+\ref{fig:graphlet_extraction} illustrates the process and results
+of signature matrix extraction schematically.
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figures/graphlet_extraction.png}
+    \caption{Graphlet extraction for the four cell lines. For each
+    loci in each contact map between chromosomes $i$ and $j$, 
+    the signature vectors of length 73 are extracted, resulting 
+    in a \textit{signature matrix} of size $|V^{ij}| \times 73$,
+    where $V^{ij}$ 
+    is the number of loci involved.}
+    \label{fig:graphlet_extraction}
+\end{figure}
+
+For a particular
+$\mathbf{C}_{ij}$, we denote $\mathbf{S}_{ij}$ as its \textit{signature 
+matrix}. Each cell $S_{ijlo}$ in $\mathbf{S}_{ij}$ captures how many
+times loci $l$ in $\mathbf{C}_{ij}$ occured as part of orbit $o$.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figures/graphlet_distance_schema.png}
+    \caption{Calculating pair-wise loci distances. For each loci (row) 
+    in each
+    contact map in MIT cell line, its distance is calculated based on
+    equation \ref{eq:distance_total} with the corresponding loci in
+    leukemic cells. The result of this process is a 
+    \textit{signature distance vector} of size
+    $|V^{ij}| = N_i+N_j$ for each contact map.
+    }
+    \label{graphlet_distance_schema}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figures/graphlet_correlation_schema.png}
+    \caption{Calulating pair-wise orbit correlations. For each orbit (column)
+    in each contact map in MIT cell line, its correlation with the
+    same orbit in the same contact map 
+    in leukemic cells is calculated. The result of
+    this process is a \textit{signature correlation} vector of size
+    73 which captures how similar frequencies of two orbits are.
+    In order to test our second hypothesis, we calculated averages
+    across contact maps (along the vertical red arrow) to test 
+    hypothesis \ref{eq:h2a}
+    and across orbits
+    (along the horizontal red arrows) to test hypothesis \ref{eq:h2b}.}
+    \label{graphlet_correlation_schema}
+\end{figure}
+
+We divided the task of graphlet comparison into two parts: first we compare
+graphlets from each contact map in normal cell lines (MIT) with the 
+same contact maps in the other three Leukemic cells. Second we compare 
+contact maps in a similar way but this time only between leukemic cells.
+In the former case, the null hypothesis is that there is no difference
+between contact maps of normal cells and leukemic cells and in the latter
+case, the null hypotheis is that there is no difference between 
+different leukemic cells.
+
+We consider two measures of \textit{difference} when comparing contact
+map graphlets across cell lines. 
+The first measure is \textit{signature distance vectors} between
+each contact map of two cell lines. 
+Let  $\mathbf{S}^A_{ij}$  and $\mathbf{S}^B_{ij}$ be
+signature matrices corresponding  to cells A and B
+respectively, then we can caclulate the 
+distance between each
+loci (row) $l$ in $S^A$ and the the same loci in $S^B$
+using the following formula from \cite{prvzulj2007biological}:
+
+\begin{equation}
+    D(\mathbf{S}^A_{ij}, \mathbf{S}^B_{ij}) = 
+    \frac{1}{73}\sqrt{\sum_{o=0}^{72}{\mathbf{D}_{.o}^2}}
+    \label{eq:distance_total}
+\end{equation}
+where elements of $\mathbf{D}$ can be calculated as follows:
+\begin{equation}
+    D_{lo} = w_o \times 
+        \frac{log(S_{ijlo}^A+1) - log(S_{ijlo}^B+1)}
+             {log(max(S_{ijlo}^A, S_{ijlo}^B) + 2)}
+    \label{eq:distance_single}
+\end{equation}
+
+This process is illustrated in Figure \ref{graphlet_distance_schema}.
+Using this distance measure, we can quantify how two loci are close to
+each other in terms of local neighborhood between the two contact maps.
+
+The second measure of comparison that we use captures how 
+similar two orbits are in terms of their count 
+frequencies across loci between two contact maps. 
+Each column in $S_{ij}$ can provide information
+regarding the \textit{frequency distribution} of orbits throughout
+the contact map $C_{ij}$. 
+We can find how similar these distributions are to each other using
+correlation measures.
+These correlations can be calculated as the following:
+\begin{equation}
+    Corr(\mathbf{S}^A_{ij}, \mathbf{S}^B{ij}) = \mathbf{c}_{ij}
+    \label{eq:correlation}
+\end{equation}
+where each element of $\mathbf{c}$ is calculated as below:
+\begin{equation}
+    c_{ijo} = Corr(\mathbf{S}^A_{ij.o}, \mathbf{S}^B_{ij.o})
+    \label{eq:correlation}
+\end{equation}
+
+For each contact map,  calculated
+similarity between orbit distributions using Pearson's r 
+correlation, which is computationally efficient.
+However, pearson's r might not be able to capture
+non-functional relationships between distributions. As a result, we
+also used Maximal Information Coefficient (MIC) 
+\cite{reshef2011detecting} in order to compare
+correlations. MIC calculates mutual information (MI) between two
+distributions, but utilizes dynamic programming in order adjust
+bin sizes and numbers in order to achieve highest MI.
+MIC values between two variables fall between 0 and 1,
+with 0 meaning the two variables are completely independent
+and 1 meaning one is dependant on the other.
+We used both Pearson's r and MI in order to compare orbit
+frequencies. Although results from both approaches were more
+or less consistent, MIC showed higher robustness than Pearson's 
+r method.
+
+\subsection{Hypotheses}
+
+With regard to the two aforementioned comparison methods, we define
+our two null hypotheses as the following:
+
+\begin{enumerate}
+    \item Average signature vector distance between each 
+        contact map of MIT cells and
+        their counterparts in the three leukemic cells
+        are equal to $0$. In mathematical terms:
+        $\forall i,j \in \{1, 2 ..., 24\}$
+        \begin{align}
+            \begin{split}
+                H_0&: \frac{1}{|V_{ij}|}\sum_{l=0}^{|V_{ij}|}{d_{ijl}} = 0 \\
+                H_1&: \frac{1}{|V_{ij}|}\sum_{l=0}^{|V_{ij}|}{d_{ijl}} > 0
+            \end{split}
+            \label{eq:h1}
+        \end{align}
+
+        where 
+        $\mathbf{d}_{ij} = D(S^{MIT}_{ij}, S^L_{ij})$ and $L \in \{ALL, RL, CALL4\}$.
+
+        \item 
+            \begin{enumerate}
+                \item Average orbit correlations within a contact map of MIT cell, 
+                    and its counterpart in leukemic cells is equal to 1
+                    for each contact map.
+                Again in mathematical terms:
+                $\forall i,j \in \{1, 2 ..., 24\}$
+                \begin{align}
+                    \begin{split}
+                        H_0&: \frac{1}{73}\sum_{o=0}^{72}{c_{ijo}} = 1 \\
+                        H_1&: \frac{1}{73}\sum_{o=0}^{72}{c_{ijo}} < 1
+                    \end{split}
+                    \label{eq:h2b}
+                \end{align}
+                        where $\mathbf{c}_{ij} = Corr(S^{MIT}_{ij}, S^L_{ij})$, $L$ 
+                        is the same as above and $N$ 
+                        is the total number of contact maps which 
+                        is equal to $275$ in our case.
+
+                \item Average orbit correlations  of MIT cell
+                    and leukemic cells across contact maps is equal to 1
+                    for each orbit.
+                Again in mathematical terms:
+
+                        \smallskip
+
+                    $\forall o \in \{0, 1 ... 72\}$
+                \begin{align}
+                    \begin{split}
+                        H_0&: \frac{1}{N}\sum_{i=1}^{23}{\sum_{j=i}^{23}{c_{ijo}}} = 1 \\
+                        H_1&: \frac{1}{N}\sum_{i=1}^{23}{\sum_{j=i}^{23}{c_{ijo}}} < 1
+                    \end{split}
+                    \label{eq:h2a}
+                \end{align}
+                        $L$ and $\mathbf{c}_{ij}$ are the same as above.
+
+            \end{enumerate}
+\end{enumerate}
+\section{results}
+
+\subsection{Hypothesis 1: Orbit Distance Comparison}
+\begin{figure*}[t]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figures/orbit-distances_all.png}
+        \caption{}
+        \label{fig:orbit-distances_all}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figures/orbit-distances_intra.png}
+        \caption{}
+        \label{fig:orbit-distances_intra}
+    \end{subfigure}
+    \caption{   Pair-wise graphlet signature difference for
+                (a) all 276 contact maps.
+                (b) only the 23 intra-chromosomal contact maps.
+                Each point on a graph is the result of averaging all
+                the distances acroos all loci of that contact map.
+                As can be viewd, although inter-chromosomal graphlets 
+                do not show significant differences, RL's inter-chromosomal
+                graphlets seem to be closer to MIT's. Also in some contact
+                maps ALL graphlets show greater distance from MIT graphlets
+                than the other two cell lines.
+             }
+    \label{fig:orbit-distances}
+\end{figure*}
+Result of pair-wise contact map graphlet distances can is
+demonstrated in Figure \ref{fig:orbit-distances}.
+Each point on the graph is the
+average distance between signature vector of two same loci 
+in the two cell lines as in Equation \ref{eq:h1}.
+in order to test hypothesis \ref{eq:h1} a one sided t-test
+was conducted. The resulting p-values showed highly significant differeces
+between graphlets extracted from all contact maps. Refer to supplementary
+material for results of all hypotheis tests.
+
+\subsection{Hypothesis 2: Orbit distribution comparison}
+We caclulated pair-wise Pearson's r correlation for each orbit in each of the 276
+contact maps from MIT data and ALL, RL and CALL4 data separately. 
+Figure \ref{fig:contact_maps_correlations}
+shows average orbit correlations across all contact maps
+(average along the red \textit{vertical} arrow in figure 
+\ref{graphlet_correlation_schema}), while
+figure \ref{fig:orbits_correlations} 
+demonstrates average correlations across all 72 orbits within each  contact map
+(average along the red \textit{horizontal} arrows in figure 
+\ref{graphlet_correlation_schema}).
+It is worth mentioning that \textit{interchromosomal} thresholded contact maps 
+represent
+a biparticde graph with the loci from each chromosome on one side. Due to this
+bipartide nature of the graphs in inter-chromosomal maps,
+count of certain orbits is always 0, resulting in
+a correlation values of 0 for them as well.
+We ignored these values  when we calculated averages across orbits 
+in figure \ref{fig:contact_maps_correlations_all} since they
+would result in a bias towards zero in averages. You can see the bias in 
+figure \ref{fig:orbits_correlations_all} where average correlations of obits
+3, 9, 10-14, 20-34, 39-48, and 51-72 are close to zero. In fact all correlations
+corresponding to these orbits are 0 except for the ones between the same 
+chromosomes which are illustrated in Figure 
+\ref{fig:orbits_correlations_intra}.
+
+\begin{figure*}[t]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_all.png}
+        \caption{}
+        \label{fig:contact_maps_correlations_all}
+    \end{subfigure}
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_intra.png}
+        \caption{}
+        \label{fig:contact_maps_correlations_intra}
+    \end{subfigure}
+    \caption{pair-wise average contact map orbit correlations
+             (a) for all contact maps
+             (b) only for intra-chromosomal contact maps
+             These values are calculated by averaging over 
+             pairwise correlations of all orbits in a 
+             contact map.
+             }
+    \label{fig:contact_maps_correlations}
+\end{figure*}
+
+\begin{figure*}[t]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth, height=.2\paperheight]{figures/orbits_correlations_all.png}
+        \caption{}
+        \label{fig:orbits_correlations_all}
+    \end{subfigure}
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth, height=.2\paperheight]{figures/orbits_correlations_intra.png}
+        \caption{}
+        \label{fig:orbits_correlations_intra}
+    \end{subfigure}
+    \caption{pair-wise average orbit correlations.
+             In figure \ref{fig:orbits_correlations_all}, each point
+             in the graph is the result of averaging pair-wise
+             orbit correlations over all contact maps, while
+             each point in figure \ref{fig:orbits_correlations_intra}
+             are averaged only over intra-chromosomal contact maps.
+             Counts for certain orbits are always zero in inter-chromosomal
+             maps, leading to average value close to zero in 
+             \ref{fig:orbits_correlations_all}.
+             }
+    \label{fig:orbits_correlations}
+\end{figure*}
+We have conducted one-sided
+t-test in order to test whether the average correlations across
+contact maps is equal to 1 (Equation \ref{eq:h2a}) and whether the average 
+correlations across orbits is equal to 1 (Equation \ref{eq:h2b}). The results
+for both test showed that all values are significantly less than 1.
+Please refer to supplementary material for result of the t-tests.
+\subsection{Comparing Cancer cells}
+\begin{figure*}[t]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figures/orbit-distances_intra_cancer.png}
+        \caption{}
+        \label{fig:orbit_distances_intra_cancer}
+    \end{subfigure}
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figures/orbits_correlations_intra_cancer.png}
+        \caption{}
+        \label{fig:orbits_correlations_intra_cancer}
+    \end{subfigure}
+    \caption{}
+    \label{fig:orbits_cancer_intra}
+\end{figure*}
+
+We also conducted the same comparison with the same hypothesis among cancer cells.
+The results for intra-chromosomal distances and correlations can be found in
+figure \ref{fig:orbits_cancer_intra}. As can be noticed, CALL4 and RL cell
+line exhibit a significantly higher average correlations for the majority of
+the chromosomes (figure \ref{fig:orbit_distances_intra_cancer}) and almost in
+all orbits (figure \ref{fig:orbits_correlations_intra_cancer}).
+\section{discussion}
+\newpage
 \section{Resources}
-\textbf{Publications related to Hi-C:}
-\begin{enumerate}
-    \item \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2858594/}
-    \item \url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0058793 }
-    \item \url{http://nar.oxfordjournals.org/content/42/7/e52.full}
-    \item \url{http://bioinformatics.oxfordjournals.org/content/early/2015/12/31/bioinformatics.btv754.abstract?keytype=ref&ijkey=A97WhKqBiEIcuzd}
-    \item \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4417147/}
-    \item \url{http://www.pnas.org/content/112/47/E6456.full}
-    \item \url{http://www.pnas.org/content/113/12/E1663.full}
-\end{enumerate}
 \textbf{Hi-C Datasets:}
 \begin{enumerate}
-    \item Original Datasets: \url{https://bcm.app.box.com/v/aidenlab/folder/11234760671}
-    \item Including cancerous cells: \url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}
-    \item Chromosome3D project: \url{http://sysbio.rnet.missouri.edu/bdm_download/chromosome3d/}
-\end{enumerate}
-\textbf{Contact Matrix Analysis:}
-\begin{enumerate}
-    \item \url{https://omictools.com/contact-matrix-normalization-category}
-    \item \url{http://hifive.docs.taylorlab.org/en/latest/}
-\end{enumerate}
-
-\textbf{Labs working on 3D Human Genome:}
-
-\begin{enumerate}
-    \item \url{http://mirnylab.mit.edu}
-    \item \url{http://dostielab.biochem.mcgill.ca}
-    \item \url{http://www.aidenlab.org/}
-    \item \url{http://web.cmb.usc.edu/people/alber/index.htm}
-    \item \url{http://calla.rnet.missouri.edu/cheng/nsf_career.html}
-\end{enumerate}
-\textbf{Resources related to Graphlet:}
-
-\begin{enumerate}
-    \item \url{https://en.wikipedia.org/wiki/Graphlets}
-    \item \url{https://academic.oup.com/bioinformatics/article/23/2/e177/202080/Biological-network-comparison-using-graphlet}
-    \item \url{http://www0.cs.ucl.ac.uk/staff/N.Przulj/index.html}
+    \item \href{https://github.com/rasoolianbehnam/watson}{Code base for this article}
+    \item \href{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}
+        {Datasets including cancerous cells}
+    \item \href{https://bcm.app.box.com/v/aidenlab/folder/11234760671}{Original Datasets}
 \end{enumerate}

### 2018-03-26 orbits/rscript.r
lost track

@@ -1,0 +1,8 @@
+library('orca')
+for (i in 0:72) {
+    filename = sprintf("orbit%02d.txt", i);
+    a <- read.csv(filename, header=FALSE); 
+    b = count5(a); 
+    c = sum(b[1, ] > 0); 
+    print(c);
+}

### 2018-03-26 rscript_intra.r

@@ -1,0 +1,34 @@
+library("orca")
+args <- commandArgs(trailingOnly = TRUE)
+chr1 <- as.integer(args[1])
+chr2 <- as.integer(args[2])
+
+mit_file_name <- sprintf("../data/data/chr%02d_chr%02d_mit.edges", chr1, chr2)
+all_file_name <- sprintf("../data/data/chr%02d_chr%02d_all.edges", chr1, chr2)
+rl_file_name <- sprintf("../data/data/chr%02d_chr%02d_rl.edges", chr1, chr2)
+call4_file_name <- sprintf("../data/data/chr%02d_chr%02d_call4.edges", chr1, chr2)
+
+print(mit_file_name)
+print(all_file_name)
+print(rl_file_name)
+print(call4_file_name)
+
+mit_file <- read.csv(mit_file_name)
+all_file <- read.csv(all_file_name)
+rl_file <- read.csv(rl_file_name)
+call4_file <- read.csv(call4_file_name)
+
+mit_graphlets <- count5(mit_file)
+all_graphlets <- count5(all_file)
+rl_graphlets <- count5(rl_file)
+call4_graphlets <- count5(call4_file)
+
+mit_graphlet_file = sprintf("../data/data/chr%02d_chr%02d_mit.graphlets", chr1, chr2)
+all_graphlet_file = sprintf("../data/data/chr%02d_chr%02d_all.graphlets", chr1, chr2)
+rl_graphlet_file = sprintf("../data/data/chr%02d_chr%02d_rl.graphlets", chr1, chr2)
+call4_graphlet_file = sprintf("../data/data/chr%02d_chr%02d_call4.graphlets", chr1, chr2)
+
+write.table(mit_graphlets, file = mit_graphlet_file ,row.names=FALSE, col.names=FALSE)
+write.table(all_graphlets, file = all_graphlet_file ,row.names=FALSE, col.names=FALSE)
+write.table(rl_graphlets, file = rl_graphlet_file ,row.names=FALSE, col.names=FALSE)
+write.table(call4_graphlets, file = call4_graphlet_file ,row.names=FALSE, col.names=FALSE)

### 2018-03-26 test_r.r

@@ -1,0 +1,33 @@
+library("orca")
+args <- commandArgs(trailingOnly = TRUE)
+chr <- as.integer(args[1])
+
+mit_file_name <- sprintf("data/chr%02d_chr%02d_mit.edges", chr, chr)
+all_file_name <- sprintf("data/chr%02d_chr%02d_all.edges", chr, chr)
+rl_file_name <- sprintf("data/chr%02d_chr%02d_rl.edges", chr, chr)
+call4_file_name <- sprintf("data/chr%02d_chr%02d_call4.edges", chr, chr)
+
+print(mit_file_name)
+print(all_file_name)
+print(rl_file_name)
+print(call4_file_name)
+
+mit_file <- read.csv(mit_file_name)
+all_file <- read.csv(all_file_name)
+rl_file <- read.csv(rl_file_name)
+call4_file <- read.csv(call4_file_name)
+
+mit_graphlets <- count5(mit_file)
+all_graphlets <- count5(all_file)
+rl_graphlets <- count5(rl_file)
+call4_graphlets <- count5(call4_file)
+
+mit_graphlet_file = sprintf("data/chr%02d_chr%02d_mit.graphlets", chr, chr)
+all_graphlet_file = sprintf("data/chr%02d_chr%02d_all.graphlets", chr, chr)
+rl_graphlet_file = sprintf("data/chr%02d_chr%02d_rl.graphlets", chr, chr)
+call4_graphlet_file = sprintf("data/chr%02d_chr%02d_call4.graphlets", chr, chr)
+
+write.table(mit_graphlets, file = mit_graphlet_file ,row.names=FALSE, col.names=FALSE)
+write.table(all_graphlets, file = all_graphlet_file ,row.names=FALSE, col.names=FALSE)
+write.table(rl_graphlets, file = rl_graphlet_file ,row.names=FALSE, col.names=FALSE)
+write.table(call4_graphlets, file = call4_graphlet_file ,row.names=FALSE, col.names=FALSE)

### 2018-03-26 utility.py

@@ -21,7 +21,7 @@ def eigendecompose(a):
     t = np.max([min, max])
     w = w / t
     v = v * t * t
-    print "result of multiplying eigenvalues and eigenvectors:"
+    print("result of multiplying eigenvalues and eigenvectors:")
     print v.dot(np.diag(w)).dot(np.linalg.inv(v))*t
     return w, v/t/t
 
@@ -98,7 +98,7 @@ def scale(m, epsilon=1e-5):
     return n
 
 #used to be simple read
-def readMat(fileName, delimiter="\t", ignoreHeader=False, remove_blanks=False):
+def readMat(fileName, delimiter="\t", ignoreHeader=False, remove_blanks=False, verbose=False):
     """
     Function:
     --------- 
@@ -124,7 +124,8 @@ def readMat(fileName, delimiter="\t", ignoreHeader=False, remove_blanks=False):
     observed
 
     """
-    print "file directory:", fileName
+    if verbose:
+        print "file directory:", fileName
     if not os.path.isfile(fileName):
         print "File %s does not exist"%fileName
         sys.exit(2)
@@ -246,7 +247,7 @@ def pearson(a, b=None):
     else:
         return pearson_sym(a)
 
-def row_wise_pearson(a, b):
+def row_wise_pearson(a, b, check_for_zeros=True):
     n1, m1 = a.shape
     n2, m2 = b.shape
     n = np.min([n1, n2])
@@ -255,6 +256,11 @@ def row_wise_pearson(a, b):
     b = b[:n, :m]
     counter2 = np.zeros(n)
     for i in range(n):
+        if check_for_zeros:
+            if np.sum(a[i, :]) == 0:
+                continue
+            if np.sum(b[i, :]) == 0:
+                continue
         counter2[i] = pearsonr(a[i, :], b[i, :])[0]
     return counter2
 
@@ -302,7 +308,7 @@ def scn(a, minDiff=1e-3, numIterations=1000):
 def gaussian_normalize(heatmap):
     return (heatmap - np.mean(heatmap) ) / np.std(heatmap)
 
-def _showImages(imageList, rows=None, cols=None, color_bar=False, titles=None, ax_labels=None):
+def _showImages(imageList, rows=None, cols=None, color_bar=False, titles=None, ax_labels=None, cmap=None, save_dir=None):
     if rows == None and cols == None:
         rows = 1
         cols = (len(imageList) + rows - 1) / rows
[…]

### 2018-03-26 papers/manuscripts/manuscript.tex
lost track
modified manuscript

@@
 
-We divided the task of graphlet comparison into two parts: first we compare
-graphlets from each contact map in normal cell lines (MIT) with the 
-same contact maps in the other three Leukemic cells. Second we compare 
-contact maps in a similar way but this time only between leukemic cells.
-In the former case, the null hypothesis is that there is no difference
-between contact maps of normal cells and leukemic cells and in the latter
-case, the null hypotheis is that there is no difference between 
-different leukemic cells.
+%We divided the task of graphlet comparison into two parts: first we compare
+%graphlets from each contact map in normal cell lines (MIT) with the 
+%same contact maps in the other three Leukemic cells. Second we compare 
+%contact maps in a similar way but this time only between leukemic cells.
+%In the former case, the null hypothesis is that there is no difference
+%between contact maps of normal cells and leukemic cells and in the latter
+%case, the null hypotheis is that there is no difference between 
+%different leukemic cells.
 
@@
 each contact map of two cell lines. 
-Let  $\mathbf{S}^A_{ij}$  and $\mathbf{S}^B_{ij}$ be
-signature matrices corresponding  to cells A and B
-respectively, then we can caclulate the 
-distance between each
-loci (row) $l$ in $S^A$ and the the same loci in $S^B$
-using the following formula from \cite{prvzulj2007biological}:
+For a pair of cells A and B, let 
+$\mathbf{S}^A_{ij}$  and $\mathbf{S}^B_{ij}$ be their
+signature matrices. The \textit{signature distance} of
+contact map $\mathbf{C}_{i,j}$ between A and B is denoted
+by $\mathbf{d}^{A,B}_{ij}$. $\mathbf{d}^{A,B}_{ij}$ 
+is a vector of size $|V_{i,j}|$
+and its elements $d^{A,B}_{i,j,l}$ are
+calculated using the following formula from \cite{prvzulj2007biological}:
 
 \begin{equation}
-    D(\mathbf{S}^A_{ij}, \mathbf{S}^B_{ij}) = 
-    \frac{1}{73}\sqrt{\sum_{o=0}^{72}{\mathbf{D}_{.o}^2}}
+    d^{A,B}_{i,j,l} = 
+    \frac{1}{73}\sqrt{\sum_{o=0}^{72}{t_{lo}^2}}
     \label{eq:distance_total}
 \end{equation}
-where elements of $\mathbf{D}$ can be calculated as follows:
+
+where elements of $t_{i,j,l,o}$ is the
+distance between each
+loci (row) $l$ in $\mathbf{S}^A$ and the the same loci in 
+$\mathbf{S}^B$ for
+orbit $o$ as is calculated as below:
+
 \begin{equation}
-    D_{lo} = w_o \times 
+    t_{lo} = w_o \times 
     \frac{log(S_{ijlo}^A+1) - log(S_{ijlo}^B+1)}
@@
 correlation measures.
-These correlations can be calculated as the following:
-\begin{equation}
-    Corr(\mathbf{S}^A_{ij}, \mathbf{S}^B{ij}) = \mathbf{c}_{ij}
-    \label{eq:correlation}
-\end{equation}
-where each element of $\mathbf{c}$ is calculated as below:
-\begin{equation}
-    c_{ijo} = Corr(\mathbf{S}^A_{ij.o}, \mathbf{S}^B_{ij.o})
-    \label{eq:correlation}
-\end{equation}
-
-For each contact map,  calculated
+These correlations are denoted by $\mathbf{m}^{A,B}_{i,j}$ and
+can be calculate using
+any plausible correlation measure. 
+In this study, for each contact map,  we calculated
 similarity between orbit distributions using Pearson's r 
@@
 
-\subsection{Hypotheses}
+If MIC is used as correlation measure, each element of 
+ $\mathbf{c}$ is calculated as below:
+\begin{equation}
+    m^{A,B}_{ijo} = MIC(\mathbf{S}^A_{ij.o}, \mathbf{S}^B_{ij.o})
+    \label{eq:mic}
+\end{equation}
+Alternatively, if we use Pearson criterion we would have:
+\begin{equation}
+    m^{A,B}_{ijo} = Pearson(\mathbf{S}^A_{ij.o}, \mathbf{S}^B_{ij.o})
+    \label{eq:pearson}
+\end{equation}
 
-With regard to the two aforementioned comparison methods, we define
-our two null hypotheses as the following:
-
-\begin{enumerate}
-    \item Average signature vector distance between each 
-        contact map of MIT cells and
-        their counterparts in the three leukemic cells
-        are equal to $0$. In mathematical terms:
-        $\forall i,j \in \{1, 2 ..., 24\}$
-        \begin{align}
-            \begin{split}
-                H_0&: \frac{1}{|V_{ij}|}\sum_{l=0}^{|V_{ij}|}{d_{ijl}} = 0 \\
-                H_1&: \frac{1}{|V_{ij}|}\sum_{l=0}^{|V_{ij}|}{d_{ijl}} > 0
-            \end{split}
-            \label{eq:h1}
-        \end{align}
-
-        where 
-        $\mathbf{d}_{ij} = D(S^{MIT}_{ij}, S^L_{ij})$ and $L \in \{ALL, RL, CALL4\}$.
-
-        \item 
-            \begin{enumerate}
-                \item Average orbit correlations within a contact map of MIT cell, 
-                    and its counterpart in leukemic cells is equal to 1
-                    for each contact map.
-                Again in mathematical terms:
-                $\forall i,j \in \{1, 2 ..., 24\}$
-                \begin{align}
-                    \begin{split}
-                        H_0&: \frac{1}{73}\sum_{o=0}^{72}{c_{ijo}} = 1 \\
-                        H_1&: \frac{1}{73}\sum_{o=0}^{72}{c_{ijo}} < 1
-                    \end{split}
-                    \label{eq:h2b}
-                \end{align}
-                        where $\mathbf{c}_{ij} = Corr(S^{MIT}_{ij}, S^L_{ij})$, $L$ 
-                        is the same as above and $N$ 
-                        is the total number of contact maps which 
-                        is equal to $275$ in our case.
-
-                \item Average orbit correlations  of MIT cell
-                    and leukemic cells across contact maps is equal to 1
-                    for each orbit.
-                Again in mathematical terms:
-
-                        \smallskip
-
-                    $\forall o \in \{0, 1 ... 72\}$
-                \begin{align}
-                    \begin{split}
-                        H_0&: \frac{1}{N}\sum_{i=1}^{23}{\sum_{j=i}^{23}{c_{ijo}}} = 1 \\
-                        H_1&: \frac{1}{N}\sum_{i=1}^{23}{\sum_{j=i}^{23}{c_{ijo}}} < 1
-                    \end{split}
-                    \label{eq:h2a}
-                \end{align}
-                        $L$ and $\mathbf{c}_{ij}$ are the same as above.
-
-            \end{enumerate}
-\end{enumerate}
 \section{results}
 
-\subsection{Hypothesis 1: Orbit Distance Comparison}
+Result of pair-wise contact map graphlet distances can is
+illustrated in Figure \ref{fig:orbit-distances}.
+Each point on the graph is the
+average of the graphlet distance vector 
+($\bar{\mathbf{d}}^{A,B}_{i,j}$)
+of the two cell lines specified in the legend.
+ A one sided paired t-test
+was conducted . The resulting p-values showed highly 
+significant differeces from zero for all pairs of
+cells. Detailed results of t-tests for each
+contact map can be fount in supplementary materials.
+For each contact map, each pair of cells are
+order based on whether they are statistially
+larger that the other or not. For example
+for contact map $C_{i,j}$, the results 
+of t-test is as follows:\\
+\smallskip
+{
+    \small
+zero  $<$  call4-mit  $<$     all-rl  $<$     mit-rl  $<$   call4-rl  $<$    all-mit  $=$  all-call4
+}\\
+\smallskip
+which means that $\mathbf{d}^{\scriptscriptstyle CALL4, MIT}_{1,1}$ is statistically larger than 0,
+but less than $\mathbf{d}^{\scriptscriptstyle ALL, RL}_{1,1}$ 
+and so forth. We can also conclude that $\mathbf{d}^{\scriptscriptstyle ALL, CALL4}_{1,1}$ is not
+statistically different from $\mathbf{d}^{\scriptscriptstyle ALL, MIT}_{1,1}$
+between graphlets extracted from all contact maps. 
+Refer to supplementary
+material for results of all hypotheis tests.
+
 \begin{figure*}[t]
@@
     \end{subfigure}
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figures/orbit-distances_intra_separate.png}
+        \caption{}
+        \label{fig:orbit-distances_intra_separate}
+    \end{subfigure}
     \caption{   Pair-wise graphlet signature difference for
@@
                 (b) only the 23 intra-chromosomal contact maps.
+                (c) all 276 contact maps as well as corresponding
+                standard errors.
                 Each point on a graph is the result of averaging all
@@
 \end{figure*}
-Result of pair-wise contact map graphlet distances can is
-demonstrated in Figure \ref{fig:orbit-distances}.
-Each point on the graph is the
-average distance between signature vector of two same loci 
-in the two cell lines as in Equation \ref{eq:h1}.
-in order to test hypothesis \ref{eq:h1} a one sided t-test
-was conducted. The resulting p-values showed highly significant differeces
-between graphlets extracted from all contact maps. Refer to supplementary
-material for results of all hypotheis tests.
 
-\subsection{Hypothesis 2: Orbit distribution comparison}
-We caclulated pair-wise Pearson's r correlation for each orbit in each of the 276
+We caclulated pair-wise MIC for each orbit in each of the 276
 contact maps from MIT data and ALL, RL and CALL4 data separately. 
@@
 shows average orbit correlations across all contact maps
-(average along the red \textit{vertical} arrow in figure 
+($\bar{\mathbf{c}}^{\scriptscriptstyle A,B}_{i,j}$: average along the red \textit{vertical} arrow in figure 
 \ref{graphlet_correlation_schema}), while

### 2018-03-26 papers/manuscripts/manuscript/images.pl

@@ -1,0 +1,470 @@
+# LaTeX2HTML 2008 (1.71)
+# Associate images original text with physical files.
+
+
+$key = q/jgei;MSF=1.6;AAT/;
+$cached_env_img{$key} = q|<IMG
+ WIDTH="1069" HEIGHT="193" ALIGN="MIDDLE" BORDER="0"
+ SRC="|."$dir".q|img22.png"
+ ALT="$ j \ge i$">|; 
+
+$key = q/i;MSF=1.6;AAT/;
+$cached_env_img{$key} = q|<IMG
+ WIDTH="1069" HEIGHT="179" ALIGN="BOTTOM" BORDER="0"
+ SRC="|."$dir".q|img4.png"
+ ALT="$ i$">|; 
+
+$key = q/V^{ij};MSF=1.6;AAT/;
+$cached_env_img{$key} = q|<IMG
+ WIDTH="1069" HEIGHT="182" ALIGN="BOTTOM" BORDER="0"
+ SRC="|."$dir".q|img31.png"
+ ALT="$ V^{ij}$">|; 
+
+$key = q/displaystylec_{ijo}=Pearson(mathbf{S}^A_{ij.o},mathbf{S}^B_{ij.o});MSF=1.6;AAT/;
+$cached_env_img{$key} = q|<IMG
+ WIDTH="1069" HEIGHT="202" ALIGN="MIDDLE" BORDER="0"
+ SRC="|."$dir".q|img48.png"
+ ALT="$\displaystyle c_{ijo} = Pearson(\mathbf{S}^A_{ij.o}, \mathbf{S}^B_{ij.o})$">|; 
+
+$key = q/{subfigure}%latex2htmlidmarker235[b]{textwidth}includegraphics[width=textwidth]{figuresslashorbit-distances_all.png}{caption{}{{subfigure};FSF=1.6;AAT/;
+$cached_env_img{$key} = q|<IMG
+ WIDTH="1069" HEIGHT="172" BORDER="0"
+ SRC="|."$dir".q|img62.png"
+ ALT="\begin{subfigure}
+% latex2html id marker 235
+[b]{\textwidth}
+\includegraphics[width=\textwidth]{figures/orbit-distances_all.png}
+\caption{}
+\end{subfigure}">|; 
+
+$key = q/L;MSF=1.6;AAT/;
[…]

### 2018-03-26 papers/manuscripts/manuscript/internals.pl

@@ -1,0 +1,130 @@
+# LaTeX2HTML 2008 (1.71)
+# Associate internals original text with physical files.
+
+
+$key = q/cite_milenkovic2010cancer/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/fig:contact_maps_correlations_all/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/eq:correlation/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/cite_milenkoviae2008uncovering/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/cite_prvzulj2007biological/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/eq:distance_total/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/fig:orbit-distances_intra/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/fig:orbit-distances/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/fig:graphlet_extraction/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/fig:contact_maps_correlations/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/local_thresholded_chr1_chr1/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/eq:h2a/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/eq:h2b/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/eq:h1/;
+$ref_files{$key} = "$dir".q|manuscript.html|; 
[…]

### 2018-03-26 papers/manuscripts/manuscript/labels.pl

@@ -1,0 +1,141 @@
+# LaTeX2HTML 2008 (1.71)
+# Associate labels original text with physical files.
+
+
+$key = q/fig:orbit_distances_intra_cancer/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/fig:orbits_correlations/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/eq:mic/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/fig:orbits_correlations_intra_cancer/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/fig:orbit-distances_all/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/fig:orbits_correlations_all/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/cite_reshef2011detecting/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/eq:distance_single/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/cite_lieberman2009comprehensive/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/fig:contact_maps_correlations_intra/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/eq:pearson/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/cite_milenkovic2010cancer/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
+$noresave{$key} = "$nosave";
+
+$key = q/fig:contact_maps_correlations_all/;
+$external_labels{$key} = "$URL/" . q|manuscript.html|; 
[…]

### 2018-03-27 papers/manuscripts/manuscript.tex
modified manuscript

@@
 shows average orbit correlations across all contact maps
-($\bar{\mathbf{c}}^{\scriptscriptstyle A,B}_{i,j}$: average along the red \textit{vertical} arrow in figure 
+($\bar{\mathbf{c}}^{\scriptscriptstyle A,B}_{i,j} 
+\quad \forall i,j \in {1 ... 23} \quad \& \quad j \le i$,
+average along the red \textit{vertical} arrow in figure 
 \ref{graphlet_correlation_schema}), while
@@
 demonstrates average correlations across all 72 orbits within each  contact map
-(average along the red \textit{horizontal} arrows in figure 
+($\frac{1}{276}\sum_{i=0}^{23}\sum_{j=i}^{23}{
+    c^{\scriptscriptstyle A,B}_{i,j}}$,
+average along the red \textit{horizontal} arrows in figure 
 \ref{graphlet_correlation_schema}).

### 2018-03-27 papers/manuscripts/manuscript.tex
manuscript modification

--- 2018-03-26 papers/manuscripts/manuscript.tex
@@
 contact map $\mathbf{C}_{i,j}$ between A and B is denoted
-by $\mathbf{d}^{A,B}_{ij}$. $\mathbf{d}^{A,B}_{ij}$ 
+by $\mathbf{d}^{\scriptscriptstyle A,B}_{ij}$. $\mathbf{d}^{\scriptscriptstyle A,B}_{ij}$ 
 is a vector of size $|V_{i,j}|$
-and its elements $d^{A,B}_{i,j,l}$ are
+and its elements $d^{\scriptscriptstyle A,B}_{i,j,l}$ are
 calculated using the following formula from \cite{prvzulj2007biological}:
@@
 \begin{equation}
-    d^{A,B}_{i,j,l} = 
+    d^{\scriptscriptstyle A,B}_{i,j,l} = 
     \frac{1}{73}\sqrt{\sum_{o=0}^{72}{t_{lo}^2}}
@@
 correlation measures.
-These correlations are denoted by $\mathbf{m}^{A,B}_{i,j}$ and
+These correlations are denoted by $\mathbf{m}^{\scriptscriptstyle A,B}_{i,j}$ and
 can be calculate using
@@
 \begin{equation}
-    m^{A,B}_{ijo} = MIC(\mathbf{S}^A_{ij.o}, \mathbf{S}^B_{ij.o})
+    m^{\scriptscriptstyle A,B}_{ijo} = MIC(\mathbf{S}^A_{ij.o}, \mathbf{S}^B_{ij.o})
     \label{eq:mic}
@@
 \begin{equation}
-    m^{A,B}_{ijo} = Pearson(\mathbf{S}^A_{ij.o}, \mathbf{S}^B_{ij.o})
+    m^{\scriptscriptstyle A,B}_{ijo} = Pearson(\mathbf{S}^A_{ij.o}, \mathbf{S}^B_{ij.o})
     \label{eq:pearson}
@@
 average of the graphlet distance vector 
-($\bar{\mathbf{d}}^{A,B}_{i,j}$)
+($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j}$)
 of the two cell lines specified in the legend.
@@
 for contact map $C_{i,j}$, the results 
-of t-test is as follows:\\
-\smallskip
-{
-    \small
+of t-test is as follows:
+\vspace{.2cm}\\
+\small{
 zero  $<$  call4-mit  $<$     all-rl  $<$     mit-rl  $<$   call4-rl  $<$    all-mit  $=$  all-call4
-}\\
-\smallskip
+}
+\vspace{.2cm}\\
 which means that $\mathbf{d}^{\scriptscriptstyle CALL4, MIT}_{1,1}$ is statistically larger than 0,
@@
     \caption{   Pair-wise graphlet signature difference for
-                (a) all 276 contact maps.
-                (b) only the 23 intra-chromosomal contact maps.
-                (c) all 276 contact maps as well as corresponding
+                (\textbf{a}) all 276 contact maps
+                ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j} \quad
+                \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$).
+                (\textbf{b}) only the 23 intra-chromosomal contact maps
+                ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,i}$).
+                (\textbf{c}) all 276 contact maps as well as corresponding
                 standard errors.
@@
 Figure \ref{fig:contact_maps_correlations}
-shows average orbit correlations across all contact maps
-($\bar{\mathbf{c}}^{\scriptscriptstyle A,B}_{i,j}$: average along the red \textit{vertical} arrow in figure 
-\ref{graphlet_correlation_schema}), while
+shows average orbit correlations across all contact maps, while
 figure \ref{fig:orbits_correlations} 
-demonstrates average correlations across all 72 orbits within each  contact map
-(average along the red \textit{horizontal} arrows in figure 
-\ref{graphlet_correlation_schema}).
+demonstrates average correlations across all 72 orbits within each  contact map.
 It is worth mentioning that \textit{interchromosomal} thresholded contact maps 
 represent
-a biparticde graph with the loci from each chromosome on one side. Due to this
+a bipartide graph with the loci from each chromosome on one side. Due to this
 bipartide nature of the graphs in inter-chromosomal maps,
@@
 would result in a bias towards zero in averages. You can see the bias in 
-figure \ref{fig:orbits_correlations_all} where average correlations of obits
-3, 9, 10-14, 20-34, 39-48, and 51-72 are close to zero. In fact all correlations
+figure \ref{fig:orbits_correlations_all} where average correlations of orbits
+$\mathbb{Q} = \{3, 9, 10{\text -}14, 20{\text -}34, 39{\text -}48, 51{\text -}72\}$ 
+are close to zero. In fact all correlations
 corresponding to these orbits are 0 except for the ones between the same 
@@
     \caption{pair-wise average contact map orbit correlations
-             (a) for all contact maps
+             (a) for all contact maps($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j} 
+            \quad \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$,
+            average along the red \textit{vertical} arrow in figure 
+            \ref{graphlet_correlation_schema})
              (b) only for intra-chromosomal contact maps
+            ($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,i} 
+            \quad \forall i \in \{1 ... 23\} $)
              These values are calculated by averaging over 
@@
              in the graph is the result of averaging pair-wise
-             orbit correlations over all contact maps, while
+             orbit correlations over all contact maps
+             ($\frac{1}{276}\sum_{i=0}^{23}\sum_{j=i}^{23}{
+             m^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j, o}} \quad 
+             \forall o \in \{0, 1, ..., 72\}$,
+             average along the red \textit{horizontal} arrows in figure 
+             \ref{graphlet_correlation_schema}), while
              each point in figure \ref{fig:orbits_correlations_intra}
-             are averaged only over intra-chromosomal contact maps.
+             are averaged only over intra-chromosomal contact maps
+             ($\frac{1}{23}\sum_{i=0}^{23}{
+             m^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,i, o}} \quad 
+         \forall o \in \{0, 1, ..., 72\}$).
              Counts for certain orbits are always zero in inter-chromosomal
@@
 t-test in order to test whether the average correlations across
-contact maps is equal to 1 (Equation \ref{eq:h2a}) and whether the average 
-correlations across orbits is equal to 1 (Equation \ref{eq:h2b}). The results
+contact maps is equal to 1  and whether the average 
+correlations across orbits is equal to 1. The results
 for both test showed that all values are significantly less than 1.
 Please refer to supplementary material for result of the t-tests.
-\subsection{Comparing Cancer cells}
-\begin{figure*}[t]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{figures/orbit-distances_intra_cancer.png}
-        \caption{}
-        \label{fig:orbit_distances_intra_cancer}
-    \end{subfigure}
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{figures/orbits_correlations_intra_cancer.png}
-        \caption{}
-        \label{fig:orbits_correlations_intra_cancer}
-    \end{subfigure}
-    \caption{}
-    \label{fig:orbits_cancer_intra}
-\end{figure*}
 
-We also conducted the same comparison with the same hypothesis among cancer cells.
-The results for intra-chromosomal distances and correlations can be found in
-figure \ref{fig:orbits_cancer_intra}. As can be noticed, CALL4 and RL cell
-line exhibit a significantly higher average correlations for the majority of
-the chromosomes (figure \ref{fig:orbit_distances_intra_cancer}) and almost in
-all orbits (figure \ref{fig:orbits_correlations_intra_cancer}).
 \section{discussion}

### 2018-03-27 papers/manuscripts/manuscript/images.pl

@@ -1,470 +1,0 @@
-# LaTeX2HTML 2008 (1.71)
-# Associate images original text with physical files.
-
-
-$key = q/jgei;MSF=1.6;AAT/;
-$cached_env_img{$key} = q|<IMG
- WIDTH="1069" HEIGHT="193" ALIGN="MIDDLE" BORDER="0"
- SRC="|."$dir".q|img22.png"
- ALT="$ j \ge i$">|; 
-
-$key = q/i;MSF=1.6;AAT/;
-$cached_env_img{$key} = q|<IMG
- WIDTH="1069" HEIGHT="179" ALIGN="BOTTOM" BORDER="0"
- SRC="|."$dir".q|img4.png"
- ALT="$ i$">|; 
-
-$key = q/V^{ij};MSF=1.6;AAT/;
-$cached_env_img{$key} = q|<IMG
- WIDTH="1069" HEIGHT="182" ALIGN="BOTTOM" BORDER="0"
- SRC="|."$dir".q|img31.png"
- ALT="$ V^{ij}$">|; 
-
-$key = q/displaystylec_{ijo}=Pearson(mathbf{S}^A_{ij.o},mathbf{S}^B_{ij.o});MSF=1.6;AAT/;
-$cached_env_img{$key} = q|<IMG
- WIDTH="1069" HEIGHT="202" ALIGN="MIDDLE" BORDER="0"
- SRC="|."$dir".q|img48.png"
- ALT="$\displaystyle c_{ijo} = Pearson(\mathbf{S}^A_{ij.o}, \mathbf{S}^B_{ij.o})$">|; 
-
-$key = q/{subfigure}%latex2htmlidmarker235[b]{textwidth}includegraphics[width=textwidth]{figuresslashorbit-distances_all.png}{caption{}{{subfigure};FSF=1.6;AAT/;
-$cached_env_img{$key} = q|<IMG
- WIDTH="1069" HEIGHT="172" BORDER="0"
- SRC="|."$dir".q|img62.png"
- ALT="\begin{subfigure}
-% latex2html id marker 235
-[b]{\textwidth}
-\includegraphics[width=\textwidth]{figures/orbit-distances_all.png}
-\caption{}
-\end{subfigure}">|; 
-
-$key = q/L;MSF=1.6;AAT/;
-$cached_env_img{$key} = q|<IMG
[…]

### 2018-03-27 papers/manuscripts/manuscript/internals.pl

@@ -1,130 +1,0 @@
-# LaTeX2HTML 2008 (1.71)
-# Associate internals original text with physical files.
-
-
-$key = q/cite_milenkovic2010cancer/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/fig:contact_maps_correlations_all/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/eq:correlation/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/cite_milenkoviae2008uncovering/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/cite_prvzulj2007biological/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/eq:distance_total/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/fig:orbit-distances_intra/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/fig:orbit-distances/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/fig:graphlet_extraction/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/fig:contact_maps_correlations/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/local_thresholded_chr1_chr1/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/eq:h2a/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/eq:h2b/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/eq:h1/;
-$ref_files{$key} = "$dir".q|manuscript.html|; 
[…]

### 2018-03-27 papers/manuscripts/manuscript/labels.pl

@@ -1,141 +1,0 @@
-# LaTeX2HTML 2008 (1.71)
-# Associate labels original text with physical files.
-
-
-$key = q/fig:orbit_distances_intra_cancer/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/fig:orbits_correlations/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/eq:mic/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/fig:orbits_correlations_intra_cancer/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/fig:orbit-distances_all/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/fig:orbits_correlations_all/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/cite_reshef2011detecting/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/eq:distance_single/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/cite_lieberman2009comprehensive/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/fig:contact_maps_correlations_intra/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/eq:pearson/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/cite_milenkovic2010cancer/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
-$noresave{$key} = "$nosave";
-
-$key = q/fig:contact_maps_correlations_all/;
-$external_labels{$key} = "$URL/" . q|manuscript.html|; 
[…]

### 2018-03-27 papers/manuscripts/manuscript.tex
modified graph in the manuscript

@@
 \jissue{12}
+
+\usepackage{tikz}
+\usetikzlibrary{shapes}
+\usetikzlibrary{positioning}
+\usetikzlibrary{arrows}
+\usetikzlibrary{fit}
+\usetikzlibrary{decorations.pathreplacing}
+\usetikzlibrary{shadows.blur}
+\usetikzlibrary{shapes.symbols}
 
@@
 \subsubsection{Notations}
-In this paper, matrices and vectors are represented as bold
+In this paper, matrices and vectors are represented with bold
 capital and bold small letters respectively.
@@
 The set of all loci involved in contact map $C_{ij}$ is denoted 
-by $V_{ij}$.
-In intra-chromosomal contact maps, $V_{i,i}$ containts only the 
-loci of that particular chromosome ($|V_i| = N_i$), while in 
-inter-chromosomal contact maps $V_{ij}$ contains the loci in
-the both of chromosomes involved ($|V_{ij}| = N_i + N_j$).
+by $\mathbb{V}_{ij}$.
+In intra-chromosomal contact maps, $\mathbb{V}_{i,i}$ containts only the 
+loci of that particular chromosome ($|\mathbb{V}_i| = N_i$), while in 
+inter-chromosomal contact maps $\mathbb{V}_{ij}$ contains the loci in
+the both of chromosomes involved ($|\mathbb{V}_{ij}| = N_i + N_j$).
 
@@
 
+%\begin{tikzpicture}
+%    \node [] (a) at (0, 0) {
+%        $\begin{pmatrix}  
+%            C_{\scriptscriptstyle 1,1,1,1}     &   C_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C_{\scriptscriptstyle 1,1,1,N_1} \\
+%            C_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
+%            \vdots                             &                & \ddots           &      \\
+%            C_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C_{\scriptscriptstyle 1,1,N_1, N_1} 
+%        \end{pmatrix}$
+%    };
+%    \node [] (b) [left=1pt of a] {$N_1$};
+%    \node [] (c) [above=1pt of a] {$N_1$};
+%\end{tikzpicture}
 \bibliography{lit}

### 2018-03-27 papers/manuscripts/manuscript.tex
updated manuscript

@@
 
-In this study, we plan to find dissimilarities between normal cells and cancerous cells,
-through investigating HiC contact maps. 
-We suspect that there are systematic differences between how chromosomes are structured
-between normal cells and cancerous cells.
-we 
-Ideally, it is desirable to compare 3D structures of 
-cell in order to make such comparisons.
-However, the main challenge that we face is that 
-3D structure of a cell is not readily available. Based on
-\cite{adhikari2016chromosome3d}, fluorescence in situ hybridizaiton
-(FISH) is used for investigating 3D configuration of chromosomes.
-However, this method can only be used locally and cannot map
-the whole structure of the chromosomes.
-In orther to find dissimilarities in the 3D structure of 
-chromosomes, we used HiC dataset.
-The HiC method, which was developed by \cite{lieberman2009comprehensive}, captures interactions between 
-chromosomal fragments in kilobase resolution. Based on HiC data, an
-\textit{interaction frequency (IF) } matrix can be developed between \textit{loci} at a desired resolution.
-A cell $IF_{ij}$ in an interaction frequency matrix captures the number of interaction detected
-in HiC dataset between locus $i$ and locus $j$ in the genome.
-An interaction matrix can be used to develop both inter- and intra-chromosomal interaction matrices.
-We believe differences in interaction matrices can be found between normal cells and cancerous ones.
+In this study, we investigated
+dissimilarities between normal cells and cancerous cells,
+through analyzing HiC contact maps. 
+Our results show that certain orbit distributions
+have significanly higher correlation 
+between Leukemic cells.
+
 \end{abstract}
+
 \section{Introduction}
@@
 how geometrically close their corresponding vectors are.
-\section{Materials and Methods}
+
 \subsubsection{Notations}
@@
 % **************************************************************
+
+\section{Materials and Methods}
+We re-used Leukemic Hi-C libraries 
+created in \cite{wang2013properties}
+These libraries we sequenced 
+for cases of primary human B-acute
+lymphoblastic leukemia (B-ALL or ALL), 
+the MHH-CALL-4 B-ALL cell
+line (CALL4), 
+and the follicular lymphoma cell-line (RL).
+Just as \cite{wang2013properties}, 
+we used normal B-cell line (GM068990)
+from \cite{lieberman2009comprehensive} 
+for our comparisons.
+We created contact maps of resolution
+500kb and normalized it using 
+the \texttt{iced} package in python
+developed by \cite{servant2015hic}.
 
@@
 and 1 meaning one is dependant on the other.
-We used both Pearson's r and MI in order to compare orbit
+We used both Pearson's r and MIC in order to compare orbit
 frequencies. Although results from both approaches were more
@@
 
-\section{results}
+\section{results and discussions}
 
 Result of pair-wise contact map graphlet distances can is
-illustrated in Figure \ref{fig:orbit-distances}.
+illustrated in Figure \ref{fig:orbit-distances_all}.
 Each point on the graph is the
@@
  A one sided paired t-test
-was conducted . The resulting p-values showed highly 
+was conducted in order to compare distances to
+zero and also to each other. 
+The resulting p-values showed highly 
 significant differeces from zero for all pairs of
 cells. Detailed results of t-tests for each
-contact map can be fount in supplementary materials.
+contact map can be found in supplementary materials.
 For each contact map, each pair of cells are
-order based on whether they are statistially
+ordered based on whether they are statistially
 larger that the other or not. For example
-for contact map $C_{i,j}$, the results 
+for contact map $C_{1,1}$, the results 
 of t-test is as follows:
@@
 \vspace{.2cm}\\
-which means that $\mathbf{d}^{\scriptscriptstyle CALL4, MIT}_{1,1}$ is statistically larger than 0,
+which means that 
+$\mathbf{d}^{\scriptscriptstyle CALL4, MIT}_{1,1}$ 
+is statistically larger than 0,
 but less than $\mathbf{d}^{\scriptscriptstyle ALL, RL}_{1,1}$ 
-and so forth. We can also conclude that $\mathbf{d}^{\scriptscriptstyle ALL, CALL4}_{1,1}$ is not
-statistically different from $\mathbf{d}^{\scriptscriptstyle ALL, MIT}_{1,1}$
+and so forth. We can also conclude that 
+$\mathbf{d}^{\scriptscriptstyle ALL, CALL4}_{1,1}$ is not
+statistically different from 
+$\mathbf{d}^{\scriptscriptstyle ALL, MIT}_{1,1}$
 between graphlets extracted from all contact maps. 
@@
 
-\begin{figure*}[t]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{figures/orbit-distances_all.png}
-        \caption{}
-        \label{fig:orbit-distances_all}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{figures/orbit-distances_intra.png}
-        \caption{}
-        \label{fig:orbit-distances_intra}
-    \end{subfigure}
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{figures/orbit-distances_intra_separate.png}
-        \caption{}
-        \label{fig:orbit-distances_intra_separate}
-    \end{subfigure}
-    \caption{   Pair-wise graphlet signature difference for
-                (\textbf{a}) all 276 contact maps
-                ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j} \quad
-                \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$).
-                (\textbf{b}) only the 23 intra-chromosomal contact maps
-                ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,i}$).
-                (\textbf{c}) all 276 contact maps as well as corresponding
-                standard errors.
-                Each point on a graph is the result of averaging all
-                the distances acroos all loci of that contact map.
-                As can be viewd, although inter-chromosomal graphlets 
-                do not show significant differences, RL's inter-chromosomal
-                graphlets seem to be closer to MIT's. Also in some contact
-                maps ALL graphlets show greater distance from MIT graphlets
-                than the other two cell lines.
-             }
-    \label{fig:orbit-distances}
-\end{figure*}
-
 We caclulated pair-wise MIC for each orbit in each of the 276
 contact maps from MIT data and ALL, RL and CALL4 data separately. 
-Figure \ref{fig:contact_maps_correlations}
+Figure \ref{fig:contact_maps_correlations_all}
 shows average orbit correlations across all contact maps, while
-figure \ref{fig:orbits_correlations} 
+figure \ref{fig:orbits_correlations_all} 
 demonstrates average correlations across all 72 orbits within each  contact map.
-It is worth mentioning that \textit{interchromosomal} thresholded contact maps 
+It is worth mentioning that interchromosomal thresholded contact maps 
 represent
@@
 corresponding to these orbits are 0 except for the ones between the same 
-chromosomes which are illustrated in Figure 
-\ref{fig:orbits_correlations_intra}.
+chromosomes.
 
-\begin{figure*}[t]
+Figure \ref{fig:orbits_correlations_all} clearly illustrates certain
+orbits of Leukemic have higher correlation to each other than to the
+normal MIT cell. In fact our statistical analysis shows that 
+\textit {for orbits in $\mathbb{Q}$, 
+intra-leukemic orbit correlations are significantly higher
+than leukemic-normal orbit correlations}. This implies
+there are significant differences between normal and
+leukemic cells in terms of their local structure.
+\begin{figure}
     \centering
-    \begin{subfigure}[b]{\textwidth}
+    \begin{subfigure}[b]{.5\textwidth}
+        \includegraphics[width=\textwidth]{figures/orbit-distances_all.png}
+        \caption{}
+        \label{fig:orbit-distances_all}
+    \end{subfigure}
+    \begin{subfigure}[b]{.5\textwidth}
         \includegraphics[width=\textwidth]{figures/contact_maps_correlations_all.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_intra.png}
-        \caption{}
-        \label{fig:contact_maps_correlations_intra}
-    \end{subfigure}
-    \caption{pair-wise average contact map orbit correlations
-             (a) for all contact maps($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j} 
-            \quad \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$,
-            average along the red \textit{vertical} arrow in figure 
-            \ref{graphlet_correlation_schema})
-             (b) only for intra-chromosomal contact maps
-            ($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,i} 
-            \quad \forall i \in \{1 ... 23\} $)
-             These values are calculated by averaging over 
-             pairwise correlations of all orbits in a 
-             contact map.
-             }
-    \label{fig:contact_maps_correlations}
-\end{figure*}
-
-\begin{figure*}[t]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth, height=.2\paperheight]{figures/orbits_correlations_all.png}
+    \begin{subfigure}[b]{.5\textwidth}
+        \includegraphics[width=\textwidth]{figures/orbits_correlations_all.png}
         \caption{}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth, height=.2\paperheight]{figures/orbits_correlations_intra.png}
-        \caption{}
-        \label{fig:orbits_correlations_intra}
-    \end{subfigure}
-    \caption{pair-wise average orbit correlations.
+    \caption{   
+        \textbf{(a) Pair-wise graphlet signature difference for
+        all 276 contact maps:}
+        Each point on a graph is the result of averaging all
+        the distances across all loci of that contact map.
+        ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j} \quad
+        \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$).  
+        \vspace{.1cm} \\
+        \textbf{(b) pair-wise average contact map orbit correlations
+         for all contact maps:}
+        ($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j} 
+        \quad \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$:
+        average along the red \textit{vertical} arrow in figure 
+        \ref{graphlet_correlation_schema}).
+        These values are calculated by averaging over 
+        pairwise correlations of orbits of
+        $\mathbb{Q}$ in a contact map.
+        \vspace{.1cm} \\
+        \textbf{(c) pair-wise average orbit correlations:}
         In figure \ref{fig:orbits_correlations_all}, each point
@@
         m^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j, o}} \quad 
-             \forall o \in \{0, 1, ..., 72\}$,
+        \forall o \in \{0, 1, ..., 72\}$:
         average along the red \textit{horizontal} arrows in figure 
-             \ref{graphlet_correlation_schema}), while
-             each point in figure \ref{fig:orbits_correlations_intra}
-             are averaged only over intra-chromosomal contact maps
-             ($\frac{1}{23}\sum_{i=0}^{23}{
-             m^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,i, o}} \quad 
-         \forall o \in \{0, 1, ..., 72\}$).
+        \ref{graphlet_correlation_schema}).
         Counts for certain orbits are always zero in inter-chromosomal
         maps, leading to average value close to zero in 
-             \ref{fig:orbits_correlations_all}.
+        Figure \ref{fig:orbits_correlations_all}.
      }
-    \label{fig:orbits_correlations}
-\end{figure*}
+    \label{fig:results_all}
+\end{figure}
+
 We have conducted one-sided
@@
 for both test showed that all values are significantly less than 1.
-Please refer to supplementary material for result of the t-tests.
+Please refer to supplementary material for result of the 
+full list of t-test results.
 
-\section{discussion}
 \newpage

### 2018-03-29 papers/manuscripts/manuscript.tex
added t-test table
Coverted the correlation image to latex

@@
 \usepackage[super]{nth}
+\usepackage{multirow}
 % Enter dates of publication
@@
 full list of t-test results.
-
+\begin{table}[]
+    \centering
+    \resizebox{.5\textwidth}{!}{
+    \begin{tabular}{l|ccccccc}
+        \rule{0pt}{25pt}
+                  & One       & MIT-RL       & ALL-RL       & ALL-MIT      & ALL-CALL4    & CALL4-MIT    & CALL4-RL     \\ \hline
+        \rule{0pt}{25pt}
+        One       & -         & \textgreater & \textgreater & \textgreater & \textgreater & \textgreater & \textgreater \\
+        \rule{0pt}{25pt}
+        MIT-RL    & \textless & -            & \textless    & \textless    & \textless    & \textless    & \textless    \\
+        \rule{0pt}{25pt}
+        ALL-RL    & \textless & \textgreater & -            & \textless    & \textless    & \textless    & \textless    \\
+        \rule{0pt}{25pt}
+        ALL-MIT   & \textless & \textgreater & \textgreater & -            & =            & =            & =            \\
+        \rule{0pt}{25pt}
+        ALL-CALL4 & \textless & \textgreater & \textgreater & =            & -            & =            & =            \\
+        \rule{0pt}{25pt}
+        CALL4-MIT & \textless & \textgreater & \textgreater & =            & =            & -            &              \\
+        CALL4-RL  & \textless & \textgreater & =            & =            & =            & =            & -           
+        \rule{0pt}{25pt}
+    \end{tabular}}
+    \caption{}
+    \label{tab:t-test}
+\end{table}
 \newpage
@@
 
-%\begin{tikzpicture}
-%    \node [] (a) at (0, 0) {
-%        $\begin{pmatrix}  
-%            C_{\scriptscriptstyle 1,1,1,1}     &   C_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C_{\scriptscriptstyle 1,1,1,N_1} \\
-%            C_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
-%            \vdots                             &                & \ddots           &      \\
-%            C_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C_{\scriptscriptstyle 1,1,N_1, N_1} 
-%        \end{pmatrix}$
-%    };
-%    \node [] (b) [left=1pt of a] {$N_1$};
-%    \node [] (c) [above=1pt of a] {$N_1$};
-%\end{tikzpicture}
+\tikzset{
+    myArrow/.style={
+    single arrow,
+    draw,
+    text width =.3cm,
+    scale=.8,
+    shade, shading=axis, left color=orange, right color=yellow,
+    shading angle=45,
+    blur shadow={shadow blur steps=5,shadow blur extra rounding=1.3pt}
+    }
+}
+
+\begin{table}[]
+    \centering
+    \resizebox{.5\textwidth}{!}{
+        \begin{tabular}{lllllp{1cm}ll}
+            &\multicolumn{1}{c}{\textbf{\huge Cell A graphlets $S^A_{i,j}$}}  & \multicolumn{1}{c}{\textbf{\huge Cell B graphlets $S^B_{i,j}$}} 
+            && \multicolumn{1}{c}{\textbf{\huge Correlation Vector $m^{A,B}_{i,j}$}} 
+            && \multicolumn{1}{c}{\textbf{\huge Correlation Matrix $M^{A,B}_{i,j}$}} \vspace{.5cm} \\
+        &\multicolumn{1}{c}{$N_1$}  & \multicolumn{1}{c}{72} && \multicolumn{1}{c}{72} \vspace{.5cm}\\
+        \rule{0pt}{40pt}
+        $N_1$ &
+        \resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            C^A_{\scriptscriptstyle 1,1,1,1}     &   C^A_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 1,1,1,N_1} \\
+            C^A_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^A_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 1,1,N_1, N_1} 
+        \end{pmatrix}$} &
+        \resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            C^B_{\scriptscriptstyle 1,1,1,1}     &   C^B_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 1,1,1,N_1} \\
+            C^B_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^B_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C^B_{\scriptscriptstyle 1,1,N_1, N_1} 
+        \end{pmatrix}$} &
+        \begin{tikzpicture}
+            \draw [->] (0, 0) -> (2, 0);
+        \end{tikzpicture} &
+        \resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            m_{\scriptscriptstyle 1,1,0}     &   m_{\scriptscriptstyle 1,1,1}  & \cdots    &    m_{\scriptscriptstyle 1,1,72}
+        \end{pmatrix}$} \vspace{1cm}\\
+
+        &\multicolumn{1}{c}{$N_2$}  & \multicolumn{1}{c}{72} && \multicolumn{1}{c}{72} \vspace{.5cm}\\
+        \rule{0pt}{45pt}
+        $N_1$ &
+        \resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            C^A_{\scriptscriptstyle 1,2,1,1}     &   C^A_{\scriptscriptstyle 1,2,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 1,2,1,N_1} \\
+            C^A_{\scriptscriptstyle 1,2,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^A_{\scriptscriptstyle 1,2,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 1,2,N_1, N_1} 
+        \end{pmatrix}$}&
+        \resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            C^B_{\scriptscriptstyle 1,2,1,1}     &   C^B_{\scriptscriptstyle 1,2,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 1,2,1,N_2} \\
+            C^B_{\scriptscriptstyle 1,2,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^B_{\scriptscriptstyle 1,2,N_2,1}   &                &                  &    C^B_{\scriptscriptstyle 1,2,N_1, N_2} 
+        \end{pmatrix}$}&
+        \begin{tikzpicture}
+            \draw [->] (0, 0) -> (2, 0);
+        \end{tikzpicture} &
+        \resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            m_{\scriptscriptstyle 1,2,0}     &   m_{\scriptscriptstyle 1,2,1}  & \cdots    &    m_{\scriptscriptstyle 1,2,72}
+        \end{pmatrix}$} \vspace{1cm}\\
+
+        &\multicolumn{1}{c}{\Large o}  & \multicolumn{1}{c}{\Large o} && \multicolumn{1}{c}{\Large o} \vspace{1cm}\\
+        &\multicolumn{1}{c}{\Large o}  & \multicolumn{1}{c}{\Large o} && \multicolumn{1}{c}{\Large o} 
+        &&\resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            m_{\scriptscriptstyle 1,1,0}     &   m_{\scriptscriptstyle 1,1,1}  & \cdots    &    m_{\scriptscriptstyle 1,1,72} \\ 
+            m_{\scriptscriptstyle 1,2,0}     &   m_{\scriptscriptstyle 1,2,1}  & \cdots    &    m_{\scriptscriptstyle 1,2,72} \\ 
+            \vdots & \vdots & \vdots \\
+            m_{\scriptscriptstyle 22,23,0}     &   m_{\scriptscriptstyle 22,23,1}  & \cdots    &    m_{\scriptscriptstyle 22,23,72} \\ 
+            m_{\scriptscriptstyle 22,23,0}     &   m_{\scriptscriptstyle 22,23,1}  & \cdots    &    m_{\scriptscriptstyle 22,23,72}
+        \end{pmatrix}$} \vspace{1cm}\\
+
+        &\multicolumn{1}{c}{\Large o}  & \multicolumn{1}{c}{\Large o} && \multicolumn{1}{c}{\Large o} \vspace{1cm}\\
+
+        &\multicolumn{1}{c}{$N_{23}$}  & \multicolumn{1}{c}{72} && \multicolumn{1}{c}{72} \vspace{.5cm}\\
+        \rule{0pt}{45pt}
+        $N_{22}$ &
+        \resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            C^A_{\scriptscriptstyle 22,23,1,1}     &   C^A_{\scriptscriptstyle 22,23,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 22,23,1,N_1} \\
+            C^A_{\scriptscriptstyle 22,23,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^A_{\scriptscriptstyle 22,23,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 22,23,N_1, N_1} 
+        \end{pmatrix}$}&
+        \resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            C^B_{\scriptscriptstyle 22,23,1,1}     &   C^B_{\scriptscriptstyle 22,23,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 22,23,1,N_2} \\
+            C^B_{\scriptscriptstyle 22,23,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^B_{\scriptscriptstyle 22,23,N_2,1}   &                &                  &    C^B_{\scriptscriptstyle 22,23,N_1, N_2} 
+        \end{pmatrix}$}&
+        \begin{tikzpicture}
+            \draw [->] (0, 0) -> (2, 0);
+        \end{tikzpicture} &
+        \resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            m_{\scriptscriptstyle 22,23,0}     &   m_{\scriptscriptstyle 22,23,1}  & \cdots    &    m_{\scriptscriptstyle 22,23,72}
+        \end{pmatrix}$} \vspace{1cm}\\
+
+        &\multicolumn{1}{c}{$N_{23}$}  & \multicolumn{1}{c}{72} && \multicolumn{1}{c}{72} \vspace{.5cm}\\
+        \rule{0pt}{45pt}
+        $N_{23}$ &
+        \resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            C^A_{\scriptscriptstyle 22,23,1,1}     &   C^A_{\scriptscriptstyle 22,23,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 22,23,1,N_1} \\
+            C^A_{\scriptscriptstyle 22,23,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^A_{\scriptscriptstyle 22,23,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 22,23,N_1, N_1} 
+        \end{pmatrix}$}&
+        \resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            C^B_{\scriptscriptstyle 22,23,1,1}     &   C^B_{\scriptscriptstyle 22,23,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 22,23,1,N_2} \\
+            C^B_{\scriptscriptstyle 22,23,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^B_{\scriptscriptstyle 22,23,N_2,1}   &                &                  &    C^B_{\scriptscriptstyle 22,23,N_1, N_2} 
+        \end{pmatrix}$}&
+        \begin{tikzpicture}
+            \draw [->] (0, 0) -> (2, 0);
+        \end{tikzpicture} &
+        \resizebox{\linewidth}{!}{%
+        $\begin{pmatrix}  
+            m_{\scriptscriptstyle 22,23,0}     &   m_{\scriptscriptstyle 22,23,1}  & \cdots    &    m_{\scriptscriptstyle 22,23,72}
+        \end{pmatrix}$}\vspace{1cm}
+
+    \end{tabular}}
+    \caption{}
+    \label{tab:t-test}
+\end{table}
+
+\resizebox{.5\textwidth}{!}{
+\begin{tikzpicture}
+    %First row
+    %first
+    \node [] (a1) at (0, 0) {
+        $\begin{pmatrix}  
+            C^A_{\scriptscriptstyle 1,1,1,1}     &   C^A_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 1,1,1,N_1} \\
+            C^A_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^A_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 1,1,N_1, N_1} 
+        \end{pmatrix}$
+    };
+    \node [] (h11) [left=1pt of a1] {$N_1$};
+    \node [] (w11) [above=1pt of a1] {$N_1$};
+
+    %second
+    \node [] (b1) [right = 1cm of a1] {
+        $\begin{pmatrix}  
+            C^B_{\scriptscriptstyle 1,1,1,1}     &   C^B_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 1,1,1,N_1} \\
+            C^B_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^B_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C^B_{\scriptscriptstyle 1,1,N_1, N_1} 
+        \end{pmatrix}$
+    };
+    \node [] (h12) [left=1pt of b1] {$N_1$};
+    \node [] (w12) [above=1pt of b1] {$73$};
+
+    %third
+    \node [] (c1) [right = 1cm of b1] {
+        $\begin{pmatrix}  
+            m_{\scriptscriptstyle 1,1,0}     &   m_{\scriptscriptstyle 1,1,1}  & \cdots    &    m_{\scriptscriptstyle 1,1,72}
+        \end{pmatrix}$
+    };
+    \node [] (w3) [above=1pt of b1] {$73$};
+    \draw [->] (b1.east) to (c1.west);
+
+    %Second Row
+    %first
+    \node [] (a2) [below=1cm of a1] {
+        $\begin{pmatrix}  
+            C^A_{\scriptscriptstyle 1,2,1,1}     &   C^A_{\scriptscriptstyle 1,2,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 1,2,1,N_1} \\
+            C^A_{\scriptscriptstyle 1,2,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^A_{\scriptscriptstyle 1,2,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 1,2,N_1, N_1} 
+        \end{pmatrix}$
+    };
+    \node [] (h21) [left=1pt of a2] {$N_1$};
+    \node [] (w21) [above=1pt of a2] {$N_2$};
+
+    %second
+    \node [] (b2) [right = 1cm of a2] {
+        $\begin{pmatrix}  
+            C^B_{\scriptscriptstyle 1,2,1,1}     &   C^B_{\scriptscriptstyle 1,2,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 1,2,1,N_2} \\
+            C^B_{\scriptscriptstyle 1,2,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^B_{\scriptscriptstyle 1,2,N_2,1}   &                &                  &    C^B_{\scriptscriptstyle 1,2,N_1, N_2} 
+        \end{pmatrix}$
+    };
+    \node [] (h22) [left=-.2cm of b2] {$\scriptstyle N_1 + N_2$};
+    \node [] (w22) [above=1pt of b2] {$73$};
+
+    %third
+    \node [] (c2) [right = 1cm of b2] {
+        $\begin{pmatrix}  
+            m_{\scriptscriptstyle 1,2,0}     &   m_{\scriptscriptstyle 1,2,1}  & \cdots    &    m_{\scriptscriptstyle 1,2,72}
+        \end{pmatrix}$
+    };
+    \node [] (w3) [above=1pt of b2] {$73$};
+    \draw [->] (b1.east) to (c1.west);
+
+    \node [] (transition) [below=1cm of a2] {};
+
+    %Second Row
+    %first
+    \node [] (a3) [below=1cm of transition] {
+        $\begin{pmatrix}  
+            C^A_{\scriptscriptstyle 22,23,1,1}     &   C^A_{\scriptscriptstyle 22,23,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 22,23,1,N_1} \\
+            C^A_{\scriptscriptstyle 22,23,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^A_{\scriptscriptstyle 22,23,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 22,23,N_1, N_1} 
+        \end{pmatrix}$
+    };
+    \node [] (h31) [left=1pt of a3] {$N_1$};
+    \node [] (w31) [above=1pt of a3] {$N_2$};
+
+    \node [] (transition) [] {};
+
+    %second
+    \node [] (b3) [right = 1cm of a3] {
+        $\begin{pmatrix}  
+            C^B_{\scriptscriptstyle 22,23,1,1}     &   C^B_{\scriptscriptstyle 22,23,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 22,23,1,N_2} \\
+            C^B_{\scriptscriptstyle 22,23,2,1}     &                &                  &      \\
+            \vdots                             &                & \ddots           &      \\
+            C^B_{\scriptscriptstyle 22,23,N_2,1}   &                &                  &    C^B_{\scriptscriptstyle 22,23,N_1, N_2} 
+        \end{pmatrix}$
+    };
+    \node [] (h32) [left=-.2cm of b3] {$\scriptstyle N_1 + N_2$};
+    \node [] (w32) [above=1pt of b3] {$73$};
+
+    %third
+    \node [] (c3) [right = 1cm of b3] {
+        $\begin{pmatrix}  
+            m_{\scriptscriptstyle 22,23,0}     &   m_{\scriptscriptstyle 22,23,1}  & \cdots    &    m_{\scriptscriptstyle 22,23,72}
+        \end{pmatrix}$
+    };
+    \node [] (w3) [above=1pt of b3] {$73$};
+    \draw [->] (b1.east) to (c1.west);
+
+\end{tikzpicture}}
 \bibliography{lit}

### 2018-03-29 papers/manuscripts/manuscript.tex
modified manuscript

--- 2018-03-27 papers/manuscripts/manuscript.tex
@@
 \end{figure}
+%$
+%\begin{pmatrix}
+%    {S}^A_{\scriptscriptstyle i,j,1,1}         &
+%    \cdots                                     &    
+%    {S}^A_{\scriptscriptstyle i,j,1,72}        \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%    \vdots                                     &                
+%                                               &      
+%    \vdots                                     \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%   {S}^A_{\scriptscriptstyle i,j,N_1,1}    &
+%   \ddots                                            &    
+%   {S}^A_{\scriptscriptstyle i,j,N_1, 72} \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%    \vdots                                     &                
+%                                               &      
+%    \vdots                                     \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%   {S}^A_{\scriptscriptstyle i,j,N_1+N_2,1}   &
+%    \cdots                                &
+%   {S}^A_{\scriptscriptstyle i,j,N_1+N_2, 72}
+%\end{pmatrix}
+%$
+%
+%$
+%\begin{pmatrix}
+%    {C}^A_{\scriptscriptstyle i,j,1,1}     &
+%    \cdots    &
+%    {C}^A_{\scriptscriptstyle i,j,1,N_1} \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%    \vdots                             &
+%    \ddots&
+%    \vdots                             \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%    {C}^A_{\scriptscriptstyle i,j,N_1,1}   &
+%    \cdots&                  
+%    S^A_{\scriptscriptstyle i,j,N_1, N_1}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\end{pmatrix}
+%$
 
@@
 
-Result of pair-wise contact map graphlet distances can is
+Result of pair-wise contact map graphlet distances is
 illustrated in Figure \ref{fig:orbit-distances_all}.
@@
 average of the graphlet distance vector 
-($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j}$)
-of the two cell lines specified in the legend.
+of the two cell lines specified in the legend
+($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j}$).
  A one sided paired t-test
@@
 significant differeces from zero for all pairs of
-cells. Detailed results of t-tests for each
+cells. The results of tests for $C_{1,1}$ 
+is shown in table \ref{tab:t-test}
+Results of all t-tests for each
 contact map can be found in supplementary materials.
@@
 ordered based on whether they are statistially
-larger that the other or not. For example
-for contact map $C_{1,1}$, the results 
-of t-test is as follows:
-\vspace{.2cm}\\
-\small{
-zero  $<$  call4-mit  $<$     all-rl  $<$     mit-rl  $<$   call4-rl  $<$    all-mit  $=$  all-call4
-}
-\vspace{.2cm}\\
-which means that 
+larger that the other or not with a signifiance
+of $0.01$.
+\begin{table}[]
+    \centering
+    \resizebox{.5\textwidth}{!}{
+    \begin{tabular}{l|ccccccc}
+        \rule{0pt}{25pt}
+                  & One       & MIT-RL       & ALL-RL       & ALL-MIT      & ALL-CALL4    & CALL4-MIT    & CALL4-RL     \\ \hline
+        \rule{0pt}{25pt}
+        One       & -         & \textgreater & \textgreater & \textgreater & \textgreater & \textgreater & \textgreater \\
+        \rule{0pt}{25pt}
+        MIT-RL    & \textless & -            & \textless    & \textless    & \textless    & \textless    & \textless    \\
+        \rule{0pt}{25pt}
+        ALL-RL    & \textless & \textgreater & -            & \textless    & \textless    & \textless    & \textless    \\
+        \rule{0pt}{25pt}
+        ALL-MIT   & \textless & \textgreater & \textgreater & -            & =            & =            & =            \\
+        \rule{0pt}{25pt}
+        ALL-CALL4 & \textless & \textgreater & \textgreater & =            & -            & =            & =            \\
+        \rule{0pt}{25pt}
+        CALL4-MIT & \textless & \textgreater & \textgreater & =            & =            & -            &              \\
+        CALL4-RL  & \textless & \textgreater & =            & =            & =            & =            & -           
+        \rule{0pt}{25pt}
+    \end{tabular}}
+    \caption{
+        Result of one-sided t-test for intrachromosomal
+        contact map of chromosome 1.
         $\mathbf{d}^{\scriptscriptstyle CALL4, MIT}_{1,1}$ 
@@
         material for results of all hypotheis tests.
+    }
+    \label{tab:t-test}
+\end{table}
 
@@
 full list of t-test results.
-
 \newpage
@@
 
-%\begin{tikzpicture}
-%    \node [] (a) at (0, 0) {
-%        $\begin{pmatrix}  
-%            C_{\scriptscriptstyle 1,1,1,1}     &   C_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C_{\scriptscriptstyle 1,1,1,N_1} \\
-%            C_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
-%            \vdots                             &                & \ddots           &      \\
-%            C_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C_{\scriptscriptstyle 1,1,N_1, N_1} 
-%        \end{pmatrix}$
-%    };
-%    \node [] (b) [left=1pt of a] {$N_1$};
-%    \node [] (c) [above=1pt of a] {$N_1$};
-%\end{tikzpicture}
 \bibliography{lit}

### 2018-03-31 utility.py
prepared the training data for deep learning model

@@ -145,7 +145,7 @@ def readMat(fileName, delimiter="\t", ignoreHeader=False, remove_blanks=False, v
         observed, a, b = removeBlankRowsAndColumns(observed)
     return observed
 
-def readYamlIntensities(filename, res, delimiter="\t", remove_blanks=False):
+def readYamlIntensities(filename, res, delimiter="\t", remove_blanks=False, symmetric=False):
     """
     Function:
     --------- 
@@ -174,7 +174,8 @@ def readYamlIntensities(filename, res, delimiter="\t", remove_blanks=False):
     for line in lines:
         #print line
         img[line[0], line[1]] = line[2]
-        img[line[1], line[0]] = line[2]
+        if symmetric:
+            img[line[1], line[0]] = line[2]
     if remove_blanks:
         img, a, b  = removeBlankRowsAndColumns(img)
     return img
@@ -817,3 +818,59 @@ def local_threshold(mat, k=1, method='max', t=1, \
                 if np.sum(mat3[i_low:i_high, j_low:j_high]) < s:
                     mat2[i, j] = 0
     return mat2
+
+def _fromLowToHigh(i, l1, l2):
+    k1 = 1
+    while k1 < len(l1) and i > l1[k1, 0]:
+                k1 += 1
+    k1 -= 1
+    if k1 > 1:
+                remi = i % l1[k1, 0]
+    else:
+                remi = i
+    
+    if remi > l1[k1, 1]:
+                print -1
+    return l2[k1, 0] + remi
+
+def _convertIndices(i, j):
+        return (fromLowToHigh(i, nss_low, nss_high), fromLowToHigh(j, nss_low, nss_high))
+def loadData(halfSize=11, root="data/"):
+    nss_low = np.load("length_low_res.npy")
+    nss_high = np.load("length_high_res.npy")
+    mit_low = np.load("mit_low_res.npy")
+    mit_high = np.load("mit_high_res.npy")   
+    halfSize = 11
+    n_low = mit_low.shape[0]
+    n_high = mit_high.shape[0] 
+    print(n_low, n_high)
+    XXX = []
+    YYY = []
+    for chr1 in range(1, 24):
+        for chr2 in range(chr1, 24):
+            n1 = nss_low[chr1, 1]
+            n2 = nss_high[chr1, 1]
+            n = np.min([n1, n2])
+            m1 = nss_low[chr2, 1]
+            m2 = nss_high[chr2, 1]
+            m = np.min([m1, m2])       
+            beg_x_low = nss_low[chr1, 0]
[…]

### 2018-04-03 utility.py
added TF_workbook to deal with the deep learning project

@@ -22,7 +22,7 @@ def eigendecompose(a):
     w = w / t
     v = v * t * t
     print("result of multiplying eigenvalues and eigenvectors:")
-    print v.dot(np.diag(w)).dot(np.linalg.inv(v))*t
+    print(v.dot(np.diag(w)).dot(np.linalg.inv(v))*t)
     return w, v/t/t
 
 def writeMatToImage(mat, fileName):
@@ -125,9 +125,9 @@ def readMat(fileName, delimiter="\t", ignoreHeader=False, remove_blanks=False, v
 
     """
     if verbose:
-        print "file directory:", fileName
+        print("file directory:", fileName)
     if not os.path.isfile(fileName):
-        print "File %s does not exist"%fileName
+        print("File %s does not exist"%fileName)
         sys.exit(2)
     file = open(fileName, 'r')
     if ignoreHeader:
@@ -192,7 +192,7 @@ def getBlankRowsAndColumns(mat, thresh=1):
     return blankRows, blankCols
 
 def removeRowsAndColumns(mat, blankRows, blankCols):
-    print "size of old matrix:", mat.shape
+    print("size of old matrix:", mat.shape)
     blankRows = sorted(blankRows, reverse=True)
     blankCols = sorted(blankCols, reverse=True)
     matrixWithRowAndColumnsRemoved = mat
@@ -200,11 +200,11 @@ def removeRowsAndColumns(mat, blankRows, blankCols):
         matrixWithRowAndColumnsRemoved = np.delete(matrixWithRowAndColumnsRemoved, i, 0)
     for i in blankCols:
         matrixWithRowAndColumnsRemoved = np.delete(matrixWithRowAndColumnsRemoved, i, 1)
-    print "size of new matrix:", matrixWithRowAndColumnsRemoved.shape
+    print("size of new matrix:", matrixWithRowAndColumnsRemoved.shape)
     return matrixWithRowAndColumnsRemoved
 
 def removeBlankRowsAndColumns(mat, thresh=1):
-    print "size of old matrix:", mat.shape
+    print("size of old matrix:", mat.shape)
     n, m = mat.shape
     blankRows, blankCols = getBlankRowsAndColumns(mat, thresh=thresh)
     symmetric = True
@@ -215,7 +215,7 @@ def removeBlankRowsAndColumns(mat, thresh=1):
         blankRows.update(blankCols)
         blankCols = blankRows
[…]

### 2018-04-04 utility.py
improved the deep learning model. added log capability to loadData in utitlty

@@ -1,13 +1,13 @@
 import csv
 import numpy as np
 import os, errno
-import cv2
+#import cv2
 import sys
 import scipy.misc
 from scipy.stats.stats import pearsonr   
 import matplotlib.pyplot as plt
 from matplotlib import colors
-from sets import Set
+#from sets import Set
 
 def rel_error(x, y):
     """ returns relative error """
@@ -317,7 +317,7 @@ def _showImages(imageList, rows=None, cols=None, color_bar=False, titles=None, a
         cols = (len(imageList) + rows - 1) / rows
     elif rows == None:
         rows = (len(imageList) + cols - 1) / cols
-    print "Number of rows and columns: %d, %d"%(rows, cols)
+    print("Number of rows and columns: %d, %d"%(rows, cols))
     fig, axes = plt.subplots(nrows=rows, ncols=cols)
     plt.subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=0.1, hspace=.6)
     count = 0
@@ -393,11 +393,11 @@ def convertBinaryMatToOrcaReadable(image, outputFileName=None, x_beg=0, y_beg=0)
              if outputFileName != None:
                  file.write("%d, %d\n"%(i+1+x_beg, j+1+y_beg))
              else:
-                 print i+1+x_beg, j+1+y_beg
+                 print(i+1+x_beg, j+1+y_beg)
 
 
 def readYaml(fileName, delimiter ="\t", symmetric=False, remove_blank=False):
-    print "file name =", fileName
+    print("file name =", fileName)
     file = open(fileName, 'r')
     lines = []
     min_rows = 1000000000
@@ -421,8 +421,8 @@ def readYaml(fileName, delimiter ="\t", symmetric=False, remove_blank=False):
             #print spl
         except:
             continue
-    print "min_rows = %d, max_rows = %d" %(min_rows, max_rows)
-    print "min_cols = %d, max_cols = %d"%( min_cols, max_cols)
+    print("min_rows = %d, max_rows = %d" %(min_rows, max_rows))
+    print("min_cols = %d, max_cols = %d"%( min_cols, max_cols))
     if symmetric:
         print("Symmetric on")
     
@@ -835,11 +835,15 @@ def _fromLowToHigh(i, l1, l2):
 
 def _convertIndices(i, j):
         return (fromLowToHigh(i, nss_low, nss_high), fromLowToHigh(j, nss_low, nss_high))
-def loadData(halfSize=11, root="./"):
[…]

### 2018-04-04 papers/manuscripts/manuscript.tex
finished for today

@@
 created in \cite{wang2013properties}
-These libraries we sequenced 
+These libraries were sequenced 
 for cases of primary human B-acute
@@
 of the thresholding procedure is a binary matrix which also can serve as
-an adjacency matrix for an unweighted, undirected graph. The graph can then be
+an adjacency matrix for an unweighted, undirected graph and can be
 used for orbit extraction.
@@
 When thresholding contact maps, it is necessary to make sure
-that both global and local features are maintained. We could consider 
-thresholding the contact maps by simply setting values above a fixed value to
+that both global and local patterns are maintained. We could consider 
+thresholding the contact maps by simply setting values above a threshold to
 one and the rest to zero; However, in practice, this method resulted in graphs
-that capture the local structure of the contact maps poorly. This is because
+that capture the local structure of the contact maps poorly. 
+This, in part, is because
 intensities follow an exponential distribution with a mean close to zero
@@
 \textit{signature matrices} of
-size $|V^{ij}|\times 73$, where $V^{ij}$ is the number of loci
+size $|\mathbb{V}^{ij}|\times 73$, where $\mathbb{V}^{ij}$ is the number of loci
 involved in contact map between chromosomes $i$ and $j$. Figure
@@
     the signature vectors of length 73 are extracted, resulting 
-    in a \textit{signature matrix} of size $|V^{ij}| \times 73$,
-    where $V^{ij}$ 
+    in a \textit{signature matrix} of size $|\mathbb{V}^{ij}| \times 73$,
+    where $\mathbb{V}^{ij}$ 
     is the number of loci involved.}
@@
     \textit{signature distance vector} of size
-    $|V^{ij}| = N_i+N_j$ for each contact map.
+    $|\mathbb{V}^{ij}| = N_i+N_j$ for each contact map.
     }
@@
 by $\mathbf{d}^{\scriptscriptstyle A,B}_{ij}$. $\mathbf{d}^{\scriptscriptstyle A,B}_{ij}$ 
-is a vector of size $|V_{i,j}|$
+is a vector of size $|\mathbb{V}_{i,j}|$
 and its elements $d^{\scriptscriptstyle A,B}_{i,j,l}$ are
@@
 Result of pair-wise contact map graphlet distances is
-illustrated in Figure \ref{fig:orbit-distances_all}.
+illustrated in Figure \ref{fig:orbit_distances_intra}.
 Each point on the graph is the
@@
 \begin{figure}
+    \includegraphics[width=.5\textwidth]{figures/orbit_distances_intra.png}
+    \caption{
+        Pair-wise graphlet signature difference for
+        ALL 276 CONTACT MAPS:
+        Each point on a graph is the result of averaging all
+        the distances across all loci of that contact map.
+        ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j} \quad
+        \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$).  
+    }
+    \label{fig:orbit_distances_intra}
+\end{figure}
+
+\begin{figure}
     \centering
-    \begin{subfigure}[b]{.5\textwidth}
-        \includegraphics[width=\textwidth]{figures/orbit-distances_all.png}
-        \caption{}
-        \label{fig:orbit-distances_all}
-    \end{subfigure}
     \begin{subfigure}[b]{.5\textwidth}
@@
         \includegraphics[width=\textwidth]{figures/orbits_correlations_all.png}
-        \caption{}
+        \caption{
+        }
         \label{fig:orbits_correlations_all}
@@
     \caption{   
-        \textbf{(a) Pair-wise graphlet signature difference for
-        all 276 contact maps:}
-        Each point on a graph is the result of averaging all
-        the distances across all loci of that contact map.
-        ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j} \quad
-        \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$).  
-        \vspace{.1cm} \\
-        \textbf{(b) pair-wise average contact map orbit correlations
+        \textbf{(a) pair-wise average contact map orbit correlations
          for all contact maps:}
@@
         \vspace{.1cm} \\
-        \textbf{(c) pair-wise average orbit correlations:}
+        \textbf{(b) pair-wise average orbit correlations:}
         In figure \ref{fig:orbits_correlations_all}, each point

### 2018-04-06 utility.py
modified gitignore not to include jupyter temp files

@@ -312,11 +312,11 @@ def gaussian_normalize(heatmap):
 def _showImages(imageList, rows=None, cols=None, color_bar=False, titles=None, ax_labels=None, cmap=None, save_dir=None):
     if rows == None and cols == None:
         rows = 1
-        cols = (len(imageList) + rows - 1) / rows
+        cols = (len(imageList) + rows - 1) // rows
     elif cols == None:
-        cols = (len(imageList) + rows - 1) / rows
+        cols = (len(imageList) + rows - 1) // rows
     elif rows == None:
-        rows = (len(imageList) + cols - 1) / cols
+        rows = (len(imageList) + cols - 1) // cols
     print("Number of rows and columns: %d, %d"%(rows, cols))
     fig, axes = plt.subplots(nrows=rows, ncols=cols)
     plt.subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=0.1, hspace=.6)
@@ -835,8 +835,9 @@ def _fromLowToHigh(i, l1, l2):
 
 def _convertIndices(i, j):
         return (fromLowToHigh(i, nss_low, nss_high), fromLowToHigh(j, nss_low, nss_high))
-def loadData(halfSize=11, root="./", log_convert=False):
+def loadDataOld(halfSize=11, root="./", log_convert=False):
     print("Starting to load data...")
+    map = {}
     nss_low = np.load("%s/length_low_res.npy"%root)
     nss_high = np.load("%s/length_high_res.npy"%root)
     mit_low = np.load("%s/mit_low_res.npy"%root)
@@ -875,7 +876,114 @@ def loadData(halfSize=11, root="./", log_convert=False):
                     Y = mit_high[xLow, yLow]
                     if X.shape[0] != 2*halfSize+1 or X.shape[1] != 2*halfSize+1:
                                                 continue
+                    map[(chr1, chr2, i, j)] = len(XXX)
                     XXX.append(X)
                     YYY.append(Y)
     print("Finished loading data.")
-    return XXX, YYY
+    return XXX, YYY, map
+def extractContactMapFromLargeMatrix(mit_low, nss_low, chr1, chr2):
+    begLowRow = nss_low[chr1, 0]
+    begLowCol = nss_low[chr2, 0]
+    n = nss_low[chr1, 1]
+    m = nss_low[chr2, 1]
[…]

### 2018-04-18 papers/manuscripts/manuscript.tex
Modified DL graph in tensorflow; improved manuscript

--- 2018-03-29 papers/manuscripts/manuscript.tex
@@
 
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figures/orbit-distances_chr14.png}
+        \caption{}
+        \label{fig:orbit-distances_chr14}
+    \end{subfigure}
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_chr14.png}
+        \caption{}
+        \label{fig:contact_maps_correlations_chr14}
+    \end{subfigure}
+    \caption{   
+        \textbf{(a) Pair-wise graphlet signature difference for
+        all 276 contact maps:}
+        Each point on a graph is the result of averaging all
+        the distances across all loci of that contact map.
+        ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j} \quad
+        \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$).  
+        \vspace{.1cm} \\
+        \textbf{(b) pair-wise average contact map orbit correlations
+         for all contact maps:}
+        ($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j} 
+        \quad \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$:
+        average along the red \textit{vertical} arrow in figure 
+        \ref{graphlet_correlation_schema}).
+        These values are calculated by averaging over 
+        pairwise correlations of orbits of
+        $\mathbb{Q}$ in a contact map.
+     }
+    \label{fig:results_all}
+\end{figure*}
+
 Result of pair-wise contact map graphlet distances is
-illustrated in Figure \ref{fig:orbit-distances_all}.
+illustrated in supplementary materials. 
+As an example, we plotted average
+distances only for chromosome 
+14 in Figure \ref{fig:orbit-distances_chr14}.
 Each point on the graph is the
@@
 ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j}$).
+
+By comparing signature distance vectors, one can find
+how contact maps
+differ from each other in terms of local structure. 
+Contact maps can serve as measures of spatial proximity between
+loci. Graphlets capture certain patterns of interaction, or
+in other words, spatial neighborhood for each loci. Thus, if
+signature vectors of two loci are close,
+ it can be inferred that they have 
+similar spatial neighborhood.
+
+As is shown in
+figure \ref{fig:orbit-distances_chr14} as well as t-test results
+(to be discussed next in this paper),
+we can compare pairs of contact maps in terms of their closeness
+to each other. 
+As an example, our results show that
+for most inter-chromosomal contact maps, ALL
+and RL cell lines are closer to each other than to other
+cell lines. as  shown in 
+\ref{fig:orbit_distances_chr14}, this observation is
+true for the first 13 inter-chromosomal 
+contact maps of chromosome 14 as well as it intra-chromosomal
+contact map.
+Although comparisons can be made for each contact map as to
+whether which contact maps are more similar to each other,
+no global pattern has been observed from graphlet distances.
+
+As an alternative, we can compare graphlets by calculating
+how often certain graphlets occur in them. By doing so
+we measure the frequency distribution
+of certain spatial structures in
+each contact map. As a result of this approach
+we can compare contact maps by calculating the 
+correlation between their orbit distributions.
+A higher correlation would mean higher similarity
+in terms of spatial structure between the loci
+involved.
+
+We caclulated pair-wise MIC values 
+for each orbit in each of the 276
+contact maps from MIT, ALL, RL, and CALL4 data separately. 
+As an example,
+figure \ref{fig:contact_maps_correlations_chr14}
+shows average orbit correlations across contact maps
+for chromosome 14.
+It corroborates the
+concolusion we previously made that ALL and RL cell lines 
+are more similar to each other than to other pairs by showing
+significanly larger (refer to supplementary material for statistical tests)
+orbit correlations between contact maps.
+It is worth mentioning that interchromosomal thresholded contact maps 
+represent
+a bipartide graph with the loci from each chromosome on one side. Due to this
+bipartide nature of the graphs in inter-chromosomal maps,
+count of certain orbits is always 0, resulting in
+a correlation values of 0 for them as well.
+We ignored these values  when we calculated averages across orbits 
+in figure \ref{fig:contact_maps_correlations_chr14} since they
+would result in a bias towards zero in averages. You can see the bias in 
+figure \ref{fig:orbits_correlations_all} where average correlations of orbits
+$\mathbb{Q} = \{3, 9, 10{\text -}14, 20{\text -}34, 39{\text -}48, 51{\text -}72\}$ 
+are close to zero. In fact all correlations
+corresponding to these orbits are 0 except for the ones between the same 
+chromosomes.
+
+This approach also allows for comparison of orbits
+themsleves. By comparing average oribit correlations
+across all contact maps of two cell lines, we can
+have a measure of how similar certain orbits are
+between cell lines. This can give us a 
+\textit{global} measure
+of how similar two cell lines are in terms of 
+\textit{local} spatial positionings.
+Figure \ref{fig:orbits_correlations_all} 
+demonstrates average correlations across all 72 orbits within each contact map.
+Figure \ref{fig:orbits_correlations_all} clearly illustrates certain
+orbits of Leukemic have higher correlation to each other than to the
+normal MIT cell. In fact our statistical analysis shows that 
+\textit {for orbits in $\mathbb{Q}$, 
+intra-leukemic orbit correlations are significantly higher
+than leukemic-normal orbit correlations}. This implies
+there are significant differences between normal and
+leukemic cells in terms of their local structure.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/orbits_correlations_all.png}
+    \caption{
+        \textbf{Pair-wise average orbit correlations:}
+        In figure \ref{fig:orbits_correlations_all}, each point
+        in the graph is the result of averaging pair-wise
+        orbit correlations over all contact maps
+        ($\frac{1}{276}\sum_{i=0}^{23}\sum_{j=i}^{23}{
+        m^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j, o}} \quad 
+        \forall o \in \{0, 1, ..., 72\}$:
+        average along the red \textit{horizontal} arrows in figure 
+        \ref{graphlet_correlation_schema}).
+        Counts for certain orbits are always zero in inter-chromosomal
+        maps, leading to average value close to zero in 
+        Figure \ref{fig:orbits_correlations_all}.
+        In this figure, cancer cells data points are depicted
+        in warm colors while normal cells are depicted in
+        cold colors in increased contrast. As can be seen
+        orbit distributions are more similar to each other
+        for cancer cells.
+    }
+    \label{fig:orbits_correlations_all}
+\end{figure*}
+
+\subsection{Statistical Analysis}
 A one sided paired t-test
-was conducted in order to compare distances to
+was conducted in order to compare pair-wise distances to
 zero and also to each other. 
@@
 For each contact map, each pair of cells are
-ordered based on whether they are statistially
+compared based on whether they are statistially
 larger that the other or not with a signifiance
 of $0.01$.
+
 \begin{table}[]
@@
     \caption{
-        Result of one-sided t-test for intrachromosomal
+        Result of one-sided t-test 
+        with significance $\alpha = 0.01$
+        for intrachromosomal
         contact map of chromosome 1.
+        As an example interpretation,
         $\mathbf{d}^{\scriptscriptstyle CALL4, MIT}_{1,1}$ 
         is statistically larger than 0,
-        but less than $\mathbf{d}^{\scriptscriptstyle ALL, RL}_{1,1}$ 
-        and so forth. We can also conclude that 
+        but less than $\mathbf{d}^{\scriptscriptstyle ALL, RL}_{1,1}$ . 
+        An equal sign actually means that the two vectors are
+        not statistically different from each other.
+        We can also conclude that 
         $\mathbf{d}^{\scriptscriptstyle ALL, CALL4}_{1,1}$ is not
@@
 \end{table}
-
-We caclulated pair-wise MIC for each orbit in each of the 276
-contact maps from MIT data and ALL, RL and CALL4 data separately. 
-Figure \ref{fig:contact_maps_correlations_all}
-shows average orbit correlations across all contact maps, while
-figure \ref{fig:orbits_correlations_all} 
-demonstrates average correlations across all 72 orbits within each  contact map.
-It is worth mentioning that interchromosomal thresholded contact maps 
-represent
-a bipartide graph with the loci from each chromosome on one side. Due to this
-bipartide nature of the graphs in inter-chromosomal maps,
-count of certain orbits is always 0, resulting in
-a correlation values of 0 for them as well.
-We ignored these values  when we calculated averages across orbits 
-in figure \ref{fig:contact_maps_correlations_all} since they
-would result in a bias towards zero in averages. You can see the bias in 
-figure \ref{fig:orbits_correlations_all} where average correlations of orbits
-$\mathbb{Q} = \{3, 9, 10{\text -}14, 20{\text -}34, 39{\text -}48, 51{\text -}72\}$ 
-are close to zero. In fact all correlations
-corresponding to these orbits are 0 except for the ones between the same 
-chromosomes.
-
-Figure \ref{fig:orbits_correlations_all} clearly illustrates certain
-orbits of Leukemic have higher correlation to each other than to the
-normal MIT cell. In fact our statistical analysis shows that 
-\textit {for orbits in $\mathbb{Q}$, 
-intra-leukemic orbit correlations are significantly higher
-than leukemic-normal orbit correlations}. This implies
-there are significant differences between normal and
-leukemic cells in terms of their local structure.
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{.5\textwidth}
-        \includegraphics[width=\textwidth]{figures/orbit-distances_all.png}
-        \caption{}
-        \label{fig:orbit-distances_all}
-    \end{subfigure}
-    \begin{subfigure}[b]{.5\textwidth}
-        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_all.png}
-        \caption{}
-        \label{fig:contact_maps_correlations_all}
-    \end{subfigure}
-    \begin{subfigure}[b]{.5\textwidth}
-        \includegraphics[width=\textwidth]{figures/orbits_correlations_all.png}
-        \caption{}
-        \label{fig:orbits_correlations_all}
-    \end{subfigure}
-    \caption{   
-        \textbf{(a) Pair-wise graphlet signature difference for
-        all 276 contact maps:}
-        Each point on a graph is the result of averaging all
-        the distances across all loci of that contact map.
-        ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j} \quad
-        \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$).  
-        \vspace{.1cm} \\
-        \textbf{(b) pair-wise average contact map orbit correlations
-         for all contact maps:}
-        ($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j} 
-        \quad \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$:
-        average along the red \textit{vertical} arrow in figure 
-        \ref{graphlet_correlation_schema}).
-        These values are calculated by averaging over 
-        pairwise correlations of orbits of
-        $\mathbb{Q}$ in a contact map.
-        \vspace{.1cm} \\
-        \textbf{(c) pair-wise average orbit correlations:}
-        In figure \ref{fig:orbits_correlations_all}, each point
-        in the graph is the result of averaging pair-wise
-        orbit correlations over all contact maps
-        ($\frac{1}{276}\sum_{i=0}^{23}\sum_{j=i}^{23}{
-        m^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j, o}} \quad 
-        \forall o \in \{0, 1, ..., 72\}$:
-        average along the red \textit{horizontal} arrows in figure 
-        \ref{graphlet_correlation_schema}).
-        Counts for certain orbits are always zero in inter-chromosomal
-        maps, leading to average value close to zero in 
-        Figure \ref{fig:orbits_correlations_all}.
-     }
-    \label{fig:results_all}
-\end{figure}
-
 We have conducted one-sided
@@
 full list of t-test results.
-\newpage
+
 \section{Resources}

### 2018-04-18 papers/manuscripts/manuscript.tex
modified manuscript

@@
 
+Ideally, it is desirable to compare 3D structures of 
+cell in order to make such comparisons.
+However, the main challenge is that 
+3D structure of a cell is not readily available. Based on
+\cite{adhikari2016chromosome3d}, fluorescence in situ hybridizaiton
+(FISH) is used for investigating 3D configuration of chromosomes.
+However, this method can only be used locally and cannot map
+the whole structure of the chromosomes.
+In orther to find dissimilarities in the 3D structure of 
+chromosomes, we used HiC dataset.
+The HiC method, which was developed by 
+\cite{lieberman2009comprehensive}, captures interactions between 
+chromosomal fragments in kilobase resolution. Based on HiC data, an
+\textit{interaction frequency (IF) } matrix can be developed between \textit{loci} at a desired resolution.
+A cell $IF_{ij}$ in an interaction frequency matrix captures the number of interaction detected
+in HiC dataset between locus $i$ and locus $j$ in the genome.
+An interaction matrix can be used to develop both inter- and intra-chromosomal interaction matrices.
+We believe differences in interaction matrices can be found between normal cells and cancerous ones.
+
+In this study, we plan to find dissimilarities between normal cells and cancerous cells,
+through investigating HiC contact maps. 
+We suspect that there are systematic differences between how chromosomes are structured
+between normal cells and cancerous cells.
+we 
+Ideally, it is desirable to compare 3D structures of 
+cell in order to make such comparisons.
+However, the main challenge that we face is that 
+3D structure of a cell is not readily available. Based on
+\cite{adhikari2016chromosome3d}, fluorescence in situ hybridizaiton
+(FISH) is used for investigating 3D configuration of chromosomes.
+However, this method can only be used locally and cannot map
+the whole structure of the chromosomes.
+In orther to find dissimilarities in the 3D structure of 
+chromosomes, we used HiC dataset.
+The HiC method, which was developed by \cite{lieberman2009comprehensive}, captures interactions between 
+chromosomal fragments in kilobase resolution. Based on HiC data, an
+\textit{interaction frequency (IF) } matrix can be developed between \textit{loci} at a desired resolution.
+A cell $IF_{ij}$ in an interaction frequency matrix captures the number of interaction detected
+in HiC dataset between locus $i$ and locus $j$ in the genome.
+An interaction matrix can be used to develop both inter- and intra-chromosomal interaction matrices.
+We believe differences in interaction matrices can be found between normal cells and cancerous ones.
+
 Graphlet comparison is a novel method used to compare large networks in order to
@@
 the network that are part of an orbit $i$. \\
-\textit{Important Result}: Proteins with similar surroundings perform
+They concluded that proteins with similar surroundings perform
 similar functions.
@@
 
-In order to threshold the matrix so that both global and local patterns are
+To the best of our knowledge, little work has dealt with the task of
+thresholding HiC contact maps. There has been some statistical approaches
+developed on similar data in other fields. 
+For example, authors of \cite{ginestet2011statistical} developed 
+Statistical Network (SPN) analysis
+where the choice of thresholding value is made by statistical inference.
+This method, although very robust, works within the framework of 
+design of experiments where the same
+network can be extracted for different 
+individuals under different treatments. Thus a relatively large
+set of different contact maps need to be available in order for
+this method to be applicable towards our end.
+
+Instead, in order to threshold the matrix so that both global and local patterns are
 captured, we borrowed the concept of \textit{adaptive thresholding} from image 
@@
 \subsection{Statistical Analysis}
-A one sided paired t-test
-was conducted in order to compare pair-wise distances to
-zero and also to each other. 
-The resulting p-values showed highly 
-significant differeces from zero for all pairs of
-cells. The results of tests for $C_{1,1}$ 
-is shown in table \ref{tab:t-test}
-Results of all t-tests for each
-contact map can be found in supplementary materials.
-For each contact map, each pair of cells are
-compared based on whether they are statistially
-larger that the other or not with a signifiance
-of $0.01$.
-
-\begin{table}[]
-    \centering
+In order to quntify our results, we have conducted one-sided
+t-test in order to test whether the average pair-wise
+MIC values across orbits are significantly different from 
+each other and also from 1. 
+however, pairwise correlation of cancer cells for
+orbits in $\mathbb{Q}$ were significantly higher than
+correlation between cancer cells and normal cells.
+The results
+for this test showed that all values are significantly less than 1;
+A summary of can be found in
+table \ref{tab:t-test}.
+We have also conducted t-tests for 
+pair-wise orbit signature vector distances across contact maps.
+Please refer to supplementary material for result of the 
+full list of t-test results.
+\begin{table}[H]
     \resizebox{.5\textwidth}{!}{
-    \begin{tabular}{l|ccccccc}
-        \rule{0pt}{25pt}
-                  & One       & MIT-RL       & ALL-RL       & ALL-MIT      & ALL-CALL4    & CALL4-MIT    & CALL4-RL     \\ \hline
-        \rule{0pt}{25pt}
-        One       & -         & \textgreater & \textgreater & \textgreater & \textgreater & \textgreater & \textgreater \\
-        \rule{0pt}{25pt}
-        MIT-RL    & \textless & -            & \textless    & \textless    & \textless    & \textless    & \textless    \\
-        \rule{0pt}{25pt}
-        ALL-RL    & \textless & \textgreater & -            & \textless    & \textless    & \textless    & \textless    \\
-        \rule{0pt}{25pt}
-        ALL-MIT   & \textless & \textgreater & \textgreater & -            & =            & =            & =            \\
-        \rule{0pt}{25pt}
-        ALL-CALL4 & \textless & \textgreater & \textgreater & =            & -            & =            & =            \\
-        \rule{0pt}{25pt}
-        CALL4-MIT & \textless & \textgreater & \textgreater & =            & =            & -            &              \\
-        CALL4-RL  & \textless & \textgreater & =            & =            & =            & =            & -           
-        \rule{0pt}{25pt}
+\begin{tabular}{c|ccccccc}
+    & $MIC_{\scriptscriptstyle MIT-CALL4}$ & $MIC_{\scriptscriptstyle MIT-RL}$ & $MIC_{\scriptscriptstyle MIT-ALL}$ & $MIC_{\scriptscriptstyle ALL-CALL4}$ & $MIC_{\scriptscriptstyle CAll4-RL}$ & $MIC_{\scriptscriptstyle ALL-RL}$ & 1   \\
+              \rule{0pt}{1pt} \\ \hline \rule{0pt}{15pt}
+              $MIC_{\scriptscriptstyle MIT-CALL4}$ & -         & $\mathbf{<}$    & $\mathbf{<}$     & $\mathbf{<}$       & $\mathbf{<}$      & $\mathbf{<}$    & $\mathbf{<}$ \\
+              \rule{0pt}{20pt}
+              $MIC_{\scriptscriptstyle MIT-RL}$    & $\mathbf{>}$       &   -    & $\mathbf{<}$     & $\mathbf{<}$       & $\mathbf{<}$      & $\mathbf{<}$    & $\mathbf{<}$ \\
+              \rule{0pt}{20pt}
+              $MIC_{\scriptscriptstyle MIT-ALL}$   & $\mathbf{>}$       & $\mathbf{>}$    &    -    & $\mathbf{<}$       & $\mathbf{<}$      & $\mathbf{<}$    & $\mathbf{<}$ \\
+              \rule{0pt}{20pt}
+              $MIC_{\scriptscriptstyle ALL-CALL4}$ & $\mathbf{>}$       & $\mathbf{>}$    & $\mathbf{>}$     &       -   & $\mathbf{<}$      & $\mathbf{<}$    & $\mathbf{<}$ \\
+              \rule{0pt}{20pt}
+              $MIC_{\scriptscriptstyle CAll4-RL}$  & $\mathbf{>}$       & $\mathbf{>}$    & $\mathbf{>}$     & $\mathbf{>}$       &    -     & $\mathbf{<}$    & $\mathbf{<}$ \\
+              \rule{0pt}{20pt}
+              $MIC_{\scriptscriptstyle ALL-RL}$    & $\mathbf{>}$       & $\mathbf{>}$    & $\mathbf{>}$     & $\mathbf{>}$       & $\mathbf{>}$      &   -    & $\mathbf{<}$ \\
+              \rule{0pt}{20pt}
+              1         & $\mathbf{>}$       & $\mathbf{>}$    & $\mathbf{>}$     & $\mathbf{>}$       & $\mathbf{>}$      & $\mathbf{>}$    &    -
 \end{tabular}}
@@
         Result of one-sided t-test 
+        comparison of MIC results 
         with significance $\alpha = 0.01$
-        for intrachromosomal
-        contact map of chromosome 1.
-        As an example interpretation,
-        $\mathbf{d}^{\scriptscriptstyle CALL4, MIT}_{1,1}$ 
-        is statistically larger than 0,
-        but less than $\mathbf{d}^{\scriptscriptstyle ALL, RL}_{1,1}$ . 
-        An equal sign actually means that the two vectors are
-        not statistically different from each other.
-        We can also conclude that 
-        $\mathbf{d}^{\scriptscriptstyle ALL, CALL4}_{1,1}$ is not
-        statistically different from 
-        $\mathbf{d}^{\scriptscriptstyle ALL, MIT}_{1,1}$
-        between graphlets extracted from all contact maps. 
-        Refer to supplementary
-        material for results of all hypotheis tests.
+        for orbits of $\mathbb{Q}$.
+        A $<$ sign means that the value in the corresponding
+        row is significantly smaller that the value in 
+        corresponding column; and a $>$ sign means the opposite.
+        An $=$ sign would have meant the values are not 
+        statistically different.
+        As can be seen, all MIC values are significantly smaller that 1,
+        meaning non on them are exactly the same; 
+        however, all Cancer vs Cancer MIC values are statistically
+        larger than Cancer vs Normal, implying that 
+        spatial positioning of loci are more similar between cancer cells.
     }
     \label{tab:t-test}
+
 \end{table}
-We have conducted one-sided
-t-test in order to test whether the average correlations across
-contact maps is equal to 1  and whether the average 
-correlations across orbits is equal to 1. The results
-for both test showed that all values are significantly less than 1.
-Please refer to supplementary material for result of the 
-full list of t-test results.
 

### 2018-04-21 HiCPlus/tex/review.tex
report started

%% define the main template style for the document
\documentclass{article}
%% import the NIPS package for LaTeX style
\usepackage[final]{nips_2017}

%% import packages that have custom options
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[pagebackref=true]{hyperref}
\usepackage[nolist,nohyperlinks]{acronym}
\usepackage{float}

%% Import general packages
\usepackage{
  amsmath, amssymb, amsfonts, nicefrac,
  algorithmic, textcomp, listings, url,
  graphicx, subfig, microtype,
  booktabs, longtable
}

% Define a shortcut for inline code blocks
\def\code#1{\texttt{#1}}

%% start the document, the Markdown parser takes over from this point
\begin{document}
\title{Enhancing HiC data resolution with convolutional neural networks}

\author{
    Behnam Rasoolian \\
    Department of Software Engineering \\
    Auburn University \\
    Auburn, AL 36832 \\
    \texttt{behnam@auburn.edu} \\
    \And
    Liangliang Xu \\
    Department of Industrial Engineering \\
    Auburn University \\
    Auburn, AL 36832 \\
    \texttt{lzx0014@auburn.edu} \\
    \And
    Zheng Zhang \\
    Department of Software Engineering \\
    Auburn University \\
    Auburn, AL 36832 \\
    \texttt{zzz0069@auburn.edu} \\
}

\maketitle
\section{Abstract}
\section{Introduction}
Study of spatial conformation of chromosomes is
of high importance in the field of (computational)
biology. Although all cell is a living being
have the same sequence of genes, it is the 
3D positioning of these genese in space that
determines how the cell functions.
Roughly said,
if two genes are close to each other in
space, they can interact with each other
in order to create a certain protein that
regulates a certain task.
Thus, being
able study this 3D configuration can help
unravel mysteries of cell functioning.
However, this spatial organization of chromosomes
can not be observed through traditional 
microscopy. As an alternative,
high-throughput chromosome conformation capture
(Hi-C) has emerged as
a powerfull method for studying the
3D organization of chromosomes in space.
In this method, a chromosome is divided into
very small equally sized
sections called \textit{loci}
which is composed of 1K to 1000K genes.
this method then
measures all pair-wise interaction frequencies 
across all chromosomes. 
In the past years, Hi-C method has lead to some
exiting discoveries about the topology of 
chromosomes such as presence of \textit{chromatin
loops}.
Hi-C data are usually provided as a $N \times N$
heatmap or \textit{contact matrix} where $N$ is 
the number of loci in the genome. Each cell in 
the heatmap indicates the number of \textit{interactions}
found between a pair of loci corresponding to the
rows and columns. `Resolution' of a Hi-C data
is the size of the loci the genome is
divided into.
As mentioned above
resolution can range from 1 kb to 1 Mb.
\textit{sequencing depth} is the most
important factor that determines the resolution
of data. A higher sequencing depth results in
capturing interactions between samller loci,
thus improving the resolution of the data.
the sequencing process is costly and 
linewar increase of resolution requires
quadratic increase of sequencing reads.
thus, most of the Hi-C data availabe have
low resolutions.

Therefore, it is required that a computational
method be developed to improve the resolution of
currently availabe Hi-C data and generate Hi-C
contact matrices of higher contrast.
Recently, deep learning 
especially Convolutional Neural Network
has emerged as a successful
method in several applications such as 
computational epigenomics. It has been
successfully used to predict DNA methylation
or gene expression patterns.

\section{The Model}
In \cite{zhang2018enhancing}, a model was
proposes as HiCPlus, that uses CNNs
to predict a high resolution contact
matrix from a down-sampled matrix.
In this project, we have used HiCPlus
model to enhance the contrast for 
our own data.

In our research, we have Hi-C data of
4 cell lines. One of which is sequenced
from a normal cell line and the other
three sequenced from cells afflicted
with three different malignancies.
Our purpose is to
compare them in terms of spatial
structure and find whether there is 
any difference in their 3D conformation
or not.
All 4 data that we have are sequenced
with low depth, resulting in relatively
low resolution. Therefore, we used the
HiCPlus model in \cite{zhang2018enhancing}
to enhace the contrast of our data.

\subsection{Overview of HiCPlus framework}
The inputs to the model are a low-resolution
and a high-resolution date from the same
cell line. In our project we used GM06990
for low-rosolution and GM12878 for
high-resolution data. The two data are
sequenced from the same cell lines with
the difference that the former data
cavers 979.4M bases while the latter
covers 85.1G bases, that is, the resolution
of GM12878 data is roughly 87 times higher
than the GM06990 data.
We then fit the ConvNet model using values at 
each position in the high-resolution matrix as 
the response variable and using its 
neighbouring points from the 
low-resolution matrix as the predictors.
The authors of \cite{zhang2018enhancing}
propose a neighborhood of size $40 \times 40$
as the neighborhoold that yields best results.
Thus in order the prepare the data, we first
divided both low- and high-resolution contact
matrices into patches of size $40 \times 40$.
The model consists of 3 convolutional layers.
The design of the model is described in table
\ref{tab:modelDesign} and illustrated in 
figure \ref{fig:modelDesign}.
\begin{table}[]
    \centering
    \begin{tabular}{clcccl}
        Number   & Name           & Filter size & Filter Numbers & Strides & Output Shape \\[5pt] \hline \hline\\
        0        & input          &   -         &-               &    -    & $1\times40\times40$    \\[5pt]
        1        & conv2d1        & 9           & 8              & 1       & $8\times32\times32$    \\[5pt]
        2        & conv2d2        & 1           & 8              & 1       & $8\times32\times32$    \\[5pt]
        3        & conv2d3        & 5           & 1              & 1       & $1\times28\times28$    \\[5pt]
        4        & output\_layer  &     -       &   -            &   -     & $1\times784$     \\[30pt]
    \end{tabular}
    \caption{My caption}
    \label{tab:modelDesign}
\end{table}
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{model.jpg}
    \caption{}
    \label{fig:modelDesign}
\end{figure}
\subsubsection{Loss Function}
We used mean squre of
differences as the loss function. As can be
seen in table \ref{tab:modelDesign} and 
\ref{fig:modelDesign}, the output of
the model hase a shape of $1 \times 784$.
In order to calculate loss function,
the model picks the middle 28 rows and colums of the
corresponing high-resolution patch and flattens
it. It then calculates the mean square of differneces
between the output of the model and the high-resolution
sub-patch. The loss function is formulated as follows:
\begin{equation}
    \mathbb{L} = \sum_{i=1}^{784}{\hat{y}_i - y_i}
\end{equation}
where $\hat{y}$ denotes the output of the model and
$y$ denotes the actual high-resolution sub-patch.

\section{Strengths and Weaknesses}

\section{Future Work}

\section{Questions \& Answers}

% MARK: bibliography
\bibliographystyle{my-unsrtnat}
\bibliography{references}

% MARK: acronyms
% a collection of Acronyms
\begin{acronym}
\acro{CNN}{Convolutional Neural Network}
\acro{GAN}{Generative Adversarial Network}
\end{acronym}

\end{document}

### 2018-04-21 HiCPlus/tex/review.tex
add to report

@@
 \usepackage{float}
+\usepackage[inline]{enumitem}
 
@@
 \section{Introduction}
+The cell of a eukaryotic species forms a multi-granularity genome structure
+in order to compactly store a very long genomic 
+DNA sequence in its small nucleus. The following describes the genome
+structure in the order of decreasing granularity
+\cite{wang2013properties}:
+\begin{enumerate*}
+\item[(1)] A \textbf{nucelotide} is the building block of
+DNA. There are 4 types of nucleotides: 
+C, G, A and T. 
+\item[(2)] Each pair of nucleotides in the DNA are called a \textbf{base}.
+A kilo-base is a group of 1000 bases.
+\item[(3)] thousands of bases join together to form \textbf{gene loci}.
+\item[(4)] A number of loci then fold into a large
+independent physical structure called \textbf{chromosome}.
+\end{enumerate*}
+
 Study of spatial conformation of chromosomes is
@@
 sections called \textit{loci}
-which is composed of 1K to 1000K genes.
+which is composed of 1K to 1M bases.
 this method then
@@
 \section{The Model}
-In \cite{zhang2018enhancing}, a model was
-proposes as HiCPlus, that uses CNNs
+In this project, we are building upon
+HiCPlus, a model proposed in 
+\cite{zhang2018enhancing}, which
+uses CNNs
 to predict a high resolution contact
 matrix from a down-sampled matrix.
-In this project, we have used HiCPlus
-model to enhance the contrast for 
-our own data.
+
+In this project, however,
+we used HiCPlus
+model to enhance the contrast of our
+low resolution data by training on
+a high resolution data.
 
@@
 to enhace the contrast of our data.
+We also have access to a high-resolution
+data with much higher resolution which
+is sequenced from exactly the same cell
+as the normal low-resolution data that
+we have. Our purpose to train the model
+by using the low- and high-resolution data
+of normal cell and then apply it on the 
+other three cells in order to improve
+their contrast.
 
@@
     \end{tabular}
-    \caption{My caption}
+    \caption{Desciption the CNN layers used in
+    our project. The model is composed of three
+    convolutional layers. The input is of shape
+    $1\times40\times40$ and the output has a
+    shape of $1\times784$. There are not deeply
+    connected layers in the model.}
     \label{tab:modelDesign}
@@
     \includegraphics[width=\textwidth]{model.jpg}
-    \caption{}
+    \caption{Illustration of the CNN layers used in
+    our project. The model is composed of three
+    convolutional layers. The input is of shape
+    $1\times40\times40$ and the output has a
+    shape of $1\times784$. There are not deeply
+    connected layers in the model.}
     \label{fig:modelDesign}
@@
 \begin{equation}
-    \mathbb{L} = \sum_{i=1}^{784}{\hat{y}_i - y_i}
+    \mathbb{L} = 
+    \frac{1}{784}\sum_{i=1}^{784}{\hat{y}_i - y_i}
 \end{equation}
@@
 $y$ denotes the actual high-resolution sub-patch.
-
-\section{Strengths and Weaknesses}
-
-\section{Future Work}
-
-\section{Questions \& Answers}
+\section{Results}
+We trained the model using low-resolution 
+ GM06990 and high-resolution
+ GM12878 data. We then used the other threed
+ data that we have (corresponding to three
+ cancerous cells) as input to the model to 
+ improve contrast.
+\section{Strengths and Weaknesses and Future Work}
+This method can be considered as a noise reduction method
+for Hi-C contact matrices. Just as all currently available
+normalization and noise reduction approaches this method
+also relies on assumptions. The major assumption of this
+approach is that CNNs can predict values in high-resolution
+matrix from the surrounding neighborhood in low-resolution
+matrix. The difference of this assumption from other 
+approaches is that it is easier to put the asumption to
+statistical tests. Authors of \cite{zhang2018enhancing}
+came to the conclusion that the assumption holds true for
+a down-sampled version of high-resolution data. Whether
+this is the case for an independent low-resolution data
+remains to be investigated in future works.
 

### 2018-04-21 HiCPlus/tex/review.tex
updated model

--- 2018-04-21 HiCPlus/tex/review.tex
@@
 \section{Introduction}
+The cell of a eukaryotic species forms a multi-granularity genome structure
+in order to compactly store a very long genomic 
+DNA sequence in its small nucleus. 
+A \textbf{nucelotide} is the building block of
+DNA. There are 4 types of nucleotides: 
+C, G, A and T. 
+Each pair of nucleotides in the DNA are called a \textbf{base}.
+A kilo-base is a group of 1000 bases.
+thousands of bases join together to form \textbf{gene loci}.
+A number of loci then fold into a large
+independent physical structure called \textbf{chromosome}
+        (\cite{wang2013properties}).
+
 Study of spatial conformation of chromosomes is
@@
 3D organization of chromosomes in space.
+The HiC method, which was developed by 
+\cite{lieberman2009comprehensive}, 
+captures interactions between
+chromosomal fragments.
 In this method, a chromosome is divided into
@@
     \includegraphics[width=\textwidth]{model.jpg}
-    \caption{}
+    \caption{Illustration of the CNN layers used in
+    our project. The model is composed of three
+    convolutional layers. The input is of shape
+    $1\times40\times40$ and the output has a
+    shape of $1\times784$. There are not deeply
+    connected layers in the model.}
     \label{fig:modelDesign}
 \end{figure}
-\subsubsection{Loss Function}
+\subsection{Loss Function}
 We used mean squre of
@@
 $y$ denotes the actual high-resolution sub-patch.
+\section{Results}
+\textbf{Platforms:}
+The original model was developed in \texttt{theano}
+and used package \texttt{lasagne} for model development.
+We implemented our model in \texttt{tensorflow}. Our 
+results can be found in the following git repository:\\
+\url{https://github.com/rasoolianbehnam/watson/tree/master/HiCPlus}\\
 
-\section{Strengths and Weaknesses}
-
-\section{Future Work}
-
-\section{Questions \& Answers}
+We trained the model using low-resolution 
+ GM06990 and high-resolution
+ GM12878 data. We then used the other threed
+ data that we have (corresponding to three
+ cancerous cells) as input to the model to 
+ improve contrast.
+\section{Strengths and Weaknesses and Future Work}
+This method can be considered as a noise reduction method
+for Hi-C contact matrices. 
+For example Balance Network Deconvolution,
+proposed by \cite{feizi2013network}
+assumes that the observed graph $G_{obs}$ is a summation of its
+direct graph $G_{dir}$ and some indirect terms as follows:
+\begin{equation}
+        \label{indirect_effects}
+            G_{obs} = G_{dir} + G_{dir}^2 + G_{dir} + ...
+\end{equation}
+Just as all currently available
+normalization and noise reduction approaches this method
+also relies on assumptions. The major assumption of this
+approach is that CNNs can predict values in high-resolution
+matrix from the surrounding neighborhood in low-resolution
+matrix. The difference of this assumption from other 
+approaches is that it is easier to put the asumption to
+statistical tests. Authors of \cite{zhang2018enhancing}
+came to the conclusion that the assumption holds true for
+a down-sampled version of high-resolution data. Whether
+this is the case for an independent low-resolution data
+remains to be investigated in future works.
 

### 2018-04-22 HiCPlus/tex/review.tex
almost finished report
done with the report

--- 2018-04-21 HiCPlus/tex/review.tex
@@
 in order to compactly store a very long genomic 
-DNA sequence in its small nucleus. The following describes the genome
-structure in the order of decreasing granularity
-\cite{wang2013properties}:
-\begin{enumerate*}
-\item[(1)] A \textbf{nucelotide} is the building block of
+DNA sequence in its small nucleus. 
+A \textbf{nucelotide} is the building block of
 DNA. There are 4 types of nucleotides: 
 C, G, A and T. 
-\item[(2)] Each pair of nucleotides in the DNA are called a \textbf{base}.
+Each pair of nucleotides in the DNA are called a \textbf{base}.
 A kilo-base is a group of 1000 bases.
-\item[(3)] thousands of bases join together to form \textbf{gene loci}.
-\item[(4)] A number of loci then fold into a large
-independent physical structure called \textbf{chromosome}.
-\end{enumerate*}
+thousands of bases join together to form \textbf{gene loci}.
+A number of loci then fold into a large
+independent physical structure called \textbf{chromosome}
+        (\cite{wang2013properties}).
 
@@
 have the same sequence of genes, it is the 
-3D positioning of these genese in space that
+3D positioning of these genes in space that
 determines how the cell functions.
@@
 (Hi-C) has emerged as
-a powerfull method for studying the
+a powerful method for studying the
 3D organization of chromosomes in space.
+The HiC method, which was developed by 
+\cite{lieberman2009comprehensive}, 
+captures interactions between
+chromosomal fragments.
 In this method, a chromosome is divided into
@@
 of data. A higher sequencing depth results in
-capturing interactions between samller loci,
+capturing interactions between smaller loci,
 thus improving the resolution of the data.
 the sequencing process is costly and 
-linewar increase of resolution requires
+linear increase of resolution requires
 quadratic increase of sequencing reads.
-thus, most of the Hi-C data availabe have
+thus, most of the Hi-C data available have
 low resolutions.
@@
 than the GM06990 data.
+As to malignant cells,
+we re-used Leukemic Hi-C libraries 
+created in \cite{wang2013properties}
+These libraries were sequenced 
+for cases of primary human B-acute
+lymphoblastic leukemia (B-ALL or ALL), 
+the MHH-CALL-4 B-ALL cell
+line (CALL4), 
+and the follicular lymphoma cell-line (RL).
+Just as \cite{wang2013properties}, 
+we used normal B-cell line (GM068990)
+from \cite{lieberman2009comprehensive} 
+for our comparisons.
+\begin{table}[]
+    \centering
+    \begin{tabular}{llcl}
+        Data                           & Short & Resolution & Used …                     \\ \hline\hline\\
+        Normal B-cell(GM12878)         & RAO   & high       & As response in training    \\[5pt]\\
+        Normal B-cell(GM06990)         & MIT   & low        & As feature in training     \\[5pt]\\
+        B-acute lymphoblastic leukemia & ALL   & low        & To predict high resolution \\[5pt]\\
+        Follicular lymphoma cell-line  & RL    & low        & To predict high resolution \\[5pt]\\
+        MHH-CALL-4                     & CALL4 & low        & To predict high resolution \\[10pt]
+    \end{tabular}
+    \caption{Data description}
+    \label{tab:data}
+\end{table}
 We then fit the ConvNet model using values at 
@@
 \end{figure}
-\subsubsection{Loss Function}
-We used mean squre of
+\subsection{Loss Function}
+We used mean square of
 differences as the loss function. As can be
@@
 In order to calculate loss function,
-the model picks the middle 28 rows and colums of the
-corresponing high-resolution patch and flattens
-it. It then calculates the mean square of differneces
+the model picks the middle 28 rows and columns of the
+corresponding high-resolution patch and flattens
+it. It then calculates the mean square of differeneces
 between the output of the model and the high-resolution
@@
 \section{Results}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{mit.png}
+    \caption{}
+\end{figure}
+\begin{figure}[H]
+    \centering
+        Malignant Cell 1: B-ALL
+        \includegraphics[width=\textwidth]{all.png}
+        \vspace{10pt}
+        Malignant Cell 2: RL
+        \includegraphics[width=\textwidth]{rl.png}
+        \vspace{10pt}
+        Malignant Cell 3: CALL4
+        \includegraphics[width=\textwidth]{call4.png}
+    \caption{}
+\end{figure}
+
+\textbf{Platforms:}
+The original model was developed in \texttt{theano} 
+framework.
+The package \texttt{lasagne} was used 
+for model development. Although we made some experiments
+with tensorflow, conducted our final traning via the
+orginal model.
+Our results can be found in a git repository (refer to
+resources section).
+
 We trained the model using low-resolution 
  GM06990 and high-resolution
- GM12878 data. We then used the other threed
+ GM12878 data, both of which are sequence from
+ the same cell. We then used the other three
  data that we have (corresponding to three
@@
  improve contrast.
+The data that we uses is described in table
+\ref{tab:data}
 \section{Strengths and Weaknesses and Future Work}
 This method can be considered as a noise reduction method
-for Hi-C contact matrices. Just as all currently available
+for Hi-C contact matrices. 
+For example Balance Network Deconvolution,
+proposed by \cite{feizi2013network}
+assumes that the observed graph $G_{obs}$ is a summation of its
+direct graph $G_{dir}$ and some indirect terms as follows:
+\begin{equation}
+        \label{indirect_effects}
+            G_{obs} = G_{dir} + G_{dir}^2 + G_{dir} + ...
+\end{equation}
+Just as all currently available
 normalization and noise reduction approaches this method
@@
 matrix. The difference of this assumption from other 
-approaches is that it is easier to put the asumption to
+approaches is that it is easier to put the assumption to
 statistical tests. Authors of \cite{zhang2018enhancing}
@@
 remains to be investigated in future works.
+\section{Resources}
+\textbf{Source code for the project:}\\
+\url{https://github.com/rasoolianbehnam/watson/tree/master/HiCPlus}\\
+\textbf{Link to the low-resolution Hi-C datasets:}\\
+\url{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/contact_file/}\\
+\textbf{Link to high-resolution Hi-C dataset:}\\
+\url{https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE63525}
 

### 2018-04-23 HiCPlus/tex/review.tex
finished report

@@
 \usepackage{float}
-\usepackage[inline]{enumitem}
-
+\usepackage{graphicx}
+\usepackage[caption = false]{subfig}
 %% Import general packages
@@
 
-In our research, we have Hi-C data of
-4 cell lines. One of which is sequenced
-from a normal cell line and the other
-three sequenced from cells afflicted
-with three different malignancies.
-Our purpose is to
-compare them in terms of spatial
+Our final purpose is to be able to
+compare the three leukemic
+cells with a normal cell
+in terms of spatial
 structure and find whether there is 
@@
 or not.
-All 4 data that we have are sequenced
+In our research, we have 5 Hi-C data sets,
+belonging to
+4 cell lines. Two data sets are  sequenced
+from a normal cell line, one 
+with high resolution (GM12878) and the
+other with low resolution (GM06990)
+The other three data sets are
+sequenced from the same
+cell lines with with three different
+type of leukemia.
+
+As mentioned above, four of the data 
+sets we have are sequenced
 with low depth, resulting in relatively
-low resolution. Therefore, we used the
-HiCPlus model in \cite{zhang2018enhancing}
-to enhace the contrast of our data.
+low resolution. 
 We also have access to a high-resolution
@@
 as the normal low-resolution data that
-we have. Our purpose to train the model
+we have. 
+Therefore, we used the
+HiCPlus model in \cite{zhang2018enhancing}
+to enhace the contrast of our data.
+We trained  the model
 by using the low- and high-resolution data
-of normal cell and then apply it on the 
+of normal cells and then applied it to the 
 other three cells in order to improve
 their contrast.
+A summary of the data and how
+they are used can be 
+found in table \ref{tab:data}.
 
@@
     \mathbb{L} = 
-    \frac{1}{784}\sum_{i=1}^{784}{\hat{y}_i - y_i}
+    \frac{1}{784}\sum_{i=1}^{784}({\hat{y}_i - y_i})^2
 \end{equation}
@@
 $y$ denotes the actual high-resolution sub-patch.
+
+We used simple gradient descent optimizer with learning
+rate of \texttt{1e-5} to train the model. The choise of
+optimizer did not make a great difference in the results.
+Our results from using Adam optimizier also were the same
+as SGD.
+
 \section{Results}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{mit.png}
-    \caption{}
+
+\begin{figure}
+        \includegraphics[width= 6in]{mit.png}
+        \caption{Results of training the data on
+        Normal cells. There is a total of almost
+        6000 loci in a contact matrix. For the
+        sake of demonstration, we only show the
+        firt 500 loci. The left contact matrix is the 
+        original low-resolution data. The middle one 
+        is the high resolution data. and the rightmost
+        picture is the result of training the model.}
+        \label{fig:train}
 \end{figure}
-\begin{figure}[H]
-    \centering
-        Malignant Cell 1: B-ALL
-        \includegraphics[width=\textwidth]{all.png}
-        \vspace{10pt}
-        Malignant Cell 2: RL
-        \includegraphics[width=\textwidth]{rl.png}
-        \vspace{10pt}
-        Malignant Cell 3: CALL4
-        \includegraphics[width=\textwidth]{call4.png}
-    \caption{}
+\begin{figure}
+        \subfloat[]{\includegraphics[width= 4in]{all.png}}\\
+        \subfloat[]{\includegraphics[width= 3.9in]{rl.png}}\\
+        \subfloat[]{\includegraphics[width= 4in]{call4.png}}\\
+        \caption{Results of running the model on
+        cancer cells. For the
+        sake of demonstration, we only show the
+        firt 500 loci. The left contact matrices 
+        are the 
+        original low-resolution data and the rightmost
+        pictures are the result of model predictions.}
+        \label{fig:predict}
 \end{figure}
@@
 \ref{tab:data}
+
+The model was ran for 30 epochs. 
+The results of training can be found in figure
+\ref{fig:train}. As can be seen the results
+are smoother and demonstrate higher contrast
+than the original model.
+Figure \ref{fig:predict} show prediction results
+from the model for the three cancer cells. The
+results also demonstrat higher contrast compared
+to original contact matrices.
+
 \section{Strengths and Weaknesses and Future Work}
@@
 for Hi-C contact matrices. 
+Just as all currently available
+normalization and noise reduction approaches this method
+also relies on assumptions. 
 For example Balance Network Deconvolution,
@@
 assumes that the observed graph $G_{obs}$ is a summation of its
-direct graph $G_{dir}$ and some indirect terms as follows:
-\begin{equation}
-        \label{indirect_effects}
-            G_{obs} = G_{dir} + G_{dir}^2 + G_{dir} + ...
-\end{equation}
-Just as all currently available
-normalization and noise reduction approaches this method
-also relies on assumptions. The major assumption of this
+direct graph $G_{dir}$ and some indirect terms 
+$G_{obs} = G_{dir} + G_{dir}^2 + G_{dir} + ...$ .
+The major assumption of this
 approach is that CNNs can predict values in high-resolution

### 2018-04-26 papers/manuscripts/manuscript.tex
new statistical analysis: Manova

@@
 chromosomal fragments in kilobase resolution. Based on HiC data, an
-\textit{interaction frequency (IF) } matrix can be developed between \textit{loci} at a desired resolution.
-A cell $IF_{ij}$ in an interaction frequency matrix captures the number of interaction detected
+\textit{interaction frequency (IF) } matrix can be developed 
+between \textit{loci} at a desired resolution.
+A cell $IF_{ij}$ in an interaction frequency matrix captures 
+the number of interaction detected
 in HiC dataset between locus $i$ and locus $j$ in the genome.
-An interaction matrix can be used to develop both inter- and intra-chromosomal interaction matrices.
-We believe differences in interaction matrices can be found between normal cells and cancerous ones.
+An interaction matrix can be used to develop both 
+inter- and intra-chromosomal interaction matrices.
+We believe differences in interaction matrices can 
+be found between normal cells and cancerous ones.
 
-In this study, we plan to find dissimilarities between normal cells and cancerous cells,
-through investigating HiC contact maps. 
-We suspect that there are systematic differences between how chromosomes are structured
-between normal cells and cancerous cells.
-we 
-Ideally, it is desirable to compare 3D structures of 
-cell in order to make such comparisons.
-However, the main challenge that we face is that 
-3D structure of a cell is not readily available. Based on
-\cite{adhikari2016chromosome3d}, fluorescence in situ hybridizaiton
-(FISH) is used for investigating 3D configuration of chromosomes.
-However, this method can only be used locally and cannot map
-the whole structure of the chromosomes.
-In orther to find dissimilarities in the 3D structure of 
-chromosomes, we used HiC dataset.
-The HiC method, which was developed by \cite{lieberman2009comprehensive}, captures interactions between 
-chromosomal fragments in kilobase resolution. Based on HiC data, an
-\textit{interaction frequency (IF) } matrix can be developed between \textit{loci} at a desired resolution.
-A cell $IF_{ij}$ in an interaction frequency matrix captures the number of interaction detected
-in HiC dataset between locus $i$ and locus $j$ in the genome.
-An interaction matrix can be used to develop both inter- and intra-chromosomal interaction matrices.
-We believe differences in interaction matrices can be found between normal cells and cancerous ones.
-
-Graphlet comparison is a novel method used to compare large networks in order to
+Graphlet comparison is a novel method used to compare 
+large networks in order to
 find local similarities in them.
-Authors of \cite{prvzulj2007biological} provide a new measure of PPI
+Authors of \cite{prvzulj2007biological} 
+provide a new measure of PPI
 network comparison
@@
 
-\cite{milenkoviae2008uncovering} 
- provide heuristics to compare two nodes based on some feature
-(or signature) vectors, which is a 73-dimensional vector
+In \cite{milenkoviae2008uncovering} the authors
+ provide heuristics to compare two nodes in a graph
+based on signature vectors, which are 73-dimensional vectors
 $\mathbf{s}^T
@@
 \subsection{Statistical Analysis}
-In order to quntify our results, we have conducted one-sided
+In order to qauntify our results, we have conducted one-sided
 t-test in order to test whether the average pair-wise

### 2018-04-26 HiCPlus/src/utility.py

@@ -926,7 +926,7 @@ def loadDataOld(halfSize=11, root="./", log_convert=False):
     print("Starting to load data...")
     nss_low = np.load("%s/length_low_res.npy"%root)
     nss_high = np.load("%s/length_high_res.npy"%root)
-    mit_low = np.load("%s/mit_low_res.npy"%root)
+    mit_low = np.load("%s/rl_low_res.npy"%root)
     mit_high = np.load("%s/mit_high_res.npy"%root)   
     if log_convert:
         mit_low = np.log(mit_low + 1)

### 2018-04-26 utility.py

@@ -1117,3 +1117,37 @@ def loadData(nx, ny, sx, sy, root="./", log_convert=False):
     out_high = np.array(out_high)
     print("finished loading data")
     return out_low, out_high, cache
+
+def manova(data):
+    D = -1
+    M = len(data)
+    for cell in data:
+        assert D < 0 or data[cell].shape[1] == D
+        D = data[cell].shape[1]
+    averages = np.zeros((M, D))
+    counts = np.zeros((M, 1))
+    count = 0
+    for cell in data:
+        averages[count] = np.mean(data[cell], axis=0)
+        counts[count, 0] = data[cell].shape[0]
+        count += 1
+    mu = np.mean(averages, axis=0, keepdims=True)
+    T = np.zeros((D, D))
+    for cell in data:
+        diff = data[cell] - mu
+        T += diff.T.dot(diff)
+    #print("T:", T)
+    diff = averages - mu
+    H = diff.T.dot(diff * counts)
+    #print("H:", H)
+    E = T - H
+    #print("E:", E)
+    detE = np.linalg.det(E)
+    detH = np.linalg.det(H)
+    #print(tmp)
+    print(detE, detH)
+    print('Wilk\'s: ',  detE / (detE+detH))
+    print('Hotelling: ', np.trace(H.dot(np.linalg.inv(E))))
+    print('Pillai-Bartlett: ', np.trace(H.dot(np.linalg.inv(H+E))))
+
+

### 2018-04-26 papers/manuscripts/manuscript.tex
added graphs

@@
         \includegraphics[width=\textwidth]{figures/orbit-distances_chr14.png}
-        \caption{}
-        \label{fig:orbit-distances_chr14}
-    \end{subfigure}
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_chr14.png}
-        \caption{}
-        \label{fig:contact_maps_correlations_chr14}
     \end{subfigure}
     \caption{   
-        \textbf{(a) Pair-wise graphlet signature difference for
+        \textbf{Pair-wise graphlet signature difference for
         all 276 contact maps:}
@@
         \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$).  
-        \vspace{.1cm} \\
-        \textbf{(b) pair-wise average contact map orbit correlations
-         for all contact maps:}
-        ($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j} 
-        \quad \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$:
-        average along the red \textit{vertical} arrow in figure 
-        \ref{graphlet_correlation_schema}).
-        These values are calculated by averaging over 
-        pairwise correlations of orbits of
-        $\mathbb{Q}$ in a contact map.
      }
@@
 leukemic cells in terms of their local structure.
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_cancer_vs_normal.png}
+    \end{subfigure}
+    \caption{
+        \textbf{Pair-wise 
+        average contact map orbit correlations
+        for all contact maps:}
+        ($\bar{\mathbf{m}}^{\scriptscriptstyle \scriptscriptstyle A,B}_{i,j} 
+        \quad \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$:
+        average along the 
+        red \textit{vertical} arrow in figure 
+        \ref{graphlet_correlation_schema}).
+        These values are calculated by averaging over 
+        pairwise correlations of orbits of
+        $\mathbb{Q}$ in a contact map.
+}
+    \label{fig:contact_map_correlations_all}
+\end{figure*}
 
@@
     \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figures/orbits_correlations_cancer_vs_normal.png}
+    \end{subfigure}
+    \begin{subfigure}[b]{\textwidth}
     \includegraphics[width=\textwidth]{figures/orbits_correlations_all.png}
+    \end{subfigure}
     \caption{

### 2018-04-28 papers/manuscripts/manuscript.tex
modified papaer

@@
 \section{results and discussions}
-
+\subsection{Contact Map Orbit Vector Distance}
 \begin{figure*}
@@
 
-As an alternative, we can compare graphlets by calculating
-how often certain graphlets occur in them. By doing so
-we measure the frequency distribution
-of certain spatial structures in
-each contact map. As a result of this approach
-we can compare contact maps by calculating the 
-correlation between their orbit distributions.
-A higher correlation would mean higher similarity
-in terms of spatial structure between the loci
-involved.
-
-We caclulated pair-wise MIC values 
-for each orbit in each of the 276
-contact maps from MIT, ALL, RL, and CALL4 data separately. 
-As an example,
-figure \ref{fig:contact_maps_correlations_chr14}
-shows average orbit correlations across contact maps
-for chromosome 14.
-It corroborates the
-concolusion we previously made that ALL and RL cell lines 
-are more similar to each other than to other pairs by showing
-significanly larger (refer to supplementary material for statistical tests)
-orbit correlations between contact maps.
-It is worth mentioning that interchromosomal thresholded contact maps 
+It is worth mentioning that interchromosomal 
+thresholded contact maps 
 represent
-a bipartide graph with the loci from each chromosome on one side. Due to this
+a bipartide graph with the loci from each chromosome 
+on one side. Due to this
 bipartide nature of the graphs in inter-chromosomal maps,
@@
 in figure \ref{fig:contact_maps_correlations_chr14} since they
-would result in a bias towards zero in averages. You can see the bias in 
-figure \ref{fig:orbits_correlations_all} where average correlations of orbits
+would result in a bias towards zero in 
+averages. You can see the bias in 
+figure \ref{fig:orbits_correlations_all} where 
+average correlations of orbits
 $\mathbb{Q} = \{3, 9, 10{\text -}14, 20{\text -}34, 39{\text -}48, 51{\text -}72\}$ 
@@
 
-This approach also allows for comparison of orbits
-themsleves. By comparing average oribit correlations
-across all contact maps of two cell lines, we can
-have a measure of how similar certain orbits are
-between cell lines. This can give us a 
-\textit{global} measure
-of how similar two cell lines are in terms of 
-\textit{local} spatial positionings.
-Figure \ref{fig:orbits_correlations_all} 
-demonstrates average correlations across all 72 orbits within each contact map.
-Figure \ref{fig:orbits_correlations_all} clearly illustrates certain
-orbits of Leukemic have higher correlation to each other than to the
-normal MIT cell. In fact our statistical analysis shows that 
-\textit {for orbits in $\mathbb{Q}$, 
-intra-leukemic orbit correlations are significantly higher
-than leukemic-normal orbit correlations}. This implies
-there are significant differences between normal and
-leukemic cells in terms of their local structure.
+\subsection{MIC Comparison}
 \begin{figure*}
@@
         \includegraphics[width=\textwidth]{figures/contact_maps_correlations_cancer_vs_normal.png}
+    \caption{}
+    \label{fig:contact_map_correlations_all}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{figures/orbits_correlations_cancer_vs_normal.png}
+    \caption{}
+    \label{fig:orbits_correlations_normal_vs_cancer}
+    \end{subfigure}
+    \begin{subfigure}[b]{\textwidth}
+    \includegraphics[width=\textwidth]{figures/orbits_correlations_all.png}
+    \caption{}
+    \label{fig:orbits_correlations_all}
     \end{subfigure}
@@
         $\mathbb{Q}$ in a contact map.
-}
-    \label{fig:contact_map_correlations_all}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{figures/orbits_correlations_cancer_vs_normal.png}
-    \end{subfigure}
-    \begin{subfigure}[b]{\textwidth}
-    \includegraphics[width=\textwidth]{figures/orbits_correlations_all.png}
-    \end{subfigure}
-    \caption{
         \textbf{Pair-wise average orbit correlations:}
@@
     }
-    \label{fig:orbits_correlations_all}
+    \label{fig:orbits_correlations}
 \end{figure*}
+
+In addition to simple graphlet distance comparison,
+we can compare graphlets by calculating
+how often certain graphlets occur in them. By doing so
+we measure the frequency distribution
+of certain spatial structures in
+each contact map. As a result of this approach
+we can compare contact maps by calculating the 
+correlation between their orbit distributions.
+A higher correlation would mean higher similarity
+in terms of spatial structure between the loci
+involved.
+
+This approach also allows for comparison of orbits
+themsleves. By comparing average oribit correlations
+across all contact maps of two cell lines, we can
+have a measure of how similar certain orbits are
+between cell lines. This can give us a 
+\textit{global} measure
+of how similar two cell lines are in terms of 
+\textit{local} spatial positionings.
+
+We caclulated pair-wise MIC values 
+for each orbit in each of the 276
+contact maps from MIT, ALL, RL, and CALL4 data separately. 
+We found statistically significant difference between
+normal vs cancer and cancer vs cancer correlations.
+The results of staistical tests are shown in table
+\ref{tab:statistical_results}. The difference
+between the two cells are also illustrated in figure
+\ref{fig:orbits_correlations}, which showes corrected
+mean difference of MIC values. Figure 
+\ref{fig:contact_map_correlations_all} shows the difference
+between average pairwise
+correlations. For most of the contact maps, correlation
+between normal and cancer cells are smaller
+than the correlation between cancer cells. This is corroborated
+by the results of statical test which verify that such difference
+is if fact signifcant.
+Figures \ref{fig:orbits_correlations_normal_vs_cancer} and
+\ref{fig:orbits_correlations_all} both show more details about
+this difference in correlation. As can be observed, for obits
+in $\mathbb{Q}$, normal correlations are smaller than cancer
+correlations, while for the rest of the orbits, there is no
+difference.
+
+Figure \ref{fig:orbits_correlations} demonstrates that certain
+orbits of Leukemic have higher correlation to each other 
+than to the
+normal MIT cell. In fact our statistical analysis shows that 
+\textit {for orbits in $\mathbb{Q}$, 
+intra-leukemic orbit correlations are significantly higher
+than leukemic-normal orbit correlations}. This implies
+there are significant differences between normal and
+leukemic cells in terms of their local structure.
 
@@
 each other and also from 1. 
-however, pairwise correlation of cancer cells for
+However, pairwise correlation of cancer cells for
 orbits in $\mathbb{Q}$ were significantly higher than
@@
 full list of t-test results.
-\begin{table}[H]
-    \resizebox{.5\textwidth}{!}{
-\begin{tabular}{c|ccccccc}
-    & $MIC_{\scriptscriptstyle MIT-CALL4}$ & $MIC_{\scriptscriptstyle MIT-RL}$ & $MIC_{\scriptscriptstyle MIT-ALL}$ & $MIC_{\scriptscriptstyle ALL-CALL4}$ & $MIC_{\scriptscriptstyle CAll4-RL}$ & $MIC_{\scriptscriptstyle ALL-RL}$ & 1   \\
-              \rule{0pt}{1pt} \\ \hline \rule{0pt}{15pt}
-              $MIC_{\scriptscriptstyle MIT-CALL4}$ & -         & $\mathbf{<}$    & $\mathbf{<}$     & $\mathbf{<}$       & $\mathbf{<}$      & $\mathbf{<}$    & $\mathbf{<}$ \\
-              \rule{0pt}{20pt}
-              $MIC_{\scriptscriptstyle MIT-RL}$    & $\mathbf{>}$       &   -    & $\mathbf{<}$     & $\mathbf{<}$       & $\mathbf{<}$      & $\mathbf{<}$    & $\mathbf{<}$ \\
-              \rule{0pt}{20pt}
-              $MIC_{\scriptscriptstyle MIT-ALL}$   & $\mathbf{>}$       & $\mathbf{>}$    &    -    & $\mathbf{<}$       & $\mathbf{<}$      & $\mathbf{<}$    & $\mathbf{<}$ \\
-              \rule{0pt}{20pt}
-              $MIC_{\scriptscriptstyle ALL-CALL4}$ & $\mathbf{>}$       & $\mathbf{>}$    & $\mathbf{>}$     &       -   & $\mathbf{<}$      & $\mathbf{<}$    & $\mathbf{<}$ \\
-              \rule{0pt}{20pt}
-              $MIC_{\scriptscriptstyle CAll4-RL}$  & $\mathbf{>}$       & $\mathbf{>}$    & $\mathbf{>}$     & $\mathbf{>}$       &    -     & $\mathbf{<}$    & $\mathbf{<}$ \\
-              \rule{0pt}{20pt}
-              $MIC_{\scriptscriptstyle ALL-RL}$    & $\mathbf{>}$       & $\mathbf{>}$    & $\mathbf{>}$     & $\mathbf{>}$       & $\mathbf{>}$      &   -    & $\mathbf{<}$ \\
-              \rule{0pt}{20pt}
-              1         & $\mathbf{>}$       & $\mathbf{>}$    & $\mathbf{>}$     & $\mathbf{>}$       & $\mathbf{>}$      & $\mathbf{>}$    &    -
-\end{tabular}}
-    \caption{
-        Result of one-sided t-test 
-        comparison of MIC results 
-        with significance $\alpha = 0.01$
-        for orbits of $\mathbb{Q}$.
-        A $<$ sign means that the value in the corresponding
-        row is significantly smaller that the value in 
-        corresponding column; and a $>$ sign means the opposite.
-        An $=$ sign would have meant the values are not 
-        statistically different.
-        As can be seen, all MIC values are significantly smaller that 1,
-        meaning non on them are exactly the same; 
-        however, all Cancer vs Cancer MIC values are statistically
-        larger than Cancer vs Normal, implying that 
-        spatial positioning of loci are more similar between cancer cells.
-    }
-    \label{tab:t-test}
-
-\end{table}
 

### 2018-04-30 papers/manuscripts/manuscript.tex
final draft of manuscript

@@
 However, the main challenge is that 
-3D structure of a cell is not readily available. Based on
-\cite{adhikari2016chromosome3d}, fluorescence in situ hybridizaiton
-(FISH) is used for investigating 3D configuration of chromosomes.
-However, this method can only be used locally and cannot map
-the whole structure of the chromosomes.
+3D structure of a cell is not readily available. 
 In orther to find dissimilarities in the 3D structure of 
@@
 be found between normal cells and cancerous ones.
+
+Recently, there has been many efforts at predicting the 3D conformation
+of chromosomes using HiC data. 
+\cite{noble2011three, rousseau2011three, hu2013bayesian, varoquaux2014statistical, trieu2014large, zhang20133d, lesne20143d, bau2011three, adhikari2016chromosome3d}.
+These efforts, although different in
+approach, usually translate 
+interaction frequencies in contact maps as an inverse measure of 
+distance. In particular \cite{adhikari2016chromosome3d} developed
+a method, Chromosome3D which uses
+distance geometry simulated annealing (DGSA) in order to
+reconstruct genome structure. These reconstructed 3D 
+structures could be used in order to compare normal and malignant
+cell lines. However, the main obstacle to doing so is that the
+process of reconstruction is computationally
+expensive. Almost all reconstruction methods rely on either 
+deterministic or heuristic optimization in order to find the best
+confomation that matches contact maps. Also, there is no real 
+way of verifying whether the reconstruction results are accurate.
+Fluorescence in situ hybridizaiton
+(FISH) is used for investigating 3D configuration of chromosomes.
+\cite{gasser2002visualizing, lanctot2007dynamic, mateos2009spatially}
+However, this method can only be used locally and cannot map
+the whole structure of the chromosomes.
 
@@
 developed by \cite{servant2015hic}.
+We also performed and extra normalization by
+performing network deconvolution \cite{feizi2013network}
+in order to remove
+the effect of indirect interactions.
 
@@
 \subsection{Contact Map Orbit Vector Distance}
-\begin{figure*}
+\begin{figure}
     \centering
-    \begin{subfigure}[b]{\textwidth}
+    \begin{subfigure}[b]{.5\textwidth}
+        \includegraphics[width=\textwidth]{figures/orbit_distances_normal_vs_cancer.png}
+        \caption{}
+        \label{fig:orbit_distances_all_a}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{.5\textwidth}
+        \includegraphics[width=\textwidth]{figures/orbit_distances_cells.png}
+        \caption{}
+        \label{fig:orbit_distances_all_b}
+    \end{subfigure}
+
+    \caption{   
+        \textbf{Average Pair-wise graphlet signature difference 
+        over all 276 contact maps:}
+        Each point on a graph is the result of averaging all
+        the distances across all loci of all contact maps for 
+        each pair of cells. A 0.1 standard deviation error
+        bar is also plotted for each point.
+        ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}$).  
+     }
+    \label{fig:orbit_distances_all}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{.5\textwidth}
         \includegraphics[width=\textwidth]{figures/orbit-distances_chr14.png}
@@
     \caption{   
-        \textbf{Pair-wise graphlet signature difference for
-        all 276 contact maps:}
-        Each point on a graph is the result of averaging all
-        the distances across all loci of that contact map.
-        ($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j} \quad
-        \forall i,j \in \{1 ... 23\} \quad \& \quad j \ge i$).  
      }
-    \label{fig:results_all}
-\end{figure*}
-
-Result of pair-wise contact map graphlet distances is
-illustrated in supplementary materials. 
-As an example, we plotted average
-distances only for chromosome 
-14 in Figure \ref{fig:orbit-distances_chr14}.
-Each point on the graph is the
-average of the graphlet distance vector 
-of the two cell lines specified in the legend
-($\bar{\mathbf{d}}^{\scriptscriptstyle A,B}_{i,j}$).
+    \label{fig:orbit_distances_chr14}
+\end{figure}
 
@@
 
-As is shown in
-figure \ref{fig:orbit-distances_chr14} as well as t-test results
-(to be discussed next in this paper),
-we can compare pairs of contact maps in terms of their closeness
+We can compare pairs of contact maps in terms of their closeness
 to each other. 
-As an example, our results show that
-for most inter-chromosomal contact maps, ALL
+As an example, in figure
+\ref{fig:orbit_distances_chr14}, all pairs of cells are
+compared to each other in terms of their distance for contact
+maps involving chromosome 14. We can se that 
+for the first 13 inter-chromosomal 
+contact maps, ALL and RL cell lines are closer to each other
+than to other cell lines.
+
+We performed one-way ANOVA statistical test to 
+see if there are significant 
+difference between cancer-normal and cancer-cancer pairs.
+We found that the difference statistically significant difference.
+($F(1, 1654) = 20.49, p < 0.0001$).
+As illustrated in figure \ref{fig:orbit_distances_all_a},
+we can see that normal-cancer cells have higher distance
+from each other than cancer-cancer pairs.
+
+We then continued to investigate each pair separately to
+see if there is any significant difference between them.
+Again, our statistical tests (ANOVA) showed significant difference
+between pairs of cells.
+The results are shown in figure \ref{fig:orbit_distances_all_b}.
+We can see that ALL-RL pair are closest to each other while
+ALL-MIT and MIT-RL are most distant. We found statistcally
+significant difference for difference between individual
+pairs except for ALL-CALL4 and CALL4-RL as well as
+MIT-RL and ALL-MIT. The results of thse tests 
+can be found in supplementary material.
+
+The results in figure \ref{fig:orbit_distances_all_b} is also
+in keeping with what we see in figure \ref{fig:orbit_distances_chr14}. For example, as mentioned earlier, our results show that
+on average, ALL
 and RL cell lines are closer to each other than to other
-cell lines. as  shown in 
-\ref{fig:orbit_distances_chr14}, this observation is
-true for the first 13 inter-chromosomal 
-contact maps of chromosome 14 as well as it intra-chromosomal
-contact map.
-Although comparisons can be made for each contact map as to
-whether which contact maps are more similar to each other,
-no global pattern has been observed from graphlet distances.
-
-It is worth mentioning that interchromosomal 
-thresholded contact maps 
-represent
-a bipartide graph with the loci from each chromosome 
-on one side. Due to this
-bipartide nature of the graphs in inter-chromosomal maps,
-count of certain orbits is always 0, resulting in
-a correlation values of 0 for them as well.
-We ignored these values  when we calculated averages across orbits 
-in figure \ref{fig:contact_maps_correlations_chr14} since they
-would result in a bias towards zero in 
-averages. You can see the bias in 
-figure \ref{fig:orbits_correlations_all} where 
-average correlations of orbits
-$\mathbb{Q} = \{3, 9, 10{\text -}14, 20{\text -}34, 39{\text -}48, 51{\text -}72\}$ 
-are close to zero. In fact all correlations
-corresponding to these orbits are 0 except for the ones between the same 
-chromosomes.
+cell lines, which is also the case in figure
+\ref{fig:orbit_distances_chr14} for majority of contact maps.
 
 \subsection{MIC Comparison}
+
 \begin{figure*}
     \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_cancer_vs_normal.png}
-    \caption{}
-    \label{fig:contact_map_correlations_all}
-    \end{subfigure}
+%    \begin{subfigure}[b]{\textwidth}
+%        \includegraphics[width=\textwidth]{figures/contact_maps_correlations_cancer_vs_normal.png}
+%    \caption{}
+%    \label{fig:contact_map_correlations_all}
+%    \end{subfigure}
 
@@
 
-In addition to simple graphlet distance comparison,
-we can compare graphlets by calculating
-how often certain graphlets occur in them. By doing so
-we measure the frequency distribution
-of certain spatial structures in
-each contact map. As a result of this approach
-we can compare contact maps by calculating the 
-correlation between their orbit distributions.
-A higher correlation would mean higher similarity
-in terms of spatial structure between the loci
-involved.
+In addition to comparing cells in terms of their
+orbit distances, we can compare them by measuring how
+often certain graphlets occur in their contact maps. By
+doing so, we measure the frequency distribution of the spatial
+structures represented by orbits in each contact map. In order
+to see how closely such structures are distributed, we can
+compare contact maps by calculating the correlation between
+their orbit distributions. A higher correlation for certain orbits
+would mean higher similarity in terms of that particular spatial
+structure between the loci involved.
 
-This approach also allows for comparison of orbits
-themsleves. By comparing average oribit correlations
-across all contact maps of two cell lines, we can
-have a measure of how similar certain orbits are
-between cell lines. This can give us a 
-\textit{global} measure
-of how similar two cell lines are in terms of 
-\textit{local} spatial positionings.
+Before going on with the results,
+it is worth mentioning that interchromosomal 
+thresholded contact maps 
+represent
+a bipartide graph with the loci from each chromosome 
+on one side. Due to this
+bipartide nature of the graphs in inter-chromosomal maps,
+count of certain orbits is always 0, resulting in
+a correlation values of 0 for them as well.
+You can see the bias in 
+figure \ref{fig:orbits_correlations} where 
+average correlations of orbits
+$\mathbb{Q} = \{3, 9, 10{\text -}14, 20{\text -}34, 39{\text -}48, 51{\text -}72\}$ 
+are close to zero. In fact all correlations
+corresponding to these orbits are 0 except for the ones between 
+the same 
+chromosomes.
 
@@
 We found statistically significant difference between
-normal vs cancer and cancer vs cancer correlations.
-The results of staistical tests are shown in table
-\ref{tab:statistical_results}. The difference
-between the two cells are also illustrated in figure
-\ref{fig:orbits_correlations}, which showes corrected
-mean difference of MIC values. Figure 
-\ref{fig:contact_map_correlations_all} shows the difference
-between average pairwise
-correlations. For most of the contact maps, correlation
-between normal and cancer cells are smaller
-than the correlation between cancer cells. This is corroborated
+cancer-cancer and normal-cancer correlations.
+($F(73, 1582)=6.29$, $p < 0.00001$, Wilk's $\Lambda = 0.775$)
+ The difference  is also illustrated in figure
+\ref{fig:orbits_correlations_normal_vs_cancer},
+which plots corrected
+mean difference of MIC values for cance-cancer and 
+normal-cancer correlations.  
+We performed statistical test to see if there is a 
+significant difference correlation between individual pairs
+of cells. Figure \ref{fig:orbits_correlations_all} demonstrate
+such difference.
+Average correlation over all contac maps
+for normal-cancer pairs are smaller
+than cancer-cancer pairs. This is corroborated
 by the results of statical test which verify that such difference
-is if fact signifcant.
+is in fact signifcant.($F(365, 7882) = 3.91$, $p < 0.00001$, 
+Wilk's $\Lambda = 0456$)
 Figures \ref{fig:orbits_correlations_normal_vs_cancer} and
@@
 normal MIT cell. In fact our statistical analysis shows that 
-\textit {for orbits in $\mathbb{Q}$, 
+\textit {for orbits NOT in $\mathbb{Q}$, 
 intra-leukemic orbit correlations are significantly higher
@@
 leukemic cells in terms of their local structure.
-
-\subsection{Statistical Analysis}
-In order to qauntify our results, we have conducted one-sided
-t-test in order to test whether the average pair-wise
-MIC values across orbits are significantly different from 
-each other and also from 1. 
-However, pairwise correlation of cancer cells for
-orbits in $\mathbb{Q}$ were significantly higher than
-correlation between cancer cells and normal cells.
-The results
-for this test showed that all values are significantly less than 1;
-A summary of can be found in
-table \ref{tab:t-test}.
-We have also conducted t-tests for 
-pair-wise orbit signature vector distances across contact maps.
-Please refer to supplementary material for result of the 
-full list of t-test results.
 

### 2018-05-23 papers/manuscripts/manuscript.tex
final draft of the manuscript

@@
 In this study, we investigated
-dissimilarities between normal cells and cancerous cells,
-through analyzing HiC contact maps. 
-Our results show that certain orbit distributions
-have significanly higher correlation 
-between Leukemic cells.
+dissimilarities between normal cells and leukemic cells
+in terms of their three dimensional conformation.
+We first thresholed HiC data corresponding to
+one normal cell line and four leukemic cells lines.
+We then used the thresholded data to extract the 
+first 72 orbits for all loci in each contact map.
+We then measured pairwise graphlet distances as
+well as pairwise graphlet distribution correlations
+for each pair of cells and compared them using 
+statistical methods.
+Our results show that normal-cancer pairs have
+significantly higher dinstances from each other
+than cancer-cancer pairs.
+Also, we concluded that for certain orbits,
+cancer-cancer pairs demonstrate higher correlations
+than normal-cancer pairs in terms of orbit frequency
+distributions.
 
@@
 \section{Introduction}
-
+This reasearch is an effort to compare the three-dimensional
+structure of cell genomes. To the best of our knowledge
+little research has dealt with quantitative comparison
+of spatial conformation of chromosomes.
 Ideally, it is desirable to compare 3D structures of 
 cell in order to make such comparisons.
-However, the main challenge is that 
+However, the main challenge in this regard
+is that 
 3D structure of a cell is not readily available. 
-In orther to find dissimilarities in the 3D structure of 
+In order to find dissimilarities in the 3D structure of 
 chromosomes, we used HiC dataset.
@@
 \cite{lieberman2009comprehensive}, captures interactions between 
-chromosomal fragments in kilobase resolution. Based on HiC data, an
+chromosomal fragments in kilobase resolution. 
+Based on HiC data, a \textit{contact map} or
 \textit{interaction frequency (IF) } matrix can be developed 
@@
 inter- and intra-chromosomal interaction matrices.
-We believe differences in interaction matrices can 
-be found between normal cells and cancerous ones.
+We have found statistically significant
+differences between interaction matrices of
+normal cells and cancerous ones.
 
-Recently, there has been many efforts at predicting the 3D conformation
+Recently, HiC data has been mostyly used
+in efforts to predict the 3D conformation
 of chromosomes using HiC data. 
-\cite{noble2011three, rousseau2011three, hu2013bayesian, varoquaux2014statistical, trieu2014large, zhang20133d, lesne20143d, bau2011three, adhikari2016chromosome3d}.
+\cite{noble2011three, 
+rousseau2011three, 
+hu2013bayesian, 
+varoquaux2014statistical, 
+trieu2014large, 
+zhang20133d, 
+lesne20143d, 
+bau2011three, 
+adhikari2016chromosome3d}.
 These efforts, although different in
@@
 interaction frequencies in contact maps as an inverse measure of 
-distance. In particular \cite{adhikari2016chromosome3d} developed
+distance. For example,  \cite{adhikari2016chromosome3d} developed
 a method, Chromosome3D which uses
@@
 expensive. Almost all reconstruction methods rely on either 
-deterministic or heuristic optimization in order to find the best
+deterministic or heuristic optimization approaches
+in order to find the best
 confomation that matches contact maps. Also, there is no real 
 way of verifying whether the reconstruction results are accurate.
+The only method of verifying such results is
 Fluorescence in situ hybridizaiton
-(FISH) is used for investigating 3D configuration of chromosomes.
+(FISH) which can capture the actual
+3D configuration of chromosomes.
 \cite{gasser2002visualizing, lanctot2007dynamic, mateos2009spatially}
@@
 
-Graphlet comparison is a novel method used to compare 
+Recently, graphlet comparison has emerged
+as a novel method for comparing
 large networks in order to
@@
 Authors of \cite{prvzulj2007biological} 
-provide a new measure of PPI
+provide a new measure of protein-protein
+interaction (PPI)
 network comparison
-based on 73 constraints. This is used in order to compare two large
-networks in order to detect similarities.
+based on 73 constraints. The method
+is used in order to compare two large
+PPI networks in order to detect similarities.
 
@@
 
-The authors of \cite{di2010fast} generalized the idea of graphlets to 
-ordered graphs were the nodes are labeled in ascending order.
-As can be viewed, there are a total of 14 orbits for graphlets of size
-2 and 3 since the label of graphlets is also included in toplogy.
-In the new definition, $d_v^i$ denotes the number of orbit $i$ touches 
-node $v$. Each node, is then assigned a vector of length 14 
-\footnote{number of orbits in graphlets of size 2 and 3}
-$(d_v^1, d_v^2, ..., d_v^{14})$ 
-and similarity of two nodes in two contact maps can be compared by
-how geometrically close their corresponding vectors are.
+In this paper, we applied the same approach of graphlet distance
+and graphlet distribution comparison on HiC data
+in order investigate genome spatial confomations differences
+between normal and leukemic cells.
+
+% **************************************************************
+% Keep this command to avoid text of first page running into the
+% first page footnotes
+\enlargethispage{-65.1pt}
+% **************************************************************
 
 \subsubsection{Notations}
-In this paper, matrices and vectors are represented with bold
+In this paper, matrices and vectors are represented using bold
 capital and bold small letters respectively.
-matrix rows and columns are represented by a \textit{dot}
+Matrix rows and columns are represented by a \textit{dot}
 notation. For example, the $i$th row of matrix $M$ is
@@
 
-We denote the set of all contact maps in cell line $T$ with 
-$\mathbb{C}^T$. If no particular cell line is addressed, the
+We denote the set of all contact maps in cell line $K$ with 
+$\mathbb{C}^K$. If no particular cell line is addressed, the
 subscripts are dropped.
 Any arbitrary member of $\mathbb{C}$ is denoted by 
-$C_{ij}$, where $i$ and $j$ ($j \ge i$) represent the two chromosomes involved. 
+$\mathbf{C}_{ij}$, where $i$ and $j$ ($j \ge i$) 
+represent the two chromosomes involved. 
 In human cells this set contains a total of 276 contact maps,
@@
 For ease of representations, intra-chromosomal contact maps are
-distinguished by a single superscript, so we have $C_{i,i} =
-C_i$.
+distinguished by a single superscript, so we have $\mathbf{C}_{i,i} =
+\mathbf{C}_i$.
 
@@
 inter-chromosomal contact maps $\mathbb{V}_{ij}$ contains the loci in
-the both of chromosomes involved ($|\mathbb{V}_{ij}| = N_i + N_j$).
-
-% **************************************************************
-% Keep this command to avoid text of first page running into the
-% first page footnotes
-\enlargethispage{-65.1pt}
-% **************************************************************
+the both of chromosomes involved 
+($\mathbb{V}_{ij} = \mathbb{V}_i \cup \mathbb{V}_j$).
 
@@
 and the follicular lymphoma cell-line (RL).
-Just as \cite{wang2013properties}, 
-we used normal B-cell line (GM068990)
+As in \cite{wang2013properties}, 
+We used normal B-cell line (GM068990)
 from \cite{lieberman2009comprehensive} 
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figures/local_thresholded_chr1_chr1.png}
+    \includegraphics[width=.47\textwidth]{figures/local_thresholded_chr1_chr1.png}
     \caption{Result of thresholding interchromosomal contact map of chromosome 1
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figures/graphlet_extraction.png}
+    \includegraphics[width=.47\textwidth]{figures/graphlet_extraction.png}
     \caption{Graphlet extraction for the four cell lines. For each
@@
     this process is a \textit{signature correlation} vector of size
-    73 which captures how similar frequencies of two orbits are.
-    In order to test our second hypothesis, we calculated averages
-    across contact maps (along the vertical red arrow) to test 
-    hypothesis \ref{eq:h2a}
-    and across orbits
-    (along the horizontal red arrows) to test hypothesis \ref{eq:h2b}.}
+    73 which captures how similar frequencies of two orbits are.}
     \label{graphlet_correlation_schema}
@@
     \caption{   
+        Pair-wise graphlet signature distances for all contact maps of
+        chromosome 14. Warm colors as used for cancer-cancer pairs and
+        cold colors are used for normal-cancer pairs. As can be seen
+        cancer-cancer pairs tend to be close to each other than to the
+        normal cell. This is specially true for the first 13 
+        inter-chromosomal contact maps.
      }
@@
 As illustrated in figure \ref{fig:orbit_distances_all_a},
-we can see that normal-cancer cells have higher distance
+we can see that normal-cancer pairs have higher distance
 from each other than cancer-cancer pairs.
@@
 Figure \ref{fig:orbits_correlations} demonstrates that certain
-orbits of Leukemic have higher correlation to each other 
+orbits of Leukemic cells
+have higher correlation to each other 
 than to the

### 2018-07-11 papers/manuscripts/manuscript.tex
mardas

@@
 \begin{abstract}
-
-In this study, we investigated
-dissimilarities between normal cells and leukemic cells
-in terms of their three dimensional conformation.
-We first thresholed HiC data corresponding to
-one normal cell line and four leukemic cells lines.
-We then used the thresholded data to extract the 
-first 72 orbits for all loci in each contact map.
-We then measured pairwise graphlet distances as
-well as pairwise graphlet distribution correlations
-for each pair of cells and compared them using 
-statistical methods.
-Our results show that normal-cancer pairs have
-significantly higher dinstances from each other
-than cancer-cancer pairs.
-Also, we concluded that for certain orbits,
-cancer-cancer pairs demonstrate higher correlations
-than normal-cancer pairs in terms of orbit frequency
-distributions.
-
+    Chromosal Conformational Capturing (3C) data,
+    particularly the Hi-C data is widely used for
+    investigating the three-dimensional (3D) 
+    chromatin conformation inside the nucleus and
+    for identifying chromatin interactions as 
+    well as topologically associating domains 
+    (TADs). However, Hi-C based structural analysis
+    for exploring local chromatin conformational 
+    preferences has not been performed yet. 
+    Here, for the first time, we present graphlet
+    based local structural analysis for normal 
+    and malignant human cell types  using chromosal
+    conformational capturing (Hi-C) data. 
+    We first applied thresholding in Hi-C interaction
+    frequency data for one normal cell line and 
+    four leukemic cells lines in order to covert 
+    them into unweighted graphs. We then mined 
+    the unweighted graphs to extract graphlet -based 
+    orbitial frequency distributions? . Subsequently
+    , pairwise graphlet distances as well as 
+    pairwise graphlet distribution correlations 
+    for each pair of cells were computed and 
+    compared using statistical methods namely 
+    ANOVA and multi-variate ANOVA. Our results 
+    demonstrate that normal-cancer pairs have 
+    significantly ($F(1, 1654) = 20.49$, $p-value
+    < 0.0001$) higher difference than cancer-cancer 
+    pairs. Furthermore, for certain orbits cancer-cancer 
+    pairs demonstrated higher correlations 
+    ($F(365, 7882)=391$, $p-value<0.00001$, and 
+    $Wilk's \quad \Lambda=0456$) than normal-cancer pairs 
+    in terms of orbit frequency distributions. 
+    Source code of GrapHiClet 
+    is freely available at 
+    \url{https://github.com/rasoolianbehnam/watson}.
+    Also, the database used for this project can be
+    found at \url{https://graphiclet.localtunnel.me/secret/}
 \end{abstract}
@@
 \section{Introduction}
-This reasearch is an effort to compare the three-dimensional
-structure of cell genomes. To the best of our knowledge
-little research has dealt with quantitative comparison
-of spatial conformation of chromosomes.
-Ideally, it is desirable to compare 3D structures of 
-cell in order to make such comparisons.
-However, the main challenge in this regard
-is that 
-3D structure of a cell is not readily available. 
-In order to find dissimilarities in the 3D structure of 
-chromosomes, we used HiC dataset.
-The HiC method, which was developed by 
-\cite{lieberman2009comprehensive}, captures interactions between 
-chromosomal fragments in kilobase resolution. 
-Based on HiC data, a \textit{contact map} or
-\textit{interaction frequency (IF) } matrix can be developed 
-between \textit{loci} at a desired resolution.
-A cell $IF_{ij}$ in an interaction frequency matrix captures 
-the number of interaction detected
-in HiC dataset between locus $i$ and locus $j$ in the genome.
-An interaction matrix can be used to develop both 
-inter- and intra-chromosomal interaction matrices.
-We have found statistically significant
-differences between interaction matrices of
-normal cells and cancerous ones.
+Genome of a eukaryotic cell is organized into a
+complex three-dimensional (3D) structure, which
+leads to a network of chromosomal interactions \cite{dekker2008gene}.
+The spatial organization of genome is one of
+the most important factors in determining its
+function \cite{fraser2007nuclear} via interactions between
+spatially close genes \cite{kagey2010mediator}. Such
+interactions can be modeled using a network approach
+\cite{kagey2010mediator}. However, our knowledge of
+3D conformation of genome is limited. Fluorescent In
+Situ Hybridization (FISH) technology, which can
+capture 3D conformation of multiple loci but cannot
+capture global layout of the genome. In order to
+address this, more advanced techniques of chromosome
+conformation capturing such as 3C \cite{dekker2002capturing},
+4C \cite{simonis2006nuclear} and 5C \cite{dostie2007mapping}
+has been introduced which are based on chromatin fragment
+fixation, using restriction-enzyme digestion and
+intra-molecular ligation. One of the most recent
+versions of chromosome conformation capturing is
+Hi-C \cite{rao20143d, lieberman2009comprehensive},
+which $IF_{ij}$ captures interactions between chromosomal
+fragments resulting in a contact map or interaction frequency
+(IF) matrix, which captures the number of interactions
+detected in Hi-C dataset between each pair of loci.
 
-Recently, HiC data has been mostyly used
-in efforts to predict the 3D conformation
-of chromosomes using HiC data. 
+Recently, Hi-C data has been mostly used to predict
+the 3D structure at the chromosome level by satisfying
+intra-chromosomal interactions or even at the
+full genome by leveraging both inter- and intra-chromosomal
+interactions
 \cite{noble2011three, 
@@
 These efforts, although different in
-approach, usually translate 
-interaction frequencies in contact maps as an inverse measure of 
-distance. For example,  \cite{adhikari2016chromosome3d} developed
-a method, Chromosome3D which uses
-distance geometry simulated annealing (DGSA) in order to
-reconstruct genome structure. These reconstructed 3D 
-structures could be used in order to compare normal and malignant
-cell lines. However, the main obstacle to doing so is that the
-process of reconstruction is computationally
-expensive. Almost all reconstruction methods rely on either 
-deterministic or heuristic optimization approaches
-in order to find the best
-confomation that matches contact maps. Also, there is no real 
-way of verifying whether the reconstruction results are accurate.
-The only method of verifying such results is
-Fluorescence in situ hybridizaiton
-(FISH) which can capture the actual
-3D configuration of chromosomes.
-\cite{gasser2002visualizing, lanctot2007dynamic, mateos2009spatially}
-However, this method can only be used locally and cannot map
-the whole structure of the chromosomes.
-
-Recently, graphlet comparison has emerged
-as a novel method for comparing
-large networks in order to
-find local similarities in them.
-Authors of \cite{prvzulj2007biological} 
-provide a new measure of protein-protein
-interaction (PPI)
-network comparison
-based on 73 constraints. The method
-is used in order to compare two large
-PPI networks in order to detect similarities.
-
-In \cite{milenkoviae2008uncovering} the authors
- provide heuristics to compare two nodes in a graph
-based on signature vectors, which are 73-dimensional vectors
-$\mathbf{s}^T
-= [s_0, s_2, ..., s_{72}]$ where $s_i$ denotes the number of nodes in
-the network that are part of an orbit $i$. \\
-They concluded that proteins with similar surroundings perform
-similar functions.
-
-In \cite{milenkovic2010cancer}, the same author investigates 
-cancer-causing genes to find similarities in their signatures. After
-clustering the genes based on \textit{signature similarity} criteria,
-some clusters contain a lot of cancerous genes.
-They use 4 different clustering methods with varying parameters to cluster
-the proteins. They then predict the cancer-relatedness of a protein 
-$i$ using
-an enrichment criteria $\frac{k}{|C_i|}$ where $C_i$ is the cluster
-where protein $i$ belongs and $k$ is the number of cancer-causing
-proteins in $C_i$ and $|C_i|$ is the size of $C_i$.
-
-In this paper, we applied the same approach of graphlet distance
-and graphlet distribution comparison on HiC data
-in order investigate genome spatial confomations differences
-between normal and leukemic cells.
-
+approach, usually translate interaction frequencies in
+contact maps as simple inverse measures of distance.
+They then try to find the coordinates of the chromosomal
+loci that would result in that particular distance
+matrix using optimization. These methods vary in
+the optimization models and methodologies used.
+Also, efforts has been made recently to learn the
+inverse conversion parameters from contact maps
+to distance matrices \cite{oluwadare2018maximum}.
+The reconstructed 3D structures could be used in
+order to compare normal and malignant cell lines.
+However, the main obstacle to doing so is that
+the process of reconstruction is computationally expensive.
+Almost all reconstruction methods rely on either
+deterministic or heuristic optimization approaches in
+order to find the best conformation that matches contact
+maps. Also, there is no experimental way of evaluating
+the accuracy of the reconstructed 3D conformations.
+One experimental way of partially validating correctness
+of reconstruction process is Fluorescence in
+situ hybridizaiton (FISH) method. However, this
+technique is limited to a few loci and cannot be
+extended to cover the whole structure of the chromosomes.
+Furthermore, the process of reconstructing 3D
+chromatic structure is computationally expensive,
+hindering their applicability at the genome-wide scale.
 % **************************************************************
@@
 
+Over the past decade, graphs have been used extensively
+in order to model domain-specific phenomena such
+as computer security, gene regulatory networks and
+social networks. These graphs are usually in
+the form of very large networks. It is often necessary
+to perform statistical analysis between graphs in
+order to compare their structure. Graphlets and
+orbits can be used in order to probe large graphs
+in order to find global and local similarities 
+\cite{shervashidze2009efficient, borgs2006counting,
+bondy1977graph}.
+This can be done by counting the number of occurrences
+of a each graphlet and/or orbits for each node
+in the whole graph and the comparing them \cite{prvzulj2007biological,
+prvzulj2004modeling}
+
+Here, we present local structural analysis between
+4 sets of Hi-C data. All four data sets are sequences
+from the same cell line, with one of them being
+a normal cell and the other three sequenced from
+three types of leukemic cells. In order to achieve
+this, we used graphlets, given their strength in
+capturing information about local structures of
+a graph. We first thresholded Hi-C interaction frequency
+matrices in order to convert in to an unweighted undirected
+graph adjacency matrix. We the extracted counts of
+the first 73 orbits for each node, identifying each
+node with a signature vector of size 73. We then
+applied graphlet distance metrics proposed in
+{prvzulj2007biological} together with statistical methods
+in order to find difference between cell lines.
+Our results show that difference of local structure
+between normal cells and leukemic cells are significantly
+larger that difference between cancer-cancer cells.
+
 \subsubsection{Notations}
-In this paper, matrices and vectors are represented using bold
-capital and bold small letters respectively.
-Matrix rows and columns are represented by a \textit{dot}
-notation. For example, the $i$th row of matrix $M$ is
-denoted by $M_{i.}$ and its $j$th column is represented
-by $M_{.j}$.
+%In this paper, matrices and vectors are represented using bold
+%capital and bold small letters respectively.
+%Matrix rows and columns are represented by a \textit{dot}
+%notation. For example, the $i$th row of matrix $M$ is
+%denoted by $M_{i.}$ and its $j$th column is represented
+%by $M_{.j}$.
 
@@
 \section{Materials and Methods}
-We re-used Leukemic Hi-C libraries 
-created in \cite{wang2013properties}
-These libraries were sequenced 
-for cases of primary human B-acute
-lymphoblastic leukemia (B-ALL or ALL), 
-the MHH-CALL-4 B-ALL cell
-line (CALL4), 
-and the follicular lymphoma cell-line (RL).
-As in \cite{wang2013properties}, 
-We used normal B-cell line (GM068990)
-from \cite{lieberman2009comprehensive} 
-for our comparisons.
-We created contact maps of resolution
-500kb and normalized it using 
-the \texttt{iced} package in python
-developed by \cite{servant2015hic}.
+Chromosomes inside the nuclei are made up of
+pairs of nucleotides called a base. As a result of
+the Hi-C process, a database is generated which
+provides interaction counts found by the method between
+a number of such bases. The minimum number of
+bases that can be captured is called the resolution of
+that database. These counts are then binned so
+that counts are aggregated for every equal-sized
+length of the chromosome (e.g. 1 Mb pairs) leading
+to an N * N interaction frequency matrix. Each
+cell (i, j) in the matrix is the aggregate count
+of all interactions found between loci i\textsuperscript{th} and
+j\textsuperscript{th} length.
+We re-used Leukemic Hi-C libraries created in
+\cite{wang2013properties}. These libraries were sequenced
+using Illumina HiSeq 2000 for cases of primary human
+B-acute lymphoblastic leukemia (B-ALL or ALL),
+the MHH-CALL-4 B-ALL cell line (CALL4), and the
+follicular lymphoma cell-line (RL) for which high-quality
+paired-end reados of 39M, 79M and 33M were obtained
+respectively As in \cite{wang2013properties}, We used
+normal B-cell line (GM068990) from as benchmark for
+our comparisons. The three datasets generated in
+\cite{wang2013properties} were valid since 98\% of
+the contact generated in \cite{wang2013properties}
+were identical to that of \cite{lieberman2009comprehensive}
+and 83\% of contacts in \cite{lieberman2009comprehensive}
+were also present in \cite{wang2013properties}. We
+created contact maps with bin sizes of  500 kilo-base
+and normalized them using normalization provided 
+HiC-Pro( \texttt{iced} package in python) developed
+by \cite{servant2015hic}.
+Normalization is necessary since Hi-C data usually
+contains different biases due to GC content,
+mappability and effective fragment length \cite{yaffe2011probabilistic,
+hu2012hicnorm}. The normalization proivdedi in
+the iced package is based on the Sinkhorn-Knopp
+algorithm which is a simple, parameter-free and
+capability to correct unknown biases.  The edges
+in a network usually include indirect dependencies because
+correlations are transitive; that is, if there is
+a strong realationship between nodes 1 and 2,
+and also a strong realationship between nodes 2
+and 3, it is highly likely that nodes relationship between
+nodes 1 and 3 is exaggerated in the network \cite{feizi2013network}.
+In order to remove the effect of indirect interactions,
 We also performed and extra normalization by
-performing network deconvolution \cite{feizi2013network}
-in order to remove
-the effect of indirect interactions.
+performing network deconvolution \cite{feizi2013network},
+which uses eigenvalue decomposition and infinite series
+sums in order to reverse the bias posed by indirect
+relationships.
+
+\subsection{Graphlets and Orbits}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.5\textwidth]{figures/graphlets.png}
+    \caption{}
+    \label{fig_graphlets}
+\end{figure}
+Recently, graphlet comparison has emerged as
+a novel method for comparing large networks in
+order to find local similarities in them. A
+graph G is a pair $(V,E)$, where $V$ is a set of
+vertices and $E \subseteq V\times V$ is a set of
+edges. A connected graph is one where there is
+a path between every pair of vertices.
+Given a graph $G(V, E)$ and $S \subseteq V$,
+then $G'(S, E')$ is a graphlet if and only if
+it is connected $E' = \{(u, v) | u, v \in V \quad \&
+\quad (u, v) \in E \rightarrow (u, v) \in E'\}$. 
+There a total of 30 graphlets
+of size 2, 3, and 5.  Figure \ref{fig_graphlets}
+demonstrates these graphlets. 
+As can be seen there is only one graphlet
+of size 2 which is equivalent to an edge; that
+is, the number of graphlet 1 in a graph is the
+same as the number of edges on the graph. There
+are also a total of 2 graphlets of size 2, 6
+of size 4 and 20 of size 5. The nodes of each graphlet
+can be partitioned into sets of topographically equivalent
+nodes called orbits. For  example, in  Figure 
+\ref{fig_graphlets}, we can see that G3 can be
+partitioned into 2 sets of nodes, the middle ones
+(white) and the outer nodes (black). 
+For the same set of graphlets,
+there are 73 orbits that are also illustrated in
+figure  Figure using nodes of difference shades.
 
@@
 
-When thresholding contact maps, it is necessary to make sure
-that both global and local features are maintained. We could consider 
-thresholding the contact maps by simply setting values above a fixed value to
-one and the rest to zero; However, in practice, this method resulted in graphs
-that capture the local structure of the contact maps poorly. This is because
-intensities follow an exponential distribution with a mean close to zero
-with a few very larges values that correspond to interactions along 
-or close to the main diagonal of the contact maps.
-Thus, picking relatively large numbers would result in ignoring interactions
-that are far from the main diagonal while picking small values will lead to
-capturing too many (insignificant) interactions.
+When thresholding contact maps, it is necessary to
+make sure that both global and local features are
+maintained. We could consider thresholding the
+contact maps by simply setting values above a
+fixed value to one and the rest to zero; However,
+in practice, this method resulted in graphs that
+capture the local structure of the contact maps
+poorly. This is because intensities follow an
+exponential distribution with a mean close to
+zero with a few very larges values that correspond to
+interactions along or close to the main diagonal of
+the contact maps.  Thus, picking relatively large
+numbers would result in ignoring interactions that
+are far from the main diagonal while picking small
+values will lead to capturing too many (insignificant)
+interactions.
 
-To the best of our knowledge, little work has dealt with the task of
-thresholding HiC contact maps. There has been some statistical approaches
-developed on similar data in other fields. 
-For example, authors of \cite{ginestet2011statistical} developed 
-Statistical Network (SPN) analysis
-where the choice of thresholding value is made by statistical inference.
-This method, although very robust, works within the framework of 
-design of experiments where the same
-network can be extracted for different 
-individuals under different treatments. Thus a relatively large
-set of different contact maps need to be available in order for
-this method to be applicable towards our end.
+To the best of our knowledge, little work has
+dealt with the task of thresholding HiC contact maps.
+There has been some statistical approaches developed
+on similar data in other fields.  For example,
+authors of \cite{ginestet2011statistical} developed
+Statistical Network (SPN) analysis where the
+choice of thresholding value is made by statistical inference.
+This method, although very robust, works within
+the framework of design of experiments where the
+same network can be extracted for different individuals
+under different treatments. Thus a relatively large
+set of different contact maps need to be available
+in order for this method to be applicable towards
+our end.
 

### 2018-07-11 papers/manuscripts/supplementary/01_thresholding.tex
mardas

--- 2018-03-08 notebook.tex
@@
     % Document parameters
-    \title{Thresholding\_local}
+    \title{01\_thresholding}
 
@@
 \textbf{Maximum Thresholding}: in max thresholding, if the pixel is the
-maximum of its neighbors with respect to the kernel, then it is set. 2.
+maximum of its neighbors with respect to the kernel, then it is set.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{def}\NormalTok{ local_threshold(mat, k}\OperatorTok{=}\DecValTok{1}\NormalTok{, method}\OperatorTok{=}\StringTok{'max'}\NormalTok{, t}\OperatorTok{=}\DecValTok{1}\NormalTok{):}
+\NormalTok{    mat2 }\OperatorTok{=}\NormalTok{ np.zeros_like(mat)}
+\NormalTok{    n, m }\OperatorTok{=}\NormalTok{ mat.shape}
+    \ControlFlowTok{if} \BuiltInTok{isinstance}\NormalTok{(k, }\BuiltInTok{tuple}\NormalTok{):}
+\NormalTok{        k1, k2 }\OperatorTok{=}\NormalTok{ k}
+    \ControlFlowTok{else}\NormalTok{:}
+\NormalTok{        k1 }\OperatorTok{=}\NormalTok{ k2 }\OperatorTok{=}\NormalTok{ k}
+    \ControlFlowTok{for}\NormalTok{ i }\KeywordTok{in} \BuiltInTok{range}\NormalTok{(k1, n}\OperatorTok{-}\NormalTok{k1):}
+        \ControlFlowTok{for}\NormalTok{ j }\KeywordTok{in} \BuiltInTok{range}\NormalTok{(k, m}\OperatorTok{-}\NormalTok{k2):}
+            \ControlFlowTok{if}\NormalTok{ method }\OperatorTok{==} \StringTok{'max'}\NormalTok{:}
+\NormalTok{                condition }\OperatorTok{=}\NormalTok{ mat[i, j] }\OperatorTok{==}\NormalTok{ np.}\BuiltInTok{max}\NormalTok{(mat[i}\OperatorTok{-}\NormalTok{k1:i}\OperatorTok{+}\NormalTok{k1, j}\OperatorTok{-}\NormalTok{k2:j}\OperatorTok{+}\NormalTok{k2])}
+            \ControlFlowTok{elif}\NormalTok{ method}\OperatorTok{==}\StringTok{'normal'}\NormalTok{:}
+\NormalTok{                temp }\OperatorTok{=}\NormalTok{ mat[i}\OperatorTok{-}\NormalTok{k1:i}\OperatorTok{+}\NormalTok{k1, j}\OperatorTok{-}\NormalTok{k2:j}\OperatorTok{+}\NormalTok{k2]}
+\NormalTok{                condition }\OperatorTok{=}\NormalTok{ mat[i, j] }\OperatorTok{>=}\NormalTok{ np.mean(temp) }\OperatorTok{+}\NormalTok{ t }\OperatorTok{*}\NormalTok{ np.std(temp)}
+            \ControlFlowTok{elif}\NormalTok{ method }\OperatorTok{=} \StringTok{'max_linear'}\NormalTok{:}
+\NormalTok{                condition }\OperatorTok{=}\NormalTok{ mat[i, j] }\OperatorTok{==}\NormalTok{ np.}\BuiltInTok{max}\NormalTok{(mat[i, j}\OperatorTok{-}\NormalTok{k1:j}\OperatorTok{+}\NormalTok{k2])}
+            \ControlFlowTok{if}\NormalTok{ condition:}
+\NormalTok{                mat2[i, j] }\OperatorTok{=} \DecValTok{1}
+    \ControlFlowTok{return}\NormalTok{ mat2}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
   \textbf{Normal Thresholding}: in normal thresholding, if the pixel is
   larger that the average of the neighbors then it is set.
-
-first I perform the most lates normalization method that I have found to
-be most useful: a combination of gaussian normalization, SCN and pearson
-correlation, in the same order mentioned. The normalized results are of
-type \texttt{pearson(scn(gaussian(graph)))}.
-
-Then I threshold the results by setting pearson values larger than 0 to
-1 and the rest to 0. In order to extract graphlets, I used the
-\emph{orca} package in R. the script \texttt{./rscript.r} read a binary
-thresholded matrix representing an unweighted graph and outputs orbtis 0
-through 72 for each node in the network. After thredholding the
-matrices, I save them so that orca in R can read it and extract orbits.
-
-By repeating the procedure explained above for all 23 chromosomes, we
-will have graphlets for all contact maps.
+\end{enumerate}
 
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}5}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
+{\color{incolor}In [{\color{incolor}1}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
         \PY{k+kn}{import} \PY{n+nn}{cv2}
-        \PY{k+kn}{from} \PY{n+nn}{utility} \PY{k+kn}{import} \PY{o}{*}
+        \PY{k+kn}{from} \PY{n+nn}{library.utility} \PY{k+kn}{import} \PY{o}{*}
         \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
@@
         \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n+nb}{filter}
+        \PY{k+kn}{from} \PY{n+nn}{sets} \PY{k+kn}{import} \PY{n}{Set}
         \PY{k+kn}{import} \PY{n+nn}{os}
@@
         \PY{o}{\PYZpc{}}\PY{k}{pylab} inline
-        \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
 \end{Verbatim}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-/home/bzr0014/watson/scripts/virt/local/lib/python2.7/site-packages/IPython/core/magics/pylab.py:161: UserWarning: pylab import has clobbered these variables: ['all', 'colors', 'log']
+/home/bzr0014/git/watson/virt/local/lib/python2.7/site-packages/IPython/core/magics/pylab.py:161: UserWarning: pylab import has clobbered these variables: ['colors', 'log']
 `\%matplotlib` prevents importing * from pylab and numpy
@@
 
-    \subsection{Initiating matrices}\label{initiating-matrices}
+    \section{Loading Data}\label{loading-data}
+
+The first step is to load the raw Hi-C contact maps. We have already
+extracted all inter- and intra-chromosomal contact maps and compiled
+them into as single large numpy array format.
 
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}18}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{2}
-         \PY{n}{chr2} \PY{o}{=} \PY{n}{chr1}
-         \PY{k}{print} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{chromosome 1: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{, chromosome 2: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
-         \PY{c+c1}{\PYZsh{}print observed\PYZus{}mit\PYZus{}original.shape}
+{\color{incolor}In [{\color{incolor}2}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
 
-         \PY{n}{mit} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}MIT/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PYZbs{}
-                       \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-         \PY{n}{call4} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}call4/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PYZbs{}
-                         \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-         \PY{n}{rl} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}RL/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+        \PY{n}{lengths\PYZus{}low\PYZus{}res} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{load}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../numpy\PYZus{}data/length\PYZus{}low\PYZus{}res.npy}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+        \PY{n}{mit\PYZus{}full}  \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{load}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../numpy\PYZus{}data/mit\PYZus{}low\PYZus{}res.npy}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{)}
+        \PY{n}{all\PYZus{}full}  \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{load}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../numpy\PYZus{}data/all\PYZus{}low\PYZus{}res.npy}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{)}
+        \PY{n}{rl\PYZus{}full}  \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{load}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../numpy\PYZus{}data/rl\PYZus{}low\PYZus{}res.npy}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{)}
+        \PY{n}{call4\PYZus{}full}  \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{load}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../numpy\PYZus{}data/call4\PYZus{}low\PYZus{}res.npy}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{)}
+        \PY{n}{data} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
+        \PY{n}{showImages}\PY{p}{(}\PY{p}{[}\PY{n}{mit\PYZus{}full} \PY{p}{,} \PY{n}{all\PYZus{}full} \PY{p}{,} \PY{n}{rl\PYZus{}full} \PY{p}{,} \PY{n}{call4\PYZus{}full} \PY{p}{]}\PY{p}{,} \PY{n}{rows}\PY{o}{=}\PY{l+m+mi}{2}\PY{p}{,} \PY{n}{titles}\PY{o}{=}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
+\end{Verbatim}
 
-         \PY{n+nb}{all} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}ALL/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+    \begin{Verbatim}[commandchars=\\\{\}]
+Number of rows and columns: 2, 2
+(4, 4)
 
-         \PY{c+c1}{\PYZsh{}There are some blank rows and columns in the matrix. let\PYZsq{}s remove them.}
-         \PY{n}{blankRows0}\PY{p}{,} \PY{n}{blankCols0} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
-         \PY{n}{blankRows1}\PY{p}{,} \PY{n}{blankCols1} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}
-         \PY{n}{blankRows2}\PY{p}{,} \PY{n}{blankCols2} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
-         \PY{n}{blankRows3}\PY{p}{,} \PY{n}{blankCols3} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_3_1.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \section{Selecting a inter-/intra-chromosomal contact
+map}\label{selecting-a-inter-intra-chromosomal-contact-map}
+
+You can chang chr1 and chr2 variables based on the contact map you want
+to investigate.
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}3}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{1}
+        \PY{n}{chr2} \PY{o}{=} \PY{l+m+mi}{2}
+        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}          \PY{o}{=} \PY{n}{get\PYZus{}contact\PYZus{}map}\PY{p}{(}\PY{n}{mit\PYZus{}full}        \PY{p}{,} \PY{n}{lengths\PYZus{}low\PYZus{}res}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
+        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}          \PY{o}{=} \PY{n}{get\PYZus{}contact\PYZus{}map}\PY{p}{(}\PY{n}{all\PYZus{}full}        \PY{p}{,} \PY{n}{lengths\PYZus{}low\PYZus{}res}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
+        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}           \PY{o}{=} \PY{n}{get\PYZus{}contact\PYZus{}map}\PY{p}{(}\PY{n}{rl\PYZus{}full}         \PY{p}{,} \PY{n}{lengths\PYZus{}low\PYZus{}res}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
+        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}        \PY{o}{=} \PY{n}{get\PYZus{}contact\PYZus{}map}\PY{p}{(}\PY{n}{call4\PYZus{}full}      \PY{p}{,} \PY{n}{lengths\PYZus{}low\PYZus{}res}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
+        \PY{n}{showImages}\PY{p}{(}\PY{n}{data}\PY{p}{,} \PY{n}{rows} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{titles}\PY{o}{=}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
+\end{Verbatim}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+Number of rows and columns: 2, 2
+(4, 4)
+
+    \end{Verbatim}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_5_1.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \subsection{Cleaning Data}\label{cleaning-data}
+
+As can be observed above, there are several rows and columns that simply
+don't contain any data and are all zeros, in the following code we clean
+the matrices to remove these zero rows and columns since they will cause
+problems in future analysis.
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}4}]:} \PY{c+c1}{\PYZsh{}There are some blank rows and columns in the matrix. let\PYZsq{}s remove them.}
+        \PY{n}{blankRows0}\PY{p}{,} \PY{n}{blankCols0} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
+        \PY{n}{blankRows1}\PY{p}{,} \PY{n}{blankCols1} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
+        \PY{n}{blankRows2}\PY{p}{,} \PY{n}{blankCols2} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
+        \PY{n}{blankRows3}\PY{p}{,} \PY{n}{blankCols3} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
         \PY{n}{blankRows} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
@@
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols3}\PY{p}{)}
-         \PY{n}{mit} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
-         \PY{n+nb}{all} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
-         \PY{n}{rl} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
-         \PY{n}{call4} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
+        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
+        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
+        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
+        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
+        \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{shape}
+        \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{shape}
+        \PY{n}{n3}\PY{p}{,} \PY{n}{m3} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{shape}
+        \PY{n}{n4}\PY{p}{,} \PY{n}{m4} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{shape}
 \end{Verbatim}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-chromosome 1: 2, chromosome 2: 2
-file directory: ../data/extracted\_all\_contact\_MIT/chr\_02\_02\_500kb.mat
-file directory: ../data/extracted\_all\_contact\_call4/chr\_02\_02\_500kb.mat
-file directory: ../data/extracted\_all\_contact\_RL/chr\_02\_02\_500kb.mat
-file directory: ../data/extracted\_all\_contact\_ALL/chr\_02\_02\_500kb.mat
-size of old matrix: (486, 486)
-size of new matrix: (480, 480)
-size of old matrix: (486, 486)
-size of new matrix: (480, 480)
-size of old matrix: (486, 486)
-size of new matrix: (480, 480)
-size of old matrix: (486, 486)
-size of new matrix: (480, 480)
+('size of old matrix:', (495, 486))
+('size of new matrix:', (454, 479))
+('size of old matrix:', (495, 486))
+('size of new matrix:', (454, 479))
+('size of old matrix:', (495, 486))
+('size of new matrix:', (454, 479))
+('size of old matrix:', (495, 486))
+('size of new matrix:', (454, 479))
+
+    \end{Verbatim}
+
+    \subsubsection{Comparing CALL4 with RL low-resolution
+data:}\label{comparing-call4-with-rl-low-resolution-data}
+
+Feel free to change D1 and D2 to pick any data from set of ```{[}'MIT',
+'ALL', 'RL', 'CALL4'{]}````.
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+{\color{incolor}In [{\color{incolor}6}]:} \PY{n}{D1} \PY{o}{=} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}
+        \PY{n}{D2} \PY{o}{=} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}
+        \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{20}\PY{p}{)}
+        \PY{c+c1}{\PYZsh{} Size of the kernel}
+        \PY{n}{k} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}
+        \PY{c+c1}{\PYZsh{} can be either \PYZsq{}max\PYZsq{} for setting the maximum value in each kernel to 1 and the rest to 0}
+        \PY{c+c1}{\PYZsh{} or \PYZsq{}normal\PYZsq{} for setting all values above mean + t * std withing the kernel to 1 and }
+        \PY{c+c1}{\PYZsh{} the rest to 0}
+        \PY{n}{method} \PY{o}{=} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}
+        \PY{c+c1}{\PYZsh{} in case of normal thresholding, t is the coefficient }
+        \PY{c+c1}{\PYZsh{} of the standard deviation; that is, n each kernel iteration K}
+        \PY{c+c1}{\PYZsh{} if K[i, j] \PYZgt{} mean(K) + t * std(K), then it is set to 1.}
+        \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{0}
+        \PY{n}{params} \PY{o}{=} \PY{n+nb+bp}{None}
+        \PY{n}{symmetric}\PY{o}{=} \PY{n}{chr1}\PY{o}{==}\PY{n}{chr2}
+        \PY{n}{D1\PYZus{}os} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{n}{D1}\PY{p}{]}\PY{o}{+}\PY{l+m+mi}{1}\PY{o}{+}\PY{l+m+mf}{1e\PYZhy{}5}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{n}{method}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{n}{t}\PY{p}{,} \PY{n}{params}\PY{o}{=}\PY{n}{params}\PY{p}{,} \PY{n}{symmetric}\PY{o}{=}\PY{n}{symmetric}\PY{p}{)}
+        \PY{n}{D2\PYZus{}os} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{n}{D2}\PY{p}{]}\PY{o}{+}\PY{l+m+mi}{1}\PY{o}{+}\PY{l+m+mf}{1e\PYZhy{}5}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{n}{method}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{n}{t}\PY{p}{,} \PY{n}{params}\PY{o}{=}\PY{n}{params}\PY{p}{,} \PY{n}{symmetric}\PY{o}{=}\PY{n}{symmetric}\PY{p}{)}
+        \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{D1\PYZus{}os}\PY{o}{.}\PY{n}{shape}
+        \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{D2\PYZus{}os}\PY{o}{.}\PY{n}{shape}
+        \PY{n}{n} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{n1}\PY{p}{,} \PY{n}{n2}\PY{p}{]}\PY{p}{)}
+        \PY{n}{m} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{m1}\PY{p}{,} \PY{n}{m2}\PY{p}{]}\PY{p}{)}
+        \PY{n}{D1\PYZus{}os} \PY{o}{=} \PY{n}{D1\PYZus{}os}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
+        \PY{n}{D1\PYZus{}data} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{n}{D1}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
+        \PY{n}{D2\PYZus{}os} \PY{o}{=} \PY{n}{D2\PYZus{}os}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
+        \PY{n}{D2\PYZus{}data} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{n}{D2}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
+        \PY{n}{a} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{n}{D1\PYZus{}os} \PY{o}{*} \PY{n}{D1\PYZus{}data}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{l+m+mi}{1}
+        \PY{n}{b} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{n}{D2\PYZus{}os} \PY{o}{*} \PY{n}{D2\PYZus{}data}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{l+m+mi}{1}
+\end{Verbatim}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+(2, 2, 2, 2)
+(2, 2, 2, 2)
 
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}19}]:} \PY{n}{n0}\PY{p}{,} \PY{n}{m0} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
-         \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
-         \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
-         \PY{n}{n3}\PY{p}{,} \PY{n}{m3} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}
-
-         \PY{n}{n} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{n0}\PY{p}{,} \PY{n}{m0}\PY{p}{,} \PY{n}{n1}\PY{p}{,} \PY{n}{m1}\PY{p}{,} \PY{n}{n2}\PY{p}{,} \PY{n}{m2}\PY{p}{,} \PY{n}{n3}\PY{p}{,} \PY{n}{m3}\PY{p}{]}\PY{p}{)}
-
-         \PY{n}{images} \PY{o}{=} \PY{p}{[}\PY{n}{mit}\PY{p}{,} \PY{n+nb}{all}\PY{p}{,} \PY{n}{rl}\PY{p}{,} \PY{n}{call4}\PY{p}{]}
-         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}
+{\color{incolor}In [{\color{incolor}8}]:} \PY{n}{images} \PY{o}{=} \PY{p}{[} \PY{n}{D1\PYZus{}os}\PY{p}{,} \PY{n}{a}\PY{p}{,} \PY{p}{(}\PY{n}{a}\PY{o}{\PYZhy{}}\PY{n}{b}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{n}{D2\PYZus{}os}\PY{p}{,}  \PY{n}{b}\PY{p}{,} \PY{n}{a} \PY{o}{*} \PY{n}{b} \PY{p}{]}
+        \PY{n}{titles} \PY{o}{=} \PY{p}{[}\PY{n}{D1}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Thresholded }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s1}{\PYZsq{}}\PY{o}{\PYZpc{}}\PY{k}{D1}, \PYZsq{}Difference\PYZsq{}, D2, \PYZsq{}Thresholded \PYZpc{}s\PYZsq{}\PYZpc{}D2, \PYZsq{}Similarity\PYZsq{}]
+        \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{titles}\PY{o}{=}\PY{n}{titles}\PY{p}{)}
 \end{Verbatim}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-Number of columnts: 2
+Number of rows and columns: 2, 3
+(6, 6)
 
@@
 
-    \begin{verbatim}
-<matplotlib.figure.Figure at 0x7f65c3721610>
-    \end{verbatim}
-
     \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_4_2.png}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_10_1.png}
     \end{center}
     { \hspace*{\fill} \\}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}20}]:} \PY{n}{mit} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{mit}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
-         \PY{n+nb}{all} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
-         \PY{n}{rl} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{rl}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
-         \PY{n}{call4} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{n}{scn}\PY{p}{(}\PY{n}{call4}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{1}\PY{p}{)}
-\end{Verbatim}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}21}]:} \PY{n}{images} \PY{o}{=} \PY{p}{[} 
-                 \PY{n}{mit}\PY{p}{,} \PY{n+nb}{all}\PY{p}{,} \PY{n}{rl}\PY{p}{,} \PY{n}{call4}
-                 \PY{p}{,} \PY{p}{(}\PY{n}{mit} \PY{o}{==} \PY{n+nb}{all}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{mit} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n+nb}{all} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{p}{,} \PY{n+nb}{all} \PY{o}{!=} \PY{n}{mit}
-                 \PY{p}{,} \PY{p}{(}\PY{n}{mit} \PY{o}{==} \PY{n}{rl}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{mit} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{rl} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{p}{,} \PY{n}{rl} \PY{o}{!=} \PY{n}{mit}
-                 \PY{p}{,} \PY{p}{(}\PY{n}{mit} \PY{o}{==} \PY{n}{call4}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{mit} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{call4} \PY{o}{!=} \PY{l+m+mi}{0}\PY{p}{)} \PY{p}{,} \PY{n}{call4} \PY{o}{!=} \PY{n}{mit}
-                  \PY{p}{]} 
-         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{5}\PY{p}{)}
-\end{Verbatim}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-Number of columnts: 2
-
-    \end{Verbatim}
-
-    \begin{verbatim}
-<matplotlib.figure.Figure at 0x7f65c3718390>
-    \end{verbatim}
-
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_6_2.png}
-    \end{center}
-    { \hspace*{\fill} \\}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}22}]:} \PY{n+nb}{min}\PY{p}{,} \PY{n+nb}{max}\PY{p}{,} \PY{n}{mean\PYZus{}mit}\PY{p}{,} \PY{n}{std\PYZus{}mit} \PY{o}{=} \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{mit}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mit}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-         \PY{n+nb}{min}\PY{p}{,} \PY{n+nb}{max}\PY{p}{,} \PY{n}{mean\PYZus{}rl}\PY{p}{,} \PY{n}{std\PYZus{}rl} \PY{o}{=} \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{rl}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{rl}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-         \PY{n+nb}{min}\PY{p}{,} \PY{n+nb}{max}\PY{p}{,} \PY{n}{mean\PYZus{}call4}\PY{p}{,} \PY{n}{std\PYZus{}call4} \PY{o}{=} \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n}{call4}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{call4}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-         \PY{n+nb}{min}\PY{p}{,} \PY{n+nb}{max}\PY{p}{,} \PY{n}{mean\PYZus{}all}\PY{p}{,} \PY{n}{std\PYZus{}all} \PY{o}{=} \PY{n}{print\PYZus{}statistics}\PY{p}{(}\PY{n+nb}{all}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{all}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\end{Verbatim}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-\#-----------------------------------------------------------------------\#
-Stats for mit: 
-max: 1.000000 | min: 0.000000 | median: 0.000000 | mean: 0.188247 | std: 0.390909
-\#-----------------------------------------------------------------------\#
-\#-----------------------------------------------------------------------\#
-Stats for rl: 
-max: 1.000000 | min: 0.000000 | median: 0.000000 | mean: 0.153229 | std: 0.360208
-\#-----------------------------------------------------------------------\#
-\#-----------------------------------------------------------------------\#
-Stats for call4: 
-max: 1.000000 | min: 0.000000 | median: 0.000000 | mean: 0.158854 | std: 0.365540
-\#-----------------------------------------------------------------------\#
-\#-----------------------------------------------------------------------\#
-Stats for all: 
-max: 1.000000 | min: 0.000000 | median: 0.000000 | mean: 0.159688 | std: 0.366316
-\#-----------------------------------------------------------------------\#
-
-    \end{Verbatim}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}23}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
-         \PY{n}{images} \PY{o}{=} \PY{p}{[}
-                 \PY{p}{(}\PY{n}{mit}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1e\PYZhy{}2}
-                 \PY{p}{,} \PY{p}{(}\PY{n+nb}{all}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1e\PYZhy{}2}
-                 \PY{p}{,} \PY{p}{(}\PY{n}{rl}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1e\PYZhy{}2}
-                 \PY{p}{,} \PY{p}{(}\PY{n}{call4}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mf}{1e\PYZhy{}2}
-                 \PY{p}{]}
-         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
-\end{Verbatim}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-Number of columnts: 4
-
-    \end{Verbatim}
-
-    \begin{verbatim}
-<matplotlib.figure.Figure at 0x7f65c3752790>
-    \end{verbatim}
-
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_8_2.png}
-    \end{center}
-    { \hspace*{\fill} \\}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}24}]:} \PY{n}{images} \PY{o}{=} \PY{p}{[}
-                 \PY{n}{log}\PY{p}{(}\PY{n}{call4}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}
-                 \PY{p}{,} \PY{n}{log}\PY{p}{(}\PY{n}{mit}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}
-                 \PY{p}{,} \PY{n}{log}\PY{p}{(}\PY{n}{rl}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}
-                 \PY{p}{,} \PY{n}{log}\PY{p}{(}\PY{n+nb}{all}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}
-                 \PY{p}{]}
-         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
-\end{Verbatim}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-Number of columnts: 4
-
-    \end{Verbatim}
-
-    \begin{verbatim}
-<matplotlib.figure.Figure at 0x7f65c37400d0>
-    \end{verbatim}
-
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_9_2.png}
-    \end{center}
-    { \hspace*{\fill} \\}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}10}]:} \PY{n}{convertBinaryMatToOrcaReadable}\PY{p}{(}\PY{n}{call4} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}call4.edges}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{)}
-         \PY{n}{convertBinaryMatToOrcaReadable}\PY{p}{(}\PY{n}{mit} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}mit.edges}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{)}
-         \PY{n}{convertBinaryMatToOrcaReadable}\PY{p}{(}\PY{n}{rl} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}rl.edges}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{)}
-         \PY{n}{convertBinaryMatToOrcaReadable}\PY{p}{(}\PY{n+nb}{all} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{data/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}all.edges}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{)}
-\end{Verbatim}
 

### 2018-07-11 papers/manuscripts/supplementary/02_from_graphlets_to_analysis.tex
mardas

% Default to the notebook output style

% Inherit from the specified cell style.

\documentclass[11pt]{article}

    \usepackage[T1]{fontenc}
    % Nicer default font (+ math font) than Computer Modern for most use cases
    \usepackage{mathpazo}

    % Basic figure setup, for now with no caption control since it's done
    % automatically by Pandoc (which extracts ![](path) syntax from Markdown).
    \usepackage{graphicx}
    % We will generate all images so they have a width \maxwidth. This means
    % that they will get their normal width if they fit onto the page, but
    % are scaled down if they would overflow the margins.
    \makeatletter
    \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
    \else\Gin@nat@width\fi}
    \makeatother
    \let\Oldincludegraphics\includegraphics
    % Set max figure width to be 80% of text width, for now hardcoded.
    \renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=.8\maxwidth]{#1}}
    % Ensure that by default, figures have no caption (until we provide a
    % proper Figure object with a Caption API and a way to capture that
    % in the conversion process - todo).
    \usepackage{caption}
    \DeclareCaptionLabelFormat{nolabel}{}
    \captionsetup{labelformat=nolabel}

    \usepackage{adjustbox} % Used to constrain images to a maximum size 
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage[utf8x]{inputenc} % Allow utf-8 characters in the tex document
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range 
    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines

    % Colors for the hyperref package
    \definecolor{urlcolor}{rgb}{0,.145,.698}
    \definecolor{linkcolor}{rgb}{.71,0.21,0.01}
    \definecolor{citecolor}{rgb}{.12,.54,.11}

    % ANSI colors
    \definecolor{ansi-black}{HTML}{3E424D}
    \definecolor{ansi-black-intense}{HTML}{282C36}
    \definecolor{ansi-red}{HTML}{E75C58}
    \definecolor{ansi-red-intense}{HTML}{B22B31}
    \definecolor{ansi-green}{HTML}{00A250}
    \definecolor{ansi-green-intense}{HTML}{007427}
    \definecolor{ansi-yellow}{HTML}{DDB62B}
    \definecolor{ansi-yellow-intense}{HTML}{B27D12}
    \definecolor{ansi-blue}{HTML}{208FFB}
    \definecolor{ansi-blue-intense}{HTML}{0065CA}
    \definecolor{ansi-magenta}{HTML}{D160C4}
    \definecolor{ansi-magenta-intense}{HTML}{A03196}
    \definecolor{ansi-cyan}{HTML}{60C6C8}
    \definecolor{ansi-cyan-intense}{HTML}{258F8F}
    \definecolor{ansi-white}{HTML}{C5C1B4}
    \definecolor{ansi-white-intense}{HTML}{A1A6B2}

    % commands and environments needed by pandoc snippets
    % extracted from the output of `pandoc -s`
    \providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
    % Add ',fontsize=\small' for more characters per line
    \newenvironment{Shaded}{}{}
    \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
    \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
    \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
    \newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
    \newcommand{\RegionMarkerTok}[1]{{#1}}
    \newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\NormalTok}[1]{{#1}}

    % Additional commands for more recent versions of Pandoc
    \newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{{#1}}}
    \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{{#1}}}
    \newcommand{\ImportTok}[1]{{#1}}
    \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{{#1}}}}
    \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{{#1}}}
    \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{{#1}}}
    \newcommand{\BuiltInTok}[1]{{#1}}
    \newcommand{\ExtensionTok}[1]{{#1}}
    \newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{{#1}}}
    \newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{{#1}}}
    \newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{02\_from\_graphlets\_to\_analysis}

    % Pygments definitions

\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@dl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@ch\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@fm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@cpf\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sa\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

    % Exact colors from NB
    \definecolor{incolor}{rgb}{0.0, 0.0, 0.5}
    \definecolor{outcolor}{rgb}{0.545, 0.0, 0.0}

    % Prevent overflowing lines due to hard-to-break entities
    \sloppy 
    % Setup hyperref package
    \hypersetup{
      breaklinks=true,  % so long urls are correctly broken across lines
      colorlinks=true,
      urlcolor=urlcolor,
      linkcolor=linkcolor,
      citecolor=citecolor,
      }
    % Slightly bigger margins than the latex defaults

    \geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

    \begin{document}

    \maketitle

    \section{Local Thresholding}\label{local-thresholding}

Here, We extract orbits for a signle chromosome in all 4 cell
lines, using a different method of thresholding. In order to do this, we
slide a kernel of size k through each pixel and check if it has a
particular property. If the property is satisified, then the pixel is
set to 1, otherwise it is set to 0. The two properties that I experiment
with are \emph{maximum thresholding} and \emph{normal thresholding}. 1.
\textbf{Maximum Thresholding}: in max thresholding, if the pixel is the
maximum of its neighbors with respect to the kernel, then it is set.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  \textbf{Normal Thresholding}: in normal thresholding, if the pixel is
  larger that the average of the neighbors then it is set.
\end{enumerate}

    \section{Loading Data}\label{loading-data}

The first step is to load the raw Hi-C contact maps. We have already
extracted all inter- and intra-chromosomal contact maps and compiled
them into as single large numpy array format.

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_3_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \section{Selecting a inter-/intra-chromosomal contact
map}\label{selecting-a-inter-intra-chromosomal-contact-map}

You can chang chr1 and chr2 variables based on the contact map you want
to investigate.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}3}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{1}
        \PY{n}{chr2} \PY{o}{=} \PY{l+m+mi}{2}
        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}          \PY{o}{=} \PY{n}{get\PYZus{}contact\PYZus{}map}\PY{p}{(}\PY{n}{mit\PYZus{}full}        \PY{p}{,} \PY{n}{lengths\PYZus{}low\PYZus{}res}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}          \PY{o}{=} \PY{n}{get\PYZus{}contact\PYZus{}map}\PY{p}{(}\PY{n}{all\PYZus{}full}        \PY{p}{,} \PY{n}{lengths\PYZus{}low\PYZus{}res}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}           \PY{o}{=} \PY{n}{get\PYZus{}contact\PYZus{}map}\PY{p}{(}\PY{n}{rl\PYZus{}full}         \PY{p}{,} \PY{n}{lengths\PYZus{}low\PYZus{}res}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}        \PY{o}{=} \PY{n}{get\PYZus{}contact\PYZus{}map}\PY{p}{(}\PY{n}{call4\PYZus{}full}      \PY{p}{,} \PY{n}{lengths\PYZus{}low\PYZus{}res}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
        \PY{n}{showImages}\PY{p}{(}\PY{n}{data}\PY{p}{,} \PY{n}{rows} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{titles}\PY{o}{=}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Number of rows and columns: 2, 2
(4, 4)

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_5_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \subsection{Cleaning Data}\label{cleaning-data}

As can be observed above, there are several rows and columns that simply
don't contain any data and are all zeros, in the following code we clean
the matrices to remove these zero rows and columns since they will cause
problems in future analysis.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}4}]:} \PY{c+c1}{\PYZsh{}There are some blank rows and columns in the matrix. let\PYZsq{}s remove them.}
        \PY{n}{blankRows0}\PY{p}{,} \PY{n}{blankCols0} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
        \PY{n}{blankRows1}\PY{p}{,} \PY{n}{blankCols1} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
        \PY{n}{blankRows2}\PY{p}{,} \PY{n}{blankCols2} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
        \PY{n}{blankRows3}\PY{p}{,} \PY{n}{blankCols3} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
        \PY{n}{blankRows} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
        \PY{n}{blankCols} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows0}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows1}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows2}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows3}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols0}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols1}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols2}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols3}\PY{p}{)}
        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
        \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{shape}
        \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{shape}
        \PY{n}{n3}\PY{p}{,} \PY{n}{m3} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{shape}
        \PY{n}{n4}\PY{p}{,} \PY{n}{m4} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{shape}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
('size of old matrix:', (495, 486))
('size of new matrix:', (454, 479))
('size of old matrix:', (495, 486))
('size of new matrix:', (454, 479))
('size of old matrix:', (495, 486))
('size of new matrix:', (454, 479))
('size of old matrix:', (495, 486))
('size of new matrix:', (454, 479))

    \end{Verbatim}

    \subsubsection{Comparing CALL4 with RL low-resolution
data:}\label{comparing-call4-with-rl-low-resolution-data}

Feel free to change D1 and D2 to pick any data from set of ```{[}'MIT',
'ALL', 'RL', 'CALL4'{]}````.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}6}]:} \PY{n}{D1} \PY{o}{=} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}
        \PY{n}{D2} \PY{o}{=} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}
        \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{20}\PY{p}{)}
        \PY{c+c1}{\PYZsh{} Size of the kernel}
        \PY{n}{k} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}
        \PY{c+c1}{\PYZsh{} can be either \PYZsq{}max\PYZsq{} for setting the maximum value in each kernel to 1 and the rest to 0}
        \PY{c+c1}{\PYZsh{} or \PYZsq{}normal\PYZsq{} for setting all values above mean + t * std withing the kernel to 1 and }
        \PY{c+c1}{\PYZsh{} the rest to 0}
        \PY{n}{method} \PY{o}{=} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal}\PY{l+s+s1}{\PYZsq{}}
        \PY{c+c1}{\PYZsh{} in case of normal thresholding, t is the coefficient }
        \PY{c+c1}{\PYZsh{} of the standard deviation; that is, n each kernel iteration K}
        \PY{c+c1}{\PYZsh{} if K[i, j] \PYZgt{} mean(K) + t * std(K), then it is set to 1.}
        \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{0}
        \PY{n}{params} \PY{o}{=} \PY{n+nb+bp}{None}
        \PY{n}{symmetric}\PY{o}{=} \PY{n}{chr1}\PY{o}{==}\PY{n}{chr2}
        \PY{n}{D1\PYZus{}os} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{n}{D1}\PY{p}{]}\PY{o}{+}\PY{l+m+mi}{1}\PY{o}{+}\PY{l+m+mf}{1e\PYZhy{}5}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{n}{method}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{n}{t}\PY{p}{,} \PY{n}{params}\PY{o}{=}\PY{n}{params}\PY{p}{,} \PY{n}{symmetric}\PY{o}{=}\PY{n}{symmetric}\PY{p}{)}
        \PY{n}{D2\PYZus{}os} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{n}{D2}\PY{p}{]}\PY{o}{+}\PY{l+m+mi}{1}\PY{o}{+}\PY{l+m+mf}{1e\PYZhy{}5}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{n}{method}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{n}{t}\PY{p}{,} \PY{n}{params}\PY{o}{=}\PY{n}{params}\PY{p}{,} \PY{n}{symmetric}\PY{o}{=}\PY{n}{symmetric}\PY{p}{)}
        \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{D1\PYZus{}os}\PY{o}{.}\PY{n}{shape}
        \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{D2\PYZus{}os}\PY{o}{.}\PY{n}{shape}
        \PY{n}{n} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{n1}\PY{p}{,} \PY{n}{n2}\PY{p}{]}\PY{p}{)}
        \PY{n}{m} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{m1}\PY{p}{,} \PY{n}{m2}\PY{p}{]}\PY{p}{)}
        \PY{n}{D1\PYZus{}os} \PY{o}{=} \PY{n}{D1\PYZus{}os}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
        \PY{n}{D1\PYZus{}data} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{n}{D1}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
        \PY{n}{D2\PYZus{}os} \PY{o}{=} \PY{n}{D2\PYZus{}os}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
        \PY{n}{D2\PYZus{}data} \PY{o}{=} \PY{n}{data}\PY{p}{[}\PY{n}{D2}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
        \PY{n}{a} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{n}{D1\PYZus{}os} \PY{o}{*} \PY{n}{D1\PYZus{}data}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{l+m+mi}{1}
        \PY{n}{b} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{n}{D2\PYZus{}os} \PY{o}{*} \PY{n}{D2\PYZus{}data}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{l+m+mi}{1}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
(2, 2, 2, 2)
(2, 2, 2, 2)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}8}]:} \PY{n}{images} \PY{o}{=} \PY{p}{[} \PY{n}{D1\PYZus{}os}\PY{p}{,} \PY{n}{a}\PY{p}{,} \PY{p}{(}\PY{n}{a}\PY{o}{\PYZhy{}}\PY{n}{b}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{n}{D2\PYZus{}os}\PY{p}{,}  \PY{n}{b}\PY{p}{,} \PY{n}{a} \PY{o}{*} \PY{n}{b} \PY{p}{]}
        \PY{n}{titles} \PY{o}{=} \PY{p}{[}\PY{n}{D1}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Thresholded }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s1}{\PYZsq{}}\PY{o}{\PYZpc{}}\PY{k}{D1}, \PYZsq{}Difference\PYZsq{}, D2, \PYZsq{}Thresholded \PYZpc{}s\PYZsq{}\PYZpc{}D2, \PYZsq{}Similarity\PYZsq{}]
        \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{titles}\PY{o}{=}\PY{n}{titles}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Number of rows and columns: 2, 3
(6, 6)

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_10_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    % Add a bibliography block to the postdoc

    \section{Graphlet Correlation
Analysis}\label{graphlet-correlation-analysis}

Remember, in notebook \emph{Thresholding}, I thresholded contact maps
and saved so that orca can read them.

In this notebook, I perform two actions: 1. I apply \texttt{count5}
procedure in orca to extract 73 orbits for each loci in each chromosome.
After this stage, graphlets will be save with \texttt{.graphlets}
extension in the \texttt{./data} folder.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  I then read the graphlets and find both loci-wise distance and
  graphlet-wise correlations between the four cell lines.
\end{enumerate}

By repeating steps 1 and 2 for all 23 chromosomes, I will have pairwise
MIC values for all orbits of all cell lines. I would eventually be able
to have a data array of shape \texttt{A(23\ *\ 73)}, for each pair of
cell lines where \texttt{A{[}i,\ j{]}} denotes the correlation between
the jth orbit in the ith chromosome.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}1}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
        \PY{k+kn}{import} \PY{n+nn}{cv2}
        \PY{k+kn}{from} \PY{n+nn}{library.utility} \PY{k+kn}{import} \PY{o}{*}
        \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n}{normalization}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n+nb}{filter}
        \PY{k+kn}{import} \PY{n+nn}{subprocess}
        \PY{k+kn}{from} \PY{n+nn}{scipy.interpolate} \PY{k+kn}{import} \PY{n}{spline}
        \PY{o}{\PYZpc{}}\PY{k}{load\PYZus{}ext} autoreload
        \PY{o}{\PYZpc{}}\PY{k}{autoreload} 2
        \PY{o}{\PYZpc{}}\PY{k}{pylab} inline
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Populating the interactive namespace from numpy and matplotlib

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/git/watson/virt/local/lib/python2.7/site-packages/IPython/core/magics/pylab.py:161: UserWarning: pylab import has clobbered these variables: ['colors', 'log']
`\%matplotlib` prevents importing * from pylab and numpy
  "\textbackslash{}n`\%matplotlib` prevents importing * from pylab and numpy"

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}2}]:} \PY{n}{chr2count} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{n}{count2chr} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{n}{count} \PY{o}{=} \PY{l+m+mi}{0}
        \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
            \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                \PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]} \PY{o}{=} \PY{n}{count}
                \PY{n}{count2chr}\PY{p}{[}\PY{n}{count}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
                \PY{n}{count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}

        \PY{n}{sameIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
            \PY{n}{sameIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{]}\PY{p}{)}
        \PY{c+c1}{\PYZsh{}print(\PYZdq{}Same indices: \PYZpc{}s\PYZbs{}n\PYZdq{}\PYZpc{}sameIndices)}
        \PY{n}{differentIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
            \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{chr1}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                \PY{n}{differentIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]}\PY{p}{)}
        \PY{c+c1}{\PYZsh{}print(\PYZdq{}Different indices: \PYZpc{}s\PYZdq{}\PYZpc{}differentIndices)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}3}]:} \PY{n}{data\PYZus{}names} \PY{o}{=} \PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{MIT}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ALL}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{RL}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{CALL4}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]}
        \PY{n}{root} \PY{o}{=} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{..}\PY{l+s+s2}{\PYZdq{}}
        \PY{n}{file\PYZus{}dir\PYZus{}template} \PY{o}{=} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{/extracted\PYZus{}all\PYZus{}contact\PYZus{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{root}\PY{p}{,}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
        \PY{n}{file\PYZus{}name\PYZus{}template} \PY{o}{=} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{/all\PYZus{}in\PYZus{}one\PYZus{}500kb.npy}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{file\PYZus{}dir\PYZus{}template}\PY{p}{)}
        \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{File Directory: }\PY{l+s+se}{\PYZbs{}\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+se}{\PYZbs{}\PYZdq{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{k}{file\PYZus{}dir\PYZus{}template})
        \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{File Name Template: }\PY{l+s+se}{\PYZbs{}\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+se}{\PYZbs{}\PYZdq{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{k}{file\PYZus{}name\PYZus{}template})

        \PY{n}{mit\PYZus{}colors} \PY{o}{=} \PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZsh{}0d75f8}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZsh{}42b395}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZsh{}99cc04}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}
        \PY{n}{cancer\PYZus{}colors} \PY{o}{=} \PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZsh{}ab1239}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZsh{}c83cb9}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZsh{}cf524e}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
File Directory: "../extracted\_all\_contact\_\%s"
File Name Template: "../extracted\_all\_contact\_\%s/all\_in\_one\_500kb.npy"

    \end{Verbatim}

    \subsection{Extracting orbits from thresholded
files}\label{extracting-orbits-from-thresholded-files}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}4}]:} \PY{c+c1}{\PYZsh{} Uncommenct the following code to extract graphlets from contact maps}
        \PY{c+c1}{\PYZsh{}for chr1 in range(1, 23):}
        \PY{c+c1}{\PYZsh{}    for chr2 in range(chr1, 23):}
        \PY{c+c1}{\PYZsh{}        command = \PYZsq{}Rscript ../external/rscript\PYZus{}intra.r \PYZpc{}s \PYZpc{}s\PYZsq{}\PYZpc{}(chr1, chr2)}
        \PY{c+c1}{\PYZsh{}        output = subprocess.check\PYZus{}output(command, subprocess.STDOUT, shell=True)}
        \PY{c+c1}{\PYZsh{}        print(output)}
\end{Verbatim}

    \subsection{Reading Already saved
orbits}\label{reading-already-saved-orbits}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}5}]:} \PY{n}{graphlets} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{data\PYZus{}names}\PY{p}{:}
            \PY{n}{graphlets}\PY{p}{[}\PY{n}{cell}\PY{p}{]} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
            \PY{n}{count} \PY{o}{=} \PY{l+m+mi}{0}
            \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                \PY{n}{graphlets}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{]} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
                \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                    \PY{n}{graphlets}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{]}\PY{p}{[}\PY{n}{chr2}\PY{p}{]} \PY{o}{=} \PY{n}{readMat}\PYZbs{}
                    \PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{/data/graphlets/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{root}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{,} \PY{n}{cell}\PY{o}{.}\PY{n}{lower}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)} 
                    \PY{n}{count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
\end{Verbatim}

    \subsection{Putting extracted graphlets in
order}\label{putting-extracted-graphlets-in-order}

The following code block assembles all 23 orbit signature vectors of a
loci into a \(23 \times 73\) matrix.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}6}]:} \PY{n}{lengths} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{k}{for} \PY{n}{key} \PY{o+ow}{in} \PY{n}{data\PYZus{}names}\PY{p}{:}
            \PY{k}{print}\PY{p}{(}\PY{n}{key}\PY{p}{)}
            \PY{n}{lengths}\PY{p}{[}\PY{n}{key}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{load}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../numpy\PYZus{}data/length\PYZus{}low\PYZus{}res.npy}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

        \PY{n}{num\PYZus{}loci} \PY{o}{=} \PY{l+m+mi}{100000}
        \PY{n}{loci\PYZus{}data} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{data\PYZus{}names}\PY{p}{:}
            \PY{n}{loci\PYZus{}data}\PY{p}{[}\PY{n}{cell1}\PY{p}{]} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
            \PY{n}{num\PYZus{}loci} \PY{o}{=} \PY{n+nb}{int}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{np}\PY{o}{.}\PY{n}{sum}\PY{p}{(}\PY{n}{lengths}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{num\PYZus{}loci}\PY{p}{]}\PY{p}{)}\PY{p}{)}
            \PY{k}{print} \PY{n}{num\PYZus{}loci}
            \PY{k}{for} \PY{n}{l} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{num\PYZus{}loci}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{:}
                \PY{n}{loci\PYZus{}data}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{l}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{zeros}\PY{p}{(}\PY{p}{(}\PY{l+m+mi}{24}\PY{p}{,} \PY{l+m+mi}{73}\PY{p}{)}\PY{p}{,} \PY{n}{dtype}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}

        \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{data\PYZus{}names}\PY{p}{:}
            \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                    \PY{n}{l1} \PY{o}{=} \PY{n}{lengths}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{,} \PY{p}{:}\PY{p}{]}
                    \PY{n}{l2} \PY{o}{=} \PY{n}{lengths}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{chr2}\PY{p}{,} \PY{p}{:}\PY{p}{]}
                    \PY{n}{temp} \PY{o}{=} \PY{n}{graphlets}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{]}\PY{p}{[}\PY{n}{chr2}\PY{p}{]}
                    \PY{k}{if} \PY{n}{chr1} \PY{o}{==} \PY{n}{chr2}\PY{p}{:}
                        \PY{k}{for} \PY{n}{l} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{temp}\PY{p}{)}\PY{p}{)}\PY{p}{:}
                            \PY{n}{loci\PYZus{}abs\PYZus{}num} \PY{o}{=} \PY{n}{l1}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]} \PY{o}{+} \PY{n}{l}
                            \PY{n}{loci\PYZus{}data}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{loci\PYZus{}abs\PYZus{}num}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{]} \PY{o}{=} \PY{n}{temp}\PY{p}{[}\PY{n}{l}\PY{p}{]}                
                    \PY{k}{else}\PY{p}{:}
                        \PY{k}{for} \PY{n}{l} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{l1}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}\PY{p}{:}
                            \PY{n}{loci\PYZus{}abs\PYZus{}num} \PY{o}{=} \PY{n}{l1}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]} \PY{o}{+} \PY{n}{l}
                            \PY{n}{loci\PYZus{}data}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{loci\PYZus{}abs\PYZus{}num}\PY{p}{]}\PY{p}{[}\PY{n}{chr2}\PY{p}{]} \PY{o}{=} \PY{n}{temp}\PY{p}{[}\PY{n}{l}\PY{p}{]}                
                        \PY{k}{for} \PY{n}{l} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{l1}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{,} \PY{n+nb}{len}\PY{p}{(}\PY{n}{temp}\PY{p}{)}\PY{p}{)}\PY{p}{:}
                            \PY{n}{loci\PYZus{}abs\PYZus{}num} \PY{o}{=} \PY{n}{l2}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]} \PY{o}{+} \PY{n}{l} \PY{o}{\PYZhy{}} \PY{n}{l1}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}
                            \PY{n}{loci\PYZus{}data}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{loci\PYZus{}abs\PYZus{}num}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{]} \PY{o}{=} \PY{n}{temp}\PY{p}{[}\PY{n}{l}\PY{p}{]}

\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
MIT
ALL
RL
CALL4
6053
6053
6053
6053

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}7}]:} \PY{c+c1}{\PYZsh{} Test of the above procedure, the absolute difference should be 0}
        \PY{n}{sum\PYZus{}diffs} \PY{o}{=} \PY{l+m+mi}{0}
        \PY{k}{for} \PY{n}{cell\PYZus{}index} \PY{o+ow}{in} \PY{n}{np}\PY{o}{.}\PY{n}{random}\PY{o}{.}\PY{n}{randint}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{n+nb}{len}\PY{p}{(}\PY{n}{data\PYZus{}names}\PY{p}{)}\PY{p}{,} \PY{n}{size}\PY{o}{=}\PY{l+m+mi}{3}\PY{p}{)}\PY{p}{:}
            \PY{n}{cell} \PY{o}{=} \PY{n}{data\PYZus{}names}\PY{p}{[}\PY{n}{cell\PYZus{}index}\PY{p}{]}
            \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n}{np}\PY{o}{.}\PY{n}{random}\PY{o}{.}\PY{n}{choice}\PY{p}{(}\PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{,} \PY{n}{size}\PY{o}{=}\PY{l+m+mi}{3}\PY{p}{)}\PY{p}{:}
                \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n}{np}\PY{o}{.}\PY{n}{random}\PY{o}{.}\PY{n}{choice}\PY{p}{(}\PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{,} \PY{n}{size}\PY{o}{=}\PY{l+m+mi}{3}\PY{p}{)}\PY{p}{:}
                    \PY{n}{i} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{argmin}\PY{p}{(}\PY{p}{[}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{]}\PY{p}{)}
                    \PY{k}{if} \PY{n}{i} \PY{o}{==} \PY{l+m+mi}{1}\PY{p}{:}
                        \PY{n}{c1} \PY{o}{=} \PY{n}{chr2}
                        \PY{n}{c2} \PY{o}{=} \PY{n}{chr1}
                    \PY{k}{else}\PY{p}{:}
                        \PY{n}{c1} \PY{o}{=} \PY{n}{chr1}
                        \PY{n}{c2} \PY{o}{=} \PY{n}{chr2}
                    \PY{k}{for} \PY{n}{loci} \PY{o+ow}{in} \PY{n}{np}\PY{o}{.}\PY{n}{random}\PY{o}{.}\PY{n}{choice}\PY{p}{(}\PY{n+nb}{range}\PY{p}{(}\PY{n}{lengths}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{n}{c1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{size}\PY{o}{=}\PY{l+m+mi}{3}\PY{p}{)}\PY{p}{:}
                        \PY{n}{sum\PYZus{}diffs} \PY{o}{+}\PY{o}{=} \PY{n+nb}{int}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{sum}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{abs}\PY{p}{(}\PY{n}{loci\PYZus{}data}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{n}{loci} \PY{o}{+} \PY{n}{lengths}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{n}{c1}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{]}\PY{p}{]}\PY{p}{[}\PY{n}{c2}\PY{p}{]} \PY{o}{\PYZhy{}} \PY{n}{graphlets}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{n}{c1}\PY{p}{]}\PY{p}{[}\PY{n}{c2}\PY{p}{]}\PY{p}{[}\PY{n}{loci}\PY{p}{]}\PY{p}{)}\PY{p}{)}\PY{p}{)}
        \PY{k}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Absolute Diference: }\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{sum\PYZus{}diffs}\PY{p}{)}\PY{p}{)}
        \PY{k}{print} \PY{n+nb}{len}\PY{p}{(}\PY{n}{loci\PYZus{}data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Absolute Diference: 0
6054

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}8}]:} \PY{c+c1}{\PYZsh{}\PYZsh{} Saving files}
        \PY{c+c1}{\PYZsh{}for cell in data\PYZus{}names:}
        \PY{c+c1}{\PYZsh{}    for loci in range(num\PYZus{}loci):}
        \PY{c+c1}{\PYZsh{}            file\PYZus{}name = \PYZdq{}data/\PYZpc{}s\PYZus{}loci\PYZpc{}d\PYZdq{}\PYZpc{}(cell, loci)}
        \PY{c+c1}{\PYZsh{}            print(file\PYZus{}name)}
        \PY{c+c1}{\PYZsh{}            np.save(file\PYZus{}name, loci\PYZus{}data[cell][loci])}
\end{Verbatim}

    \subsection{Calculating Loci-wise
distances:}\label{calculating-loci-wise-distances}

Now we can compare contact maps with each other based on the
\emph{signature distance} measure. For each contact map and each pair of
cells, we can perform a t-test on the signature distances in order to
see whether the differences are 0 or not. In the following code blocks,
first we calculate the signature distances between each pair of cells
and then some visualizaitons demonstrate how cells are different.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}9}]:} \PY{n}{chr2count} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{n}{count2chr} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{n}{count} \PY{o}{=} \PY{l+m+mi}{0}
        \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
            \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                \PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]} \PY{o}{=} \PY{n}{count}
                \PY{n}{count2chr}\PY{p}{[}\PY{n}{count}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
                \PY{n}{count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}

        \PY{n}{cells} \PY{o}{=} \PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{all}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{rl}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{call4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}
        \PY{n}{graphlets} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
            \PY{n}{graphlets}\PY{p}{[}\PY{n}{cell}\PY{p}{]} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
            \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                \PY{n}{graphlets}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{]} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
                \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                    \PY{n}{graphlets}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{]}\PY{p}{[}\PY{n}{chr2}\PY{p}{]} \PY{o}{=} \PY{n}{readMat}\PYZbs{}
                    \PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{/data/graphlets/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{.graphlets}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PYZbs{}
                     \PY{p}{(}\PY{n}{root}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{,} \PY{n}{cell}\PY{p}{)}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}

        \PY{n}{distances} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{n}{actual\PYZus{}distances} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
            \PY{n}{distances}\PY{p}{[}\PY{n}{cell}\PY{p}{]} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
            \PY{n}{actual\PYZus{}distances}\PY{p}{[}\PY{n}{cell}\PY{p}{]} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}

        \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
            \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
                \PY{k}{if} \PY{n}{cell2} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{n}{cell1}\PY{p}{:}
                    \PY{k}{continue}
                \PY{n}{distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{zeros}\PY{p}{(}\PY{p}{(}\PY{n}{count}\PY{p}{,} \PY{l+m+mi}{4}\PY{p}{)}\PY{p}{)}
                \PY{n}{distances}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{n}{cell1}\PY{p}{]} \PY{o}{=} \PY{n}{distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}
                \PY{n}{actual\PYZus{}distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]} \PY{o}{=} \PY{p}{[}\PY{n+nb+bp}{None}\PY{p}{]} \PY{o}{*} \PY{p}{(}\PY{n}{count}\PY{p}{)}
                \PY{n}{actual\PYZus{}distances}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{n}{cell1}\PY{p}{]} \PY{o}{=} \PY{n}{actual\PYZus{}distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}
                \PY{c+c1}{\PYZsh{}cell (i, j) will store correlation between orbital j in }
                \PY{c+c1}{\PYZsh{}ith chromosome}

        \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
            \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
                \PY{k}{if} \PY{n}{cell2} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{n}{cell1}\PY{p}{:}
                    \PY{k}{continue}
                \PY{k}{print}\PY{p}{(}\PY{n}{cell1}\PY{p}{,} \PY{n}{cell2}\PY{p}{)}
                \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                    \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                        \PY{n}{count} \PY{o}{=} \PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]}
                        \PY{n}{temp} \PY{o}{=}  \PY{n}{row\PYZus{}wise\PYZus{}graphlet\PYZus{}distance}\PY{p}{(}\PY{n}{graphlets}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{]}\PY{p}{[}\PY{n}{chr2}\PY{p}{]}\PYZbs{}
                                        \PY{p}{,} \PY{n}{graphlets}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{]}\PY{p}{[}\PY{n}{chr2}\PY{p}{]}\PY{p}{)}
                        \PY{n}{actual\PYZus{}distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{n}{count}\PY{p}{]} \PY{o}{=} \PY{n}{temp}
                        \PY{n}{distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{n}{count}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{nanmean}\PY{p}{(}\PY{n}{temp}\PY{p}{)}
                        \PY{n}{distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{n}{count}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{nanstd}\PY{p}{(}\PY{n}{temp}\PY{p}{,} \PY{n}{ddof}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
                        \PY{n}{t0}\PY{p}{,} \PY{n}{pvalue} \PY{o}{=} \PY{n}{t\PYZus{}test}\PY{p}{(}\PY{n}{temp}\PY{p}{,} \PY{n}{one\PYZus{}sided}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
                        \PY{n}{distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{n}{count}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{]} \PY{o}{=} \PY{n}{t0}
                        \PY{n}{distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{n}{count}\PY{p}{,} \PY{l+m+mi}{3}\PY{p}{]} \PY{o}{=} \PY{n}{pvalue}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
('mit', 'rl')
('all', 'mit')
('all', 'rl')
('all', 'call4')
('call4', 'mit')
('call4', 'rl')

    \end{Verbatim}

    \subsubsection{All pair-wise signature
distances}\label{all-pair-wise-signature-distances}

The following is a graph comparing contact maps in terms of average
loci-loci distances. For each pair of cells \(A\) and \(B\),
\(\bar{d}^{\hspace{.2cm}A,B}_{ij}\) is calculated. As can be seen in the
third graph, which also shows errors of half standard deviation, we can
see that almost none of the graphlet distances are not within half a
standard deviation of zero.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}10}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{200}\PY{p}{,} \PY{l+m+mi}{90}\PY{p}{)}
         \PY{n}{myIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{14}
         \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{k}{if} \PY{n}{chr1} \PY{o}{\PYZlt{}} \PY{n}{chr2}\PY{p}{:}
                 \PY{n}{myIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]}\PY{p}{)}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{myIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr2}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{]}\PY{p}{)}
         \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{25}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
         \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{n}{x} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{distances}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{rl}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}\PY{p}{)}
         \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{distances}\PY{p}{:}
             \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{:}
                 \PY{k}{if} \PY{n}{cell1} \PY{o}{\PYZgt{}}\PY{o}{=} \PY{n}{cell2}\PY{p}{:}
                     \PY{k}{continue}
                 \PY{n}{y} \PY{o}{=} \PY{n}{distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{n}{myIndices}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{]}
                 \PY{n}{x} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{arange}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{y}\PY{p}{)}\PY{p}{)}\PY{o}{+}\PY{l+m+mi}{1}
                 \PY{n}{xnew} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{n}{x}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{n}{x}\PY{o}{.}\PY{n}{max}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{l+m+mi}{500}\PY{p}{)} \PY{c+c1}{\PYZsh{}300 represents number of points to make between T.min and T.max}
                 \PY{n}{y\PYZus{}smooth} \PY{o}{=} \PY{n}{spline}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,}\PY{n}{xnew}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{scatter}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{)}
                 \PY{k}{if} \PY{n}{cell1} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}} \PY{o+ow}{or} \PY{n}{cell2} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}
                     \PY{n}{color} \PY{o}{=} \PY{n}{mit\PYZus{}colors}\PY{p}{[}\PY{n}{mit\PYZus{}count}\PY{p}{]}
                     \PY{n}{mit\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
                 \PY{k}{else}\PY{p}{:}
                     \PY{n}{color} \PY{o}{=} \PY{n}{cancer\PYZus{}colors}\PY{p}{[}\PY{n}{cancer\PYZus{}count}\PY{p}{]}        
                     \PY{n}{cancer\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{xnew}\PY{p}{,} \PY{n}{y\PYZus{}smooth}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{ vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{cell1}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{cell2}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PYZbs{}
                         \PY{p}{,} \PY{n}{linewidth}\PY{o}{=}\PY{l+m+mi}{4}\PY{p}{,}  \PY{n}{alpha}\PY{o}{=}\PY{o}{.}\PY{l+m+mi}{5}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{)}       
                 \PY{c+c1}{\PYZsh{}ax.plot(x, y, marker=\PYZdq{}.\PYZdq{}, label=\PYZdq{}\PYZpc{}s vs \PYZpc{}s\PYZdq{}\PYZpc{}(cell1, cell2))}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylim}\PY{p}{(}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mf}{1.5}\PY{p}{]}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Average loci\PYZhy{}loci distance}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{20}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Contact maps of chromosome }\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s1}{\PYZsq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{20}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xticks}\PY{p}{(}\PY{n}{x}\PY{p}{)}

         \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{prop}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{size}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}\PY{l+m+mi}{15}\PY{p}{\PYZcb{}}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/git/watson/virt/lib/python2.7/site-packages/ipykernel\_launcher.py:20: DeprecationWarning: `spline` is deprecated!
spline is deprecated in scipy 0.19.0, use Bspline class instead.

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \section{MIC Analysis}\label{mic-analysis}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}11}]:} \PY{n}{header} \PY{o}{=} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{MIT,ALL,RL,CALL4}\PY{l+s+s2}{\PYZdq{}}
         \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                 \PY{k}{for} \PY{n}{orbit} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{73}\PY{p}{)}\PY{p}{:}
                     \PY{n}{filename} \PY{o}{=} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{/data/orbits/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}orbit}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{.csv}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{root}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{,} \PY{n}{orbit}\PY{p}{)}
                     \PY{n}{n} \PY{o}{=} \PY{l+m+mi}{100000000}
                     \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{data\PYZus{}names}\PY{p}{:}
                         \PY{n}{cell} \PY{o}{=} \PY{n}{cell}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}
                         \PY{n}{n} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{graphlets}\PY{p}{[}\PY{n}{cell}\PY{o}{.}\PY{n}{lower}\PY{p}{(}\PY{p}{)}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{]}\PY{p}{[}\PY{n}{chr2}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{n}{orbit}\PY{p}{]}\PY{o}{.}\PY{n}{shape}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{,} \PY{n}{n}\PY{p}{]}\PY{p}{)}
                     \PY{n}{temp} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{zeros}\PY{p}{(}\PY{p}{(}\PY{n}{n}\PY{p}{,} \PY{n+nb}{len}\PY{p}{(}\PY{n}{data\PYZus{}names}\PY{p}{)}\PY{p}{)}\PY{p}{)}
                     \PY{n}{count} \PY{o}{=} \PY{l+m+mi}{0}
                     \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{data\PYZus{}names}\PY{p}{:}
                         \PY{n}{temp}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{n}{count}\PY{p}{]} \PY{o}{=} \PY{n}{graphlets}\PY{p}{[}\PY{n}{cell}\PY{o}{.}\PY{n}{lower}\PY{p}{(}\PY{p}{)}\PY{p}{]}\PY{p}{[}\PY{n}{chr1}\PY{p}{]}\PY{p}{[}\PY{n}{chr2}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{n}{orbit}\PY{p}{]}
                         \PY{n}{count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
                     \PY{n}{np}\PY{o}{.}\PY{n}{savetxt}\PY{p}{(}\PY{n}{filename}\PY{p}{,} \PY{n}{temp}\PY{p}{,} \PY{n}{delimiter}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{,}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{header}\PY{o}{=}\PY{n}{header}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}12}]:} \PY{c+c1}{\PYZsh{}for chr1 in range(1, 24):}
         \PY{c+c1}{\PYZsh{}    for chr2 in range(chr1, 24):}
         \PY{c+c1}{\PYZsh{}        for orbit in range(73):}
         \PY{c+c1}{\PYZsh{}            file\PYZus{}name = \PYZdq{}data/chr\PYZpc{}02d\PYZus{}chr\PYZpc{}02d\PYZus{}orbit\PYZpc{}02d.csv\PYZdq{}\PYZpc{}(chr1, chr2, orbit)}
         \PY{c+c1}{\PYZsh{}            command = \PYZdq{}java \PYZhy{}jar mine.jar \PYZpc{}s \PYZhy{}allPairs\PYZdq{}\PYZpc{}file\PYZus{}name}
         \PY{c+c1}{\PYZsh{}            print(command)}
         \PY{c+c1}{\PYZsh{}            os.system(command)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}13}]:} \PY{n}{cells} \PY{o}{=} \PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{all}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{rl}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{call4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}
         \PY{n}{chr2count} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
         \PY{n}{count2chr} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
         \PY{n}{count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                 \PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]} \PY{o}{=} \PY{n}{count}
                 \PY{n}{count2chr}\PY{p}{[}\PY{n}{count}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
                 \PY{n}{count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}

         \PY{n}{mics} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
         \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
             \PY{n}{mics}\PY{p}{[}\PY{n}{cell}\PY{p}{]} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}

         \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
             \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
                 \PY{k}{if} \PY{n}{cell2} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{n}{cell1}\PY{p}{:}
                     \PY{k}{continue}
                 \PY{n}{mics}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{zeros}\PY{p}{(}\PY{p}{(}\PY{n}{count}\PY{p}{,} \PY{l+m+mi}{73}\PY{p}{)}\PY{p}{)}
                 \PY{n}{mics}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{n}{cell1}\PY{p}{]} \PY{o}{=} \PY{n}{mics}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}
                 \PY{c+c1}{\PYZsh{}cell (i, j) will store correlation between orbital j in }
                 \PY{c+c1}{\PYZsh{}ith chromosome}

         \PY{c+c1}{\PYZsh{}for cell1 in cells:}
         \PY{c+c1}{\PYZsh{}    for cell2 in cells:}
         \PY{c+c1}{\PYZsh{}        if cell2 \PYZlt{}= cell1:}
         \PY{c+c1}{\PYZsh{}            continue}
         \PY{c+c1}{\PYZsh{}        print(cell1, cell2)}
         \PY{c+c1}{\PYZsh{}        count = 0 }
         \PY{c+c1}{\PYZsh{}        for chr1 in range(1, 24):}
         \PY{c+c1}{\PYZsh{}            for chr2 in range(chr1, 24):}
         \PY{c+c1}{\PYZsh{}                mics[cell1][cell2][count, :] =  row\PYZus{}wise\PYZus{}pearson(graphlets[cell1][chr1][chr2].T\PYZbs{}}
         \PY{c+c1}{\PYZsh{}                                , graphlets[cell2][chr1][chr2].T)}
         \PY{c+c1}{\PYZsh{}                count+=1}
         \PY{k+kn}{import} \PY{n+nn}{string}
         \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                 \PY{k}{for} \PY{n}{orbit} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{73}\PY{p}{)}\PY{p}{:}
                     \PY{n}{filename} \PY{o}{=} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/mics/chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}chr}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}orbit}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{.csv,allpairs,cv=0.0,B=n\PYZca{}0.6,Results.csv}\PY{l+s+s2}{\PYZdq{}}\PYZbs{}
                     \PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{,} \PY{n}{orbit}\PY{p}{)}
                     \PY{k}{print}\PY{p}{(}\PY{n}{filename}\PY{p}{)}
                     \PY{n}{csvfile} \PY{o}{=} \PY{n+nb}{open}\PY{p}{(}\PY{n}{filename}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
                     \PY{n}{csvfile}\PY{o}{.}\PY{n}{readline}\PY{p}{(}\PY{p}{)}
                     \PY{k}{for} \PY{n}{line} \PY{o+ow}{in} \PY{n}{csvfile}\PY{p}{:}
                         \PY{n}{splitted} \PY{o}{=} \PY{n}{line}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{,}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
                         \PY{n}{a} \PY{o}{=} \PY{n}{string}\PY{o}{.}\PY{n}{replace}\PY{p}{(}\PY{n}{splitted}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZsh{} }\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{lower}\PY{p}{(}\PY{p}{)}
                         \PY{n}{b} \PY{o}{=} \PY{n}{string}\PY{o}{.}\PY{n}{replace}\PY{p}{(}\PY{n}{splitted}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZsh{} }\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{o}{.}\PY{n}{lower}\PY{p}{(}\PY{p}{)}
                         \PY{n}{c} \PY{o}{=} \PY{n+nb}{float}\PY{p}{(}\PY{n}{splitted}\PY{p}{[}\PY{l+m+mi}{2}\PY{p}{]}\PY{p}{)}
                         \PY{c+c1}{\PYZsh{}print(a, b, c)}
                         \PY{n}{mics}\PY{p}{[}\PY{n}{a}\PY{p}{]}\PY{p}{[}\PY{n}{b}\PY{p}{]}\PY{p}{[}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]}\PY{p}{,} \PY{n}{orbit}\PY{p}{]} \PY{o}{=} \PY{n}{c}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}14}]:} \PY{n}{numPairs} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{n}{cellPair2num} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
         \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{mics}\PY{p}{:}
             \PY{n}{cellPair2num}\PY{p}{[}\PY{n}{cell1}\PY{p}{]} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
             \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{mics}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{:}
                 \PY{k}{if} \PY{n}{cell1} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{n}{cell2}\PY{p}{:}
                     \PY{k}{continue}
                 \PY{n}{cellPair2num}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]} \PY{o}{=} \PY{n}{numPairs}
                 \PY{n}{numPairs} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
         \PY{n}{vectorMic} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{zeros}\PY{p}{(}\PY{p}{(}\PY{n}{numPairs}\PY{p}{,} \PY{n}{count}\PY{p}{,} \PY{l+m+mi}{73}\PY{p}{)}\PY{p}{)}
         \PY{k}{print}\PY{p}{(}\PY{n}{vectorMic}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
         \PY{n}{pairCount} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{mics}\PY{p}{:}
             \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{mics}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{:}
                 \PY{k}{if} \PY{n}{cell1} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{n}{cell2}\PY{p}{:}
                     \PY{k}{continue}        
                 \PY{n}{vectorMic}\PY{p}{[}\PY{n}{pairCount}\PY{p}{]} \PY{o}{=} \PY{n}{mics}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}
                 \PY{n}{pairCount} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
         \PY{k}{print}\PY{p}{(}\PY{n}{numPairs}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
(6, 276, 73)
6

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}16}]:} \PY{n}{sameIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{n}{sameIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{]}\PY{p}{)}
         \PY{c+c1}{\PYZsh{}print(\PYZdq{}Same indices: \PYZpc{}s\PYZbs{}n\PYZdq{}\PYZpc{}sameIndices)}
         \PY{n}{differentIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{k}{for} \PY{n}{chr1} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{chr1}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
                 \PY{n}{differentIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]}\PY{p}{)}
         \PY{c+c1}{\PYZsh{}print(\PYZdq{}Different indices: \PYZpc{}s\PYZbs{}n\PYZdq{}\PYZpc{}differentIndices)}

         \PY{n}{indices} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[} \PY{l+m+mi}{0}\PY{p}{,}  \PY{l+m+mi}{1}\PY{p}{,}  \PY{l+m+mi}{2}\PY{p}{,}  \PY{l+m+mi}{4}\PY{p}{,}  \PY{l+m+mi}{5}\PY{p}{,}  \PY{l+m+mi}{6}\PY{p}{,}  \PY{l+m+mi}{7}\PY{p}{,}  \PY{l+m+mi}{8}\PY{p}{,} \PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{16}\PY{p}{,} \PY{l+m+mi}{17}\PY{p}{,} \PY{l+m+mi}{18}\PY{p}{,} \PY{l+m+mi}{19}\PY{p}{,} \PY{l+m+mi}{20}\PY{p}{,} \PY{l+m+mi}{21}\PY{p}{,} \PY{l+m+mi}{22}\PY{p}{,} \PY{l+m+mi}{23}\PY{p}{,}
                 \PY{l+m+mi}{35}\PY{p}{,} \PY{l+m+mi}{36}\PY{p}{,} \PY{l+m+mi}{37}\PY{p}{,} \PY{l+m+mi}{38}\PY{p}{,} \PY{l+m+mi}{49}\PY{p}{,} \PY{l+m+mi}{50}\PY{p}{]}\PY{p}{)} 
         \PY{n}{nonIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{73}\PY{p}{)}\PY{p}{:}
             \PY{k}{if} \PY{n}{i} \PY{o+ow}{not} \PY{o+ow}{in} \PY{n}{indices}\PY{p}{:}
                 \PY{n}{nonIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{i}\PY{p}{)}

         \PY{c+c1}{\PYZsh{}print(\PYZdq{}Indices: \PYZpc{}s\PYZbs{}n\PYZdq{}\PYZpc{}indices)}
         \PY{c+c1}{\PYZsh{}print(\PYZdq{}Non\PYZhy{}indices: \PYZpc{}s\PYZdq{}\PYZpc{}nonIndices)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}17}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{200}\PY{p}{,} \PY{l+m+mi}{90}\PY{p}{)}
         \PY{n}{custIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{14}
         \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{k}{if} \PY{n}{chr1} \PY{o}{\PYZlt{}} \PY{n}{chr2}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]}\PY{p}{)}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr2}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{]}\PY{p}{)}
         \PY{k}{print}\PY{p}{(}\PY{n}{mics}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{rl}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
         \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{25}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
         \PY{n}{x} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{mics}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{rl}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}\PY{p}{)}
         \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{cellPair2num}\PY{p}{:}
             \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{cellPair2num}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{:}
                 \PY{n}{tmp} \PY{o}{=} \PY{n}{vectorMic} \PY{o}{\PYZhy{}} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{vectorMic}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n}{keepdims}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
                 \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{nanmean}\PY{p}{(}\PY{n}{tmp}\PY{p}{[}\PY{n}{cellPair2num}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{p}{:}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{n}{indices}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}

                 \PY{n}{x} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{y}\PY{p}{)}\PY{p}{)}\PY{p}{)} \PY{o}{+} \PY{l+m+mi}{1}
                 \PY{n}{xnew} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{n}{x}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{n}{x}\PY{o}{.}\PY{n}{max}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{l+m+mi}{500}\PY{p}{)} \PY{c+c1}{\PYZsh{}300 represents number of points to make between T.min and T.max}
                 \PY{n}{y\PYZus{}smooth} \PY{o}{=} \PY{n}{spline}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,}\PY{n}{xnew}\PY{p}{)}
                 \PY{k}{if} \PY{n}{cell1} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}} \PY{o+ow}{or} \PY{n}{cell} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}
                     \PY{n}{color} \PY{o}{=} \PY{n}{mit\PYZus{}colors}\PY{p}{[}\PY{n}{mit\PYZus{}count}\PY{p}{]}
                     \PY{n}{mit\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
                 \PY{k}{else}\PY{p}{:}
                     \PY{n}{color} \PY{o}{=} \PY{n}{cancer\PYZus{}colors}\PY{p}{[}\PY{n}{cancer\PYZus{}count}\PY{p}{]}
                     \PY{n}{cancer\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{scatter}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{xnew}\PY{p}{,} \PY{n}{y\PYZus{}smooth}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{ vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{cell1}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{cell}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PYZbs{}
                         \PY{p}{,} \PY{n}{linewidth}\PY{o}{=}\PY{l+m+mi}{4}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{o}{.}\PY{l+m+mi}{5}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylim}\PY{p}{(}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Contact Maps of Chromosome }\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{25}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Average MIC}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{25}\PY{p}{)}
                 \PY{c+c1}{\PYZsh{}ax.set\PYZus{}xticks(x)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{prop}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{size}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}\PY{l+m+mi}{15}\PY{p}{\PYZcb{}}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
(276, 73)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/git/watson/virt/lib/python2.7/site-packages/ipykernel\_launcher.py:21: DeprecationWarning: `spline` is deprecated!
spline is deprecated in scipy 0.19.0, use Bspline class instead.

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_22_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}18}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{200}\PY{p}{,} \PY{l+m+mi}{90}\PY{p}{)}
         \PY{n}{custIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{14}
         \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{k}{if} \PY{n}{chr1} \PY{o}{\PYZlt{}} \PY{n}{chr2}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]}\PY{p}{)}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr2}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{]}\PY{p}{)}
         \PY{k}{print}\PY{p}{(}\PY{n}{mics}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{rl}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
         \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{25}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
         \PY{n}{x} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{mics}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{rl}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}\PY{p}{)}
         \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{cellPair2num}\PY{p}{:}
             \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{cellPair2num}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{:}
                 \PY{n}{tmp} \PY{o}{=} \PY{n}{vectorMic} \PY{o}{\PYZhy{}} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{vectorMic}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}\PY{p}{,} \PY{n}{keepdims}\PY{o}{=}\PY{n+nb+bp}{True}\PY{p}{)}
                 \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{nanmean}\PY{p}{(}\PY{n}{tmp}\PY{p}{[}\PY{n}{cellPair2num}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{p}{:}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{p}{:}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}

                 \PY{n}{x} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{y}\PY{p}{)}\PY{p}{)}\PY{p}{)} \PY{o}{+} \PY{l+m+mi}{1}
                 \PY{n}{xnew} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{n}{x}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{n}{x}\PY{o}{.}\PY{n}{max}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{l+m+mi}{500}\PY{p}{)} \PY{c+c1}{\PYZsh{}300 represents number of points to make between T.min and T.max}
                 \PY{n}{y\PYZus{}smooth} \PY{o}{=} \PY{n}{spline}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,}\PY{n}{xnew}\PY{p}{)}
                 \PY{k}{if} \PY{n}{cell1} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}} \PY{o+ow}{or} \PY{n}{cell} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}
                     \PY{n}{color} \PY{o}{=} \PY{n}{mit\PYZus{}colors}\PY{p}{[}\PY{n}{mit\PYZus{}count}\PY{p}{]}
                     \PY{n}{mit\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
                 \PY{k}{else}\PY{p}{:}
                     \PY{n}{color} \PY{o}{=} \PY{n}{cancer\PYZus{}colors}\PY{p}{[}\PY{n}{cancer\PYZus{}count}\PY{p}{]}
                     \PY{n}{cancer\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{scatter}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{xnew}\PY{p}{,} \PY{n}{y\PYZus{}smooth}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{ vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{cell1}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{cell}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PYZbs{}
                         \PY{p}{,} \PY{n}{linewidth}\PY{o}{=}\PY{l+m+mi}{4}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{o}{.}\PY{l+m+mi}{5}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylim}\PY{p}{(}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Contact Maps of Chromosome }\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{25}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Average MIC}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{25}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xticks}\PY{p}{(}\PY{n}{x}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{prop}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{size}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}\PY{l+m+mi}{15}\PY{p}{\PYZcb{}}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
(276, 73)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/git/watson/virt/lib/python2.7/site-packages/ipykernel\_launcher.py:21: DeprecationWarning: `spline` is deprecated!
spline is deprecated in scipy 0.19.0, use Bspline class instead.

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_23_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}19}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{200}\PY{p}{,} \PY{l+m+mi}{90}\PY{p}{)}
         \PY{n}{custIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{14}
         \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{k}{if} \PY{n}{chr1} \PY{o}{\PYZlt{}} \PY{n}{chr2}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]}\PY{p}{)}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr2}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{]}\PY{p}{)}
         \PY{k}{print}\PY{p}{(}\PY{n}{mics}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{rl}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
         \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{25}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
         \PY{n}{x} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{mics}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{rl}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}\PY{p}{)}
         \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{mics}\PY{p}{:}
             \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{mics}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{:}
                 \PY{k}{if} \PY{n}{cell} \PY{o}{\PYZlt{}} \PY{n}{cell1}\PY{p}{:}
                     \PY{k}{continue}
                 \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{nanmean}\PY{p}{(}\PY{n}{mics}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{n}{custIndices}\PY{p}{,} \PY{p}{:}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{n}{indices}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
                 \PY{n}{x} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{y}\PY{p}{)}\PY{p}{)}\PY{p}{)} \PY{o}{+} \PY{l+m+mi}{1}
                 \PY{n}{xnew} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{n}{x}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{n}{x}\PY{o}{.}\PY{n}{max}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{l+m+mi}{500}\PY{p}{)} \PY{c+c1}{\PYZsh{}300 represents number of points to make between T.min and T.max}
                 \PY{n}{y\PYZus{}smooth} \PY{o}{=} \PY{n}{spline}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,}\PY{n}{xnew}\PY{p}{)}
                 \PY{k}{if} \PY{n}{cell1} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}} \PY{o+ow}{or} \PY{n}{cell} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}
                     \PY{n}{color} \PY{o}{=} \PY{n}{mit\PYZus{}colors}\PY{p}{[}\PY{n}{mit\PYZus{}count}\PY{p}{]}
                     \PY{n}{mit\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
                 \PY{k}{else}\PY{p}{:}
                     \PY{n}{color} \PY{o}{=} \PY{n}{cancer\PYZus{}colors}\PY{p}{[}\PY{n}{cancer\PYZus{}count}\PY{p}{]}
                     \PY{n}{cancer\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{scatter}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{xnew}\PY{p}{,} \PY{n}{y\PYZus{}smooth}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{ vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{cell1}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{cell}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PYZbs{}
                         \PY{p}{,} \PY{n}{linewidth}\PY{o}{=}\PY{l+m+mi}{4}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{o}{.}\PY{l+m+mi}{5}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylim}\PY{p}{(}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Contact Maps of Chromosome }\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{25}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Average MIC}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{25}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xticks}\PY{p}{(}\PY{n}{x}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{prop}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{size}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}\PY{l+m+mi}{15}\PY{p}{\PYZcb{}}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
(276, 73)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/git/watson/virt/lib/python2.7/site-packages/ipykernel\_launcher.py:21: DeprecationWarning: `spline` is deprecated!
spline is deprecated in scipy 0.19.0, use Bspline class instead.

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_24_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}20}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{25}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
         \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{n}{legends} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{chosen\PYZus{}cell} \PY{o+ow}{in} \PY{n}{mics}\PY{p}{:}
             \PY{k}{for} \PY{n}{cell} \PY{o+ow}{in} \PY{n}{mics}\PY{p}{[}\PY{n}{chosen\PYZus{}cell}\PY{p}{]}\PY{p}{:}
                 \PY{k}{if} \PY{n}{cell} \PY{o}{\PYZlt{}} \PY{n}{chosen\PYZus{}cell}\PY{p}{:}
                     \PY{k}{continue}
                 \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{nanmean}\PY{p}{(}\PY{n}{mics}\PY{p}{[}\PY{n}{chosen\PYZus{}cell}\PY{p}{]}\PY{p}{[}\PY{n}{cell}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{indices}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}
                 \PY{n}{x} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{y}\PY{p}{)}\PY{p}{)}\PY{p}{)}
                 \PY{n}{xnew} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{n}{x}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{n}{x}\PY{o}{.}\PY{n}{max}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{l+m+mi}{500}\PY{p}{)} \PY{c+c1}{\PYZsh{}300 represents number of points to make between T.min and T.max}
                 \PY{n}{y\PYZus{}smooth} \PY{o}{=} \PY{n}{spline}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,}\PY{n}{xnew}\PY{p}{)}
                 \PY{k}{if} \PY{n}{chosen\PYZus{}cell} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}} \PY{o+ow}{or} \PY{n}{cell} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}
                     \PY{n}{color} \PY{o}{=} \PY{n}{mit\PYZus{}colors}\PY{p}{[}\PY{n}{mit\PYZus{}count}\PY{p}{]}
                     \PY{n}{mit\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
                 \PY{k}{else}\PY{p}{:}
                     \PY{n}{color} \PY{o}{=} \PY{n}{cancer\PYZus{}colors}\PY{p}{[}\PY{n}{cancer\PYZus{}count}\PY{p}{]}
                     \PY{n}{cancer\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1} 
                 \PY{n}{ax}\PY{o}{.}\PY{n}{scatter}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{)}
                 \PY{n}{tmp}\PY{p}{,} \PY{o}{=} \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{xnew}\PY{p}{,} \PY{n}{y\PYZus{}smooth}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{ vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chosen\PYZus{}cell}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{cell}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PYZbs{}
                                \PY{p}{,} \PY{n}{linewidth}\PY{o}{=}\PY{l+m+mi}{4}\PY{p}{,} \PY{n}{alpha}\PY{o}{=}\PY{o}{.}\PY{l+m+mi}{5}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{)}
                 \PY{c+c1}{\PYZsh{}tmp, = ax.plot(x, y, marker=\PYZdq{}.\PYZdq{}, label=\PYZdq{}\PYZpc{}s vs \PYZpc{}s\PYZdq{}\PYZpc{}(chosen\PYZus{}cell, cell))}
                 \PY{n}{legends}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{tmp}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Orbit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{25}\PY{p}{)}
                 \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIC}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{25}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{handles}\PY{o}{=}\PY{n}{legends}\PY{p}{,} \PY{n}{loc}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{prop}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{size}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}\PY{l+m+mi}{15}\PY{p}{\PYZcb{}}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/git/watson/virt/lib/python2.7/site-packages/ipykernel\_launcher.py:12: DeprecationWarning: `spline` is deprecated!
spline is deprecated in scipy 0.19.0, use Bspline class instead.
  if sys.path[0] == '':

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_25_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \subsection{MIC statsitical analysis}\label{mic-statsitical-analysis}

    \subsubsection{Comparison between contact
maps}\label{comparison-between-contact-maps}

    \subsubsection{Comparison between contact maps only considering non-zero
orbits}\label{comparison-between-contact-maps-only-considering-non-zero-orbits}

    \subsubsection{Comparison between
orbits}\label{comparison-between-orbits}

    \subsubsection{Comparison between orbits only for intra-chromosomal
contact
maps}\label{comparison-between-orbits-only-for-intra-chromosomal-contact-maps}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}21}]:} \PY{n}{numData} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
             \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
                 \PY{k}{if} \PY{n}{cell2} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{n}{cell1}\PY{p}{:}
                     \PY{k}{continue}
                 \PY{n}{datashape} \PY{o}{=} \PY{n}{mics}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{o}{.}\PY{n}{shape}
                 \PY{n}{numData} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
         \PY{n}{axis} \PY{o}{=} \PY{l+m+mi}{1}
         \PY{n}{xIndices} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{276}\PY{p}{)}
         \PY{n}{yIndices} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{73}\PY{p}{)}
         \PY{n}{yIndices} \PY{o}{=} \PY{n}{indices}
         \PY{n}{averages} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{n}{counts} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{n}{data} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
         \PY{n}{count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
             \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
                 \PY{k}{if} \PY{n}{cell2} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{n}{cell1}\PY{p}{:}
                     \PY{k}{continue}        
                 \PY{n}{tag} \PY{o}{=} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{ vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{cell1}\PY{p}{,} \PY{n}{cell2}\PY{p}{)}
                 \PY{n}{tmp} \PY{o}{=} \PY{n}{mics}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{n}{xIndices}\PY{p}{,} \PY{p}{:}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{n}{yIndices}\PY{p}{]}
                 \PY{n}{averages}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{tmp}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{axis}\PY{p}{)}\PY{p}{)}
                 \PY{n}{counts}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{tmp}\PY{o}{.}\PY{n}{shape}\PY{p}{[}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{axis}\PY{p}{]}\PY{p}{)}           
                 \PY{k}{if} \PY{n}{axis} \PY{o}{==} \PY{l+m+mi}{1}\PY{p}{:}
                     \PY{n}{data}\PY{p}{[}\PY{n}{tag}\PY{p}{]} \PY{o}{=} \PY{n}{tmp}
                 \PY{k}{else}\PY{p}{:}
                     \PY{n}{data}\PY{p}{[}\PY{n}{tag}\PY{p}{]} \PY{o}{=} \PY{n}{tmp}\PY{o}{.}\PY{n}{T}
                 \PY{n}{count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
         \PY{n}{averages} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{averages}\PY{p}{)}
         \PY{n}{counts} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{counts}\PY{p}{,} \PY{n}{dtype}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{o}{.}\PY{n}{reshape}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{k}{print}\PY{p}{(}\PY{n}{averages}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
(6, 23)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}22}]:} \PY{k}{print}\PY{p}{(}\PY{n}{data}\PY{o}{.}\PY{n}{keys}\PY{p}{(}\PY{p}{)}\PY{p}{)}
         \PY{n}{manova}\PY{p}{(}\PY{n}{data}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{wilk}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
['all vs rl', 'call4 vs mit', 'mit vs rl', 'all vs call4', 'all vs mit', 'call4 vs rl']
Method Used: WILK
('n: ', 1656.0)
('k: ', 23)
('m: ', 6)
('a: ', 1640.5)
('b\_num', 13221.0)
('b\_denom', 549.0)
('b: ', 4.907338098512752)
('c: ', 56.5)
('gamma: ', 0.5654068065417478)
('s', 5)
('t', 8.5)
('u', 813.0)
('df1', 115)
('df2', 7993.988150610169)
('F', 8.565054626003658)
('alpha:', 0.05)
('F-crit:', 1.2284905642879855)
('p-value:', 1.1711969397971584e-128)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}23}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{25}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
         \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{14}
         \PY{n}{custIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{k}{if} \PY{n}{chr1} \PY{o}{\PYZlt{}} \PY{n}{chr2}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]}\PY{p}{)}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr2}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{]}\PY{p}{)}
         \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{n}{i} \PY{o}{=} \PY{o}{\PYZhy{}}\PY{l+m+mi}{1}
         \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{tag} \PY{o+ow}{in} \PY{n}{data}\PY{p}{:}
             \PY{n}{i} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
             \PY{k}{print}\PY{p}{(}\PY{n}{averages}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
             \PY{n}{means} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{averages}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}
             \PY{n}{y} \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{nanmean}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)} \PY{o}{\PYZhy{}} \PY{n}{means}\PY{p}{)}
             \PY{n}{x} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{y}\PY{p}{)}\PY{p}{)}\PY{p}{)}
             \PY{n}{xnew} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{n}{x}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{n}{x}\PY{o}{.}\PY{n}{max}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{l+m+mi}{500}\PY{p}{)} \PY{c+c1}{\PYZsh{}300 represents number of points to make between T.min and T.max}
             \PY{n}{y\PYZus{}smooth} \PY{o}{=} \PY{n}{spline}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,}\PY{n}{xnew}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{scatter}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{)}
             \PY{k}{if} \PY{n}{tag}\PY{o}{.}\PY{n}{find}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)} \PY{o}{\PYZgt{}}\PY{o}{=} \PY{l+m+mi}{0}\PY{p}{:}
                 \PY{n}{color} \PY{o}{=} \PY{n}{mit\PYZus{}colors}\PY{p}{[}\PY{n}{mit\PYZus{}count}\PY{p}{]}
                 \PY{n}{mit\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{color} \PY{o}{=} \PY{n}{cancer\PYZus{}colors}\PY{p}{[}\PY{n}{cancer\PYZus{}count}\PY{p}{]}        
                 \PY{n}{cancer\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
             \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{xnew}\PY{p}{,} \PY{n}{y\PYZus{}smooth}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{tag}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PYZbs{}
                     \PY{p}{,} \PY{n}{linewidth}\PY{o}{=}\PY{l+m+mi}{4}\PY{p}{,}  \PY{n}{alpha}\PY{o}{=}\PY{o}{.}\PY{l+m+mi}{5}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color}\PY{p}{)}       
             \PY{c+c1}{\PYZsh{}ax.plot(x, y, marker=\PYZdq{}.\PYZdq{}, label=\PYZdq{}\PYZpc{}s vs \PYZpc{}s\PYZdq{}\PYZpc{}(cell1, cell2))}
             \PY{c+c1}{\PYZsh{}ax.set\PYZus{}ylim([\PYZhy{}1.5, 1.5])}
             \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Average loci\PYZhy{}loci distance}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{12}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Contact maps of chromosome }\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s1}{\PYZsq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{12}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Corrected Average MIC}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{20}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Contact maps of chromosome }\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s1}{\PYZsq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{20}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Orbits}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{20}\PY{p}{)}    
             \PY{c+c1}{\PYZsh{}ax.set\PYZus{}xticks(x)}
             \PY{c+c1}{\PYZsh{}ax.set\PYZus{}ylim([\PYZhy{}.2, .2])}

         \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{prop}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{size}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}\PY{l+m+mi}{15}\PY{p}{\PYZcb{}}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
(6, 23)
(6, 23)
(6, 23)
(6, 23)
(6, 23)
(6, 23)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/git/watson/virt/lib/python2.7/site-packages/ipykernel\_launcher.py:20: DeprecationWarning: `spline` is deprecated!
spline is deprecated in scipy 0.19.0, use Bspline class instead.

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_33_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}24}]:} \PY{n}{newData} \PY{o}{=} \PY{p}{\PYZob{}}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal vs cancer}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}\PY{p}{[}\PY{p}{]}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{cancer vs cancer}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}\PY{p}{[}\PY{p}{]}\PY{p}{\PYZcb{}}
         \PY{k}{for} \PY{n}{tag} \PY{o+ow}{in} \PY{n}{data}\PY{p}{:}
             \PY{k}{if} \PY{n}{tag}\PY{o}{.}\PY{n}{find}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)} \PY{o}{\PYZgt{}}\PY{o}{=} \PY{l+m+mi}{0}\PY{p}{:}
                 \PY{n}{newData}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal vs cancer}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{)}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{newData}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{cancer vs cancer}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{)}
         \PY{k}{for} \PY{n}{tag} \PY{o+ow}{in} \PY{n}{newData}\PY{p}{:}
             \PY{k}{print}\PY{p}{(}\PY{n}{tag}\PY{p}{)}
             \PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{)}
             \PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]} \PY{o}{=} \PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{o}{.}\PY{n}{reshape}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{o}{.}\PY{n}{shape}\PY{p}{[}\PY{l+m+mi}{2}\PY{p}{]}\PY{p}{)}
             \PY{k}{print}\PY{p}{(}\PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
normal vs cancer
(828, 23)
cancer vs cancer
(828, 23)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}25}]:} \PY{k}{print}\PY{p}{(}\PY{n}{newData}\PY{o}{.}\PY{n}{keys}\PY{p}{(}\PY{p}{)}\PY{p}{)}
         \PY{n}{manova}\PY{p}{(}\PY{n}{newData}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{wilk}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
['normal vs cancer', 'cancer vs cancer']
Method Used: WILK
('n: ', 1656.0)
('k: ', 23)
('m: ', 2)
('a: ', 1642.5)
('b\_num', 525.0)
('b\_denom', 525.0)
('b: ', 1.0)
('c: ', 10.5)
('gamma: ', 0.8137462912026895)
('s', 1)
('t', 10.5)
('u', 815.0)
('df1', 23)
('df2', 1632.0)
('F', 16.240830195044396)
('alpha:', 0.05)
('F-crit:', 1.5358774221121692)
('p-value:', 7.068138545917349e-58)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}26}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{25}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
         \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{14}
         \PY{n}{custIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{k}{if} \PY{n}{chr1} \PY{o}{\PYZlt{}} \PY{n}{chr2}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]}\PY{p}{)}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr2}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{]}\PY{p}{)}
         \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{n}{i} \PY{o}{=} \PY{o}{\PYZhy{}}\PY{l+m+mi}{1}
         \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{tag} \PY{o+ow}{in} \PY{n}{newData}\PY{p}{:}
             \PY{n}{i} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
             \PY{k}{print}\PY{p}{(}\PY{n}{averages}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
             \PY{n}{means} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{averages}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}
             \PY{n}{y} \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)} \PY{o}{\PYZhy{}} \PY{n}{means}\PY{p}{)}
             \PY{n}{y\PYZus{}err} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{o}{.}\PY{l+m+mi}{1}
             \PY{n}{x} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{y}\PY{p}{)}\PY{p}{)}\PY{p}{)}
             \PY{n}{xnew} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{n}{x}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{n}{x}\PY{o}{.}\PY{n}{max}\PY{p}{(}\PY{p}{)}\PY{p}{,}\PY{l+m+mi}{500}\PY{p}{)} \PY{c+c1}{\PYZsh{}300 represents number of points to make between T.min and T.max}
             \PY{n}{y\PYZus{}smooth} \PY{o}{=} \PY{n}{spline}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,}\PY{n}{xnew}\PY{p}{)}
             \PY{k}{if} \PY{n}{tag} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal vs cancer}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}
                 \PY{n}{color1} \PY{o}{=} \PY{n}{mit\PYZus{}colors}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}
                 \PY{n}{color2} \PY{o}{=} \PY{n}{mit\PYZus{}colors}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{color1} \PY{o}{=} \PY{n}{cancer\PYZus{}colors}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}
                 \PY{n}{color2} \PY{o}{=} \PY{n}{cancer\PYZus{}colors}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}
             \PY{n}{ax}\PY{o}{.}\PY{n}{scatter}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{xnew}\PY{p}{,} \PY{n}{y\PYZus{}smooth}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ }\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{tag}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PYZbs{}
                     \PY{p}{,} \PY{n}{linewidth}\PY{o}{=}\PY{l+m+mi}{4}\PY{p}{,}  \PY{n}{alpha}\PY{o}{=}\PY{o}{.}\PY{l+m+mi}{5}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color1}\PY{p}{)}
             \PY{c+c1}{\PYZsh{}ax.errorbar(x, y, yerr=y\PYZus{}err, linestyle=\PYZdq{}dashed\PYZdq{}, marker=\PYZdq{}None\PYZdq{}, color=color2)}
             \PY{c+c1}{\PYZsh{}ax.plot(x, y, marker=\PYZdq{}.\PYZdq{}, label=\PYZdq{}\PYZpc{}s vs \PYZpc{}s\PYZdq{}\PYZpc{}(cell1, cell2))}
             \PY{c+c1}{\PYZsh{}ax.set\PYZus{}ylim([\PYZhy{}1.5, 1.5])}
             \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Corrected Average MIC}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{20}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Contact maps of chromosome }\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s1}{\PYZsq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{20}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Contact Maps}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{20}\PY{p}{)}
             \PY{c+c1}{\PYZsh{}ax.set\PYZus{}xticks(x)}
             \PY{c+c1}{\PYZsh{}ax.set\PYZus{}ylim([\PYZhy{}.3, .3])}

         \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{prop}\PY{o}{=}\PY{p}{\PYZob{}}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{size}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}\PY{l+m+mi}{15}\PY{p}{\PYZcb{}}\PY{p}{)}
         \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
(6, 23)
(6, 23)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/git/watson/virt/lib/python2.7/site-packages/ipykernel\_launcher.py:21: DeprecationWarning: `spline` is deprecated!
spline is deprecated in scipy 0.19.0, use Bspline class instead.

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_36_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}31}]:} \PY{n}{numData} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
             \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
                 \PY{k}{if} \PY{n}{cell2} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{n}{cell1}\PY{p}{:}
                     \PY{k}{continue}
                 \PY{n}{datashape} \PY{o}{=} \PY{n}{distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{o}{.}\PY{n}{shape}
                 \PY{c+c1}{\PYZsh{}print(datashape)}
                 \PY{n}{numData} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
         \PY{n}{axis} \PY{o}{=} \PY{l+m+mi}{1}
         \PY{n}{xIndices} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{276}\PY{p}{)}
         \PY{n}{yIndices} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{)}
         \PY{n}{yIndices} \PY{o}{=} \PY{n}{indices}
         \PY{n}{averages} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{n}{counts} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{n}{data} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
         \PY{n}{count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{cell1} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
             \PY{k}{for} \PY{n}{cell2} \PY{o+ow}{in} \PY{n}{cells}\PY{p}{:}
                 \PY{k}{if} \PY{n}{cell2} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{n}{cell1}\PY{p}{:}
                     \PY{k}{continue}        
                 \PY{n}{tag} \PY{o}{=} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{ vs }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{cell1}\PY{p}{,} \PY{n}{cell2}\PY{p}{)}
                 \PY{n}{tmp} \PY{o}{=} \PY{n}{distances}\PY{p}{[}\PY{n}{cell1}\PY{p}{]}\PY{p}{[}\PY{n}{cell2}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{]}\PY{o}{.}\PY{n}{reshape}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
                 \PY{n}{averages}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{tmp}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{axis}\PY{p}{)}\PY{p}{)}
                 \PY{n}{counts}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{tmp}\PY{o}{.}\PY{n}{shape}\PY{p}{[}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{axis}\PY{p}{]}\PY{p}{)}           
                 \PY{k}{if} \PY{n}{axis} \PY{o}{==} \PY{l+m+mi}{1}\PY{p}{:}
                     \PY{n}{data}\PY{p}{[}\PY{n}{tag}\PY{p}{]} \PY{o}{=} \PY{n}{tmp}
                 \PY{k}{else}\PY{p}{:}
                     \PY{n}{data}\PY{p}{[}\PY{n}{tag}\PY{p}{]} \PY{o}{=} \PY{n}{tmp}\PY{o}{.}\PY{n}{T}
                 \PY{n}{count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
         \PY{n}{averages} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{averages}\PY{p}{)}
         \PY{n}{counts} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{counts}\PY{p}{,} \PY{n}{dtype}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{uint32}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{o}{.}\PY{n}{reshape}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{c+c1}{\PYZsh{}print(averages.shape)}
         \PY{n}{manova}\PY{p}{(}\PY{n}{data}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{wilk}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Method Used: WILK
('n: ', 1656.0)
('k: ', 1)
('m: ', 6)
('a: ', 1651.5)
('b\_num', 21.0)
('b\_denom', 21.0)
('b: ', 1.0)
('c: ', 1.5)
('gamma: ', 0.9111131405886976)
('s', 1)
('t', 1.5)
('u', 824.0)
('df1', 5)
('df2', 1650.0)
('F', 32.19431517229249)
('alpha:', 0.05)
('F-crit:', 2.219521132720305)
('p-value:', 2.1404345664824635e-31)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}32}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{3}\PY{p}{)}
         \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{14}
         \PY{n}{custIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{k}{if} \PY{n}{chr1} \PY{o}{\PYZlt{}} \PY{n}{chr2}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]}\PY{p}{)}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr2}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{]}\PY{p}{)}
         \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{n}{i} \PY{o}{=} \PY{o}{\PYZhy{}}\PY{l+m+mi}{1}
         \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{tag} \PY{o+ow}{in} \PY{n}{data}\PY{p}{:}
             \PY{n}{i} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
             \PY{k}{print}\PY{p}{(}\PY{n}{averages}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
             \PY{n}{means} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{averages}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}
             \PY{n}{x} \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)} \PY{o}{\PYZhy{}} \PY{n}{means}\PY{p}{)}
             \PY{n}{x\PYZus{}err} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{o}{.}\PY{l+m+mo}{05}
             \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{ones\PYZus{}like}\PY{p}{(}\PY{n}{x}\PY{p}{)} \PY{o}{*} \PY{n}{i}\PY{o}{*}\PY{o}{.}\PY{l+m+mi}{1}
             \PY{n}{xnew} \PY{o}{=} \PY{n}{x}\PY{c+c1}{\PYZsh{}np.linspace(x.min(),x.max(),500) \PYZsh{}300 represents number of points to make between T.min and T.max}
             \PY{n}{y\PYZus{}smooth} \PY{o}{=} \PY{n}{y}\PY{c+c1}{\PYZsh{}spline(x, y,xnew)}
             \PY{k}{if} \PY{n}{tag}\PY{o}{.}\PY{n}{find}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)} \PY{o}{\PYZgt{}}\PY{o}{=} \PY{l+m+mi}{0}\PY{p}{:}
                 \PY{n}{color1} \PY{o}{=} \PY{n}{mit\PYZus{}colors}\PY{p}{[}\PY{n}{mit\PYZus{}count}\PY{p}{]}
                 \PY{n}{color2} \PY{o}{=} \PY{n}{mit\PYZus{}colors}\PY{p}{[}\PY{n}{mit\PYZus{}count}\PY{p}{]}
                 \PY{n}{mit\PYZus{}count}\PY{o}{+}\PY{o}{=}\PY{l+m+mi}{1}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{color1} \PY{o}{=} \PY{n}{cancer\PYZus{}colors}\PY{p}{[}\PY{n}{cancer\PYZus{}count}\PY{p}{]}
                 \PY{n}{color2} \PY{o}{=} \PY{n}{cancer\PYZus{}colors}\PY{p}{[}\PY{n}{cancer\PYZus{}count}\PY{p}{]}
                 \PY{n}{cancer\PYZus{}count} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
             \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{xnew}\PY{p}{,} \PY{n}{y\PYZus{}smooth}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{o}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{tag}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PYZbs{}
                     \PY{p}{,} \PY{n}{linewidth}\PY{o}{=}\PY{l+m+mi}{5}\PY{p}{,}  \PY{n}{alpha}\PY{o}{=}\PY{o}{.}\PY{l+m+mi}{5}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color1}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{errorbar}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{xerr}\PY{o}{=}\PY{n}{x\PYZus{}err}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{dashed}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{None}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color1}\PY{p}{,} \PY{n}{linewidth}\PY{o}{=}\PY{l+m+mi}{5}\PY{p}{)}
             \PY{c+c1}{\PYZsh{}ax.plot(x, y, marker=\PYZdq{}.\PYZdq{}, label=\PYZdq{}\PYZpc{}s vs \PYZpc{}s\PYZdq{}\PYZpc{}(cell1, cell2))}
             \PY{c+c1}{\PYZsh{}ax.set\PYZus{}ylim([\PYZhy{}1.5, 1.5])}
             \PY{c+c1}{\PYZsh{}ax.set\PYZus{}ylabel(\PYZsq{}Corrected Average MIC\PYZsq{}, fontsize=20)}
         \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Corrected Average Distance}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{20}\PY{p}{)}
         \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}yticks}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{arange}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{data}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{o}{.}\PY{l+m+mi}{1}\PY{p}{)}
         \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}yticklabels}\PY{p}{(}\PY{n}{data}\PY{o}{.}\PY{n}{keys}\PY{p}{(}\PY{p}{)}\PY{p}{)}
         \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlim}\PY{p}{(}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{o}{.}\PY{l+m+mi}{12}\PY{p}{,} \PY{o}{.}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}

         \PY{c+c1}{\PYZsh{}plt.legend(prop=\PYZob{}\PYZsq{}size\PYZsq{}:15\PYZcb{})}
         \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
(6, 1)
(6, 1)
(6, 1)
(6, 1)
(6, 1)
(6, 1)

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_38_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}33}]:} \PY{n}{newData} \PY{o}{=} \PY{p}{\PYZob{}}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal vs cancer}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}\PY{p}{[}\PY{p}{]}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{cancer vs cancer}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}\PY{p}{[}\PY{p}{]}\PY{p}{\PYZcb{}}
         \PY{k}{for} \PY{n}{tag} \PY{o+ow}{in} \PY{n}{data}\PY{p}{:}
             \PY{k}{if} \PY{n}{tag}\PY{o}{.}\PY{n}{find}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mit}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)} \PY{o}{\PYZgt{}}\PY{o}{=} \PY{l+m+mi}{0}\PY{p}{:}
                 \PY{n}{newData}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal vs cancer}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{)}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{newData}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{cancer vs cancer}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{data}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{)}
         \PY{k}{for} \PY{n}{tag} \PY{o+ow}{in} \PY{n}{newData}\PY{p}{:}
             \PY{c+c1}{\PYZsh{}print(tag)}
             \PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{)}
             \PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]} \PY{o}{=} \PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{o}{.}\PY{n}{reshape}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{o}{.}\PY{n}{shape}\PY{p}{[}\PY{l+m+mi}{2}\PY{p}{]}\PY{p}{)}
             \PY{c+c1}{\PYZsh{}print(newData[tag].shape)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}34}]:} \PY{k}{print}\PY{p}{(}\PY{n}{newData}\PY{o}{.}\PY{n}{keys}\PY{p}{(}\PY{p}{)}\PY{p}{)}
         \PY{n}{manova}\PY{p}{(}\PY{n}{newData}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{hotelling}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
['normal vs cancer', 'cancer vs cancer']
Method Used: HOTELLING
('n: ', 1656.0)
('k: ', 1)
('m: ', 2)
('s', 1)
('t', -0.5)
('u', 826.0)
('T20: ', 0.012390436681119634)
('df1', 1.0)
('df2', 1654.0)
('F', 20.493782270571874)
('alpha:', 0.05)
('F-crit:', 3.8470871354481613)
('p-value:', 6.409969039925188e-06)

    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}35}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{3}\PY{p}{)}
         \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{14}
         \PY{n}{custIndices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
         \PY{k}{for} \PY{n}{chr2} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{24}\PY{p}{)}\PY{p}{:}
             \PY{k}{if} \PY{n}{chr1} \PY{o}{\PYZlt{}} \PY{n}{chr2}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{]}\PY{p}{)}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{custIndices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{chr2count}\PY{p}{[}\PY{p}{(}\PY{n}{chr2}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{]}\PY{p}{)}
         \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplot}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
         \PY{n}{i} \PY{o}{=} \PY{o}{\PYZhy{}}\PY{l+m+mi}{1}
         \PY{n}{mit\PYZus{}count} \PY{o}{=} \PY{n}{cancer\PYZus{}count} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{k}{for} \PY{n}{tag} \PY{o+ow}{in} \PY{n}{newData}\PY{p}{:}
             \PY{n}{i} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
             \PY{k}{print}\PY{p}{(}\PY{n}{averages}\PY{o}{.}\PY{n}{shape}\PY{p}{)}
             \PY{n}{means} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{averages}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}
             \PY{n}{x} \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)} \PY{o}{\PYZhy{}} \PY{n}{means}\PY{p}{)}
             \PY{n}{x\PYZus{}err} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{n}{newData}\PY{p}{[}\PY{n}{tag}\PY{p}{]}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{o}{.}\PY{l+m+mi}{1}
             \PY{n}{y} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{ones\PYZus{}like}\PY{p}{(}\PY{n}{x}\PY{p}{)} \PY{o}{*} \PY{n}{i}\PY{o}{*}\PY{o}{.}\PY{l+m+mi}{1}
             \PY{n}{xnew} \PY{o}{=} \PY{n}{x}\PY{c+c1}{\PYZsh{}np.linspace(x.min(),x.max(),500) \PYZsh{}300 represents number of points to make between T.min and T.max}
             \PY{n}{y\PYZus{}smooth} \PY{o}{=} \PY{n}{y}\PY{c+c1}{\PYZsh{}spline(x, y,xnew)}
             \PY{k}{if} \PY{n}{tag} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{normal vs cancer}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}
                 \PY{n}{color1} \PY{o}{=} \PY{n}{mit\PYZus{}colors}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}
                 \PY{n}{color2} \PY{o}{=} \PY{n}{mit\PYZus{}colors}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}
             \PY{k}{else}\PY{p}{:}
                 \PY{n}{color1} \PY{o}{=} \PY{n}{cancer\PYZus{}colors}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}
                 \PY{n}{color2} \PY{o}{=} \PY{n}{cancer\PYZus{}colors}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}    
             \PY{c+c1}{\PYZsh{}ax.scatter(x, y)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{xnew}\PY{p}{,} \PY{n}{y\PYZus{}smooth}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{o}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{tag}\PY{o}{.}\PY{n}{upper}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PYZbs{}
                     \PY{p}{,} \PY{n}{linewidth}\PY{o}{=}\PY{l+m+mi}{3}\PY{p}{,}  \PY{n}{alpha}\PY{o}{=}\PY{o}{.}\PY{l+m+mi}{5}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color1}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{errorbar}\PY{p}{(}\PY{n}{x}\PY{p}{,} \PY{n}{y}\PY{p}{,} \PY{n}{xerr}\PY{o}{=}\PY{n}{x\PYZus{}err}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{dashed}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{None}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{n}{color1}\PY{p}{)}
             \PY{c+c1}{\PYZsh{}ax.plot(x, y, marker=\PYZdq{}.\PYZdq{}, label=\PYZdq{}\PYZpc{}s vs \PYZpc{}s\PYZdq{}\PYZpc{}(cell1, cell2))}
             \PY{c+c1}{\PYZsh{}ax.set\PYZus{}ylim([\PYZhy{}1.5, 1.5])}
             \PY{c+c1}{\PYZsh{}ax.set\PYZus{}ylabel(\PYZsq{}Corrected Average MIC\PYZsq{}, fontsize=20)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Corrected Average Distance}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{20}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}yticks}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{arange}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{newData}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{o}{.}\PY{l+m+mi}{1}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}yticklabels}\PY{p}{(}\PY{n}{newData}\PY{o}{.}\PY{n}{keys}\PY{p}{(}\PY{p}{)}\PY{p}{)}
             \PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlim}\PY{p}{(}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{o}{.}\PY{l+m+mo}{075}\PY{p}{,} \PY{o}{.}\PY{l+m+mo}{050}\PY{p}{]}\PY{p}{)}

         \PY{c+c1}{\PYZsh{}plt.legend(prop=\PYZob{}\PYZsq{}size\PYZsq{}:15\PYZcb{})}
         \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
(6, 1)
(6, 1)

    \end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_41_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    % Add a bibliography block to the postdoc

    \end{document}

### 2018-10-16 papers/manuscripts/manuscript.tex
save

@@
 applied graphlet distance metrics proposed in
-{prvzulj2007biological} together with statistical methods
+\cite{prvzulj2007biological} together with statistical methods
 in order to find difference between cell lines.
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figures/graphlets.png}
+    \includegraphics[width=.5\textwidth]{figures/graphlets.jpg}
+    %\includegraphics[width=.5\textwidth]{/home/bzr0014/Dropbox/graphlets.png}
+    %\includegraphics[width=.5\textwidth]{/home/bzr0014/Dropbox/graphlets.jpg}
     \caption{}

### 2018-10-16 data/get_data.sh

@@ -1,2 +1,2 @@
-wget "https://graphiclet.localtunnel.me/secret/data.zip"
+wget "127.0.0.1/secret/data.zip"
 unzip data.zip && rm data.zip

### 2018-10-16 papers/manuscripts/run.sh

@@ -1,4 +1,5 @@
 pdflatex $1
+#while [ 1 ];do find test.md -mmin -.0333 -exec pandoc --bibliography=./lit.bib -o test.pdf test.md \;; sleep 2; done
 #bibtex basics.aux
 #pdflatex basics.tex
 #pdfllatex basics.tex

### 2018-10-16 papers/manuscripts/manuscript.tex
save

@@
-\documentclass[a4,center,fleqn]{NAR}
+\documentclass[]{article}
+\usepackage[top=1in, bottom=1.25in, left=1in, right=1in]{geometry}
 \usepackage{hyperref}
@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{setspace}
@@
 % Enter dates of publication
-\copyrightyear{2017}
-\pubdate{18 March 2017}
-\pubyear{2017}
-\jvolume{37}
-\jissue{12}
+%\copyrightyear{2017}
+%\pubdate{18 March 2017}
+%\pubyear{2017}
+%\jvolume{37}
+%\jissue{12}
 
@@
 %\articlesubtype{This is the article type (optional)}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{authblk}
+
+\title{HiC Contact Map Comaprison Using Graphlet Approach}
+\author[1]{Behnam Rasoolian \thanks{Tel: +1 334 5212814; Email: bzr0014@auburn.edu}}
+\author[1]{Debswapna Bhattacharya}
+\affil[1]{Department of Computer Science and Software Engineering, Auburn University}
+\date{}
+\renewcommand\Authands{ and }
 
 \begin{document}
-\title{HiC Contact Map Comaprison Using Graphlet Approach}
-
-\author{%
-    Behnam Rasoolian\,$^{1,*}$,
-    Debswapna Bhattacharya\,$^{1}$
-    \footnote{
-    Tel: +1 334 5212814; Email: bzr0014@auburn.edu}}
-
-    \address{%
-        $^{1}$ Auburn University
-        }
-        % Affiliation must include:
-        % Department name, institution name, full road and district address,
-        % state, Zip or postal code, country
-
-%        \history{%
-%            Received January 1, 2009;
-%            Revised February 1, 2009;
-%            Accepted March 1, 2009}
 
@@
 % first page footnotes
-\enlargethispage{-65.1pt}
+%\enlargethispage{-65.1pt}
 % **************************************************************
@@
 \subsection{Graphlets and Orbits}
-\begin{figure}[H]
+\begin{figure}
     \centering
-    \includegraphics[width=.5\textwidth]{figures/graphlets.jpg}
+    \includegraphics[width=\textwidth]{figures/graphlets.jpg}
     %\includegraphics[width=.5\textwidth]{/home/bzr0014/Dropbox/graphlets.png}
@@
 results.
-\begin{figure}[t]
+\begin{figure}
     \centering
-    \includegraphics[width=.47\textwidth]{figures/local_thresholded_chr1_chr1.png}
+    \includegraphics[width=\textwidth]{figures/local_thresholded_chr1_chr1.png}
     \caption{Result of thresholding interchromosomal contact map of chromosome 1
@@
     \centering
-    \includegraphics[width=.47\textwidth]{figures/graphlet_extraction.png}
+    \includegraphics[width=\textwidth]{figures/graphlet_extraction.png}
     \caption{Graphlet extraction for the four cell lines. For each
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figures/graphlet_distance_schema.png}
+    \includegraphics[width=\textwidth]{figures/graphlet_distance_schema.png}
     \caption{Calculating pair-wise loci distances. For each loci (row) 
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figures/graphlet_correlation_schema.png}
+    \includegraphics[width=\textwidth]{figures/graphlet_correlation_schema.png}
     \caption{Calulating pair-wise orbit correlations. For each orbit (column)
@@
     \centering
-    \begin{subfigure}[b]{.5\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \includegraphics[width=\textwidth]{figures/orbit_distances_normal_vs_cancer.png}
@@
 
-    \begin{subfigure}[b]{.5\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \includegraphics[width=\textwidth]{figures/orbit_distances_cells.png}
@@
     \centering
-    \begin{subfigure}[b]{.5\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \includegraphics[width=\textwidth]{figures/orbit-distances_chr14.png}
@@
 
-\begin{figure*}
+\begin{figure}
     \centering
@@
     \label{fig:orbits_correlations}
-\end{figure*}
+\end{figure}
 
@@
 \bibliographystyle{unsrt}
+
 \end{document}
